### 2019-12-27 tex/mixedft_evolution_ms.tex
initial commit of manuscript scraps

\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{D_{\text{KS}}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{D_\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\Reff}{\ensuremath{\text{Re}_{\text{ff}}}}
\newcommand{\Peff}{\ensuremath{\text{Pe}_{\text{ff}}}}

\newcommand\mnras{{MNRAS}}%

\begin{document}
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Geoffrey M. Vasil}
\affiliation{University of Sydney School of Mathematics and Statistics, Sydney, NSW 2006, Australia}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Lydia Korre}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}

\title{Mixed thermal boundary conditions impose an unnecessary thermal rundown on convection simulations}

\begin{abstract}
Astrophysical studies of convection often impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
In this work, we study \RB convection to show that the use of mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
We show that an evolved simulation with mixed thermal boundaries exhibits dynamics whose mean measurements are indistinguishable from a comparable simulation where the temperature is fixed at both boundaries.
We note that thermal relaxation is composed of two parts: changes in the energy reservoir of the system being studied, and changes in the stratification of the system.
Changes in the energy reservoir result from poor choices of initial conditions and boundary conditions, while changes in stratification are the result of interesting convective dynamics.
We warn that measurements made in simulations while the energy reservoir is changing reflect very different dynamics than relaxed simulations.
Finally, we note that the relaxation of these systems effectively amount to a sweep through parameter space, and may be interesting in and of themselves.
\end{abstract}
\maketitle

%%%%%%%%%%%%
%%%%%%%%%%%
% INTRO
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Introduction}

%%%%%%%%%%%%
%%%%%%%%%%%
% EXPERIMENT
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Simulation Details}
\label{sec:simulations}
We study incompressible \RB convection under the same nondimensionalization as we have done previously \cite{anders&all2018}, and including the effects of vertically directed global rotation as in \cite{julien&all1996},
\begin{align}
\Div{\bm{u}} &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \sqrt{\frac{\nu}{2\Omega L_z^2}},
\end{equation}
where $\Delta$ is the dimensionless temperature jump across the domain (described below with our boundary conditions), $\Omega$ is the global rotation frequency, and all other parameters are as described in our previous work \cite{anders&all2018}.
These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.

In this work, we study two illustrative 3D simulations of rotating convection. 
These simulations employ stress-free, impenetrable upper and lower boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5,
\label{eqn:vel_bcs}
\end{equation}
which are typical of simulations of astrophysical convection \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
We also later include some select two-dimensional simulations for comparison to the \RB convection literature which employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}
We study two configurations of thermal boundary conditions: (1) ``mixed'' boundaries where we fix the temperature at the top the flux at the bottom, and (2) fixed-temperature boundaries at the top and the bottom, or:
\begin{equation}
(1): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
(2): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
\end{equation}
For case (1), the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and for case 2 the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$.

We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016} to evolve Eqs.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), and (\ref{eqn:bouss_energy}) forward in time.
For our 2D simulations, we use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; for our 3D simulations, we use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}. 
The code used to run simulations and the code and data used to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
We study two- (2D) and three-dimensional (3D) convection in which the domain is a cartesian box, whose dimensionless vertical extent is $z \in [-0.5, 0.5]$, and which is horizontally periodic with an extent of $x, y \in [-\Gamma/2, \Gamma/2]$, where $\Gamma = 2$ is the aspect ratio.
In 2D simulations, we set $v = \partial_y = 0$.
For our 2D simulations, we set the aspect ratio to $\Gamma = 2$; for our 3D simulations, we set the aspect ratio to $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset, as has been done by previous authors \cite{stellmach&all2014}.

The initial temperature profile is linearly unstable, $T_0(z) = 0.5 - z$. 
On top of this profile, we fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered so as to match the thermal boundary conditions.
This ensures that the initial perturbations are much smaller than the evolved convective temperature perturbations, even at large Ra.
We filter this noise spectrum in coefficient space, 
such that only the lower 25\% of the coefficients
have power; this low-pass filter is used to avoid populating the
highest wavenumbers with noise in order to improve the stability of our
spectral timestepping methods.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ra & Nu arguments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolved quantities}
\label{sec:ra_nu_relations}
Throughout this work we will measure and report the evolved value of the Nusselt number.
We define and measure the Nusselt number instantaneously as
\begin{equation}
\text{Nu} \equiv \angles{\frac{w T - \Peff^{-1} \partial_z T}{-\Peff^{-1} \angles{\partial_z T}}}
= 1 + \Peff\frac{\angles{w T}}{-\Delta T},
\end{equation}
where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A dx dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A dx dy dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature different between the top and bottom plate.
In the evolved, statistically stationary state, when fixed temperature boundaries are employed, $\text{Nu} = \text{Flux} = 1 + \Peff\angles{wT}$, and when mixed boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
\begin{equation}
\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu},
\end{equation}
and we will measure both values of Ra as our simulations evolve.

Some additional quantities of interest will be reported throughout this paper.
We will measure the evolved Peclet number of the convective flows in all sections, and in section \ref{sec:rotating_results} we will also report the value of the Rossby number.
We measure these nondimensional quantities instantaneously as
\begin{equation}
\text{Pe} = \angles{|\bm{u}|}\Peff,\qquad \text{Ro} = \angles{|\bm{\omega}|}\text{Ek }\Reff,
\end{equation}
where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\section{Results}
\label{sec:results}

\subsection{Classical \RB Convection}
\label{sec:2d_results}

\subsection{Rotating \RB Convection}
\label{sec:rotating_results}

%\begin{figure}[b]
%\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
%\caption{ \ref{fig:oscillating_plumes}.
%\label{fig:nu_v_time} }
%\end{figure}

%\begin{table}[b!]
%\caption{
%}
%\setlength{\tabcolsep}{12pt}
%\label{table:speed}
%\begin{center}
%\begin{tabularx}{0.72\textwidth}{ c r r c c c }
%\hline																	
%$S$	&	nz$\times$nx$\times$ny	&	$N_{\text{CPU}}$	&	
%$t_{\text{CPU, SE}}$ & $t_{\text{CPU, AE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
%\hline
%%2 sig figs, scientific notation, swap SE and AE, right justify Ncpu, 2 sig figs ratio, right justify communicates biggerness. 
%$10^2$	&	64$\times$128	&	32    &  2.2              & 4.4               &     2.0  \\
%$10^3$	&	128$\times$256	&	64    &  53               & 21                &     0.39 \\
%$10^4$	&	256$\times$512	&	128   &  1.2$\times 10^3$ & 1.8$\times 10^2$  &     0.15  \\
%$10^5$	&	512$\times$1024&	256   &  2.4$\times 10^4$ & 2.8$\times 10^3$  &     0.12 \\
%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
%\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
%\hline
%$10^1$	&	32$\times$64$\times$64	    & 512       &   62                 &        1.1$\times 10^2$   & 1.7\\
%$10^2$	&	64$\times$128$\times$128	& 512       &   1.9$\times 10^2$   &        1.1$\times 10^2$   & 0.60 \\
%$10^3$	&	128$\times$256$\times$256	& 2048      &   7.0$\times 10^3$   &        1.4$\times 10^3$   & 0.20 \\
%$10^4$	&	256$\times$512$\times$512	& 8192      &   3.3$\times 10^5$   &        2.3$\times 10^4$   & 0.070\\
%\hline																	
%\end{tabularx}
%\end{center}
%\end{table}

%%%%%%%%%%%%
%%%%%%%%%%%
% CONCLUSION
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Discussion \& Conclusions}
\label{sec:extensions}

\begin{acknowledgments}
EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
\end{acknowledgments}

\bibliography{biblio.bib}
\end{document}

### 2019-12-27 figures_and_data/rbc_scalar_comparisons.py
adds rough script for fig 1

@@ -1,0 +1,220 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
+                    start_ind += len(arr)
+        else:
[…]

### 2019-12-28 figures_and_data/rbc_1D_profiles.py
scripts for first 3 figures added

@@ -1,0 +1,252 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+import dedalus.public as de
+
+
+mColor = 'olivedrab'
+fColor = 'darkorange'
+
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
+                    start_ind += len(arr)
+        else:
[…]

### 2019-12-28 figures_and_data/rbc_dynamics_asymmetries.py

@@ -1,0 +1,200 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+import dedalus.public as de
+
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
+                    start_ind += len(arr)
+        else:
+            with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
[…]

### 2019-12-28 figures_and_data/rbc_scalar_comparisons.py

@@ -93,10 +93,10 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-plt.axhline(np.mean(mixed_trace['ra_flux'])/1e9, color='black', lw=1)
-plt.axhline(np.mean(fixed_trace['ra_temp'])/1e9, color='orange', lw=1, ls='-.')
-plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/1e9, color='black', lw=2, ls='-.')
-plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/1e9, color='orange', lw=2)
+plt.axhline(np.mean(mixed_trace['ra_flux'])/1e9, color='olivedrab', lw=1)
+plt.axhline(np.mean(fixed_trace['ra_temp'])/1e9, color='darkorange', lw=1, ls='-.')
+plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/1e9, color='olivedrab', lw=2, ls='-.')
+plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/1e9, color='darkorange', lw=2)
 ax.set_ylabel(r'Ra/$10^9$')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
 plt.yscale('log')
@@ -111,9 +111,9 @@ ax = axs[1]
 
 Nu_final_temp = np.mean(fixed_trace['Nu'][-5000:])
 
-plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['Nu']/Nu_final_temp, color='black', lw=2)
-plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['Nu']/Nu_final_temp, color='orange', lw=2)
-plt.axhline(1, c='r', lw=0.5)
+plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['Nu']/Nu_final_temp, color='olivedrab', lw=2)
+plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['Nu']/Nu_final_temp, color='darkorange', lw=2)
+plt.axhline(1, c='darkorange', lw=1)
[…]

### 2019-12-28 tex/mixedft_evolution_ms.tex
initial start to writeup of results

@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
+\caption{ 
+\label{fig:rbc_scalar_comparisons} }
+\end{figure}
+
+In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we compare the time evolution of a mixed-FT (green) case to a fixed-T (orange) simulation.
+In the top-left panel, we show the evolution of both the temperature and flux Rayleigh numbers of both simulations.
+We show the input (flux) Ra of the mixed-FT case and the input (temp) Ra of the fixed-T case as horizontal lines, and overplot the evolution of the Ra$_{\Delta T}$ for the mixed-FT case and the evolution of Ra$_{\partial_z T}$ for the fixed-T case.
+While the fixed-T case's flux Ra rapidly latches onto its final value, the mixed-FT case's temp Ra takes thousands of freefall times to equilibrate to its final value.
+This fast evolution (fixed-T) and slow evolution (mixed-FT) is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
+
+A naive estimate of the thermal evolution timescale of these system is $t_{\text{therm}} = \sqrt{\Peff} = \sqrt{\text{Ra Pr}}$ \cite{anders&all2018}.
+For the mixed-FT simulation presented here with Ra = 2.61 $\times 10^9$, this prediction returns $t_{\text{therm}} \approx 5\times 10^{4}$.
+**I need to do a derivation and think about this more.
+
+In the upper right panel of Fig.~\ref{fig:rbc_scalar_comparisons}, we show a plot of Nu vs Ra.
+The green line shows the path through this space that our mixed-FT simulation traces out.
+For reference, we show values of Nu reported for various fixed-T runs from previous work and from our own simulations conducted here.
+Remarkably, the mixed-FT case seems to reliably perform a sweep through this parameter space.
+However, despite seemingly tracing out the ``proper'' values of Nu(t) vs. Ra(t), the same is not true of the Reynolds number.
+In the lower right panel, we plot the trace of Re vs Ra, and see that the mixed-FT case achieves a high value of Re compared to fixed-T cases as it sweeps toward lower values of Ra.
+This makes sense; the mixed-FT simulation experiences a vigorous injection of kinetic energy during the convective transient and must slowly wind down from this energized state over time.
+These traces through parameter space demonstrate that, unless measurements are taken after convergence is achieved, the dynamics sampled in a mixed-FT case may be misleading.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
+\caption{ 
+\label{fig:rbc_1D_profiles} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our fixed-T and mixed-FT cases.
+In the upper left panel, we show the mean temperature profiles achieved in the evolved state of both simulations.
+Throughout the full depth, these profiles differ by less than 2\%, as shown in the lower left panel.
+In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
+Surprisingly, despite symmetrical boundary conditiosn in fixed-T simulations and asymmetrical boundary conditions in mixed-FT cases, we find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
+In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
+Once again, these profiles agree to within < 2\%.
+
+In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases.
+the fluxes show very good agreement just like the temperature profile.
+Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
+Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boudnary layers.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
+\caption{ 
+\label{fig:rbc_dynamics_asymmetries} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which mixed-FT boundaries introduce into the simulation.
+In the left panel, we plot the probability distribution functions of temperature measurements taken throughout the full domain.
+These PDFs agree remarkably well for cold temperature (near the shared fixed-T boundary) and through the mean, but diverge for hot temperatures (where the boundary conditions differ).
+We find that the mixed-FT pdf has a much longer tail and is capable of achieving much hotter instantaneous temperature values than a fixed-T boundary can.
+In order to understand how this is possible, we examine a snapshot of the full temperature field.
+In the middle panel, we plot the temperature anomaly -- the temperature field with the mean vertical profile subtracted from it.
+We have outlined a portion of a cold plume near the upper (fixed-T) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the lower right panels.
+The fixed-T upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
+The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area.
+
+\subsection{Fixed-Temp simulations can be used to skip thermal relaxation}
+
+This evidence all suggests that, in a time-averaged, horizontally-averaged, or volume-averaged sense, fixed-T and mixed-FT simulations are 1-to-1 comparable.
+However, their dynamics have subtle differences, and it is possible that these differences could be interesting in studies of astrophysical convection (for example, more extreme plume values like those achieved at the fixed-flux plate may interact with a stable layer differently than the more regulated values achieved by a fixed-T plate).
+The evolutionary time of mixed-FT cases unfortunately makes running down such simulations in the highly-turbulent, large Rayleigh number regime nearly impossible.
+Fortunately, the similarities between these different boundary conditions suggests that the final state of a fixed-temperature simulation, which is rapidly achieved, could serve as an ideal set of initial conditions for a mixed-FT case.
+
+Here's a description of how you scale fixed T  to mixed FT.
+
+In Fig. \ref{fig:Whatever}, we show that indeed this stuff works.
+
+This suggests that thermal relaxation takes place in two parts:
+\begin{enumerate}
+\item Changes to the experimental energy reservoir,
+\item Restratification of the experiment.
+\end{enumerate}
+The former of these can be skipped through the choice of ``smart'' boundary conditions.
+The latter seems to be unimportant in a simple system like the \RB convection studied here.
+Takeaway: don't choose boudnary conditiosn where the initial and final energy reservoir are really different.
+
 \subsection{Rotating \RB Convection}

### 2019-12-31 tex/mixedft_evolution_ms.tex
adds fourth figure and starts to get narrative flow down

@@
 \section{Introduction}
+\label{sec:introduction}
+Convection is a crucial heat transport mechanism in the atmospheres of stars and planets.
+Numerical simulations are the basis for most modern studies into the nature of astrophysical convection.
+These studies examine models which range from simplified, two-dimensional Boussinesq \RB convection (sources, sources) to fully three-dimensional, magnetohydrodynamical, global dynamo simulations (sources, sources).
+Regardless of the degree of apparent realism included in these models, convective processes in these numerical simulations are fundamentally driven by some combination of internal heating profiles and imposed boundary conditions.
+It is common in astrophysical studies to impose ``mixed'' thermal boundary conditions (hereafter ``mixedFT'') in which the flux is fixed at one end of the domain whereas a thermodynamic quantitiy (e.g., temperature) is fixed at the other end (sources, sources).
+In this work, we will hereafter focus on \RB convection under the Boussinesq approximation, such that the only thermodynamic quantity of interest in the temperature.
+
+Despite mixedFT boundary conditions being a common choice of numericists, we are unaware of any work which compares the dynamics produced by mixed thermal boundaries to the most traditional choice of boundary conditions in the \RB literature: fixed temperature at the top and bottom (hereafter fixedT).
+While there is some work \cite{johnston&doering2009} comparing simulations in which the flux is fixed at \emph{both} boundaries (hereafer fixedF), the central result of this work is that fixedF and fixedT boundary conditions exhibit the same mean heat transport as quantified by the Nusselt number.
+This result suggests that mixedFT boundaries should transport heat in the same manner as fixedT boundaries, but the choice of mixedFT boundaries introduces complexities into the convective system which neither set of fixed boundaries is exposed to.
+First, the evolved mean temperature of a simulation with mixedFT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
+Second, mixedFT boundary conditions break the symmetry of the system, which may have important consequences on the convective dynamics.
+
+In this letter, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
+We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
+We also find that as the temperature jump across the domain evolves over the course of this relaxation, the convective system effectively performs a sweep through Ra parameter space.
+We have reported in the past on clever mechanisms which have been devised to skip past this thermal relaxation \cite{anders&all2018}, and here we show that changing the boundary conditions of an evolved fixedT simulation to mixedFT boundaries is likely the simplest mechanism for fast-forwarding through this long rundown.
+We furthermore find that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not seem to appreciably change the mean convective state when compared to fixedT boundaries.
 
@@
 \begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
+\caption{ 
+\label{fig:rbc_restart_description} }
+\end{figure}
+
+The evidence displayed in Fig.~\ref{fig:rbc_scalar_comparisons} suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
+This suggests that one can take advantage of the fast evolution on display in fixedT simulations to achieve rapidly equilibrated mixedFT simulations.
+This is fortunate, as the rundown in mixedFT simulations is very costly:  not only do the turbulent dynamics at the large initial Rayleigh number need to be resolved (requiring more spectral modes to run the simulation), but thousands of freefall times must pass before convergence.
+For a sense of scale, the first thousand freefall time units of the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons} took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours.
+For comparison, the same time evolution (essentially the whole simulation) for fixedT boundary conditions took  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours.
+After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
+This means that at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is more than an order of magnitude larger than a fixedT simulation.
+
+We take advantage of the fast evolution of fixedT simulations to achieve equilibrated mixedFT simulations by switching the boundary conditions on an equilibrated fixedT run.
+Our procedure for achieving converged mixedFT dynamics using fixedT simulations is simple and takes place over these steps:
+\begin{enumerate}
+\item Run a fixedT simulation from convective transient to its statistically stationary state. 
+Measure $\angles{\text{Nu}}$ in that state.
+\item Re-nondimensionalize from a fixed temperature at the boundaries to a fixed flux.
+This will involve setting the input Rayleigh number to a flux Ra, or $\text{Ra}_{\text{in}} = \angles{\text{Nu}}\text{Ra}_{\Delta T}$.
+In our freefall nondimensionalization, this means setting the velocities in the mixedFT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{T}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{T}} / \angles{\text{Nu}}$.
+\item Restart the simulation with mixedFT boundaries and continue timestepping.
+\end{enumerate}
+
+In the left panels of Fig. \ref{fig:rbc_restart_description}, we show that this procedure indeed seems to work.
+We ran a simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
+We restarted this simulation using mixedFT boundaries after roughly one thousand time units at an input value of Ra$_{\partial_z T} = 2.61 \times 10^9$.
+Rolling averages of Ra$_{\Delta T} / 10^8$ and Ra$_{\partial_z T} / (2.61 \times 10^9)$ are shown through the full simulation.
+As can been seen in the lower and bottom left panels, at the beginning of the simulation when fixedT boundary conditions are used, the flux at the lower boundary fluctuates but the temperature is precisely constant.
+When these boundaries are switched for mixedFT boundaries, the left flux holds steady but the temperature is able to fluctuate.
+Unlike in the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the mixedFT state, as the thermal profile has been equilibrated by the early fixedT portion of the run.
+
+In order to verify if this restarting procedure achieves the same dynamics as a long rundown, we compare probability distribution functions of various quantities in our convective domains.
+We display these PDFs in the right four panels of Fig.~\ref{fig:rbc_restart_description}.
+We show the probability distributions of the temperature field (upper left), the enstrophy (upper right), the convective enthalpy flux (lower left), and the vertical velocity (lower right).
+Visually, these PDFs are essentially identical, with perhaps small variations in their tails due to random extreme events which occur in one simulation but not the other.
+The means, standard deviations, skewness, and kurtosis of each PDF is displayed in Table~\ref{table:pdf_values}, and the agreement is quite good.
+
+\begin{table}[ht]
+\caption{
+}
+\setlength{\tabcolsep}{12pt}
+\label{table:speed}
+\begin{center}
+\begin{tabularx}{\textwidth}{c c c c c c}
+\hline																	
+Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
+%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
+\hline
+$T$				&	mixedFT		&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.1		&	15 \\
+				&	mixedFT,r	&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.3		&	17 \\
+\hline
+$\omega^2$		&	mixedFT		&		$1.3$					&	$6.4$					&	19		&	$5.2 \times 10^2$ \\
+				&	mixedFT,r	&		$1.5$					&	$6.9$					&	18		&	$5.0 \times 10^2$ \\
+\hline
+$wT$			&	mixedFT		&		$1.9 \times 10^{-5}$	&	$9.4 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+				&	mixedFT,r	&		$1.9 \times 10^{-5}$	&	$9.3 \times 10^{-4}$	&	0.18	&	$3.2$ \\
+\hline
+$wT$			&	mixedFT		&		$7.9 \times 10^{-7}$	&	$4.9 \times 10^{-2}$	&	0.016	&	$2.7$ \\
+				&	mixedFT,r	&		$-1.0 \times 10^{-6}$	&	$4.8 \times 10^{-2}$	&	0.02	&	$2.8$ \\
+\hline																	
+\end{tabularx}
+\end{center}
+\end{table}
+
+The successful degree with which this mechanism reproduces the evolved dynamics suggests that thermal relaxation occurs in two parts:
+\begin{enumerate}
+\item Changes to the experimental energy reservoir, and
+\item Restratification of the experiment.
+\end{enumerate}
+Through the use of complicated clever techniques \cite{anders&all2018} or simply through the choice of ``smart'' boundary conditions, the first of these pieces of thermal relaxation can be skipped.
+For \RB convection with no-slip boundaries at the top and bottom plate, the latter part of thermal relaxation seems to be unimportant.
+When complications such as stable layers are included in the model, we do not generally expect the latter piece of restratification to be completely insignificant, but for the simple case studied here it seems to be.
+
+\subsection{Asymmetries induced by mixed boundaries}
+\label{sec:asymmetries}
+Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixed-FT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
+
+\begin{figure}
 \includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
@@
 
-This evidence all suggests that, in a time-averaged, horizontally-averaged, or volume-averaged sense, fixed-T and mixed-FT simulations are 1-to-1 comparable.
-However, their dynamics have subtle differences, and it is possible that these differences could be interesting in studies of astrophysical convection (for example, more extreme plume values like those achieved at the fixed-flux plate may interact with a stable layer differently than the more regulated values achieved by a fixed-T plate).
-The evolutionary time of mixed-FT cases unfortunately makes running down such simulations in the highly-turbulent, large Rayleigh number regime nearly impossible.
-Fortunately, the similarities between these different boundary conditions suggests that the final state of a fixed-temperature simulation, which is rapidly achieved, could serve as an ideal set of initial conditions for a mixed-FT case.
-
-Here's a description of how you scale fixed T  to mixed FT.
-
-In Fig. \ref{fig:Whatever}, we show that indeed this stuff works.
-
-This suggests that thermal relaxation takes place in two parts:
-\begin{enumerate}
-\item Changes to the experimental energy reservoir,
-\item Restratification of the experiment.
-\end{enumerate}
-The former of these can be skipped through the choice of ``smart'' boundary conditions.
-The latter seems to be unimportant in a simple system like the \RB convection studied here.
-Takeaway: don't choose boudnary conditiosn where the initial and final energy reservoir are really different.
-
 \subsection{Rotating \RB Convection}
 \label{sec:rotating_results}
-
-%\begin{figure}[b]
-%\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
-%\caption{ \ref{fig:oscillating_plumes}.
-%\label{fig:nu_v_time} }
-%\end{figure}
-
-%\begin{table}[b!]
-%\caption{
-%}
-%\setlength{\tabcolsep}{12pt}
-%\label{table:speed}
-%\begin{center}
-%\begin{tabularx}{0.72\textwidth}{ c r r c c c }
-%\hline																	
-%$S$	&	nz$\times$nx$\times$ny	&	$N_{\text{CPU}}$	&	
-%$t_{\text{CPU, SE}}$ & $t_{\text{CPU, AE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
-%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
-%\hline
-%%2 sig figs, scientific notation, swap SE and AE, right justify Ncpu, 2 sig figs ratio, right justify communicates biggerness. 
-%$10^2$	&	64$\times$128	&	32    &  2.2              & 4.4               &     2.0  \\
-%$10^3$	&	128$\times$256	&	64    &  53               & 21                &     0.39 \\
-%$10^4$	&	256$\times$512	&	128   &  1.2$\times 10^3$ & 1.8$\times 10^2$  &     0.15  \\
-%$10^5$	&	512$\times$1024&	256   &  2.4$\times 10^4$ & 2.8$\times 10^3$  &     0.12 \\
-%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-%\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
-%\hline
-%$10^1$	&	32$\times$64$\times$64	    & 512       &   62                 &        1.1$\times 10^2$   & 1.7\\
-%$10^2$	&	64$\times$128$\times$128	& 512       &   1.9$\times 10^2$   &        1.1$\times 10^2$   & 0.60 \\
-%$10^3$	&	128$\times$256$\times$256	& 2048      &   7.0$\times 10^3$   &        1.4$\times 10^3$   & 0.20 \\
-%$10^4$	&	256$\times$512$\times$512	& 8192      &   3.3$\times 10^5$   &        2.3$\times 10^4$   & 0.070\\
-%\hline																	
-%\end{tabularx}
-%\end{center}
-%\end{table}
 
@@
 \bibliography{biblio.bib}
+
+\appendix
+\section{Table of Simulations}
+
+\begin{table}[ht]
+\caption{
+}
+\setlength{\tabcolsep}{12pt}
+\label{table:speed}
+\begin{center}
+\begin{tabularx}{\textwidth}{c c c c c c c c c}
+\hline																	
+BCs	&	Ra	&	Pr	&	Ek	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
+%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
+\hline
+fixedT	&	$1.00 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
+mixedFT	&	$2.61 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
+fixedT	&	$2.15 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
+fixedT	&	$4.64 \times 10^8$	&	1	&	$\infty$	&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
+fixedT	&	$1.00 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
+fixedT	&	$2.15 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
+\hline																	
+\end{tabularx}
+\end{center}
+\end{table}
+
 \end{document}

### 2019-12-31 figures_and_data/rbc_dynamics_asymmetries.py

@@ -78,7 +78,6 @@ fixed_data = read_pdfs(fixed_ras, fixed_dirs)
 mixed_scalars = read_data(mixed_ras, mixed_dirs)
 fixed_scalars = read_data(fixed_ras, fixed_dirs)
 
-
 mk = '{:.4e}'.format(2.61e9)
 fk = '{:.4e}'.format(1.00e8)
 

### 2019-12-31 figures_and_data/rbc_restart_description.py

@@ -1,0 +1,223 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+#matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'left_T', 'right_T']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
+                    start_ind += len(arr)
+        else:
+            with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
[…]

### 2019-12-31 figures_and_data/rbc_scalar_comparisons.py

@@ -93,16 +93,26 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-plt.axhline(np.mean(mixed_trace['ra_flux'])/1e9, color='olivedrab', lw=1)
-plt.axhline(np.mean(fixed_trace['ra_temp'])/1e9, color='darkorange', lw=1, ls='-.')
-plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/1e9, color='olivedrab', lw=2, ls='-.')
-plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/1e9, color='darkorange', lw=2)
-ax.set_ylabel(r'Ra/$10^9$')
+plt.axhline(np.mean(mixed_trace['ra_flux'])/2.61e9, color='olivedrab', lw=1)
+plt.axhline(np.mean(fixed_trace['ra_temp'])/2.61e9, color='darkorange', lw=1, ls='-.')
+plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.61e9, color='olivedrab', lw=2, ls='-.')
+plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.61e9, color='darkorange', lw=2)
+ax.set_ylabel(r'Ra/$2.61\times 10^9$')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
 plt.yscale('log')
 
-plt.text(-1500, 0.13, r'Ra$_{\Delta T}$')
-plt.text(-2500, 1.5, r'Ra$_{\partial_z T}$')
+
+##Approx function for evolution of Ra
+#Nu_final_temp = np.mean(fixed_trace['Nu'][-5000:])
+#t_S = np.sqrt(2.61e9 / 1298)
+#t_best = t_S / 2
+#t_kappa = 5e4 / (Nu_final_temp/2)**2
+##plt.plot(mixed_trace['sim_time']-mixed_trace['sim_time'][-1], (1/26.1)+(1/2-1/26.1)*np.exp(-mixed_trace['sim_time']/t_kappa), c='k', lw=0.5) #1418
[…]

### 2020-01-02 tex/mixedft_evolution_ms.tex
rough draft of rayleigh benard parts of the ms mostly done

--- 2019-12-27 tex/mixedft_evolution_ms.tex
@@
 \affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
+\author{Jeffrey S. Oishi}
+\affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
 
@@
 Astrophysical studies of convection often impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection to show that the use of mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
-We show that an evolved simulation with mixed thermal boundaries exhibits dynamics whose mean measurements are indistinguishable from a comparable simulation where the temperature is fixed at both boundaries.
-We note that thermal relaxation is composed of two parts: changes in the energy reservoir of the system being studied, and changes in the stratification of the system.
-Changes in the energy reservoir result from poor choices of initial conditions and boundary conditions, while changes in stratification are the result of interesting convective dynamics.
-We warn that measurements made in simulations while the energy reservoir is changing reflect very different dynamics than relaxed simulations.
-Finally, we note that the relaxation of these systems effectively amount to a sweep through parameter space, and may be interesting in and of themselves.
+In this work, we study \RB convection to show that the use of these mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
+We demonstrate that the mean behavior of an evolved simulation with mixed thermal boundaries corresponds to an equivalent simulation with fixed temperature boundaries at the top and bottom.
+We show that the fast evolution of fixed-temperature simulations can be taken advantage of to rapidly relax simulations with mixed boundaries.
+In the measurements presented here, we find that the asymmetries created by mixed boundaries do not importantly affect spatially averaged dynamics, but we do find that more extreme values of temperature can occur near a fixed flux boundary than a fixed temperature boundary.
+We also demonstrate that these findings carry over to more complicated problems through a brief examination of rotating convection.
+These results suggest that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
+Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for \RB convection.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
+Convection is a crucial heat transport mechanism in the atmospheres of stars and planets.
+Numerical simulations are the basis for most modern studies into the nature of astrophysical convection.
+Some modern studies examine convection in the highly simplified Boussinesq approximation \cite{spiegel&veronis1960}.
+Others study more complex ``dynamo simulations,'' incorporating complicating effects such as magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
+Regardless of the degree of apparent realism included in these models, convective processes in these numerical simulations are fundamentally driven by some combination of imposed boundary conditions and internal heating profiles which in turn determine key properties of the evolved dynamics \cite{goluskin2015}.
+In astrophysical studies, a common choice of thermal boundary conditions \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
+In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection under the Boussinesq approximation.
+In this model, the only thermodynamic quantity of interest in the temperature, and we will hereafter refer to this choice of boundary conditions (fixed flux at the bottom, fixed temperature at the top) as ``mixedFT'' boundaries.
+
+Despite mixedFT boundary conditions being a common choice of numericists, we are unaware of any work which compares the dynamics produced by mixed thermal boundaries to the most traditional choice of boundary conditions in the \RB literature: fixed temperature at the top and bottom (hereafter ``fixedT'' boundaries).
+Due to the fact that mixedFT boundaries fix the flux through the convective system, this set of boundaries is expected to behave in a fundamentally similar way to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
+While there is some work \cite{johnston&doering2009} comparing fixedF and fixedT boundaries, past work primarily focused on the scaling of heat transport laws (quantified by a Nusselt number, Nu) as the convective driving is increased (quantified by the Rayleigh number, Ra).
+The equivalence of fixedF and fixedT scaling laws suggests that mixedFT scaling should also be identical.
+However, the choice of mixedFT boundaries introduces complexities into the convective system which neither fixedF or fixedT boundaries are exposed to.
+First, the evolved mean temperature of a simulation with mixedFT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
+Second, mixedFT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.
+
+In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
+We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
+We also find that this rapid thermal evolution can be bypassed by combining the results of fixedT and mixedFT simulations.
+We furthermore find that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not seem to appreciably change the mean convective state when compared to fixedT boundaries, even when the Rayleigh number is large.
+We present these findings as follows.
+In section \ref{sec:simulations}, we describe our experimental setup and numerical methods.
+In section \ref{sec:results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
+In section \ref{sec:rotating_results}, we briefly show that these findings carry over to a more complex system: rotating \RB convection.
+Finally, in section \ref{sec:discussion}, we briefly describe the implications of this work for the field of astrophysical convection.
 
@@
 \label{sec:simulations}
-We study incompressible \RB convection under the same nondimensionalization as we have done previously \cite{anders&all2018}, and including the effects of vertically directed global rotation as in \cite{julien&all1996},
+We study incompressible \RB convection under the same nondimensionalization as we have done previously \cite{anders&all2018}.
+In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so we include it here for generality.
+The equations of motion are
 \begin{align}
@@
 \end{align}
-where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature, $\varpi$ is the reduced pressure which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
 The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
@@
 These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
+In our cases where rotation is not included, we set Ek$\,= \infty$.
+The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
+The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain.
 
-In this work, we study two illustrative 3D simulations of rotating convection. 
-These simulations employ stress-free, impenetrable upper and lower boundaries,
-\begin{equation}
-\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5,
-\label{eqn:vel_bcs}
-\end{equation}
-which are typical of simulations of astrophysical convection \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
-We also later include some select two-dimensional simulations for comparison to the \RB convection literature which employ no-slip, impenetrable boundaries,
+Throughout the bulk of this work, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
+For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
 \begin{equation}
@@
 \end{equation}
-We study two configurations of thermal boundary conditions: (1) ``mixed'' boundaries where we fix the temperature at the top the flux at the bottom, and (2) fixed-temperature boundaries at the top and the bottom, or:
+The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset, as has been done by previous authors \cite{stellmach&all2014}.
+These rotating simulations employ stress-free, impenetrable boundaries,
 \begin{equation}
-(1): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
-(2): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
+\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
+\label{eqn:vel_bcs}
 \end{equation}
-For case (1), the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and for case 2 the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$.
+We study both mixedFT and fixedT thermal boundary conditions,
+\begin{equation}
+(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
+(\text{fixedT}): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
+\end{equation}
+In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
+In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the inputer Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
 
-We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016} to evolve Eqs.~(\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), and (\ref{eqn:bouss_energy}) forward in time.
-For our 2D simulations, we use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; for our 3D simulations, we use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
+We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
+Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
 The code used to run simulations and the code and data used to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
-We study two- (2D) and three-dimensional (3D) convection in which the domain is a cartesian box, whose dimensionless vertical extent is $z \in [-0.5, 0.5]$, and which is horizontally periodic with an extent of $x, y \in [-\Gamma/2, \Gamma/2]$, where $\Gamma = 2$ is the aspect ratio.
-In 2D simulations, we set $v = \partial_y = 0$.
-For our 2D simulations, we set the aspect ratio to $\Gamma = 2$; for our 3D simulations, we set the aspect ratio to $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset, as has been done by previous authors \cite{stellmach&all2014}.
-
-The initial temperature profile is linearly unstable, $T_0(z) = 0.5 - z$. 
-On top of this profile, we fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered so as to match the thermal boundary conditions.
-This ensures that the initial perturbations are much smaller than the evolved convective temperature perturbations, even at large Ra.
-We filter this noise spectrum in coefficient space, 
-such that only the lower 25\% of the coefficients
-have power; this low-pass filter is used to avoid populating the
-highest wavenumbers with noise in order to improve the stability of our
-spectral timestepping methods.
+We fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
+We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolved quantities}
+\subsection{Nondimensional Output Quantities}
 \label{sec:ra_nu_relations}
@@
 \end{equation}
-where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A dx dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A dx dy dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature different between the top and bottom plate.
-In the evolved, statistically stationary state, when fixed temperature boundaries are employed, $\text{Nu} = \text{Flux} = 1 + \Peff\angles{wT}$, and when mixed boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
+where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
+In the evolved, statistically stationary state, when fixedT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)}$, and when mixedFT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
 This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
 \begin{equation}
-\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu},
+\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu}.
+\label{eqn:ra_relation}
 \end{equation}
-and we will measure both values of Ra as our simulations evolve.
+In other words, in addition to measuring the efficiency of convective heat transport, the Nusselt number is also the unit of conversion between a temperature and a flux nondimensionalization in the evolved state.
 
@@
 
-\subsection{Classical \RB Convection}
+\subsection{Time Evolution}
 \label{sec:2d_results}
 
-\subsection{Rotating \RB Convection}
-\label{sec:rotating_results}
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
+\caption{ 
+	(left three panels) time traces of rolling averages over 50 freefall times of a mixedFT simulation (green) and a fixedT (orange) simulation.
+	(top left panel) The Rayleigh number, normalized by the input Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$ value of the mixedFT simulation.
+	(middle and bottom left panels) The Nusselt number and Peclet number evolution of the simulations is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation.
+	(right two panels) Parameter space plots of Nusselt (upper) and Peclet (lower) vs. Ra$_{\Delta T}$.
+	The green traces show the time evolution of the mixedFT case, while the orange circles and black crosses show comparison fixedT simulations.
+	The orange star in each plot corresponds to the fixedT case whose time evolution is shown on the left.
+\label{fig:rbc_scalar_comparisons} }
+\end{figure}
 
-%\begin{figure}[b]
-%\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
-%\caption{ \ref{fig:oscillating_plumes}.
-%\label{fig:nu_v_time} }
-%\end{figure}
+In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a mixedFT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
+This simulation had a coefficient resolution of (nz, nx) = (1024, 2048) and was evolved forward in time for ten days on 512 cpus.
+The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$, with a coefficient resolution of (nz, nx) = (512, 1024) which was time evolved for one thousand freefall time units after the initial convective transient (which took roughly one day on 256 cpus).
+The mixedFT case is displayed in green, and the fixedT case is displayed in orange; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
+In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
+The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the mixedFT simulation, and this final value corresponds to the input value of the equivalent fixedT case.
+On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reches its final value, which corresponds to the input value for the mixedFT simulation.
+This discrepancy in evolution timescales, where fixedT simulations evolve quickly and mixedFT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
+All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.
 
-%\begin{table}[b!]
-%\caption{
-%}
-%\setlength{\tabcolsep}{12pt}
-%\label{table:speed}
-%\begin{center}
-%\begin{tabularx}{0.72\textwidth}{ c r r c c c }
-%\hline																	
-%$S$	&	nz$\times$nx$\times$ny	&	$N_{\text{CPU}}$	&	
-%$t_{\text{CPU, SE}}$ & $t_{\text{CPU, AE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
+In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot Nu and Pe vs Ra$_{\Delta T}$.
+The green line shown in each panel is the path through parameter space that the mixed-FT simulation traces out over its time evolution.
+In the upper right (Nu vs Ra) plot, we have divided all Nu values by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by \cite{johnston&doering2009}.
+In the lower right (Re vs Ra) plot, we have divided out a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
+The orange circles show the mean values of Nu and Pe from select fixedT simulations through this parameter space, the details of which are presented in appendix \ref{app:table}; in all cases, we plot the sample mean, and the standard deviation of the sample mean is smaller than the plotted points.
+The orange star is the simulation whose time evolution is shown on the left.
+The black crosses are the reported values of Nu from the supplemental materials of \cite{zhu&all2018}, presented for comparison.
+Remarkably, the mixedFT case seems to reliably perform a sweep through this parameter space.
+However, despite seemingly tracing out the ``proper'' values of Nu(t) vs.
+Ra$_{\Delta T}$(t), we find that the mixedFT simulation achieves a larger value of the Peclet number than the comparison fixedT simulations until it converges to its final state.
+These traces through parameter space help to demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
+\caption{ 
+	(left three panels) time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
+	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
+	The mean value of the simulation's temperature gradient (middle panel) and temperature (bottom panel) are displayed, showing the change in the enforce boundary condition.
+	In the middle panel, during the fixedT portion of the simulation, we plot $\angles{Nu}\partial_z T$, while in the bottom panel, during the mixedFT portion, we plot $T / \angles{Nu}$ due to the change in temperature nondimensionalization for the different boundary conditions.
+	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
+	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
+	In each plot, we show the PDF of the dynamics at the end of the mixedFT simulation that experienced a long rundown (green lines in Fig.~\ref{fig:rbc_scalar_comparisons}), as well as dynamics from the grey shaded region displayed in the left three panels here.
+\label{fig:rbc_restart_description} }
+\end{figure}
+
+The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
+It seems plausible that one should be able to take advantage of the fast evolution on display in fixedT simulations to achieve rapidly equilibrated mixedFT simulations.
+The rundown in mixedFT simulations is very costly: not only do the turbulent dynamics at the large initial Rayleigh number need to be resolved (requiring more spectral modes to run the simulation), but thousands of freefall times must pass before convergence.
+For a sense of scale, the first thousand freefall time units of the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons} took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours.
+For comparison, the same time evolution (essentially the whole simulation) for fixedT boundary conditions took  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours.
+After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
+This means that at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is more than an order of magnitude larger than a fixedT simulation.
+
+We now describe a procedure which takes advantage of the fast evolution of fixedT simulations to achieve equilibrated mixedFT simulations.
+In essence, the full evolved flow fields in the fixedT simulation are properly re-nondimensionalized and fed into a mixedFT simulation as initial conditions.
+More precisely, the procedure for achieving converged mixedFT dynamics using fixedT simulations takes place over these steps:
+\begin{enumerate}
+\item Run a fixedT simulation from convective transient to its statistically stationary state. 
+Measure $\angles{\text{Nu}}$ in that state.
+\item Re-nondimensionalize from $\Delta = \Delta T$ to $\Delta = L_z \partial_z T$ in the definition of the Rayleigh number.
+This means changing from an input of Ra$_{\Delta T}$ to Ra$_{\partial_z T}$ as in Eqn.~\ref{eqn:ra_relation}.
+In our freefall nondimensionalization, this means setting the velocities in the mixedFT simulation to $\bm{u}_{\text{mixedFT}} = \bm{u}_{\text{fixedT}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{mixedFT}} = T_{\text{fixedT}} / \angles{\text{Nu}}$.
+\item Restart the simulation with mixedFT boundaries and continue timestepping.
+\end{enumerate}
+
+In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show time traces of a simulation in which we employ this procedure.
+We initialize a fixedT simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
+Roughly one hundred freefall times after the convective transient, we restarted this simulation using mixedFT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
+We note that this is the same Ra$_{\partial_z T}$ as the mixedFT case presented in the green lines in Fig.~\ref{fig:rbc_scalar_comparisons}.
+In the upper left panel, rolling averages over 25 freefall times of Ra$_{\Delta T} / 10^8$ and Ra$_{\partial_z T} / (2.61 \times 10^9)$ are shown in the through the full simulation.
+The time at which we switch from fixedT to mixedFT boundaries is noted by the vertical black line.
+In the middle and bottom panels, we show the time evolution of the instantaneous temperature derivative and temperature value at the bottom plate.
+In the fixedT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
+In the mixedFT final state, the temperature derivative is held constant at a value of 1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
+Unlike in the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the mixedFT state, as the thermal profile was rapidly relaxed by the early fixedT portion of the run.
+
+While these time traces show that this procedure bypasses the long thermal rundown on display in Fig.~\ref{fig:rbc_scalar_comparisons}, this does not prove that the dynamics in the final state are equivalent.
+We now compare probability distribution functions (PDFs) of various quantities in our restarted mixedFT simulation to the mixedFT simulation that stepped through a long rundown.
+For the last 500 freefall times of each simulation (e.g., the grey shaded region in Fig.~\ref{fig:rbc_restart_description}), we sample the full flow field once each freefall time.
+We interpolate the (unevenly spaced) vertical chebyshev gridpoints onto an evenly spaced grid before histogramming flow values using 500 bins.
+In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we display PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
+In Table~\ref{table:pdf_values}, we display the first four moments of each of these distributions,
+\begin{equation}
+\begin{split}
+&\mu(A) \equiv \sum_{i} A_i\,P(A_i)\,\Delta A,\qquad\qquad\qquad\qquad\qquad\qquad\,\,
+\sigma(A) \equiv \sqrt{\sum_{i}[A_i-\mu(A)]^2 P(A_i) \Delta A},\\
+&\text{Skewness}(A) \equiv \frac{1}{\sigma(A)^3}\sum_i [A_i-\mu(A)]^3 P(A_i) \Delta A,\qquad
+\text{Kurtosis}(A) \equiv \frac{1}{\sigma(A)^4}\sum_i [A_i-\mu(A)]^4 P(A_i) \Delta A,
+\end{split}
+\label{eqn:pdf_moments}
+\end{equation}
+where $A$ is the quantity, $P(A)$ is the PDF of quantity $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the PDF bins, and $i$ is the index of the bin..
+Visually, the PDFs of dynamics in a mixedFT and a restarted fixedT-to-mixedFT simulation are essentially identical.
+In all cases except for the enstrophy, the four moments of the PDFs between the two runs are also very similar.
+These simulations have no-slip boundaries, so the enstrophy is concentrated near the plume impacting sites within the boundary layers.
+The small differences between the enstrophy PDFs perhaps points to slightly different plume morphologies being sampled during the 500 freefall time units in the two runs, but the similarities between the two cases in other important quantities (specfically in nonlinear transport) lead us to believe that this difference is unimportant.
+
+\begin{table}[t!]
+\caption{ 
+	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
+}
+\setlength{\tabcolsep}{12pt}
+\label{table:pdf_values}
+\begin{center}
+\begin{tabularx}{\textwidth}{c c c c c c}
+\hline																	
+Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
 %\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
 %\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
-%\hline
-%%2 sig figs, scientific notation, swap SE and AE, right justify Ncpu, 2 sig figs ratio, right justify communicates biggerness. 
-%$10^2$	&	64$\times$128	&	32    &  2.2              & 4.4               &     2.0  \\
-%$10^3$	&	128$\times$256	&	64    &  53               & 21                &     0.39 \\
-%$10^4$	&	256$\times$512	&	128   &  1.2$\times 10^3$ & 1.8$\times 10^2$  &     0.15  \\
-%$10^5$	&	512$\times$1024&	256   &  2.4$\times 10^4$ & 2.8$\times 10^3$  &     0.12 \\
-%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-%\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
-%\hline
-%$10^1$	&	32$\times$64$\times$64	    & 512       &   62                 &        1.1$\times 10^2$   & 1.7\\
-%$10^2$	&	64$\times$128$\times$128	& 512       &   1.9$\times 10^2$   &        1.1$\times 10^2$   & 0.60 \\
-%$10^3$	&	128$\times$256$\times$256	& 2048      &   7.0$\times 10^3$   &        1.4$\times 10^3$   & 0.20 \\
-%$10^4$	&	256$\times$512$\times$512	& 8192      &   3.3$\times 10^5$   &        2.3$\times 10^4$   & 0.070\\
-%\hline																	
-%\end{tabularx}
-%\end{center}
-%\end{table}
+\hline
+$T$				&	mixedFT		&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.1		&	15 \\
+				&	mixedFT,r	&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.3		&	18 \\
+\hline
+$\omega^2$		&	mixedFT		&		$1.3$					&	$6.4$					&	19		&	$5.2 \times 10^2$ \\
+				&	mixedFT,r	&		$3.9$					&	$7.4$					&	18		&	$4.5 \times 10^2$ \\
+\hline
+$wT$			&	mixedFT		&		$1.9 \times 10^{-5}$	&	$9.4 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+				&	mixedFT,r	&		$1.9 \times 10^{-5}$	&	$9.3 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+\hline
+$w$				&	mixedFT		&		$7.9 \times 10^{-7}$	&	$4.9 \times 10^{-2}$	&	0.016	&	$2.7$ \\
+				&	mixedFT,r	&		$-5.2 \times 10^{-6}$	&	$4.8 \times 10^{-2}$	&	0.0066	&	$2.8$ \\
+\hline																	
+\end{tabularx}
+\end{center}
+\end{table}
+
+We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of a mixedFT simulation.
+We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
+We note however that the fixedT-to-mixedFT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified \RB convection setup that we are aware of.
+The successful degree with which this mechanism reproduces the evolved dynamics suggests that thermal relaxation occurs in two parts:
+\begin{enumerate}
+\item Changes to the experimental energy reservoir, and
+\item Restratification of the experiment.
+\end{enumerate}
+The rapid evolution of fixedT runs, whose experimental energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in \RB convection.
+The long rundown of mixedFT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir, and the mean temperature of the simulation, drifting over time.
+The coupling of fixedT and mixedFT experiments essentially bypasses this first step of relaxation, and because the \RB system being studied here restratifies instantaneously, mixedFT dynamics can be sampled shortly after changing boundary conditions.
+It is plausible that the inclusion of stable layers within the domain where convective motions cannot rapidly mix the thermodynamic state would require the use of more complicated accelerated evolution techniques, such as those we previously described \cite{anders&all2018}, due to the non-negligible restratification timescales of those systems.
+
+\subsection{Asymmetries induced by mixed boundaries}
+\label{sec:asymmetries}
+Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixed-FT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
+[NOTE: in the version of the paper we will later submit, we will hopefully study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
+For now, we'll carry on with the same values as in the previous section.]
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
+\caption{ 
+\label{fig:rbc_1D_profiles} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our fixed-T and mixed-FT cases.
+In the upper left panel, we show the mean temperature profiles achieved in the evolved state of both simulations.
+Throughout the full depth, these profiles differ by less than 2\%, as shown in the lower left panel.
+In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
+Surprisingly, despite symmetrical boundary conditions in fixed-T simulations and asymmetrical boundary conditions in mixed-FT cases, we find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
+In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
+Once again, these profiles agree to within $< 2\%$.
+
+In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases.
+the fluxes show very good agreement just like the temperature profile.
+Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
+Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boudnary layers.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
+\caption{ 
+\label{fig:rbc_dynamics_asymmetries} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which mixedFT boundaries introduce into the simulation.
+In the left panel, we plot PDFs of the temperature fields in comparable fixedT and mixedFT simulations.
+These PDFs agree remarkably well for cold temperatures (near the shared fixed-T boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
+We find that the mixedFT pdf has a much longer tail and is capable of achieving much hotter instantaneous temperature values than a fixedT simulation.
+In order to understand how this is possible, we examine a snapshot of the full temperature field.
+In the middle panel, we plot the temperature anomaly -- the temperature field with the mean vertical profile subtracted from it.
+We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the lower right panels.
+The fixed-T upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
+The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area, thus allowing for the asymmetry in the tails of the temperature PDF.
+
+We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{rbc_1D_profiles}).
+However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
+For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with impliciation for the solar dynamo.
+These results suggest that the choice of imposed boundary conditions can affect the extreme events that a simulation is capable of achieving.
+
+\section{Rotating \RB Convection}
+\label{sec:rotating_results}
+Here we show that in Rotating convection, not only does thermal evolution take forever, but it can even vastly change the Rossby number of your simulation, taking you from e.g., Ro $\sim$ 1 (rotationally unconstrained) to Ro $\sim$ 1/10 (rotationally constrained).
+So as you add more physics, making sure that you're past the rundown is even more important.
+Fortunately, for rotating RBC, our same trick works.
+
+(that's the idea for this section, sims are still chugging away)
 
@@
 \section{Discussion \& Conclusions}
-\label{sec:extensions}
+\label{sec:discussion}
+
+Here we basically say everything we said again, but in short form, and then we perhaps talk about the implications for astrophysics.
+Doesn't hurt to repeat all of the imprtant points we made all over again.
 
@@
 \bibliography{biblio.bib}
+
+\appendix
+\section{Table of Simulations}
+\label{app:table}
+
+\begin{table}[ht]
+\caption{
+}
+\setlength{\tabcolsep}{12pt}
+\label{table:speed}
+\begin{center}
+\begin{tabularx}{\textwidth}{c c c c c c c c c}
+\hline																	
+BCs	&	Ra	&	Pr	&	Ek	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
+%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
+\hline
+fixedT	&	$1.00 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
+mixedFT	&	$2.61 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
+fixedT	&	$2.15 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
+fixedT	&	$4.64 \times 10^8$	&	1	&	$\infty$	&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
+fixedT	&	$1.00 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
+fixedT	&	$2.15 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
+\hline																	
+\end{tabularx}
+\end{center}
+\end{table}
+
 \end{document}

### 2020-01-02 figures_and_data/rbc_restart_description.py

@@ -93,20 +93,23 @@ mk = '{:.4e}'.format(2.61e9)
 rk = '{:.4e}'.format(2.61e9)
 
 # Get rolling averages of all data; Output is every 0.1 time units
-avg_window = 100 #time units
+avg_window = 25 #time units
 mixed_trace = mixed_data[mk]
 fixed_trace = fixed_data[fk]
 partial_restarted_trace = restarted_data[rk]
 
 restarted_trace = OrderedDict()
 
+good_fixed_times = fixed_trace['sim_time'] <= partial_restarted_trace['sim_time'][0]
+
 for k in fixed_trace.keys():
+    fixed = fixed_trace[k][good_fixed_times]
     if k == 'left_flux' or k == 'right_flux':
-        restarted_trace[k] = np.concatenate((fixed_trace[k]/26.1**(3./2), partial_restarted_trace[k][1:])) 
+        restarted_trace[k] = np.concatenate((fixed/26.1**(3./2), partial_restarted_trace[k][1:])) 
     elif 'T' in k:
-        restarted_trace[k] = np.concatenate((fixed_trace[k], partial_restarted_trace[k][1:]*26.1)) 
+        restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:]*26.1)) 
     else:
-        restarted_trace[k] = np.concatenate((fixed_trace[k], partial_restarted_trace[k][1:])) 
+        restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:])) 
 
 dff = pd.DataFrame(data=fixed_trace)
 rolledf = dff.rolling(window=avg_window*10, min_periods=avg_window*10).mean()
@@ -130,10 +133,9 @@ subplots = [( (50 , 0  ),       300,    330),
             ( (500 , 700),       450,    300),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
-
 for i in [0, 1, 2]:
-    axs[i].fill_between([1500, 2000], 1e-2, 10, alpha=0.2, color='grey')
-    axs[i].axvline(fixed_trace['sim_time'][-1], c='k', lw=0.5)
[…]

### 2020-01-02 figures_and_data/rbc_scalar_comparisons.py

@@ -66,7 +66,7 @@ mixed_data = read_data(mixed_ras, mixed_dirs)
 fixed_data = read_data(fixed_ras, fixed_dirs)
 
 # Get rolling averages of all data; Output is every 0.1 time units
-avg_window = 100 #time units
+avg_window = 50 #time units
 fixed_trace = fixed_data['{:.4e}'.format(1.00e8)]
 mixed_trace = mixed_data['{:.4e}'.format(2.61e9)]
 dff = pd.DataFrame(data=fixed_trace)
@@ -126,7 +126,9 @@ plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['Nu']/Nu_final
 plt.axhline(1, c='darkorange', lw=1)
 plt.yscale('log')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
+plt.ylim(0.7, 3)
 ax.set_ylabel(r'Nu/Nu$_{\Delta T}$')
+
 
 #Panel 3, Pe evolution
 plt.sca(axs[2])

### 2020-01-02 tex/mixedft_evolution_ms.tex
adds fig 3 / 4 caption + a bit of appendix table caption

@@
 \caption{ 
+	(upper left) The horizontally- and time-averaged temperature profile is shown for a mixedFT (green) and fixedT (orange) simulation.
+	(upper middle) The horizontally- and time-averaged temperature profile is shown for upflow regions (solid lines) and downflow regions (dashed lines) respectively.
+	(upper right) The horizontally- and time-averaged fluxes in the system are shown.
+	(bottom panels) The percentage difference between the corresponding quantities in the top panels are displayed, and in most cases measurements agree to within a few percent through the full depth of the domain.
 \label{fig:rbc_1D_profiles} }
@@
 \caption{ 
+	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
+	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
+	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
+	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
 \label{fig:rbc_dynamics_asymmetries} }
@@
 
-We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{rbc_1D_profiles}).
+We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
 However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
@@
 \caption{
+	Input and output values from the simulations in this work are shown.
+	The ``Nu comp'' values are comparison Nusselt number values reported in \cite{zhu&all2018}.
+	Values of Nu and Re are the sample mean; the standard deviation of the sample mean is shown for Nu measurements, and is smaller than the number of significant figures reported for Re measurements.
 }

### 2020-01-15 tex/mixedft_evolution_ms.tex
initial rotation stuff

@@
 Astrophysical studies of convection often impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection to show that the use of these mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
+In this work, we study \RB convection (RBC) to show that the use of these mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
 We demonstrate that the mean behavior of an evolved simulation with mixed thermal boundaries corresponds to an equivalent simulation with fixed temperature boundaries at the top and bottom.
@@
 These results suggest that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
-Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for \RB convection.
+Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
 \end{abstract}
@@
 \label{sec:introduction}
-Convection is a crucial heat transport mechanism in the atmospheres of stars and planets.
+Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
 Numerical simulations are the basis for most modern studies into the nature of astrophysical convection.
 Some modern studies examine convection in the highly simplified Boussinesq approximation \cite{spiegel&veronis1960}.
-Others study more complex ``dynamo simulations,'' incorporating complicating effects such as magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
+Others study more complex ``dynamo simulations'', incorporating complicating effects such as magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
 Regardless of the degree of apparent realism included in these models, convective processes in these numerical simulations are fundamentally driven by some combination of imposed boundary conditions and internal heating profiles which in turn determine key properties of the evolved dynamics \cite{goluskin2015}.
@@
 In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection under the Boussinesq approximation.
-In this model, the only thermodynamic quantity of interest in the temperature, and we will hereafter refer to this choice of boundary conditions (fixed flux at the bottom, fixed temperature at the top) as ``mixedFT'' boundaries.
+In this model, the only thermodynamic quantity of interest is the temperature, and we will hereafter refer to this choice of boundary conditions (fixed flux at the bottom, fixed temperature at the top) as ``mixedFT'' boundaries.
 
@@
 Due to the fact that mixedFT boundaries fix the flux through the convective system, this set of boundaries is expected to behave in a fundamentally similar way to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
-While there is some work \cite{johnston&doering2009} comparing fixedF and fixedT boundaries, past work primarily focused on the scaling of heat transport laws (quantified by a Nusselt number, Nu) as the convective driving is increased (quantified by the Rayleigh number, Ra).
+While there is some work \cite{johnston&doering2009} comparing fixedF and fixedT boundaries, past work primarily focused on the scaling of heat transport laws (quantified by a Nusselt number, Nu) as the convective driving is increased (quantified by the Rayleigh number, Ra) [more refs].
 The equivalence of fixedF and fixedT scaling laws suggests that mixedFT scaling should also be identical.
@@
 \label{sec:simulations}
-We study incompressible \RB convection under the same nondimensionalization as we have done previously \cite{anders&all2018}.
+We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
 In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so we include it here for generality.
@@
 \end{align}
-where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature, $\varpi$ is the reduced pressure which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi = [defn]$ is the reduced pressure which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
 The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
@@
 \end{equation}
-where $\Delta$ is the dimensionless temperature jump across the domain (described below with our boundary conditions), $\Omega$ is the global rotation frequency, and all other parameters are as described in our previous work \cite{anders&all2018}.
+where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency \cite{anders&all2018}.
 These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
@@
 The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
+$\Delta$ is the dimensionless temperature jump across the domain; depending on our choice of boundary condition, $\Delta$ defines either a temperature or flux Rayleigh number,
+\begin{equation}
+\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
+\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
+\end{equation}
 
@@
 In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
-In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the inputer Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
+In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
 
@@
 \caption{ 
-	(left three panels) time traces of rolling averages over 50 freefall times of a mixedFT simulation (green) and a fixedT (orange) simulation.
+	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT simulation (green) and a fixedT (orange) simulation.
 	(top left panel) The Rayleigh number, normalized by the input Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$ value of the mixedFT simulation.
@@
 The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the mixedFT simulation, and this final value corresponds to the input value of the equivalent fixedT case.
-On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reches its final value, which corresponds to the input value for the mixedFT simulation.
+On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reaches its final value, which corresponds to the input value for the mixedFT simulation.
 This discrepancy in evolution timescales, where fixedT simulations evolve quickly and mixedFT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
@@
 \caption{ 
-	(left three panels) time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
+	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
 	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
-	The mean value of the simulation's temperature gradient (middle panel) and temperature (bottom panel) are displayed, showing the change in the enforce boundary condition.
+	The mean value of the simulation's temperature gradient (middle panel) and temperature (bottom panel) are displayed, showing the change in the enforced boundary condition.
 	In the middle panel, during the fixedT portion of the simulation, we plot $\angles{Nu}\partial_z T$, while in the bottom panel, during the mixedFT portion, we plot $T / \angles{Nu}$ due to the change in temperature nondimensionalization for the different boundary conditions.
@@
 We initialize a fixedT simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
-Roughly one hundred freefall times after the convective transient, we restarted this simulation using mixedFT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
+Roughly one hundred freefall times after the convective transient, we restart this simulation using mixedFT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
 We note that this is the same Ra$_{\partial_z T}$ as the mixedFT case presented in the green lines in Fig.~\ref{fig:rbc_scalar_comparisons}.
@@
 where $A$ is the quantity, $P(A)$ is the PDF of quantity $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the PDF bins, and $i$ is the index of the bin..
-Visually, the PDFs of dynamics in a mixedFT and a restarted fixedT-to-mixedFT simulation are essentially identical.
+Visually the PDFs of dynamics in a mixedFT and a restarted fixedT-to-mixedFT simulation are essentially identical.
 In all cases except for the enstrophy, the four moments of the PDFs between the two runs are also very similar.
@@
 In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases.
-the fluxes show very good agreement just like the temperature profile.
+The fluxes show very good agreement just like the temperature profile.
 Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
-Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boudnary layers.
+Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boundary layers.
 
@@
 However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
-For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with impliciation for the solar dynamo.
+For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with implications for the solar dynamo.
 These results suggest that the choice of imposed boundary conditions can affect the extreme events that a simulation is capable of achieving.
@@
 \label{sec:rotating_results}
-Here we show that in Rotating convection, not only does thermal evolution take forever, but it can even vastly change the Rossby number of your simulation, taking you from e.g., Ro $\sim$ 1 (rotationally unconstrained) to Ro $\sim$ 1/10 (rotationally constrained).
-So as you add more physics, making sure that you're past the rundown is even more important.
-Fortunately, for rotating RBC, our same trick works.
+We now extend our study of 2D RBC to a more complicated experiment.
+Here, we examine rotating RBC with an Ekman number of $10^{-6}$.
+We study a fixedT case whose supercriticality is $\sim 3$ with Ra$_{\Delta T} = 2.75\times 10^9$, and a corresponding mixedFT case with $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$.
+We furthermore employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices \cite{couston&all2019}.
 
-(that's the idea for this section, sims are still chugging away)
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we once compare the time evolution of the mixedFT and fixedT cases.
+The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
+Even in the presence of strong rotation, the fixedT case's fluxes immediately equilibrate, but the mixedFT case takes thousands of freefall times to achieve thermal relaxation.
+In the middle left panel, we show the evolution of the Rossby number.
+While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro$\sim 0.1$, the initial state of the mixedFT simulation is only weakly rotationally constrained (Ro$\sim 1$).
+The degree of rotational constraint felt by the flows decreases slowly toward its final state over thousands of freefall times.
+In the bottom left panel, we display the evolution of the Peclet number over time.
+Somewhat surprisingly, the peak value of Pe is found not during the convective transient but rather a few hundreds of freefall times later.
+After achieving this peak value, the mean Pe monotonically decreases toward its final state.
+We suspect that initially large value of Ra$_{\Delta T}$ in the mixedFT case drives high velocity flow associated with a developed large scale vortex (LSV).
+As Ra$_{\Delta T}$ and convective driving decrease over time, the driving of the kinetic energy in this LSV eventually reaches an equilibrium value before decreasing, leading to the ``bump'' in the Pe trace.
+
+In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.
+Ra(t) for our mixedFT case (thick green line) and the evolved value of Nu in the fixedT case (orange star).
+We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of \cite{cheng&all2015}.
+We note that these comparison values are in cylindrical domains with Pr=7, whereas we are in Cartesian geometry with Pr=1, some some differences are expected.
+The evolution of Nu vs Ra is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
+Although the simulation details of mixedFT simulations are not, on average, useful, this case of rotating convection is one case where they could be.
+The scaling of Nu vs Ra in the rotationally constrained regime is poorly understood [cite, cite], but a single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space.
+The evolution of these simulation could therefore perhaps be used to understand how the nature of convection changes as it develops into an increasingly rotationally constrained regime.
+However, we once again caution the reader that if they are primarily intersted in the evolved simulation dynamics, then the transient dynamics can be very misleading.
+Not only does the mixedFT transient state exhibit more turbulence and heat transport than an evolved state, but the degree of rotational constraint -- and therefore the dominant scale of convection -- also changes appreciably over time.
+
+In the bottom right panels of Fig.~\ref{fig:rotating_panels}, we examine the evolution of dominant flow structures over the course of thermal relaxation.
+Shown is the vertically integrated vertical component of the vorticity.
+As shown in the left panel, a dominant LSV which is aligned with the global rotation forms at early times.
+Over thousands of freefall times, this LSV evolves into a long-lived vortex pair, displayed in the middle panel.
+Finally, in the evolved state, this vortex pair solution begins to oscillate with domain-wide jets, such as those displayed in the right panel.
+We find that the the fixedT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 frefall timescales of evolution that we simulated.
+
+Importantly, the convective transient of the mixedFT simulation studied here requires significantly higher spectral resolution to resolve than the evolved state.
+The fixedT simulation shown in this section was computed stably at $128^3$.
+On the other hand, the convective transient of the mixedFT simulation was computed at $512\times384^2$.
+In order to reduce the computational cost of this simulation, we reduced the vertical resolution twice as the simulation became more rotationally constrained.
+One hundred freefall times after transient, we reduced the resolution to $256\times384^2$.
+About $3.3 \times 10^3$ freefall times into the simulation, we further reduced the vertical resolution to $128\times384^2$.
+At each of these times, we found that the simulation solution could not be reproduced with fidelity upon lowering the horizontal resolution.
+This suggests that small scale turbulent velocity structure injected by the vigorous transient is long lived throughout the thermal evolution of the simulation.
+
+We also note that the difference in computational cost required to reach the equilibrated solution is staggering.
+The number of iteration per cpu-hour was 4.25 at $512\times384^2$, 10.6 at $256\times384^2$, and 38 at $128\times384^2$.
+The first resolution was run for $1.59 \times 10^5$ iterations, the second for $2.22 \times 10^6$ iterations, and the third for $3.30 \times 10^6$ iterations.
+
+On the other hand, the fixedT simulation got 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
+\caption{ 
+	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
+	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
+	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
+	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
+\label{fig:rotating_panels} }
+\end{figure}
 
@@
 \begin{acknowledgments}
+We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in mixedFT simulations. 
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
@@
 \hline																	
+\hline																	
+fixedT	&	$2.75 \times 10^9$		&	1	&	$10^{-6}$	&	128$^3$				&	?					&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$ \\
+mixedFT	&	$2.1 \times 10^{10}$	&	1	&	$10^{-6}$	&	nz$\times$384$^2$	&	?					&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$ \\
+\hline																	
 \end{tabularx}

### 2020-01-16 tex/mixedft_evolution_ms.tex
rough draft of paper done.

@@
 \end{align}
-where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi = [defn]$ is the reduced pressure which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
 The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
@@
 \end{equation}
-where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency \cite{anders&all2018}.
+where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency.
 These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In our cases where rotation is not included, we set Ek$\,= \infty$.
+In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
 The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
@@
 \end{equation}
+We study both mixedFT and fixedT thermal boundary conditions,
+\begin{equation}
+(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
+(\text{fixedT}): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
+\end{equation}
+In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
+In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
 
@@
 \end{equation}
-We study both mixedFT and fixedT thermal boundary conditions,
-\begin{equation}
-(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
-(\text{fixedT}): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
-\end{equation}
-In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
-In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
 
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
-In the evolved, statistically stationary state, when fixedT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)}$, and when mixedFT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
+In the evolved, statistically stationary state, when fixedT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)\Peff}$, and when mixedFT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
 This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
@@
 \section{Results}
-\label{sec:results}
+\label{sec:2d_results}
 
 \subsection{Time Evolution}
-\label{sec:2d_results}
 
@@
 The long rundown of mixedFT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir, and the mean temperature of the simulation, drifting over time.
-The coupling of fixedT and mixedFT experiments essentially bypasses this first step of relaxation, and because the \RB system being studied here restratifies instantaneously, mixedFT dynamics can be sampled shortly after changing boundary conditions.
-It is plausible that the inclusion of stable layers within the domain where convective motions cannot rapidly mix the thermodynamic state would require the use of more complicated accelerated evolution techniques, such as those we previously described \cite{anders&all2018}, due to the non-negligible restratification timescales of those systems.
+Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for mixedFT boundaries, and our procedure uses fixedT dynamics to choose a more ideal set of initial conditions.
 
@@
 \label{sec:asymmetries}
-Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixed-FT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
+Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixedFT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
 [NOTE: in the version of the paper we will later submit, we will hopefully study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
@@
 
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our fixed-T and mixed-FT cases.
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our fixedT and mixedFT cases.
 In the upper left panel, we show the mean temperature profiles achieved in the evolved state of both simulations.
@@
 In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
-Surprisingly, despite symmetrical boundary conditions in fixed-T simulations and asymmetrical boundary conditions in mixed-FT cases, we find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
+Surprisingly, despite symmetrical boundary conditions in fixedT simulations and asymmetrical boundary conditions in mixedFT cases, we find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
 In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
@@
 	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
-	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	The right tail of the distribution (near the cold fixedflux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
 	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
@@
 In the left panel, we plot PDFs of the temperature fields in comparable fixedT and mixedFT simulations.
-These PDFs agree remarkably well for cold temperatures (near the shared fixed-T boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
+These PDFs agree remarkably well for cold temperatures (near the shared fixedT boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
 We find that the mixedFT pdf has a much longer tail and is capable of achieving much hotter instantaneous temperature values than a fixedT simulation.
@@
 In the middle panel, we plot the temperature anomaly -- the temperature field with the mean vertical profile subtracted from it.
-We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the lower right panels.
-The fixed-T upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
+We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
+The fixedT upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
 The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area, thus allowing for the asymmetry in the tails of the temperature PDF.
@@
 However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
-For example, some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017}, with implications for the solar dynamo.
-These results suggest that the choice of imposed boundary conditions can affect the extreme events that a simulation is capable of achieving.
+We explore this further in the discussion in section \ref{sec:discussion}.
 
@@
 \label{sec:rotating_results}
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
+\caption{ 
+	(left three panels) Time traces of rolling averages over 50 freefall times of a rotating mixedFT simulation (green) and a fixedT (orange) simulation.
+	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the fixedT simulation.
+	(middle left panel) The Rossby number evolution of both simulation; the bulk flow of the mixedFT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the fixedT simulation is in this latter state through its full evolution.
+	(bottom left panel) The Peclet number evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the fixedT simulation.
+	(right upper panel) Parameter space plots of Nusselt vs. Ra$_{\Delta T}$.
+	Circlular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
+	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
+	Data from our mixedFT experiment are shown as a thick green trace, and the fixedT experiment's average is shown as a large orange star.
+	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the mixedFT simulation.
+	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
+	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in \cite{stellmach&all2014}.
+	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
+	The fixedT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
+	The three vertical black lines in the left panels signify the times at which this snapshots are taken.
+\label{fig:rotating_panels} }
+\end{figure}
+
 We now extend our study of 2D RBC to a more complicated experiment.
-Here, we examine rotating RBC with an Ekman number of $10^{-6}$.
+Here, we examine 3D rotating RBC with an Ekman number of $10^{-6}$.
 We study a fixedT case whose supercriticality is $\sim 3$ with Ra$_{\Delta T} = 2.75\times 10^9$, and a corresponding mixedFT case with $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$.
-We furthermore employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices \cite{couston&all2019}.
+Both simulations have an aspect ratio $\Gamma = 0.481$, which is roughly ten times larger than the critical wavelength of fixedT convection at Ek = $10^{-6}$.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices \cite{couston&all2019}.
 
-In the left three panels of Fig.~\ref{fig:rotating_panels}, we once compare the time evolution of the mixedFT and fixedT cases.
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of the mixedFT and fixedT cases.
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
@@
 In the middle left panel, we show the evolution of the Rossby number.
-While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro$\sim 0.1$, the initial state of the mixedFT simulation is only weakly rotationally constrained (Ro$\sim 1$).
+While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro $\,\sim 0.1$, the initial state of the mixedFT simulation is only weakly rotationally constrained (Ro $\,\sim 1$).
 The degree of rotational constraint felt by the flows decreases slowly toward its final state over thousands of freefall times.
@@
 After achieving this peak value, the mean Pe monotonically decreases toward its final state.
-We suspect that initially large value of Ra$_{\Delta T}$ in the mixedFT case drives high velocity flow associated with a developed large scale vortex (LSV).
+We suspect that the initially large value of Ra$_{\Delta T}$ in the mixedFT case drives high velocity flow associated with a developed large scale vortex (LSV).
 As Ra$_{\Delta T}$ and convective driving decrease over time, the driving of the kinetic energy in this LSV eventually reaches an equilibrium value before decreasing, leading to the ``bump'' in the Pe trace.
@@
 We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of \cite{cheng&all2015}.
-We note that these comparison values are in cylindrical domains with Pr=7, whereas we are in Cartesian geometry with Pr=1, some some differences are expected.
-The evolution of Nu vs Ra is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Although the simulation details of mixedFT simulations are not, on average, useful, this case of rotating convection is one case where they could be.
-The scaling of Nu vs Ra in the rotationally constrained regime is poorly understood [cite, cite], but a single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space.
-The evolution of these simulation could therefore perhaps be used to understand how the nature of convection changes as it develops into an increasingly rotationally constrained regime.
-However, we once again caution the reader that if they are primarily intersted in the evolved simulation dynamics, then the transient dynamics can be very misleading.
-Not only does the mixedFT transient state exhibit more turbulence and heat transport than an evolved state, but the degree of rotational constraint -- and therefore the dominant scale of convection -- also changes appreciably over time.
+We note that these comparison values are in cylindrical domains with Pr=7, whereas we are in Cartesian geometry with Pr=1, so some differences are expected.
+As has been seen previously, the evolution of Nu vs Ra in the rotationally constrained regime is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
 
@@
 
-Importantly, the convective transient of the mixedFT simulation studied here requires significantly higher spectral resolution to resolve than the evolved state.
-The fixedT simulation shown in this section was computed stably at $128^3$.
-On the other hand, the convective transient of the mixedFT simulation was computed at $512\times384^2$.
-In order to reduce the computational cost of this simulation, we reduced the vertical resolution twice as the simulation became more rotationally constrained.
-One hundred freefall times after transient, we reduced the resolution to $256\times384^2$.
-About $3.3 \times 10^3$ freefall times into the simulation, we further reduced the vertical resolution to $128\times384^2$.
-At each of these times, we found that the simulation solution could not be reproduced with fidelity upon lowering the horizontal resolution.
+We note briefly that the transition from the unconstrained to rotationally constrained regime may be one area where the time evolution of mixedFT simulations could be useful.
+The scaling of Nu vs Ra in the rotationally constrained regime is much less well understood than it is in classical RBC [cite, cite].
+A single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}.
+In the nonrotating case, Nu(t) vs.~Ra(t) produced the expected result (Fig.~\ref{fig:rbc_scalar_comparison}), so this approach may be one way to cleverly fill in this parameter space.
+However, it is probable that the best course of action is simply to run a large suite of fixedT simulations that cover the same track for two reasons:
+\begin{enumerate}
+\item The long thermal rundown has some short-lived memory of the higher-Ra$_{\Delta T}$ state that it was recently in.
+This is seen both in the post-transient bump of Pe in Fig.~\ref{fig:rotating_panels}, and also was found from a practical computing standpoint.
+In order to reduce the computational cost of this mixedFT simulation, we reduced the vertical resolution from $512\times384^2$ to $256\times384^2$ (after about 100 freefall times) and then later to $128\times384^2$ (after about $3.3 \times 10^3$ freefall times).
+At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduced the simulation solution with fidelity.
+For comparison, the fixedT simulation whose dynamics are identical to the evolved mixedFT simulation was well resolved at a coefficient resolution of $128^3$.
 This suggests that small scale turbulent velocity structure injected by the vigorous transient is long lived throughout the thermal evolution of the simulation.
-
-We also note that the difference in computational cost required to reach the equilibrated solution is staggering.
-The number of iteration per cpu-hour was 4.25 at $512\times384^2$, 10.6 at $256\times384^2$, and 38 at $128\times384^2$.
-The first resolution was run for $1.59 \times 10^5$ iterations, the second for $2.22 \times 10^6$ iterations, and the third for $3.30 \times 10^6$ iterations.
-
-On the other hand, the fixedT simulation got 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
-\caption{ 
-	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
-	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
-	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
-	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
-	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
-\label{fig:rotating_panels} }
-\end{figure}
+\item The cost of running a turbulent mixedFT simulation, compared to running its comparison fixedT simulation, is astounding.
+The mixedFT case ran for roughly $1.4 \times 10^4$ freefall time units total, and the number of iterations achieved per cpu-hour was $\sim$0.733 at $512\times384^2$, $\sim$2.03 at $256\times384^2$, and $\sim$6.79 at $128\times384^2$.
+The simulation stepped through $1.59 \times 10^5$, $2.22 \times 10^6$, and $3.30 \times 10^6$ iterations at these resolutions, respectively, for a combined total of 2.32 million cpu-hours.
+For comparison, the fixedT simulation ran for $5 \times 10^3$ freefall units at $128^3$, took 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
+In other words, the computational cost of the mixedFT simulation was \emph{two orders of magnitude} larger than its comparison fixedT case; even though it sampled many different values of Ra$_{\Delta T}$ momentarily, its cost makes this hardly worth it.
+\end{enumerate}
 
@@
 \label{sec:discussion}
+In summary, we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``mixedFT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``fixedT'' boundaries, where temperature is fixed at the top and bottom.
+We find that mixedFT experiments experience a long thermal relaxation which is not experienced by fixedT simulations.
+Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
+\begin{enumerate}
+\item Thermal relaxation has two components: (a) changes in the energy reservoir and (b) changes in the experimental stratification.
+We find that the long relaxation of mixedFT simulations is due to changes in the experimental energy reservoir; this reservoir is roughly constant in fixedT simulations.
+On the other hand, RBC seems to restratify itself nearly instantaneously, as suggested by the rapid equilibration of our fixedT simulations.
+\item The thermal relaxation process of a mixedFT simulation essentially performs a sweep through Ra$_{\Delta T}$ parameter space.
+We find that the heat transport (the Nusselt number) follows classical scaling laws through this parameter space sweep, but does so in the presence of increased turbulent velocities (quantified by the Reynolds number).
+\item Despite minor asymmetries in the instantaneously measured flows, the mean state of a mixedFT simulation appears equally symmetrical to fixedT simulations.
+\item The great computational expense of achieving thermal relaxation in a mixedFT simulation can be avoided by using the evolved state of a fixedT simulation as a ``better'' set of initial conditions for a mixedFT simulation.
+In other words, the proper choice of initial conditions can ensure that the evolved experimental energy reservoir is close to the initial state.
+\item If dynamical measurements are taken during the thermal relaxation of a mixedFT simulation, they may be misleading.
+Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
+\end{enumerate}
 
-Here we basically say everything we said again, but in short form, and then we perhaps talk about the implications for astrophysics.
-Doesn't hurt to repeat all of the imprtant points we made all over again.
+In this work, we have studied the simplest possible case of convection: \RB convection; we will now comment on open avenues of research that should be investigated and some lessons to be learned for astrophysical convection.
+Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.
+This is not always true --- for example, in the late stages of the lifetimes of stars, some burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation [cite, cite].
+The use of mixedFT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
+However, for stages in the lifetimes of stellar or planetary atmospheres or interiors that survive for much longer than their respective Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the fixedT or evolved mixedFT cases here.
+
+One question which our study of RBC is not able to study is: how long does it take for a given convective system to restratify?
+Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
+It is, however, probable that clever techniques could be used to rapidly restratify atmospheres \cite{anders&all2018}, and this should be examined in more detail for a given thermal stratification.
+
+RBC is fundamentally symmetrical, but many processes in astrophysics occuring in density-stratified domains in which the symmetries of the problem are fundamentally broken.
+In the present study, we observed that flux boundaries achieve more extreme values than temperature boundaries.
+In studies of overshooting or penetrating convection, these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
+Some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.
+
+Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains.
+These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
+We found here in our mixedFT rotating simulation that the early unrelaxed state generated a mean flow that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+If we had terminated our mixedFT rotating simulation too early, we would not have seen this feature evolve as the simulation relaxed and progressed into a more rotationally constrained, lower Rossby number state.
+Many dynamo simulations are performed in highly turbulent regimes at the cutting-edge of what is achievable using modern computational resources.
+As a result, timestepping through thousands of freefall timescales is not possible in these simulations.
+It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
+Some authors [cite, cite] employ fixed-flux boundary conditions at \emph{both} boundaries in these simulations, and our results here suggest that such a choice is wise in these simulations.
+
+In conclusion, we note that our results here should provide astrophysical convection simulations with reason for caution and optimism.
+As a community of convection modellers, it is crucial that we understand the consequences that our choices of boundary conditions have on our experiments so that we do not misinterpret the evolved dynamics.
+However, through the proper setup of experiments (here, fixedT instead of mixedFT boundary conditions), some of the problems that we face in numerics (thermal relaxation) can simply disappear.
 
@@
 \caption{
-	Input and output values from the simulations in this work are shown.
+	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
 	The ``Nu comp'' values are comparison Nusselt number values reported in \cite{zhu&all2018}.
 	Values of Nu and Re are the sample mean; the standard deviation of the sample mean is shown for Nu measurements, and is smaller than the number of significant figures reported for Re measurements.
+	Resolutions marked by a $*$ show the initial, highest resolution utilized in the simulation.
+	The 2D mixedFT Ra = $4.83 \times 10^{10}$ simulation's resolution was changed to $1024\times2048$ about 500 freefall time units after transient.
+	The rotating mixedFT case's resolution was reduced to $256\times384^2$ about one hundred freefall time units after transient, and was further reduced to $128\times384^2$ about $3.3\times 10^3$ freefall times after transient.
+	``f-to-m'' simulations are mixedFT simulations which use an evolved fixedT simulation as initial conditions, and their cpu-hour cost does not include the cost of the fixedT transient.
 }
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{c c c c c c c c c}
+\begin{tabularx}{\textwidth}{c c c c c c c}
 \hline																	
-BCs	&	Ra	&	Pr	&	Ek	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
-%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
+BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
+\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
+\multicolumn{7}{c}{\vspace{0.1cm}2D Runs ($\Gamma = 2$, no-slip)} \\
 \hline
-fixedT	&	$1.00 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
-mixedFT	&	$2.61 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
-fixedT	&	$2.15 \times 10^8$	&	1	&	$\infty$	&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
-fixedT	&	$4.64 \times 10^8$	&	1	&	$\infty$	&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
-fixedT	&	$1.00 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
-fixedT	&	$2.15 \times 10^9$	&	1	&	$\infty$	&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
+fixedT	&	$1.00 \times 10^8$		&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
+mixedFT	&	$2.61 \times 10^9$		&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
+f-to-m	&	$2.61 \times 10^9$		&	512x1024	&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ \\
+fixedT	&	$2.15 \times 10^8$		&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
+fixedT	&	$4.64 \times 10^8$		&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
+fixedT	&	$1.00 \times 10^9$		&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
+mixedFT	&	$4.83 \times 10^{10}$	&	2048x4096*	&	---					&	---				&	48.3	&	--- \\
+f-to-m	&	$4.83 \times 10^{10}$	&	1024x2048	&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ \\
+fixedT	&	$2.15 \times 10^9$		&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
+fixedT	&	$4.64 \times 10^9$		&	1536x3072	&	---					&	---				&	76.3	&	--- \\
+fixedT	&	$1.00 \times 10^{10}$	&	2048x4096	&	---					&	---				&	95.1	&	--- \\
+f-to-m	&	$9.51 \times 10^{11}$	&	2048x4096	&	---					&	---				&	95.1	&	--- \\
 \hline																	
+\multicolumn{7}{c}{\vspace{0.1cm}3D Rotating Runs (Ek = $10^{-6}$, $\Gamma = 0.481$, stress-free)} \\
 \hline																	
-fixedT	&	$2.75 \times 10^9$		&	1	&	$10^{-6}$	&	128$^3$				&	?					&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$ \\
-mixedFT	&	$2.1 \times 10^{10}$	&	1	&	$10^{-6}$	&	nz$\times$384$^2$	&	?					&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$ \\
+fixedT	&	$2.75 \times 10^9$		&	128$^3$				&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$ \\
+mixedFT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$ \\
 \hline																	

### 2020-01-16 figures_and_data/rbc_dynamics_asymmetries.py

@@ -85,14 +85,14 @@ fk = '{:.4e}'.format(1.00e8)
 fig = plt.figure(figsize=(7.5, 2))
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [( (50 , 0),         900,    300),
-            ( (50 , 400),       900,    400),
-            ( (350, 800),       300,    150),
-            ( (650, 800),       300,    150)
+subplots = [( (0 , 0),          900,    300),
+            ( (0 , 400),        900,    400),
+            ( (0, 800),         425,    150),
+            ( (425, 800),       425,    150)
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 
-cax = plt.subplot(gs.new_subplotspec((100, 800), 125, 150))
+cax = plt.subplot(gs.new_subplotspec((950, 825), 50, 125))
 
 # Panel 1, PDF comparison
 plt.sca(axs[0])
@@ -148,8 +148,8 @@ zz_b, xx_b = np.meshgrid(z_big.flatten(), x_big.flatten())
 T_field.set_scales(big_scale, keep_data=True)
 c = ax.pcolormesh(xx_b, zz_b, T_field['g'], cmap='RdBu_r', rasterized=True, vmin=-dT/2, vmax=dT/2)
 
-top_plume_bounds = [(-0.75, -0.5, -0.5, -0.75, -0.75),  (0.5, 0.5, 0.4, 0.4, 0.5)]
-bot_plume_bounds = [(0.65, 0.9, 0.9, 0.65, 0.65), (-0.4, -0.4, -0.5, -0.5, -0.4)]
+top_plume_bounds = [(-0.75, -0.6, -0.6, -0.75, -0.75),  (0.5, 0.5, 0.4, 0.4, 0.5)]
+bot_plume_bounds = [(0.25, 0.4, 0.4, 0.25, 0.25), (-0.4, -0.4, -0.5, -0.5, -0.4)]
 for i in range(4):
     plt.plot(top_plume_bounds[0][i:i+2], top_plume_bounds[1][i:i+2], c='k')
     plt.plot(bot_plume_bounds[0][i:i+2], bot_plume_bounds[1][i:i+2], c='k')
@@ -183,11 +183,11 @@ for i in [2, 3]:
     axs[i].set_yticks(())
 
 #Colorbar
-bar = plt.colorbar(c, cax=cax, orientation='horizontal')
[…]

### 2020-01-16 figures_and_data/rbc_scalar_comparisons.py

@@ -57,13 +57,17 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
 base_dir = './data/rbc/'
 mixed_dirs = glob.glob("{:s}mixedFT_2d/ra*/".format(base_dir))
 fixed_dirs = glob.glob("{:s}fixedT_2d/ra*/".format(base_dir))
+restarted_dirs = glob.glob("{:s}restarted_mixed_T2m/ra*/".format(base_dir))
 numbered_dirs  = [(f, float(f.split("{:s}mixedFT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 numbered_dirs  = [(f, float(f.split("{:s}fixedT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+numbered_dirs  = [(f, float(f.split("{:s}restarted_mixed_T2m/ra".format(base_dir))[-1].split("/")[0])) for f in restarted_dirs]
+restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_data(mixed_ras, mixed_dirs)
 fixed_data = read_data(fixed_ras, fixed_dirs)
+restarted_data = read_data(restarted_ras, restarted_dirs)
 
 # Get rolling averages of all data; Output is every 0.1 time units
 avg_window = 50 #time units
@@ -93,11 +97,13 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-plt.axhline(np.mean(mixed_trace['ra_flux'])/2.61e9, color='olivedrab', lw=1)
-plt.axhline(np.mean(fixed_trace['ra_temp'])/2.61e9, color='darkorange', lw=1, ls='-.')
-plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.61e9, color='olivedrab', lw=2, ls='-.')
[…]

### 2020-01-16 figures_and_data/rotating_panels.py

@@ -1,0 +1,285 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'Ro']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(r, int(r.split('run')[-1].split('_')[0])) for r in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
[…]

### 2020-01-18 tex/mixedft_evolution_ms.tex
rough draft of paper complete

@@
-\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
+\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography, superscriptaddress]{revtex4-1}
 \usepackage{tabularx}
@@
 
-\title{Mixed thermal boundary conditions impose an unnecessary thermal rundown on convection simulations}
+\title{Thermal relaxation is important in convective simulations: \\
+on the time evolution of flows and how to avoid unnecessary thermal rundown}
 
@@
 Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
-Numerical simulations are the basis for most modern studies into the nature of astrophysical convection.
-Some modern studies examine convection in the highly simplified Boussinesq approximation \cite{spiegel&veronis1960}.
-Others study more complex ``dynamo simulations'', incorporating complicating effects such as magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
-Regardless of the degree of apparent realism included in these models, convective processes in these numerical simulations are fundamentally driven by some combination of imposed boundary conditions and internal heating profiles which in turn determine key properties of the evolved dynamics \cite{goluskin2015}.
-In astrophysical studies, a common choice of thermal boundary conditions \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
-In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection under the Boussinesq approximation.
-In this model, the only thermodynamic quantity of interest is the temperature, and we will hereafter refer to this choice of boundary conditions (fixed flux at the bottom, fixed temperature at the top) as ``mixedFT'' boundaries.
+The nature of astrophysical convection is primarily studied through the use of numerical simulations which range from studies of the highly simplified Boussinesq approximation \cite{spiegel&veronis1960} to more complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
+Regardless of the degree of apparent realism of the employed simulations, numerical convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
+A common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
+In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
+In this model, temperature is the only thermodynamic quantity and we use the term ``mixedFT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.
 
-Despite mixedFT boundary conditions being a common choice of numericists, we are unaware of any work which compares the dynamics produced by mixed thermal boundaries to the most traditional choice of boundary conditions in the \RB literature: fixed temperature at the top and bottom (hereafter ``fixedT'' boundaries).
-Due to the fact that mixedFT boundaries fix the flux through the convective system, this set of boundaries is expected to behave in a fundamentally similar way to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
-While there is some work \cite{johnston&doering2009} comparing fixedF and fixedT boundaries, past work primarily focused on the scaling of heat transport laws (quantified by a Nusselt number, Nu) as the convective driving is increased (quantified by the Rayleigh number, Ra) [more refs].
-The equivalence of fixedF and fixedT scaling laws suggests that mixedFT scaling should also be identical.
+Despite mixedFT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing mixedFT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``fixedT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our fixedT and mixedFT are repsectively called RB1 and RB3.}).
+It is generally assumed that mixedFT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
+FixedF and fixedT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that mixedFT should fall on the same scaling laws.
 However, the choice of mixedFT boundaries introduces complexities into the convective system which neither fixedF or fixedT boundaries are exposed to.
@@
 In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
+We also compare the flows in evolved, thermally relaxed mixedFT simulations to the flows in evolved fixedT simulations.
 We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
-We also find that this rapid thermal evolution can be bypassed by combining the results of fixedT and mixedFT simulations.
-We furthermore find that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not seem to appreciably change the mean convective state when compared to fixedT boundaries, even when the Rayleigh number is large.
+However, this long thermal evolution can be bypassed by using the results of fixedT simulations as initial conditions for mixedFT simulations.
+If a mixedFT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
+Our results also suggest that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to fixedT siulations.
 We present these findings as follows.
-In section \ref{sec:simulations}, we describe our experimental setup and numerical methods.
-In section \ref{sec:results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
-In section \ref{sec:rotating_results}, we briefly show that these findings carry over to a more complex system: rotating \RB convection.
-Finally, in section \ref{sec:discussion}, we briefly describe the implications of this work for the field of astrophysical convection.
+In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
+In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
+In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
+Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.
 
@@
 We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
-In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so we include it here for generality.
+In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
 The equations of motion are
@@
 \begin{equation}
-(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
-(\text{fixedT}): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
+(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
+(\text{fixedT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
 \end{equation}
@@
 \end{equation}
-The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset, as has been done by previous authors \cite{stellmach&all2014}.
+The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}.
 These rotating simulations employ stress-free, impenetrable boundaries,
@@
 We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
-Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
-The code used to run simulations and the code and data used to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
+Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D rotating simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
+The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT simulation (green) and a fixedT (orange) simulation.
-	(top left panel) The Rayleigh number, normalized by the input Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$ value of the mixedFT simulation.
-	(middle and bottom left panels) The Nusselt number and Peclet number evolution of the simulations is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation.
-	(right two panels) Parameter space plots of Nusselt (upper) and Peclet (lower) vs. Ra$_{\Delta T}$.
-	The green traces show the time evolution of the mixedFT case, while the orange circles and black crosses show comparison fixedT simulations.
+	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT (orange) and a fixedT (purple) simulation.
+	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the fixedT simulation.
+	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation (reported in appendix \ref{app:table}).
+	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
+	The Nu vs Ra plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
+	The Re vs Ra plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
+	The time evolution of the mixedFT case is shown as an orange trace with the arrows showing the sense of time.
+	Purple circles show our measured values of Nu in fixedT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
 	The orange star in each plot corresponds to the fixedT case whose time evolution is shown on the left.
+	Black crosses show comparison fixedT simulations as reported by ref.~\ref{zhu&all2018}.
 \label{fig:rbc_scalar_comparisons} }
@@
 In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a mixedFT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
-This simulation had a coefficient resolution of (nz, nx) = (1024, 2048) and was evolved forward in time for ten days on 512 cpus.
-The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$, with a coefficient resolution of (nz, nx) = (512, 1024) which was time evolved for one thousand freefall time units after the initial convective transient (which took roughly one day on 256 cpus).
-The mixedFT case is displayed in green, and the fixedT case is displayed in orange; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
+The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$.
+The mixedFT case is displayed in orange, and the fixedT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
 In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
@@
 
-In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot Nu and Pe vs Ra$_{\Delta T}$.
-The green line shown in each panel is the path through parameter space that the mixed-FT simulation traces out over its time evolution.
-In the upper right (Nu vs Ra) plot, we have divided all Nu values by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by \cite{johnston&doering2009}.
-In the lower right (Re vs Ra) plot, we have divided out a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
-The orange circles show the mean values of Nu and Pe from select fixedT simulations through this parameter space, the details of which are presented in appendix \ref{app:table}; in all cases, we plot the sample mean, and the standard deviation of the sample mean is smaller than the plotted points.
-The orange star is the simulation whose time evolution is shown on the left.
-The black crosses are the reported values of Nu from the supplemental materials of \cite{zhu&all2018}, presented for comparison.
-Remarkably, the mixedFT case seems to reliably perform a sweep through this parameter space.
-However, despite seemingly tracing out the ``proper'' values of Nu(t) vs.
-Ra$_{\Delta T}$(t), we find that the mixedFT simulation achieves a larger value of the Peclet number than the comparison fixedT simulations until it converges to its final state.
-These traces through parameter space help to demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.
+In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot compensated scaling plots of Nu and Pe vs Ra$_{\Delta T}$.
+Over the course of its thermal relaxation, the mixedFT case performs a sweep through Ra$_{\Delta T}$ parameter space.
+During this parameter space sweep, the mixedFT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by fixedT simulations and which has been reported by previous authors.
+However, we find that the value of Pe measured in the mixedFT simulation through its relaxation  is larger than the value of the Peclet number in comparison fixedT simulations until it converges to its final state.
+These traces through parameter space demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.
+During the rundown, the dynamics in mixedFT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
+Both of these effects make interpretation of their results difficult until the final, equilibrated state.
 
@@
 	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
+	The time at which we switch from fixedT to mixedFT boundaries is noted by the vertical black line.
 	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
-	The mean value of the simulation's temperature gradient (middle panel) and temperature (bottom panel) are displayed, showing the change in the enforced boundary condition.
-	In the middle panel, during the fixedT portion of the simulation, we plot $\angles{Nu}\partial_z T$, while in the bottom panel, during the mixedFT portion, we plot $T / \angles{Nu}$ due to the change in temperature nondimensionalization for the different boundary conditions.
+	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
+	In the fixedT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
+	In the mixedFT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
 	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
-	In each plot, we show the PDF of the dynamics at the end of the mixedFT simulation that experienced a long rundown (green lines in Fig.~\ref{fig:rbc_scalar_comparisons}), as well as dynamics from the grey shaded region displayed in the left three panels here.
+	In each plot, we compare the PDF of the mixedFT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (fixedT-to-mixedFT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
 \label{fig:rbc_restart_description} }
@@
 
-The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
-It seems plausible that one should be able to take advantage of the fast evolution on display in fixedT simulations to achieve rapidly equilibrated mixedFT simulations.
-The rundown in mixedFT simulations is very costly: not only do the turbulent dynamics at the large initial Rayleigh number need to be resolved (requiring more spectral modes to run the simulation), but thousands of freefall times must pass before convergence.
-For a sense of scale, the first thousand freefall time units of the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons} took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours.
-For comparison, the same time evolution (essentially the whole simulation) for fixedT boundary conditions took  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours.
-After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
-This means that at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is more than an order of magnitude larger than a fixedT simulation.
+The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} between the mixedFT and fixedT simulations suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
+It should therefore be possible to take advantage of the fast evolution of fixedT simulations to achieve rapidly equilibrated mixedFT simulations, which would save a great deal of computing time in solving mixedFT simulations.
+The rundown in mixedFT simulations is very costly for two reasons: the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state and thousands of freefall times must pass during relaxation.
+For example, for the cases displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, the first thousand freefall time units took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours for the mixedFT simulation, but only  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours for the fixedT simulation.
+After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary relaxed state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
+Even at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is therefore more than an order of magnitude larger than a fixedT simulation.
 
 We now describe a procedure which takes advantage of the fast evolution of fixedT simulations to achieve equilibrated mixedFT simulations.
-In essence, the full evolved flow fields in the fixedT simulation are properly re-nondimensionalized and fed into a mixedFT simulation as initial conditions.
-More precisely, the procedure for achieving converged mixedFT dynamics using fixedT simulations takes place over these steps:
+In short, the full evolved flow fields in the fixedT simulation are properly re-nondimensionalized and used as initial conditions for a mixedFT simulation.
+To achieve this, we perform these steps:
 \begin{enumerate}
-\item Run a fixedT simulation from convective transient to its statistically stationary state. 
+\item Run a fixedT simulation to its statistically stationary state ($\sim100+$ time units). 
 Measure $\angles{\text{Nu}}$ in that state.
-\item Re-nondimensionalize from $\Delta = \Delta T$ to $\Delta = L_z \partial_z T$ in the definition of the Rayleigh number.
-This means changing from an input of Ra$_{\Delta T}$ to Ra$_{\partial_z T}$ as in Eqn.~\ref{eqn:ra_relation}.
+\item Re-nondimensionalize from $\Delta = \Delta T \rightarrow \partial_z T$, and from Ra$_{\Delta T}\rightarrow$Ra$_{\partial_z T}$, as in Eqn.~\ref{eqn:ra_relation}.
 In our freefall nondimensionalization, this means setting the velocities in the mixedFT simulation to $\bm{u}_{\text{mixedFT}} = \bm{u}_{\text{fixedT}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{mixedFT}} = T_{\text{fixedT}} / \angles{\text{Nu}}$.
@@
 \end{enumerate}
-
 In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show time traces of a simulation in which we employ this procedure.
@@
 Roughly one hundred freefall times after the convective transient, we restart this simulation using mixedFT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
-We note that this is the same Ra$_{\partial_z T}$ as the mixedFT case presented in the green lines in Fig.~\ref{fig:rbc_scalar_comparisons}.
-In the upper left panel, rolling averages over 25 freefall times of Ra$_{\Delta T} / 10^8$ and Ra$_{\partial_z T} / (2.61 \times 10^9)$ are shown in the through the full simulation.
-The time at which we switch from fixedT to mixedFT boundaries is noted by the vertical black line.
-In the middle and bottom panels, we show the time evolution of the instantaneous temperature derivative and temperature value at the bottom plate.
-In the fixedT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
-In the mixedFT final state, the temperature derivative is held constant at a value of 1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
-Unlike in the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the mixedFT state, as the thermal profile was rapidly relaxed by the early fixedT portion of the run.
+We note that this is the same Ra$_{\partial_z T}$ as the mixedFT case presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
+In the left panels, we show the temporal behavior of the Rayleigh numbers (top panel), and the flux (middle panel) and temperature (bottom panel) at the bottom boundary of the simulation.
+The change from fixedT to mixedFT boundaries is shown as a vertical line.
+Unlike in the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the mixedFT state, due to the rapid relaxation achieved during the fixedT portion of the simulation.
 
-While these time traces show that this procedure bypasses the long thermal rundown on display in Fig.~\ref{fig:rbc_scalar_comparisons}, this does not prove that the dynamics in the final state are equivalent.
+While these time traces show that this procedure bypasses the long thermal rundown on display in Fig.~\ref{fig:rbc_scalar_comparisons}, this does not prove that the dynamics in the final state faithfully reproduce those achieved by a thermal rundown.
 We now compare probability distribution functions (PDFs) of various quantities in our restarted mixedFT simulation to the mixedFT simulation that stepped through a long rundown.
@@
 \begin{enumerate}
-\item Changes to the experimental energy reservoir, and
+\item Changes to the simulation energy reservoir, and
 \item Restratification of the experiment.
 \end{enumerate}
-The rapid evolution of fixedT runs, whose experimental energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in \RB convection.
-The long rundown of mixedFT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir, and the mean temperature of the simulation, drifting over time.
+The rapid evolution of fixedT runs, whose energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in RBC. 
+The long rundown of mixedFT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
 Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for mixedFT boundaries, and our procedure uses fixedT dynamics to choose a more ideal set of initial conditions.
@@
 Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixedFT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
-[NOTE: in the version of the paper we will later submit, we will hopefully study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
-For now, we'll carry on with the same values as in the previous section.]
+[NOTE: in the version of the paper that will be submitted, we will study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
+These simulations are almost done running on Pleiades, so for now we'll carry on with the same values as in the previous section.]
 
@@
 In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
-Surprisingly, despite symmetrical boundary conditions in fixedT simulations and asymmetrical boundary conditions in mixedFT cases, we find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
+Surprisingly, despite symmetrical boundary conditions in fixedT simulations and asymmetrical boundary conditions in mixedFT cases, we on average find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
 In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
@@
 
-In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases.
-The fluxes show very good agreement just like the temperature profile.
+In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases, which also show good agreement between mixedFT and fixedT.
 Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
 Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boundary layers.
+[NOTE: I need to figure out how to quantify the flux agreement better. Ideas?]
 
@@
 \caption{ 
-	(left panel) PDFs of temperature measurements of a mixedFT (green) and fixedT (orange) case are displayed.
-	The right tail of the distribution (near the cold fixedflux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	(left panel) PDFs of temperature measurements of a mixedFT (orange) and fixedT (purple) case are displayed.
+	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
 	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
@@
 These PDFs agree remarkably well for cold temperatures (near the shared fixedT boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
-We find that the mixedFT pdf has a much longer tail and is capable of achieving much hotter instantaneous temperature values than a fixedT simulation.
+Interestingly, there are no temperature fluctuations which exceed the specified boundary values in the convective domain for fixedT simulations.
+However, the mixedFT PDF has a much longer tail and achieves regions which are 50\% hotter than the average bottom boundary value.
 In order to understand how this is possible, we examine a snapshot of the full temperature field.
-In the middle panel, we plot the temperature anomaly -- the temperature field with the mean vertical profile subtracted from it.
+In the middle panel, we plot the temperature anomaly, or the temperature field with the mean vertical profile subtracted from it.
 We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
@@
 
-In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.
-Ra(t) for our mixedFT case (thick green line) and the evolved value of Nu in the fixedT case (orange star).
-We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of \cite{cheng&all2015}.
+In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.~Ra(t) for our mixedFT case (thick orange line with teal interior) and the evolved value of Nu in the fixedT case (teal star with purple outline).
+We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
+The overplotted line is the best-fit line for values of Ra $\geq 10^{10}$ from ref.~\cite{cheng&all2015}.
 We note that these comparison values are in cylindrical domains with Pr=7, whereas we are in Cartesian geometry with Pr=1, so some differences are expected.
-As has been seen previously, the evolution of Nu vs Ra in the rotationally constrained regime is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
+As has been seen previously, the evolution of Nu vs.~Ra in the rotationally constrained regime is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
+The evolution of Nu(t) vs.~Ra(t) in the mixedFT simulation seems to trace out the fixedT trend well, once again [NOTE: crap, I probably need some more fixedT comparisons.
+Bummer.
+They're fairly cheap, I'll sub them.].
 
@@
 The scaling of Nu vs Ra in the rotationally constrained regime is much less well understood than it is in classical RBC [cite, cite].
-A single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}.
-In the nonrotating case, Nu(t) vs.~Ra(t) produced the expected result (Fig.~\ref{fig:rbc_scalar_comparison}), so this approach may be one way to cleverly fill in this parameter space.
+A single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}, so this approach may be one way to cleverly fill in this parameter space.
 However, it is probable that the best course of action is simply to run a large suite of fixedT simulations that cover the same track for two reasons:
@@
 \item The long thermal rundown has some short-lived memory of the higher-Ra$_{\Delta T}$ state that it was recently in.
-This is seen both in the post-transient bump of Pe in Fig.~\ref{fig:rotating_panels}, and also was found from a practical computing standpoint.
+This is seen both in the post-transient bump of Pe in the bottom left panel of Fig.~\ref{fig:rotating_panels}, and also was found from a practical computing standpoint.
 In order to reduce the computational cost of this mixedFT simulation, we reduced the vertical resolution from $512\times384^2$ to $256\times384^2$ (after about 100 freefall times) and then later to $128\times384^2$ (after about $3.3 \times 10^3$ freefall times).
@@
 For comparison, the fixedT simulation ran for $5 \times 10^3$ freefall units at $128^3$, took 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
-In other words, the computational cost of the mixedFT simulation was \emph{two orders of magnitude} larger than its comparison fixedT case; even though it sampled many different values of Ra$_{\Delta T}$ momentarily, its cost makes this hardly worth it.
+In other words, the computational cost of the mixedFT simulation was \emph{two orders of magnitude} larger than its comparison fixedT case.
 \end{enumerate}
@@
 
-\section{Discussion \& Conclusions}
+\section{Conclusions \& Discussion}
 \label{sec:discussion}
-In summary, we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``mixedFT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``fixedT'' boundaries, where temperature is fixed at the top and bottom.
-We find that mixedFT experiments experience a long thermal relaxation which is not experienced by fixedT simulations.
+In summary, we find that mixedFT experiments experience a long thermal relaxation which is not experienced by fixedT simulations.
+Here we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``mixedFT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``fixedT'' boundaries, where temperature is fixed at the top and bottom.
 Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
 \begin{enumerate}
-\item Thermal relaxation has two components: (a) changes in the energy reservoir and (b) changes in the experimental stratification.
-We find that the long relaxation of mixedFT simulations is due to changes in the experimental energy reservoir; this reservoir is roughly constant in fixedT simulations.
+\item Thermal relaxation in RBC has two components: (a) changes in the energy reservoir and (b) changes in the stratification.
+We find that the long relaxation of mixedFT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in fixedT simulations due to the lack of evolution of the average domain temperature.
 On the other hand, RBC seems to restratify itself nearly instantaneously, as suggested by the rapid equilibration of our fixedT simulations.
@@
 We find that the heat transport (the Nusselt number) follows classical scaling laws through this parameter space sweep, but does so in the presence of increased turbulent velocities (quantified by the Reynolds number).
-\item Despite minor asymmetries in the instantaneously measured flows, the mean state of a mixedFT simulation appears equally symmetrical to fixedT simulations.
-\item The great computational expense of achieving thermal relaxation in a mixedFT simulation can be avoided by using the evolved state of a fixedT simulation as a ``better'' set of initial conditions for a mixedFT simulation.
-In other words, the proper choice of initial conditions can ensure that the evolved experimental energy reservoir is close to the initial state.
+\item Despite minor asymmetries in the instantaneously measured flows of mixedFT simulations, we find no difference between the mean state of these simulations and the more classic fixedT simulations.
+\item Great computational expense achieving thermal relaxation in a mixedFT simulation can be avoided by using the evolved state of a fixedT simulation as a ``better'' set of initial conditions for a mixedFT simulation.
+In other words, the proper choice of initial conditions can ensure that the initial and evolved energy reservoirs are not vastly different.
 \item If dynamical measurements are taken during the thermal relaxation of a mixedFT simulation, they may be misleading.
@@
 \end{enumerate}
+
+[NOTE: This is basically wild speculation and flailing. I need to get refs in here, maybe rearrange, maybe take stuff out. Open to suggestions. I find discussion sections difficult.]
 
@@
 The use of mixedFT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
-However, for stages in the lifetimes of stellar or planetary atmospheres or interiors that survive for much longer than their respective Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the fixedT or evolved mixedFT cases here.
+However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the fixedT or evolved mixedFT cases here.
 
-One question which our study of RBC is not able to study is: how long does it take for a given convective system to restratify?
-Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
-It is, however, probable that clever techniques could be used to rapidly restratify atmospheres \cite{anders&all2018}, and this should be examined in more detail for a given thermal stratification.
+One question which our study of RBC is not able to study is: how long does it take for a complex convective system to restratify?
+Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains [cite, cite] should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
+It is, however, probable that clever techniques could be used to rapidly restratify atmospheres \cite{anders&all2018}, and these techniques should be studied separately from cases where the thermal reservoir and stratification evolve simultaneously.
 
-RBC is fundamentally symmetrical, but many processes in astrophysics occuring in density-stratified domains in which the symmetries of the problem are fundamentally broken.
+RBC is fundamentally symmetrical, but many natural convective processes occur in density-stratified domains in which the symmetries of the problem are fundamentally broken.
 In the present study, we observed that flux boundaries achieve more extreme values than temperature boundaries.
-In studies of overshooting or penetrating convection, these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
+In studies of overshooting or penetrative convection [cite, cite], these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
 Some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.
+This should be investigated in more detail.
 
-Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains.
+Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains [cite, cite].
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
-We found here in our mixedFT rotating simulation that the early unrelaxed state generated a mean flow that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+We found here in our mixedFT rotating simulation that the early unrelaxed state generated a mean flow (large scale vortex, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
 If we had terminated our mixedFT rotating simulation too early, we would not have seen this feature evolve as the simulation relaxed and progressed into a more rotationally constrained, lower Rossby number state.
@@
 It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
-Some authors [cite, cite] employ fixed-flux boundary conditions at \emph{both} boundaries in these simulations, and our results here suggest that such a choice is wise in these simulations.
+Some authors [cite, cite] employ fixed-flux boundary conditions at \emph{both} boundaries in these simulations, and our results here suggest that such a choice may be ideal.
 
@@
 \hline																	
-BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Re \\
+BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Pe \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\

### 2020-01-18 figures_and_data/rbc_1D_profiles.py

@@ -19,8 +19,8 @@ import pandas as pd
 import dedalus.public as de
 
 
-mColor = 'olivedrab'
-fColor = 'darkorange'
+mColor = 'darkorange'
+fColor = 'indigo'
 
 
 def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):

### 2020-01-18 figures_and_data/rbc_dynamics_asymmetries.py

@@ -17,6 +17,8 @@ import h5py
 import pandas as pd
 import dedalus.public as de
 
+mColor = 'darkorange'
+fColor = 'indigo'
 
 def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
     full_data = OrderedDict()
@@ -92,7 +94,7 @@ subplots = [( (0 , 0),          900,    300),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 
-cax = plt.subplot(gs.new_subplotspec((950, 825), 50, 125))
+cax = plt.subplot(gs.new_subplotspec((950, 825), 50, 100))
 
 # Panel 1, PDF comparison
 plt.sca(axs[0])
@@ -102,15 +104,15 @@ fx, fp, fdx = [fixed_data[fk]['T'][k] for k in ['xs', 'pdf', 'dx']]
 
 delta_T_mixed = mixed_scalars[mk]['delta_T']
 dT = np.mean(delta_T_mixed[-5000:])
-plt.plot(mx/dT, mp*dT, label='mixed-FT', c='olivedrab')
-plt.plot(fx, fp, label='fixed-T', c='darkorange')
+plt.plot(mx/dT, mp*dT, label='mixedFT', c=mColor)
+plt.plot(fx, fp, label='fixedT', c=fColor)
 plt.yscale('log')
-ax.set_ylabel(r'$P(T/\Delta T)$')
-ax.set_xlabel(r'$T/\Delta T$')
+ax.set_ylabel(r'$P(T/\Delta T)$', labelpad=-1)
+ax.set_xlabel(r'$T/\Delta T$', labelpad=-1)
 ax.legend(loc='upper right', frameon=False, fontsize=7, markerfirst=False, borderpad=0.1)
 
-ax.fill_between(mx/dT, 1e-16, mp*dT, color='olivedrab', alpha=0.5)
-ax.fill_between(fx, 1e-16, fp, color='darkorange', alpha=0.5)
+ax.fill_between(mx/dT, 1e-16, mp*dT, color=mColor, alpha=0.5)
+ax.fill_between(fx, 1e-16, fp, color=fColor, alpha=0.5)
 
 minv = np.min((np.min(mp[mp > 0]*dT), np.min(fp[fp > 0])))
[…]

### 2020-01-18 figures_and_data/rbc_restart_description.py

@@ -142,10 +142,10 @@ for i in [0, 1, 2]:
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-plt.plot(rolledr['sim_time'], rolledr['ra_flux']/2.61e9, color='black', lw=1, label=r'Ra$_{\partial_z T}$')
-plt.plot(rolledr['sim_time'], rolledr['ra_temp']/1.00e8, color='black', lw=1, label=r'Ra$_{\Delta T}$', ls='--')
+plt.plot(rolledr['sim_time'], rolledr['ra_flux']/2.61e9, color='black', lw=1, ls='-.', label=r'Ra$_{\partial_z T}/26.1$')#\langle\mathrm{Nu}\rangle$')
+plt.plot(rolledr['sim_time'], rolledr['ra_temp']/1.00e8, color='black', lw=1, label=r'Ra$_{\Delta T}$')
 ax.legend(loc='lower right', frameon=False, borderpad=0, fontsize=7)
-ax.set_ylabel(r'Ra/Ra$_{\mathrm{in}}$')
+ax.set_ylabel(r'Ra/$10^8$')
 plt.ylim(0.925, 1.075)
 ax.set_yticks((0.95, 1, 1.05))
 plt.yscale('log')
@@ -160,7 +160,7 @@ Nu_final_temp = np.mean(fixed_trace['Nu'][-5000:])
 plt.plot(rolledr['sim_time'], rolledr['left_flux']*np.sqrt(2.61e9), color='black', lw=1)
 print(rolledr['left_flux'])
 #plt.axhline(1, c='black', lw=1)
-ax.set_ylabel(r'left $|\partial_z T|$')
+ax.set_ylabel(r'left $\frac{\mathrm{Pe}_{\mathrm{ff}}^{-1}|\partial_z T|}{\mathrm{Flux}}$')
 ax.set_ylim(0.925, 1.075)
 ax.set_yticks((0.95, 1, 1.05))
 
@@ -171,7 +171,7 @@ ax = axs[2]
 
 plt.plot(rolledr['sim_time'], rolledr['left_T'], color='black', lw=1)
 #plt.axhline(1, c='black', lw=1)
-ax.set_ylabel(r'left $T$')
+ax.set_ylabel(r'left $T/\Delta T$')
 #plt.yscale('log')
 ax.set_xlabel(r'$t$')
 ax.set_ylim(0.925, 1.075)
@@ -187,8 +187,8 @@ for i, field in enumerate(keys):
 
[…]

### 2020-01-18 figures_and_data/rbc_scalar_comparisons.py

@@ -16,6 +16,9 @@ import h5py
 
 import pandas as pd
 
+mColor = 'darkorange'#olivedrab'
+fColor = 'indigo'
+
 def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
     """
     Reads scalar data in from a folder containing a series of subfolders of different Ra values.
@@ -97,11 +100,11 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-ax.plot([1, 1], [1,1], color='olivedrab', lw=2, label='mixedFT')
-plt.axhline(np.mean(mixed_trace['ra_flux'])/1e8, color='olivedrab', lw=1)
-plt.axhline(np.mean(fixed_trace['ra_temp'])/1e8, color='darkorange', lw=1, ls='-.')
-ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/1e8, color='olivedrab', lw=2, ls='-.', label='')
-ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/1e8, color='darkorange', lw=2, label='fixedT')
+ax.plot([1, 1], [1,1], color=mColor, lw=2, label='mixedFT')
+plt.axhline(np.mean(mixed_trace['ra_flux'])/1e8, color=mColor, lw=1, ls='-.')
+plt.axhline(np.mean(fixed_trace['ra_temp'])/1e8, color=fColor, lw=1)
+ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/1e8, color=mColor, lw=2, label='')
+ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/1e8, color=fColor, lw=1, ls='-.', label='fixedT')
 ax.legend(loc='center', frameon=True, fontsize=7)
 ax.set_ylabel(r'Ra/$10^8$')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
@@ -117,8 +120,8 @@ plt.yscale('log')
[…]

### 2020-01-18 figures_and_data/rotating_panels.py

@@ -16,6 +16,10 @@ import h5py
 
 import pandas as pd
 
+
+mColor = 'darkorange'#olivedrab'
+fColor = 'indigo'
+
 def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'Ro']):
     """
     Reads scalar data in from a folder containing a series of subfolders of different Ra values.
@@ -91,13 +95,14 @@ gs = gridspec.GridSpec(1000, 1000)
 subplots = [( (50 , 0  ),       300,    430),
             ( (350, 0  ),       300,    430),
             ( (650, 0  ),       300,    430),
-            ( (50 , 530),       400,    540),
+            ( (100 , 530),      350,    540),
             ( (600, 450),       350,    180),
             ( (600, 630),       350,    180),
             ( (600, 810),       350,    180),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec((950, 580), 50, 280))
+caxEk = plt.subplot(gs.new_subplotspec((70, 560), 30, 510))
 
 
 #Show times of dynamics panels
@@ -111,11 +116,11 @@ for i in range(3):
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-ax.plot([1, 1], [1,1], color='olivedrab', lw=2, label='mixedFT')
-plt.axhline(np.mean(mixed_trace['ra_flux'])/2.75e9, color='olivedrab', lw=1)
-plt.axhline(np.mean(fixed_trace['ra_temp'])/2.75e9, color='darkorange', lw=1, ls='-.')
-ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.75e9, color='olivedrab', lw=2, ls='-.', label='')
-ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.75e9, color='darkorange', lw=2, label='fixedT')
[…]

### 2020-02-06 tex/mixedft_evolution_ms.tex
changes 'mixedFT->FT' and 'fixedT->TT' in manuscript; also adds information to simulation table.

@@
 In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
-In this model, temperature is the only thermodynamic quantity and we use the term ``mixedFT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.
+In this model, temperature is the only thermodynamic quantity and we use the term ``FT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.
 
-Despite mixedFT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing mixedFT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``fixedT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our fixedT and mixedFT are repsectively called RB1 and RB3.}).
-It is generally assumed that mixedFT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
-FixedF and fixedT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that mixedFT should fall on the same scaling laws.
-However, the choice of mixedFT boundaries introduces complexities into the convective system which neither fixedF or fixedT boundaries are exposed to.
-First, the evolved mean temperature of a simulation with mixedFT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
-Second, mixedFT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.
+Despite FT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing FT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``TT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT and FT are repsectively called RB1 and RB3.}).
+It is generally assumed that FT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
+FixedF and TT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
+However, the choice of FT boundaries introduces complexities into the convective system which neither fixedF or TT boundaries are exposed to.
+First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
+Second, FT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.
 
-In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
-We also compare the flows in evolved, thermally relaxed mixedFT simulations to the flows in evolved fixedT simulations.
-We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
-However, this long thermal evolution can be bypassed by using the results of fixedT simulations as initial conditions for mixedFT simulations.
-If a mixedFT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
-Our results also suggest that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to fixedT siulations.
+In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed.
+We also compare the flows in evolved, thermally relaxed FT simulations to the flows in evolved TT simulations.
+We find that the thermal evolution and relaxation of FT systems is very long compared to TT systems, where it is nearly instantaneous.
+However, this long thermal evolution can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
+If a FT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
+Our results also suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to TT siulations.
 We present these findings as follows.
 In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
-In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
+In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
 In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
@@
 \end{equation}
-We study both mixedFT and fixedT thermal boundary conditions,
+We study both FT and TT thermal boundary conditions,
 \begin{equation}
-(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
-(\text{fixedT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
+(\text{FT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
+(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
 \end{equation}
-In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
-In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
+In the case of FT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
+In the case of TT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
 
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
-In the evolved, statistically stationary state, when fixedT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)\Peff}$, and when mixedFT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
+In the evolved, statistically stationary state, when TT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)\Peff}$, and when FT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
 This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT (orange) and a fixedT (purple) simulation.
-	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the fixedT simulation.
-	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation (reported in appendix \ref{app:table}).
+	(left three panels) Time traces of rolling averages over 50 freefall times of a FT (orange) and a TT (purple) simulation.
+	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the TT simulation.
+	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
 	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
@@
 	The Re vs Ra plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
-	The time evolution of the mixedFT case is shown as an orange trace with the arrows showing the sense of time.
-	Purple circles show our measured values of Nu in fixedT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
-	The orange star in each plot corresponds to the fixedT case whose time evolution is shown on the left.
-	Black crosses show comparison fixedT simulations as reported by ref.~\ref{zhu&all2018}.
+	The time evolution of the FT case is shown as an orange trace with the arrows showing the sense of time.
+	Purple circles show our measured values of Nu in TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
+	The orange star in each plot corresponds to the TT case whose time evolution is shown on the left.
+	Black crosses show comparison TT simulations as reported by ref.~\ref{zhu&all2018}.
 \label{fig:rbc_scalar_comparisons} }
@@
 
-In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a mixedFT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
-The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$.
-The mixedFT case is displayed in orange, and the fixedT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
+In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a FT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
+The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a TT case with Ra$_{\Delta T} = 10^8$.
+The FT case is displayed in orange, and the TT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
 In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
-The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the mixedFT simulation, and this final value corresponds to the input value of the equivalent fixedT case.
-On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reaches its final value, which corresponds to the input value for the mixedFT simulation.
-This discrepancy in evolution timescales, where fixedT simulations evolve quickly and mixedFT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
+The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the FT simulation, and this final value corresponds to the input value of the equivalent TT case.
+On the other hand, the value of Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
+This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
 All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.
@@
 In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot compensated scaling plots of Nu and Pe vs Ra$_{\Delta T}$.
-Over the course of its thermal relaxation, the mixedFT case performs a sweep through Ra$_{\Delta T}$ parameter space.
-During this parameter space sweep, the mixedFT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by fixedT simulations and which has been reported by previous authors.
-However, we find that the value of Pe measured in the mixedFT simulation through its relaxation  is larger than the value of the Peclet number in comparison fixedT simulations until it converges to its final state.
-These traces through parameter space demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.
-During the rundown, the dynamics in mixedFT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
+Over the course of its thermal relaxation, the FT case performs a sweep through Ra$_{\Delta T}$ parameter space.
+During this parameter space sweep, the FT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by TT simulations and which has been reported by previous authors.
+However, we find that the value of Pe measured in the FT simulation through its relaxation  is larger than the value of the Peclet number in comparison TT simulations until it converges to its final state.
+These traces through parameter space demonstrate the importance of waiting until a FT simulation has reached its equilibrated state.
+During the rundown, the dynamics in FT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
 Both of these effects make interpretation of their results difficult until the final, equilibrated state.
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
-	The time at which we switch from fixedT to mixedFT boundaries is noted by the vertical black line.
+	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with TT boundary conditions and then is switched to FT boundary conditions.
+	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
 	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
 	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
-	In the fixedT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
-	In the mixedFT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
+	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
+	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
 	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
-	In each plot, we compare the PDF of the mixedFT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (fixedT-to-mixedFT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
+	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (TT-to-FT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
 \label{fig:rbc_restart_description} }
@@
 
-The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} between the mixedFT and fixedT simulations suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
-It should therefore be possible to take advantage of the fast evolution of fixedT simulations to achieve rapidly equilibrated mixedFT simulations, which would save a great deal of computing time in solving mixedFT simulations.
-The rundown in mixedFT simulations is very costly for two reasons: the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state and thousands of freefall times must pass during relaxation.
-For example, for the cases displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, the first thousand freefall time units took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours for the mixedFT simulation, but only  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours for the fixedT simulation.
-After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary relaxed state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
-Even at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is therefore more than an order of magnitude larger than a fixedT simulation.
+The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} between the FT and TT simulations suggests that, in a volume-averaged sense, there is a comparable TT experiment for each FT experiment.
+It should therefore be possible to take advantage of the fast evolution of TT simulations to achieve rapidly equilibrated FT simulations, which would save a great deal of computing time in solving FT simulations.
+The rundown in FT simulations is very costly for two reasons: the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state and thousands of freefall times must pass during relaxation.
+For example, for the cases displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, the first thousand freefall time units took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours for the FT simulation, but only  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours for the TT simulation.
+After these thousand freefall time units, the TT simulation has spent hundreds of freefall times in a statistically stationary relaxed state, whereas the FT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
+Even at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a FT simulation is therefore more than an order of magnitude larger than a TT simulation.
 
-We now describe a procedure which takes advantage of the fast evolution of fixedT simulations to achieve equilibrated mixedFT simulations.
-In short, the full evolved flow fields in the fixedT simulation are properly re-nondimensionalized and used as initial conditions for a mixedFT simulation.
+We now describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
+In short, the full evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for a FT simulation.
 To achieve this, we perform these steps:
 \begin{enumerate}
-\item Run a fixedT simulation to its statistically stationary state ($\sim100+$ time units). 
+\item Run a TT simulation to its statistically stationary state ($\sim100+$ time units). 
 Measure $\angles{\text{Nu}}$ in that state.
 \item Re-nondimensionalize from $\Delta = \Delta T \rightarrow \partial_z T$, and from Ra$_{\Delta T}\rightarrow$Ra$_{\partial_z T}$, as in Eqn.~\ref{eqn:ra_relation}.
-In our freefall nondimensionalization, this means setting the velocities in the mixedFT simulation to $\bm{u}_{\text{mixedFT}} = \bm{u}_{\text{fixedT}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{mixedFT}} = T_{\text{fixedT}} / \angles{\text{Nu}}$.
-\item Restart the simulation with mixedFT boundaries and continue timestepping.
+In our freefall nondimensionalization, this means setting the velocities in the FT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{TT}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{TT}} / \angles{\text{Nu}}$.
+\item Restart the simulation with FT boundaries and continue timestepping.
 \end{enumerate}
 In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show time traces of a simulation in which we employ this procedure.
-We initialize a fixedT simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
-Roughly one hundred freefall times after the convective transient, we restart this simulation using mixedFT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
-We note that this is the same Ra$_{\partial_z T}$ as the mixedFT case presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
+We initialize a TT simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
+Roughly one hundred freefall times after the convective transient, we restart this simulation using FT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
+We note that this is the same Ra$_{\partial_z T}$ as the FT case presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
 In the left panels, we show the temporal behavior of the Rayleigh numbers (top panel), and the flux (middle panel) and temperature (bottom panel) at the bottom boundary of the simulation.
-The change from fixedT to mixedFT boundaries is shown as a vertical line.
-Unlike in the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the mixedFT state, due to the rapid relaxation achieved during the fixedT portion of the simulation.
+The change from TT to FT boundaries is shown as a vertical line.
+Unlike in the FT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the FT state, due to the rapid relaxation achieved during the TT portion of the simulation.
 
 While these time traces show that this procedure bypasses the long thermal rundown on display in Fig.~\ref{fig:rbc_scalar_comparisons}, this does not prove that the dynamics in the final state faithfully reproduce those achieved by a thermal rundown.
-We now compare probability distribution functions (PDFs) of various quantities in our restarted mixedFT simulation to the mixedFT simulation that stepped through a long rundown.
+We now compare probability distribution functions (PDFs) of various quantities in our restarted FT simulation to the FT simulation that stepped through a long rundown.
 For the last 500 freefall times of each simulation (e.g., the grey shaded region in Fig.~\ref{fig:rbc_restart_description}), we sample the full flow field once each freefall time.
@@
 where $A$ is the quantity, $P(A)$ is the PDF of quantity $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the PDF bins, and $i$ is the index of the bin..
-Visually the PDFs of dynamics in a mixedFT and a restarted fixedT-to-mixedFT simulation are essentially identical.
+Visually the PDFs of dynamics in a FT and a restarted TT-to-FT simulation are essentially identical.
 In all cases except for the enstrophy, the four moments of the PDFs between the two runs are also very similar.
@@
 \hline
-$T$				&	mixedFT		&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.1		&	15 \\
-				&	mixedFT,r	&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.3		&	18 \\
+$T$				&	FT		&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.1		&	15 \\
+				&	FT,r	&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.3		&	18 \\
 \hline
-$\omega^2$		&	mixedFT		&		$1.3$					&	$6.4$					&	19		&	$5.2 \times 10^2$ \\
-				&	mixedFT,r	&		$3.9$					&	$7.4$					&	18		&	$4.5 \times 10^2$ \\
+$\omega^2$		&	FT		&		$1.3$					&	$6.4$					&	19		&	$5.2 \times 10^2$ \\
+				&	FT,r	&		$3.9$					&	$7.4$					&	18		&	$4.5 \times 10^2$ \\
 \hline
-$wT$			&	mixedFT		&		$1.9 \times 10^{-5}$	&	$9.4 \times 10^{-4}$	&	0.16	&	$3.1$ \\
-				&	mixedFT,r	&		$1.9 \times 10^{-5}$	&	$9.3 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+$wT$			&	FT		&		$1.9 \times 10^{-5}$	&	$9.4 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+				&	FT,r	&		$1.9 \times 10^{-5}$	&	$9.3 \times 10^{-4}$	&	0.16	&	$3.1$ \\
 \hline
-$w$				&	mixedFT		&		$7.9 \times 10^{-7}$	&	$4.9 \times 10^{-2}$	&	0.016	&	$2.7$ \\
-				&	mixedFT,r	&		$-5.2 \times 10^{-6}$	&	$4.8 \times 10^{-2}$	&	0.0066	&	$2.8$ \\
+$w$				&	FT		&		$7.9 \times 10^{-7}$	&	$4.9 \times 10^{-2}$	&	0.016	&	$2.7$ \\
+				&	FT,r	&		$-5.2 \times 10^{-6}$	&	$4.8 \times 10^{-2}$	&	0.0066	&	$2.8$ \\
 \hline																	
@@
 
-We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of a mixedFT simulation.
+We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of a FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
-We note however that the fixedT-to-mixedFT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified \RB convection setup that we are aware of.
+We note however that the TT-to-FT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified \RB convection setup that we are aware of.
 The successful degree with which this mechanism reproduces the evolved dynamics suggests that thermal relaxation occurs in two parts:
@@
 \end{enumerate}
-The rapid evolution of fixedT runs, whose energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in RBC. 
-The long rundown of mixedFT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
-Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for mixedFT boundaries, and our procedure uses fixedT dynamics to choose a more ideal set of initial conditions.
+The rapid evolution of TT runs, whose energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in RBC. 
+The long rundown of FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
+Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and our procedure uses TT dynamics to choose a more ideal set of initial conditions.
 
@@
 \label{sec:asymmetries}
-Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated mixedFT simulations, we study highly turbulent convection with mixedFT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
+Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated FT simulations, we study highly turbulent convection with FT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
 [NOTE: in the version of the paper that will be submitted, we will study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
@@
 \caption{ 
-	(upper left) The horizontally- and time-averaged temperature profile is shown for a mixedFT (green) and fixedT (orange) simulation.
+	(upper left) The horizontally- and time-averaged temperature profile is shown for a FT (green) and TT (orange) simulation.
 	(upper middle) The horizontally- and time-averaged temperature profile is shown for upflow regions (solid lines) and downflow regions (dashed lines) respectively.
@@
 
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our fixedT and mixedFT cases.
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our TT and FT cases.
 In the upper left panel, we show the mean temperature profiles achieved in the evolved state of both simulations.
@@
 In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
-Surprisingly, despite symmetrical boundary conditions in fixedT simulations and asymmetrical boundary conditions in mixedFT cases, we on average find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
+Surprisingly, despite symmetrical boundary conditions in TT simulations and asymmetrical boundary conditions in FT cases, we on average find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
 In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
@@
 
-In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases, which also show good agreement between mixedFT and fixedT.
+In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases, which also show good agreement between FT and TT.
 Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
@@
 \caption{ 
-	(left panel) PDFs of temperature measurements of a mixedFT (orange) and fixedT (purple) case are displayed.
-	The right tail of the distribution (near the cold fixed-flux boundary for the mixedFT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
-	(middle panel) A snapshot of the temperature anomaly in a mixedFT simulation.
+	(left panel) PDFs of temperature measurements of a FT (orange) and TT (purple) case are displayed.
+	The right tail of the distribution (near the cold fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	(middle panel) A snapshot of the temperature anomaly in a FT simulation.
 	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
@@
 
-In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which mixedFT boundaries introduce into the simulation.
-In the left panel, we plot PDFs of the temperature fields in comparable fixedT and mixedFT simulations.
-These PDFs agree remarkably well for cold temperatures (near the shared fixedT boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
-Interestingly, there are no temperature fluctuations which exceed the specified boundary values in the convective domain for fixedT simulations.
-However, the mixedFT PDF has a much longer tail and achieves regions which are 50\% hotter than the average bottom boundary value.
+In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation.
+In the left panel, we plot PDFs of the temperature fields in comparable TT and FT simulations.
+These PDFs agree remarkably well for cold temperatures (near the shared TT boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
+Interestingly, there are no temperature fluctuations which exceed the specified boundary values in the convective domain for TT simulations.
+However, the FT PDF has a much longer tail and achieves regions which are 50\% hotter than the average bottom boundary value.
 In order to understand how this is possible, we examine a snapshot of the full temperature field.
@@
 We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
-The fixedT upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
+The TT upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
 The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area, thus allowing for the asymmetry in the tails of the temperature PDF.
 
-We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between mixedFT and fixedT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
+We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between FT and TT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
 However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 50 freefall times of a rotating mixedFT simulation (green) and a fixedT (orange) simulation.
-	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the fixedT simulation.
-	(middle left panel) The Rossby number evolution of both simulation; the bulk flow of the mixedFT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the fixedT simulation is in this latter state through its full evolution.
-	(bottom left panel) The Peclet number evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the fixedT simulation.
+	(left three panels) Time traces of rolling averages over 50 freefall times of a rotating FT simulation (green) and a TT (orange) simulation.
+	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
+	(middle left panel) The Rossby number evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the TT simulation is in this latter state through its full evolution.
+	(bottom left panel) The Peclet number evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
 	(right upper panel) Parameter space plots of Nusselt vs. Ra$_{\Delta T}$.
@@
 	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
-	Data from our mixedFT experiment are shown as a thick green trace, and the fixedT experiment's average is shown as a large orange star.
-	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the mixedFT simulation.
+	Data from our FT experiment are shown as a thick green trace, and the TT experiment's average is shown as a large orange star.
+	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
 	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
@@
 	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
-	The fixedT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
+	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
 	The three vertical black lines in the left panels signify the times at which this snapshots are taken.
@@
 Here, we examine 3D rotating RBC with an Ekman number of $10^{-6}$.
-We study a fixedT case whose supercriticality is $\sim 3$ with Ra$_{\Delta T} = 2.75\times 10^9$, and a corresponding mixedFT case with $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$.
-Both simulations have an aspect ratio $\Gamma = 0.481$, which is roughly ten times larger than the critical wavelength of fixedT convection at Ek = $10^{-6}$.
+We study a TT case whose supercriticality is $\sim 3$ with Ra$_{\Delta T} = 2.75\times 10^9$, and a corresponding FT case with $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$.
+Both simulations have an aspect ratio $\Gamma = 0.481$, which is roughly ten times larger than the critical wavelength of TT convection at Ek = $10^{-6}$.
 These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices \cite{couston&all2019}.
 
-In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of the mixedFT and fixedT cases.
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of the FT and TT cases.
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
-Even in the presence of strong rotation, the fixedT case's fluxes immediately equilibrate, but the mixedFT case takes thousands of freefall times to achieve thermal relaxation.
+Even in the presence of strong rotation, the TT case's fluxes immediately equilibrate, but the FT case takes thousands of freefall times to achieve thermal relaxation.
 In the middle left panel, we show the evolution of the Rossby number.
-While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro $\,\sim 0.1$, the initial state of the mixedFT simulation is only weakly rotationally constrained (Ro $\,\sim 1$).
+While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro $\,\sim 0.1$, the initial state of the FT simulation is only weakly rotationally constrained (Ro $\,\sim 1$).
 The degree of rotational constraint felt by the flows decreases slowly toward its final state over thousands of freefall times.
@@
 After achieving this peak value, the mean Pe monotonically decreases toward its final state.
-We suspect that the initially large value of Ra$_{\Delta T}$ in the mixedFT case drives high velocity flow associated with a developed large scale vortex (LSV).
+We suspect that the initially large value of Ra$_{\Delta T}$ in the FT case drives high velocity flow associated with a developed large scale vortex (LSV).
 As Ra$_{\Delta T}$ and convective driving decrease over time, the driving of the kinetic energy in this LSV eventually reaches an equilibrium value before decreasing, leading to the ``bump'' in the Pe trace.
 
-In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.~Ra(t) for our mixedFT case (thick orange line with teal interior) and the evolved value of Nu in the fixedT case (teal star with purple outline).
+In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.~Ra(t) for our FT case (thick orange line with teal interior) and the evolved value of Nu in the TT case (teal star with purple outline).
 We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
@@
 As has been seen previously, the evolution of Nu vs.~Ra in the rotationally constrained regime is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
-The evolution of Nu(t) vs.~Ra(t) in the mixedFT simulation seems to trace out the fixedT trend well, once again [NOTE: crap, I probably need some more fixedT comparisons.
+The evolution of Nu(t) vs.~Ra(t) in the FT simulation seems to trace out the TT trend well, once again [NOTE: crap, I probably need some more TT comparisons.
 Bummer.
@@
 Finally, in the evolved state, this vortex pair solution begins to oscillate with domain-wide jets, such as those displayed in the right panel.
-We find that the the fixedT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 frefall timescales of evolution that we simulated.
+We find that the the TT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 frefall timescales of evolution that we simulated.
 
-We note briefly that the transition from the unconstrained to rotationally constrained regime may be one area where the time evolution of mixedFT simulations could be useful.
+We note briefly that the transition from the unconstrained to rotationally constrained regime may be one area where the time evolution of FT simulations could be useful.
 The scaling of Nu vs Ra in the rotationally constrained regime is much less well understood than it is in classical RBC [cite, cite].
-A single mixedFT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}, so this approach may be one way to cleverly fill in this parameter space.
-However, it is probable that the best course of action is simply to run a large suite of fixedT simulations that cover the same track for two reasons:
+A single FT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}, so this approach may be one way to cleverly fill in this parameter space.
+However, it is probable that the best course of action is simply to run a large suite of TT simulations that cover the same track for two reasons:
 \begin{enumerate}
@@
 This is seen both in the post-transient bump of Pe in the bottom left panel of Fig.~\ref{fig:rotating_panels}, and also was found from a practical computing standpoint.
-In order to reduce the computational cost of this mixedFT simulation, we reduced the vertical resolution from $512\times384^2$ to $256\times384^2$ (after about 100 freefall times) and then later to $128\times384^2$ (after about $3.3 \times 10^3$ freefall times).
+In order to reduce the computational cost of this FT simulation, we reduced the vertical resolution from $512\times384^2$ to $256\times384^2$ (after about 100 freefall times) and then later to $128\times384^2$ (after about $3.3 \times 10^3$ freefall times).
 At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduced the simulation solution with fidelity.
-For comparison, the fixedT simulation whose dynamics are identical to the evolved mixedFT simulation was well resolved at a coefficient resolution of $128^3$.
+For comparison, the TT simulation whose dynamics are identical to the evolved FT simulation was well resolved at a coefficient resolution of $128^3$.
 This suggests that small scale turbulent velocity structure injected by the vigorous transient is long lived throughout the thermal evolution of the simulation.
-\item The cost of running a turbulent mixedFT simulation, compared to running its comparison fixedT simulation, is astounding.
-The mixedFT case ran for roughly $1.4 \times 10^4$ freefall time units total, and the number of iterations achieved per cpu-hour was $\sim$0.733 at $512\times384^2$, $\sim$2.03 at $256\times384^2$, and $\sim$6.79 at $128\times384^2$.
+\item The cost of running a turbulent FT simulation, compared to running its comparison TT simulation, is astounding.
+The FT case ran for roughly $1.4 \times 10^4$ freefall time units total, and the number of iterations achieved per cpu-hour was $\sim$0.733 at $512\times384^2$, $\sim$2.03 at $256\times384^2$, and $\sim$6.79 at $128\times384^2$.
 The simulation stepped through $1.59 \times 10^5$, $2.22 \times 10^6$, and $3.30 \times 10^6$ iterations at these resolutions, respectively, for a combined total of 2.32 million cpu-hours.
-For comparison, the fixedT simulation ran for $5 \times 10^3$ freefall units at $128^3$, took 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
-In other words, the computational cost of the mixedFT simulation was \emph{two orders of magnitude} larger than its comparison fixedT case.
+For comparison, the TT simulation ran for $5 \times 10^3$ freefall units at $128^3$, took 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
+In other words, the computational cost of the FT simulation was \emph{two orders of magnitude} larger than its comparison TT case.
 \end{enumerate}
@@
 \label{sec:discussion}
-In summary, we find that mixedFT experiments experience a long thermal relaxation which is not experienced by fixedT simulations.
-Here we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``mixedFT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``fixedT'' boundaries, where temperature is fixed at the top and bottom.
+In summary, we find that FT experiments experience a long thermal relaxation which is not experienced by TT simulations.
+Here we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
 Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
@@
 \item Thermal relaxation in RBC has two components: (a) changes in the energy reservoir and (b) changes in the stratification.
-We find that the long relaxation of mixedFT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in fixedT simulations due to the lack of evolution of the average domain temperature.
-On the other hand, RBC seems to restratify itself nearly instantaneously, as suggested by the rapid equilibration of our fixedT simulations.
-\item The thermal relaxation process of a mixedFT simulation essentially performs a sweep through Ra$_{\Delta T}$ parameter space.
+We find that the long relaxation of FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations due to the lack of evolution of the average domain temperature.
+On the other hand, RBC seems to restratify itself nearly instantaneously, as suggested by the rapid equilibration of our TT simulations.
+\item The thermal relaxation process of a FT simulation essentially performs a sweep through Ra$_{\Delta T}$ parameter space.
 We find that the heat transport (the Nusselt number) follows classical scaling laws through this parameter space sweep, but does so in the presence of increased turbulent velocities (quantified by the Reynolds number).
-\item Despite minor asymmetries in the instantaneously measured flows of mixedFT simulations, we find no difference between the mean state of these simulations and the more classic fixedT simulations.
-\item Great computational expense achieving thermal relaxation in a mixedFT simulation can be avoided by using the evolved state of a fixedT simulation as a ``better'' set of initial conditions for a mixedFT simulation.
+\item Despite minor asymmetries in the instantaneously measured flows of FT simulations, we find no difference between the mean state of these simulations and the more classic TT simulations.
+\item Great computational expense achieving thermal relaxation in a FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for a FT simulation.
 In other words, the proper choice of initial conditions can ensure that the initial and evolved energy reservoirs are not vastly different.
-\item If dynamical measurements are taken during the thermal relaxation of a mixedFT simulation, they may be misleading.
+\item If dynamical measurements are taken during the thermal relaxation of a FT simulation, they may be misleading.
 Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
@@
 This is not always true --- for example, in the late stages of the lifetimes of stars, some burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation [cite, cite].
-The use of mixedFT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the fixedT or evolved mixedFT cases here.
+The use of FT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
+However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the TT or evolved FT cases here.
 
@@
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
-We found here in our mixedFT rotating simulation that the early unrelaxed state generated a mean flow (large scale vortex, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
-If we had terminated our mixedFT rotating simulation too early, we would not have seen this feature evolve as the simulation relaxed and progressed into a more rotationally constrained, lower Rossby number state.
+We found here in our FT rotating simulation that the early unrelaxed state generated a mean flow (large scale vortex, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+If we had terminated our FT rotating simulation too early, we would not have seen this feature evolve as the simulation relaxed and progressed into a more rotationally constrained, lower Rossby number state.
 Many dynamo simulations are performed in highly turbulent regimes at the cutting-edge of what is achievable using modern computational resources.
@@
 As a community of convection modellers, it is crucial that we understand the consequences that our choices of boundary conditions have on our experiments so that we do not misinterpret the evolved dynamics.
-However, through the proper setup of experiments (here, fixedT instead of mixedFT boundary conditions), some of the problems that we face in numerics (thermal relaxation) can simply disappear.
+However, through the proper setup of experiments (here, TT instead of FT boundary conditions), some of the problems that we face in numerics (thermal relaxation) can simply disappear.
 
 \begin{acknowledgments}
-We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in mixedFT simulations. 
+We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
@@
 	Resolutions marked by a $*$ show the initial, highest resolution utilized in the simulation.
-	The 2D mixedFT Ra = $4.83 \times 10^{10}$ simulation's resolution was changed to $1024\times2048$ about 500 freefall time units after transient.
-	The rotating mixedFT case's resolution was reduced to $256\times384^2$ about one hundred freefall time units after transient, and was further reduced to $128\times384^2$ about $3.3\times 10^3$ freefall times after transient.
-	``f-to-m'' simulations are mixedFT simulations which use an evolved fixedT simulation as initial conditions, and their cpu-hour cost does not include the cost of the fixedT transient.
+	The 2D FT Ra = $4.83 \times 10^{10}$ simulation's resolution was changed to $1024\times2048$ about 500 freefall time units after transient.
+	The rotating FT case's resolution was reduced to $256\times384^2$ about one hundred freefall time units after transient, and was further reduced to $128\times384^2$ about $3.3\times 10^3$ freefall times after transient.
+	``TT-to-FT'' simulations are FT simulations which use an evolved TT simulation as initial conditions, and their cpu-hour cost does not include the cost of the TT transient.
 }
-\setlength{\tabcolsep}{12pt}
+\setlength{\tabcolsep}{8pt}
 \label{table:speed}
 \begin{center}
-\begin{tabularx}{\textwidth}{c c c c c c c}
+\begin{tabularx}{\textwidth}{c c c c c c c c}
 \hline																	
-BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Pe \\
+BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Pe  & Ro \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-fixedT	&	$1.00 \times 10^8$		&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ \\
-mixedFT	&	$2.61 \times 10^9$		&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ \\
-f-to-m	&	$2.61 \times 10^9$		&	512x1024	&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ \\
-fixedT	&	$2.15 \times 10^8$		&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ \\
-fixedT	&	$4.64 \times 10^8$		&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ \\
-fixedT	&	$1.00 \times 10^9$		&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ \\
-mixedFT	&	$4.83 \times 10^{10}$	&	2048x4096*	&	---					&	---				&	48.3	&	--- \\
-f-to-m	&	$4.83 \times 10^{10}$	&	1024x2048	&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ \\
-fixedT	&	$2.15 \times 10^9$		&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ \\
-fixedT	&	$4.64 \times 10^9$		&	1536x3072	&	---					&	---				&	76.3	&	--- \\
-fixedT	&	$1.00 \times 10^{10}$	&	2048x4096	&	---					&	---				&	95.1	&	--- \\
-f-to-m	&	$9.51 \times 10^{11}$	&	2048x4096	&	---					&	---				&	95.1	&	--- \\
+TT			&	$1.00 \times 10^8$		&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
+FT			&	$2.61 \times 10^9$		&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
+TT-to-FT	&	$2.61 \times 10^9$		&	512x1024	&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
+TT			&	$2.15 \times 10^8$		&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
+TT			&	$4.64 \times 10^8$		&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
+TT			&	$1.00 \times 10^9$		&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
+FT			&	$4.83 \times 10^{10}$	&	2048x4096*	&	$4.75 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
+TT-to-FT	&	$4.83 \times 10^{10}$	&	1024x2048	&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
+TT			&	$2.15 \times 10^9$		&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
+TT			&	$4.64 \times 10^9$		&	1536x3072	&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
+TT			&	$1.00 \times 10^{10}$	&	2048x4096	&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
+TT-to-FT	&	$9.51 \times 10^{11}$	&	2048x4096	&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
 \hline																	
@@
 \hline																	
-fixedT	&	$2.75 \times 10^9$		&	128$^3$				&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$ \\
-mixedFT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$ \\
+TT	&	$1.38 \times 10^9$		&	128$\times$64$^2$	&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
+TT	&	$1.83 \times 10^9$		&	128$\times$64$^2$	&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
+TT	&	$2.29 \times 10^9$		&	128$^3$				&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
+TT	&	$2.75 \times 10^9$		&	128$^3$				&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
+FT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
+TT	&	$3.67 \times 10^9$		&	128$^3$				&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
+TT	&	$4.58 \times 10^9$		&	128$^3$				&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
+TT	&	$5.50 \times 10^9$		&	192$^3$				&	---					&	$22.6$			&	---		&	$6.36 \times 10^3$  & $(2.95 \pm 0.11) \times 10^{-1}$ \\
+TT	&	$6.42 \times 10^9$		&	192$^3$				&	---					&	$29.3$			&	---		&	$7.84 \times 10^3$  & $(3.64 \pm 0.15) \times 10^{-1}$ \\
+TT	&	$7.33 \times 10^9$		&	256$^3$				&	---					&	$36.1$			&	---		&	$9.11 \times 10^3$  & $(4.31 \pm 0.16) \times 10^{-1}$ \\
+TT	&	$8.25 \times 10^9$		&	256$^3$				&	---					&	$43.0$			&	---		&	$*1.03 \times 10^4$ & $(4.98 \pm 0.21) \times 10^{-1}$ \\
+TT	&	$9.17 \times 10^9$		&	256$^3$				&	---					&	$48.9$			&	---		&	$*1.15 \times 10^4$ & $(5.60 \pm 0.23) \times 10^{-1}$ \\
+TT	&	$1.834 \times 10^{10}$	&	256$^3$				&	---					&	---				&	---		&	--- & --- \\
 \hline																	

### 2020-02-06 figures_and_data/rbc_scalar_comparisons.py
lots of improvements to scalar comparison figure

@@ -16,8 +16,9 @@ import h5py
 
 import pandas as pd
 
-mColor = 'darkorange'#olivedrab'
-fColor = 'indigo'
+mColor  = 'darkorange'#olivedrab'
+mColor2 = 'gold'
+fColor  = 'indigo'
 
 def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
     """
@@ -28,6 +29,8 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
                 partial_data[k] = []
@@ -73,9 +76,9 @@ fixed_data = read_data(fixed_ras, fixed_dirs)
 restarted_data = read_data(restarted_ras, restarted_dirs)
 
 # Get rolling averages of all data; Output is every 0.1 time units
-avg_window = 50 #time units
-fixed_trace = fixed_data['{:.4e}'.format(1.00e8)]
-mixed_trace = mixed_data['{:.4e}'.format(2.61e9)]
+avg_window = 100 #time units
+fixed_trace = fixed_data['{:.4e}'.format(1.00e9)]
+mixed_trace = mixed_data['{:.4e}'.format(4.83e10)]
 dff = pd.DataFrame(data=fixed_trace)
 rolledf = dff.rolling(window=avg_window*10, min_periods=avg_window*10).mean()
 dfm = pd.DataFrame(data=mixed_trace)
@@ -100,15 +103,21 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-ax.plot([1, 1], [1,1], color=mColor, lw=2, label='mixedFT')
[…]

### 2020-02-11 tex/mixedft_evolution_ms.tex
some improvements to manuscript, more references, etc.

@@
 \newcommand\mnras{{MNRAS}}%
+\newcommand\apjl{{The Astrophysical Journal Letters}}%
 
@@
 We note briefly that the transition from the unconstrained to rotationally constrained regime may be one area where the time evolution of FT simulations could be useful.
-The scaling of Nu vs Ra in the rotationally constrained regime is much less well understood than it is in classical RBC [cite, cite].
+The scaling of Nu vs Ra in the rotationally constrained regime is more complex than in unrotational convection due to first order dominance of geostrophy \citep{julien&all2012, plumley&julien2019}.
 A single FT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}, so this approach may be one way to cleverly fill in this parameter space.
@@
 Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.
-This is not always true --- for example, in the late stages of the lifetimes of stars, some burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation [cite, cite].
+This is not always true --- for example, in the late stages of the lifetimes of stars, some burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
 The use of FT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
@@
 One question which our study of RBC is not able to study is: how long does it take for a complex convective system to restratify?
-Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains [cite, cite] should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
+Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains \citep{brummell&all2002, kapyla&all2019, pratt&all2017, korre&all2019} should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
 It is, however, probable that clever techniques could be used to rapidly restratify atmospheres \cite{anders&all2018}, and these techniques should be studied separately from cases where the thermal reservoir and stratification evolve simultaneously.
@@
 In the present study, we observed that flux boundaries achieve more extreme values than temperature boundaries.
-In studies of overshooting or penetrative convection [cite, cite], these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
+In studies of overshooting or penetrative convection, these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
 Some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.
@@
 
-Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains [cite, cite].
+Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains \cite{brown&all2010, yadav&all2016, strugarek&all2017, strugarek&all2018}.
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
@@
 It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
-Some authors [cite, cite] employ fixed-flux boundary conditions at \emph{both} boundaries in these simulations, and our results here suggest that such a choice may be ideal.
+Some authors \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018, matilsky&all2019} employ FF boundary conditions, and our results here suggest that such a choice may be ideal.
 

### 2020-02-11 figures_and_data/rbc_1D_profiles.py

@@ -12,6 +12,8 @@ matplotlib.rcParams.update({'font.size': 9})
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+
 import h5py
 
 import pandas as pd
@@ -88,29 +90,38 @@ def read_asymms(ra_list, dir_list):
 
 mixed_dirs = glob.glob("./data/rbc/mixedFT_2d/ra*/")
 fixed_dirs = glob.glob("./data/rbc/fixedT_2d/ra*/")
+restarted_dirs = glob.glob("./data/rbc/restarted_mixed_T2m/ra*/")
 numbered_dirs  = [(f, float(f.split("./data/rbc/mixedFT_2d/ra")[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 numbered_dirs  = [(f, float(f.split("./data/rbc/fixedT_2d/ra")[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+numbered_dirs  = [(f, float(f.split("./data/rbc/restarted_mixed_T2m/ra")[-1].split("/")[0])) for f in restarted_dirs]
+restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_profs = read_profs(mixed_ras, mixed_dirs)
 fixed_profs = read_profs(fixed_ras, fixed_dirs)
+restarted_profs = read_profs(restarted_ras, restarted_dirs)
 mixed_scalars = read_data(mixed_ras, mixed_dirs)
 fixed_scalars = read_data(fixed_ras, fixed_dirs)
+restarted_scalars = read_data(restarted_ras, restarted_dirs)
 mixed_asymms = read_asymms(mixed_ras, mixed_dirs)
 fixed_asymms = read_asymms(fixed_ras, fixed_dirs)
+restarted_asymms = read_asymms(restarted_ras, restarted_dirs)
 
 
-mk = '{:.4e}'.format(2.61e9)
-fk = '{:.4e}'.format(1.00e8)
[…]

### 2020-02-11 figures_and_data/rbc_dynamics_asymmetries.py

@@ -70,18 +70,26 @@ def read_pdfs(ra_list, dir_list):
 
 mixed_dirs = glob.glob("./data/rbc/mixedFT_2d/ra*/")
 fixed_dirs = glob.glob("./data/rbc/fixedT_2d/ra*/")
+restarted_dirs = glob.glob("./data/rbc/restarted_mixed_T2m/ra*/")
 numbered_dirs  = [(f, float(f.split("./data/rbc/mixedFT_2d/ra")[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 numbered_dirs  = [(f, float(f.split("./data/rbc/fixedT_2d/ra")[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+numbered_dirs  = [(f, float(f.split("./data/rbc/restarted_mixed_T2m/ra")[-1].split("/")[0])) for f in restarted_dirs]
+restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_pdfs(mixed_ras, mixed_dirs)
 fixed_data = read_pdfs(fixed_ras, fixed_dirs)
+restarted_data = read_pdfs(restarted_ras, restarted_dirs)
 mixed_scalars = read_data(mixed_ras, mixed_dirs)
 fixed_scalars = read_data(fixed_ras, fixed_dirs)
+restarted_scalars = read_data(restarted_ras, restarted_dirs)
 
-mk = '{:.4e}'.format(2.61e9)
-fk = '{:.4e}'.format(1.00e8)
+#mk = '{:.4e}'.format(2.61e9)
+#fk = '{:.4e}'.format(1.00e8)
+
+mk = '{:.4e}'.format(9.51e11)
+fk = '{:.4e}'.format(1.00e10)
 
 # Set up figure subplots
 fig = plt.figure(figsize=(7.5, 2))
@@ -99,13 +107,13 @@ cax = plt.subplot(gs.new_subplotspec((950, 825), 50, 100))
 # Panel 1, PDF comparison
 plt.sca(axs[0])
 ax = axs[0]
[…]

### 2020-02-11 figures_and_data/rotating_panels.py

@@ -116,11 +116,11 @@ for i in range(3):
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-ax.plot([1, 1], [1,1], color=mColor, lw=2, label='mixedFT')
+ax.plot([1, 1], [1,1], color=mColor, lw=2, label='FT')
 plt.axhline(np.mean(mixed_trace['ra_flux'])/2.75e9, color=mColor, lw=1, ls='-.')
 plt.axhline(np.mean(fixed_trace['ra_temp'])/2.75e9, color=fColor, lw=1)
 ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.75e9, color=mColor, lw=2, label='')
-ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.75e9, color=fColor, lw=1, ls='-.', label='fixedT')
+ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.75e9, color=fColor, lw=1, ls='-.', label='TT')
 ax.legend(loc='center', frameon=True, fontsize=7)
 ax.set_ylabel(r'Ra/$(2.75 \times 10^9)$')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
@@ -133,8 +133,8 @@ plt.sca(axs[1])
 ax = axs[1]
 
 
-plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['Ro'], color=mColor, lw=2, label='mixedFT')
-plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['Ro'], color=fColor, lw=2, label='fixedT')
+plt.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['Ro'], color=mColor, lw=2, label='FT')
+plt.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['Ro'], color=fColor, lw=2, label='TT')
 plt.axhline(1, c=fColor, lw=1)
 plt.yscale('log')
 plt.xlim(-mixed_trace['sim_time'][-1], 0)
@@ -149,8 +149,8 @@ ax = axs[2]
 
 
 Pe_final_temp = np.mean(fixed_trace['Pe'][-5000:])
[…]

### 2020-02-15 tex/mixedft_evolution_ms.tex
good second draft of paper complete

@@
 \begin{abstract}
-Astrophysical studies of convection often impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection (RBC) to show that the use of these mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
-We demonstrate that the mean behavior of an evolved simulation with mixed thermal boundaries corresponds to an equivalent simulation with fixed temperature boundaries at the top and bottom.
-We show that the fast evolution of fixed-temperature simulations can be taken advantage of to rapidly relax simulations with mixed boundaries.
-In the measurements presented here, we find that the asymmetries created by mixed boundaries do not importantly affect spatially averaged dynamics, but we do find that more extreme values of temperature can occur near a fixed flux boundary than a fixed temperature boundary.
-We also demonstrate that these findings carry over to more complicated problems through a brief examination of rotating convection.
-These results suggest that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
+Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
+In this work, we study \RB convection (RBC) to show that the use of these mixed (FT) thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain (TT).
+In the evolved state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries, and the fast evolution of TT simulations can be taken advantage of to rapidly relax FT simulations.
+We show that these findings carry over to more complicated problems through a brief examination of rotating convection.
+We furthermore find that FT boundaries introduce minor asymmetries into the flow fields, with the fixed flux boundary producing more extreme events than the fixed temperature boundary, but that these asymmetries do not appreciably affect the bulk flows.
+We conclude that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
 Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
@@
 Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
-The nature of astrophysical convection is primarily studied through the use of numerical simulations which range from studies of the highly simplified Boussinesq approximation \cite{spiegel&veronis1960} to more complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
-Regardless of the degree of apparent realism of the employed simulations, numerical convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
-A common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
-In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
-In this model, temperature is the only thermodynamic quantity and we use the term ``FT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.
+Numerical simulations are a commonly-used tool in studies into the nature of convection.
+These studies range from examinations of convection in the simplified Boussinesq approximation \cite{spiegel&veronis1960, ahlers&all2009, plumley&julien2019} to highly complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
+In these simulations, convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
+One common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
+However, in Boussinesq studies of \RB convection, the most frequently-utilized choice of boundary conditions is to fix the temperature at both boundaries.
+We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
 
-Despite FT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing FT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``TT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT and FT are repsectively called RB1 and RB3.}).
-It is generally assumed that FT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
-FixedF and TT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
-However, the choice of FT boundaries introduces complexities into the convective system which neither fixedF or TT boundaries are exposed to.
-First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
-Second, FT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.
+In this work, we examine how the choice of using ``mixed'' boundaries affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
+In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
+We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT, FF, and FT are repsectively called RB1, RB2, and RB3.}.
+It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2015}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
+The scaling of the convective heat transport, quantified by the Nusselt number, as a function of increased convective driving, quantified by the Rayleigh number, has been shown to be equivalent for FF and TT boundaries \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
+However, FT boundaries introduce complexities into the convective solution which neither FF or TT boundaries are exposed to.
+First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time \cite{anders&all2018}.
+Second, FT boundary conditions are fundamentally asymmetric, and it is unclear if these asymmetries affect the evolved convective solution.
 
-In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed.
-We also compare the flows in evolved, thermally relaxed FT simulations to the flows in evolved TT simulations.
+In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed, and we compare evolved FT solutions to the most commonly studied TT solutions.
 We find that the thermal evolution and relaxation of FT systems is very long compared to TT systems, where it is nearly instantaneous.
 However, this long thermal evolution can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
-If a FT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
-Our results also suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to TT siulations.
+We also find that during their thermal relaxation, FT simulations simulations perform a sweep through parameter space, effectively sampling dynamics at various values of the Rayleigh number over their evolution.
+Finally, our results suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not importantly change the mean convective state when compared to TT siulations.
+
 We present these findings as follows.
@@
 In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
-The equations of motion are
+The Boussinesq equations of motion are
 \begin{align}
@@
 \end{align}
-where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
-The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+The dimensionless control parameters are the Rayleigh (Ra), Prandtl (Pr), and Ekman (Ek) numbers, defined respectively as
 \begin{equation}
-\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \sqrt{\frac{\nu}{2\Omega L_z^2}},
+\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \frac{\nu}{2\Omega L_z^2},
 \end{equation}
-where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency.
-These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
+where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale.
+These parameters set the freefall Reynolds and P\'{e}clet numbers, 
+\begin{equation}
+\Reff = \sqrt{\frac{\text{Ra}}{\text{Pr}}},\qquad
+\Peff = \text{Pr }\Reff,
+\end{equation}
+and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
 In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
-The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
+The extent of our numerical domain is vertically $z = [-0.5, 0.5]$ and horizontally $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
 The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
-$\Delta$ is the dimensionless temperature jump across the domain; depending on our choice of boundary condition, $\Delta$ defines either a temperature or flux Rayleigh number,
+Depending on our choice of boundary condition, $\Delta$ is set by either the temperature jump across the domain or by the temperature gradient length scale.
+In the case of the former, Ra$_{\Delta T}$ is a temperature Rayleigh number; in the case of the latter, Ra$_{\partial_z T}$ is a flux Rayleigh number,
 \begin{equation}
@@
 \end{equation}
-We study both FT and TT thermal boundary conditions,
+In this work, we study both FT and TT thermal boundary conditions,
 \begin{equation}
-(\text{FT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
+(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5};\qquad\qquad
 (\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
 \end{equation}
-In the case of FT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
-In the case of TT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.
+In the case of FT boundaries, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is Ra$_{\partial_z T}$, while for TT boundaries, $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is Ra$_{\Delta T}$.
 
-Throughout the bulk of this work, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
+In section \ref{sec:2d_results}, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
 For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
 \begin{equation}
-u = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
+u = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
 \label{eqn:vel_bcs}
@@
 The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}.
+For the cases studied here at Ek = $10^{-6}$, $\lambda_c(10^{-6}) = 4.81 \times 10^{-2}$.
 These rotating simulations employ stress-free, impenetrable boundaries,
 \begin{equation}
-\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
+\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
 \label{eqn:vel_bcs}
@@
 \label{sec:ra_nu_relations}
-Throughout this work we will measure and report the evolved value of the Nusselt number.
-We define and measure the Nusselt number instantaneously as
+Throughout this work we will measure and report the evolved value of the Nusselt number (Nu).
+We define and measure Nu instantaneously as
 \begin{equation}
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
-In the evolved, statistically stationary state, when TT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)\Peff}$, and when FT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
-This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
+In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
+This implies that Nu is the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
 \begin{equation}
@@
 \end{equation}
-In other words, in addition to measuring the efficiency of convective heat transport, the Nusselt number is also the unit of conversion between a temperature and a flux nondimensionalization in the evolved state.
 
-Some additional quantities of interest will be reported throughout this paper.
-We will measure the evolved Peclet number of the convective flows in all sections, and in section \ref{sec:rotating_results} we will also report the value of the Rossby number.
-We measure these nondimensional quantities instantaneously as
+Throughout this work, we will also measure the evolved P\'{e}clet number (Pe) and in section \ref{sec:rotating_results} we will measure the Rossby number (Ro).
+These nondimensional quantities are defined as
 \begin{equation}
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 50 freefall times of a FT (orange) and a TT (purple) simulation.
-	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the TT simulation.
+	(left three panels) Time traces of rolling averages over 100 freefall times of a FT (orange) and a TT (purple) simulation.
+	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation.
 	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
 	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
-	The Nu vs Ra plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
-	The Re vs Ra plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
-	The time evolution of the FT case is shown as an orange trace with the arrows showing the sense of time.
+	The Nu vs Ra.~plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
+	The Re vs Ra.~plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of Pe \cite{ahlers&all2009}.
+	The orange trace shows the time evolution of the FT case from the left panels with the arrows showing the sense of time.
+	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
 	Purple circles show our measured values of Nu in TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
-	The orange star in each plot corresponds to the TT case whose time evolution is shown on the left.
-	Black crosses show comparison TT simulations as reported by ref.~\ref{zhu&all2018}.
+	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
+	Black crosses show comparison TT simulations as reported by ref.~\cite{zhu&all2018}.
 \label{fig:rbc_scalar_comparisons} }
@@
 
-In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a FT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
-The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a TT case with Ra$_{\Delta T} = 10^8$.
-The FT case is displayed in orange, and the TT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
-In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
-The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the FT simulation, and this final value corresponds to the input value of the equivalent TT case.
-On the other hand, the value of Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
-This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
-All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.
+In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we display the evolution of a FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ (orange lines) and a TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
+Simulation time in nondimensional freefall units is shown on the x-axis; each simulation's end time, $t_{\text{final}}$, is subtracted so that the final evolved states can be more directly compared, and so that $x = 0$ corresponds to the end of the simulation.
+The lines shown are rolling averages taken over 100 freefall time units.
+In the top-left panel, the evolution of Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ is shown in each simulation.
+In the FT simulation, Ra$_{\Delta T}$ evolves towards its final value over thousands of simulation time units; this final value corresponds to the input value of the equivalent TT case.
+In comparison, Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
+This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of Nu (middle panel) and Pe (bottom panel).
 
-In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot compensated scaling plots of Nu and Pe vs Ra$_{\Delta T}$.
-Over the course of its thermal relaxation, the FT case performs a sweep through Ra$_{\Delta T}$ parameter space.
-During this parameter space sweep, the FT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by TT simulations and which has been reported by previous authors.
-However, we find that the value of Pe measured in the FT simulation through its relaxation  is larger than the value of the Peclet number in comparison TT simulations until it converges to its final state.
-These traces through parameter space demonstrate the importance of waiting until a FT simulation has reached its equilibrated state.
-During the rundown, the dynamics in FT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
-Both of these effects make interpretation of their results difficult until the final, equilibrated state.
+The right panels of Fig.~\ref{fig:rbc_scalar_comparisons} show that the evolution of Ra$_{\Delta T}$ in FT simulations is akin to a sweep through Ra$_{\Delta T}$ parameter space.
+The orange lines show the evolution of the Ra$_{\partial_z T} = 4.83 \times 10^{10}$ case shown on the left, and the yellow lines show the evolution of a Ra$_{\partial_z T} = 2.61 \times 10^{9}$.
+The arrow give the sense of time in the simulations.
+For comparison, we have computed TT simulations throughout this parameter space (purple circles) and we have overplotted the reported results of ref.~\cite{zhu&all2018}.
+The purple circles filled with orange and yellow circles respectively show the comparison TT simulations for the evolved FT simulations.
+In the upper panel, we show a compensated scaling plot for Nu vs.~Ra$_{\Delta T}$, compensated by the best fit reported in ref.~\cite{johnston&doering2009}.
+The lower panel is a compensated scaling plot of Pe vs~Ra$_{\Delta T}$, compensated by the expected scaling \cite{ahlers&all2009}.
+We find that the FT simulations are more turbulent (higher Pe) and carry marginally more flux (higher Nu) than comparable TT simulations as they sweep through this parameter space.
+The dynamics in FT simulations evolve slowly during the rundown, and these traces demonstrate the importance of waiting until a FT simulation has reached its equilibrated state before sampling and analyzing the nonlinear convective state.
+Furthermore, the heightened values of Nu and especially Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
 
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with TT boundary conditions and then is switched to FT boundary conditions.
+	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
 	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
-	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
+	(top left panel) The evolution of Ra over time is shown; Ra$_{\partial_z T}/(48.3\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
 	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
-	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
-	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
-	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
+	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\text{Nu}$.
+	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
+	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown (the grey shaded region in the left three panels).
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
-	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (TT-to-FT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
+	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}; green PDF) to the PDF of the TT-to-FT case (grey PDF).
 \label{fig:rbc_restart_description} }
@@
 It should therefore be possible to take advantage of the fast evolution of TT simulations to achieve rapidly equilibrated FT simulations, which would save a great deal of computing time in solving FT simulations.
-The rundown in FT simulations is very costly for two reasons: the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state and thousands of freefall times must pass during relaxation.
-For example, for the cases displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, the first thousand freefall time units took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours for the FT simulation, but only  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours for the TT simulation.
-After these thousand freefall time units, the TT simulation has spent hundreds of freefall times in a statistically stationary relaxed state, whereas the FT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
-Even at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a FT simulation is therefore more than an order of magnitude larger than a TT simulation.
+The rundown in FT simulations is very costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state, and (2) thousands of freefall times must pass during relaxation.
+For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, with a modest Ra$_{\Delta T} = 10^9$, the full evolution of the FT simulation cost $4.75 \times 10^5$ cpu-hours, while the TT equivalent case cost $5.58 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
 
-We now describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
-In short, the full evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for a FT simulation.
+We now briefly describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
+In short, the evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for a FT simulation.
+Throughout this work, we will refer to simulations conducted this way as ``TT-to-FT'' simulations.
 To achieve this, we perform these steps:
 \begin{enumerate}
-\item Run a TT simulation to its statistically stationary state ($\sim100+$ time units). 
-Measure $\angles{\text{Nu}}$ in that state.
+\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
+Measure $\text{Nu}$ in that state.
 \item Re-nondimensionalize from $\Delta = \Delta T \rightarrow \partial_z T$, and from Ra$_{\Delta T}\rightarrow$Ra$_{\partial_z T}$, as in Eqn.~\ref{eqn:ra_relation}.
-In our freefall nondimensionalization, this means setting the velocities in the FT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{TT}} / \sqrt{\angles{\text{Nu}}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{TT}} / \angles{\text{Nu}}$.
+In our freefall nondimensionalization, this means setting the velocities in the FT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{TT}} / \sqrt{\text{Nu}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{TT}} / \text{Nu}$.
 \item Restart the simulation with FT boundaries and continue timestepping.
 \end{enumerate}
-In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show time traces of a simulation in which we employ this procedure.
-We initialize a TT simulation at Ra$_{\Delta T} = 10^8$, which has been reported to have $\text{Nu} \approx 26.1$ \cite{zhu&all2018}.
-Roughly one hundred freefall times after the convective transient, we restart this simulation using FT boundaries according to our above procedure with an input Ra$_{\partial_z T} = 2.61 \times 10^9$, and we run this simulation for a further thousand time units.
-We note that this is the same Ra$_{\partial_z T}$ as the FT case presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-In the left panels, we show the temporal behavior of the Rayleigh numbers (top panel), and the flux (middle panel) and temperature (bottom panel) at the bottom boundary of the simulation.
-The change from TT to FT boundaries is shown as a vertical line.
+At the end of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, we change the boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$ and restart the simulation using the above procedure.
+In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show the temporal behavior of Ra (top panel), the flux at the bottom boundary (middle panel), and the temperature difference between the top and bottom boundaries (bottom panel).
+The change from TT to FT boundaries is shown by the thin vertical line.
 Unlike in the FT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the FT state, due to the rapid relaxation achieved during the TT portion of the simulation.
 
-While these time traces show that this procedure bypasses the long thermal rundown on display in Fig.~\ref{fig:rbc_scalar_comparisons}, this does not prove that the dynamics in the final state faithfully reproduce those achieved by a thermal rundown.
-We now compare probability distribution functions (PDFs) of various quantities in our restarted FT simulation to the FT simulation that stepped through a long rundown.
-For the last 500 freefall times of each simulation (e.g., the grey shaded region in Fig.~\ref{fig:rbc_restart_description}), we sample the full flow field once each freefall time.
-We interpolate the (unevenly spaced) vertical chebyshev gridpoints onto an evenly spaced grid before histogramming flow values using 500 bins.
-In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we display PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
+In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare probability distribution functions (PDFs) of flow fields in this TT-to-FT simulation and the comparable FT simulation shown in Fig.~\ref{fig:rbc_restart_description}.
+To create these PDFs, we sample the full simulation flow field once every simulation freefall time unit over the final 500 time units of each simulation (e.g., the grey shaded region in the left panels of Fig.~\ref{fig:rbc_restart_description}).
+We interpolate the (unevenly spaced) vertical Chebyshev gridpoints onto an evenly spaced grid before histogramming the flow values.
+Shown are PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
 In Table~\ref{table:pdf_values}, we display the first four moments of each of these distributions,
@@
 \end{equation}
-where $A$ is the quantity, $P(A)$ is the PDF of quantity $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the PDF bins, and $i$ is the index of the bin..
-Visually the PDFs of dynamics in a FT and a restarted TT-to-FT simulation are essentially identical.
-In all cases except for the enstrophy, the four moments of the PDFs between the two runs are also very similar.
-These simulations have no-slip boundaries, so the enstrophy is concentrated near the plume impacting sites within the boundary layers.
-The small differences between the enstrophy PDFs perhaps points to slightly different plume morphologies being sampled during the 500 freefall time units in the two runs, but the similarities between the two cases in other important quantities (specfically in nonlinear transport) lead us to believe that this difference is unimportant.
+where $A$ is a flow quantity, $P(A)$ is the PDF of $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the discrete PDF bins, and $i$ is the index of the bin.
+The PDFs are very visually similar, and there is generally good agreement between the moments of the PDFs.
+The FT simulation here is not perfectly converged to many decimal places; the few \% difference between the modal values of the temperature PDFs is due to this lack of perfect convergence, and given infinite time the peak of the green FT PDF would shift left.
+The remaining discrepancies between the PDFs are small and seem to primarily be due to the randomness of the flows in the time windows over which we sampled the simulations.
 
@@
 \hline
-$T$				&	FT		&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.1		&	15 \\
-				&	FT,r	&		$1.9 \times 10^{-2}$	&	$4.3 \times 10^{-3}$	&	1.3		&	18 \\
+$T$				&	FT			&		$1.11 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.179		&	26.5 \\
+				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
 \hline
-$\omega^2$		&	FT		&		$1.3$					&	$6.4$					&	19		&	$5.2 \times 10^2$ \\
-				&	FT,r	&		$3.9$					&	$7.4$					&	18		&	$4.5 \times 10^2$ \\
+$\omega^2$		&	FT			&		$20.2$					&	$9.66$					&	71.4		&	$9.65\times 10^3$ \\
+				&	TT-to-FT	&		$28.6$					&	$10.0$					&	96.8		&	$1.97 \times 10^4$ \\
 \hline
-$wT$			&	FT		&		$1.9 \times 10^{-5}$	&	$9.4 \times 10^{-4}$	&	0.16	&	$3.1$ \\
-				&	FT,r	&		$1.9 \times 10^{-5}$	&	$9.3 \times 10^{-4}$	&	0.16	&	$3.1$ \\
+$wT$			&	FT			&		$4.51 \times 10^{-6}$	&	$5.43 \times 10^{-4}$	&	0.0437	&	$2.99$ \\
+				&	TT-to-FT	&		$4.40 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0114	&	$3.07$ \\
 \hline
-$w$				&	FT		&		$7.9 \times 10^{-7}$	&	$4.9 \times 10^{-2}$	&	0.016	&	$2.7$ \\
-				&	FT,r	&		$-5.2 \times 10^{-6}$	&	$4.8 \times 10^{-2}$	&	0.0066	&	$2.8$ \\
+$w$				&	FT			&		$1.56 \times 10^{-5}$	&	$4.86 \times 10^{-2}$	&	0.0133	&	$2.92$ \\
+				&	TT-to-FT	&		$-1.74 \times 10^{-5}$	&	$4.82 \times 10^{-2}$	&	-0.0174	&	$3.02$ \\
 \hline																	
@@
 The long rundown of FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
-Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and our procedure uses TT dynamics to choose a more ideal set of initial conditions.
+Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
+
+\subsubsection{Changing Timescales}
+\label{sec:timescales}
+One surprising result of our FT simulations is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
+As noted above in our TT-to-FT procedure, the velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
+This implies that every nondimensional freefall time in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in a FT simulation.
+This is on display in Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher frequency in the TT portion of the simulation than in the FT portion.
+However, we note briefly that in FT simulations, Ra$_{\partial_z T}$ is the input Ra, and it is larger than Ra$_{\Delta T}$ by a factor of $\text{Nu}$.
+Thus, the \emph{thermal diffusion timescale}, which scales like $\sqrt{\text{Ra}_{\text{input}}}$, is also larger in FT simulations by a factor of $\sqrt{\text{Nu}}$.
+This means that one convective overturn timescale occurs over the same fraction of a nondimensional \emph{diffusion} timescale regardless of boundary condition or temperature nondimensionalization.
+These results suggest that comparisons of systems which are nondimensionalized on the flux and the temperature may be more straightforward in a thermal diffusion nondimensionalization \cite{goluskin2015} than the freefall nondimensionalization we have used throughout this work.
 
@@
 \label{sec:asymmetries}
-Now that we have verified a mechanism for rapidly and self-consistently achieving thermally equilibrated FT simulations, we study highly turbulent convection with FT boundaries in an effort to understand the nature of asymmetries introduced to the problem by these boundary conditions.
-[NOTE: in the version of the paper that will be submitted, we will study Ra$_{\Delta T} = 10^{10}$ / Ra$_{\partial_z T} \sim 10^{12}$.
-These simulations are almost done running on Pleiades, so for now we'll carry on with the same values as in the previous section.]
 
@@
 \caption{ 
-	(upper left) The horizontally- and time-averaged temperature profile is shown for a FT (green) and TT (orange) simulation.
-	(upper middle) The horizontally- and time-averaged temperature profile is shown for upflow regions (solid lines) and downflow regions (dashed lines) respectively.
-	(upper right) The horizontally- and time-averaged fluxes in the system are shown.
-	(bottom panels) The percentage difference between the corresponding quantities in the top panels are displayed, and in most cases measurements agree to within a few percent through the full depth of the domain.
+	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
+	The boundary layer regions are separated from the bulk by thin vertical lines.
+	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
+	The insets show the \% difference between the FT and TT solutions.
+	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.
 \label{fig:rbc_1D_profiles} }
@@
 
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the horizontally averaged, vertical profiles of our TT and FT cases.
-In the upper left panel, we show the mean temperature profiles achieved in the evolved state of both simulations.
-Throughout the full depth, these profiles differ by less than 2\%, as shown in the lower left panel.
-In the upper middle panel, we show the mean temperature profile in downflow areas compared to the mean temperature profile achieved in upflow areas.
-Surprisingly, despite symmetrical boundary conditions in TT simulations and asymmetrical boundary conditions in FT cases, we on average find precisely the same asymmetries in upflows/downflows for both sets of boundary conditions.
-In general, we find that the boundary layer in upflows is more gradual in hot plumes, and the same is true for downflows and cold plumes.
-Once again, these profiles agree to within $< 2\%$.
+We now study the asymmetries introduced into a solution by FT boundaries.
+We run a TT and TT-to-FT simulation at Ra$_{\Delta T} = 10^{10}$ and Ra$_{\partial_z T} = 9.51 \times 10^{11}$, respectively.
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally averaged, profiles of the temperature and fluxes in these two cases.
+Time averages are taken over 500 nondimensional freefall time units, sampled once every 0.1 time units (note, as per section \ref{sec:timescales}, that this means that roughly 10x more dynamics are sampled by the TT simulations).
+The left three panels show (top) the mean temperature profile, (middle) the mean temperature profile in the upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$).
+Most of the interesting structure of these profiles is in the boundary layers, located between the edges of the plots and the thin vertical black lines.
+Zoomed in views of the bottom and top boundary layers are respectively shown in the middle and right columns.
+Inset panels show the percentage difference between the FT and TT solutions.
+In the case of the flux panels (bottom row), we do not show the \% difference in the conductive flux; the two cases agree to $\sim$1\% in the boundary layers, and the maximum deviation away from zero in the interior is less than 0.01.
 
-In the upper right panel of Fig.~\ref{fig:rbc_1D_profiles}, we plot the system fluxes for both cases, which also show good agreement between FT and TT.
-Throughout the bulk of the domain, the convective enthalpy fluxes agree to within a few \% or less (solid line in bottom right panel).
-Due to the conductive fluxes approaching zero in the interior, we cannot measure a \% difference for this flux in the bulk, but we find that it is again within a few percent in the boundary layers.
-[NOTE: I need to figure out how to quantify the flux agreement better. Ideas?]
+We find remarkable ($< 1\%$) agreement between the temperature profiles throughout the full depth of the domain.
+When we examine the temperature in upflows and downflows respectively, we find similarly good agreement near the upper (fixed temperature) boundary, but differences of a few percent between the FT and TT case right near the bottom boundary layer.
+Specifically, we find that FT (upflows/downflows) are slightly (warmer/cooler) than their TT counterparts at the hot, bottom boundary.
+These differences are interesting, and are explored further in Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
+While there are very small differences between the condcutive fluxes, we do find differences between the convective fluxes of up to $\sim 6\%$ at most.
+We anticipate that these differences are merely a result of a small sample of convective dynamics in the FT case and do not point to appreciably differences in the heat transport.
 
@@
 \caption{ 
-	(left panel) PDFs of temperature measurements of a FT (orange) and TT (purple) case are displayed.
-	The right tail of the distribution (near the cold fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
-	(middle panel) A snapshot of the temperature anomaly in a FT simulation.
-	The black outline boxes around the roots of the plumes are expanded in the bottom right panels.
+	(left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
+	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
+	(middle panel) A snapshot of the temperature anomaly in the FT simulation.
+	The black outline boxes around the roots of the plumes are zoomed in in the right two panels.
 	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
@@
 
-In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation.
+In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation near the fixed-flux boundary.
 In the left panel, we plot PDFs of the temperature fields in comparable TT and FT simulations.
-These PDFs agree remarkably well for cold temperatures (near the shared TT boundary) and through the mean, but diverge in the tail of the PDF for hot temperatures (where the boundary conditions differ).
+These PDFs agree remarkably well near the mean and for cold temperatures (near the fixed temperature boundary), but diverge in the tail of the PDF for hot temperatures where $T/\Delta T \gtrsim 0.8$, where the boundary conditions differ.
 Interestingly, there are no temperature fluctuations which exceed the specified boundary values in the convective domain for TT simulations.
-However, the FT PDF has a much longer tail and achieves regions which are 50\% hotter than the average bottom boundary value.
+However, the FT PDF has a much longer tail and the FT solution achieves fluid parcels which are hotter than the average bottom boundary value by more than 50\%.
 In order to understand how this is possible, we examine a snapshot of the full temperature field.
@@
 	(left three panels) Time traces of rolling averages over 50 freefall times of a rotating FT simulation (green) and a TT (orange) simulation.
-	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
-	(middle left panel) The Rossby number evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the TT simulation is in this latter state through its full evolution.
-	(bottom left panel) The Peclet number evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
-	(right upper panel) Parameter space plots of Nusselt vs. Ra$_{\Delta T}$.
+	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
+	(middle left panel) Ro evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the TT simulation is in this latter state through its full evolution.
+	(bottom left panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
+	(right upper panel) Parameter space plots of Nu vs.~Ra$_{\Delta T}$.
 	Circlular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
 	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
-	Data from our FT experiment are shown as a thick green trace, and the TT experiment's average is shown as a large orange star.
+	Data from our FT experiment are shown as a thick orange line with a blue interior, and the corresponding TT experiment's average is shown as a purple star with a blue interior.
+	Some comparison TT simulations through this parameter space are shown as purple circles with a blue interior.
 	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
 	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
-	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in \cite{stellmach&all2014}.
+	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
 	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
@@
 
-We now extend our study of 2D RBC to a more complicated experiment.
-Here, we examine 3D rotating RBC with an Ekman number of $10^{-6}$.
-We study a TT case whose supercriticality is $\sim 3$ with Ra$_{\Delta T} = 2.75\times 10^9$, and a corresponding FT case with $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$.
-Both simulations have an aspect ratio $\Gamma = 0.481$, which is roughly ten times larger than the critical wavelength of TT convection at Ek = $10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices \cite{couston&all2019}.
+We now extend our study to a more complicated experiment: 3D rotating RBC with an Ekman number of $10^{-6}$.
+We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \cite{couston&all2019}.
 
@@
 Even in the presence of strong rotation, the TT case's fluxes immediately equilibrate, but the FT case takes thousands of freefall times to achieve thermal relaxation.
-In the middle left panel, we show the evolution of the Rossby number.
-While the evolved states of both simulations exhibit rotationally constrained dynamics with Ro $\,\sim 0.1$, the initial state of the FT simulation is only weakly rotationally constrained (Ro $\,\sim 1$).
-The degree of rotational constraint felt by the flows decreases slowly toward its final state over thousands of freefall times.
-In the bottom left panel, we display the evolution of the Peclet number over time.
-Somewhat surprisingly, the peak value of Pe is found not during the convective transient but rather a few hundreds of freefall times later.
-After achieving this peak value, the mean Pe monotonically decreases toward its final state.
-We suspect that the initially large value of Ra$_{\Delta T}$ in the FT case drives high velocity flow associated with a developed large scale vortex (LSV).
-As Ra$_{\Delta T}$ and convective driving decrease over time, the driving of the kinetic energy in this LSV eventually reaches an equilibrium value before decreasing, leading to the ``bump'' in the Pe trace.
+In the middle panel, we show the evolution of Ro; the evolved flows in both simulations exhibit rotationally constrained dynamics with Ro $\,\approx 0.1$, the flows in the FT simulation initially experience weak rotational influence (Ro $\,\approx 1$).
+In the bottom panel, we display the evolution of Pe over time.
+Strangely, the peak value of Pe occurs a few hundred freefall times after the convective transient.
+After achieving this peak value, Pe monotonically decreases toward its equilibrium state.
 
-In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot the evolution of Nu(t) vs.~Ra(t) for our FT case (thick orange line with teal interior) and the evolved value of Nu in the TT case (teal star with purple outline).
-We have additionally plotted data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
-The overplotted line is the best-fit line for values of Ra $\geq 10^{10}$ from ref.~\cite{cheng&all2015}.
-We note that these comparison values are in cylindrical domains with Pr=7, whereas we are in Cartesian geometry with Pr=1, so some differences are expected.
-As has been seen previously, the evolution of Nu vs.~Ra in the rotationally constrained regime is very steep compared to the nonrotating RBC cases in Fig.~\ref{fig:rbc_scalar_comparisons}.
-The evolution of Nu(t) vs.~Ra(t) in the FT simulation seems to trace out the TT trend well, once again [NOTE: crap, I probably need some more TT comparisons.
-Bummer.
-They're fairly cheap, I'll sub them.].
+In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot a parameter space cut of Nu vs.~Ra for rotating simulations.
+we have evolved select TT cases, and their values are plotted as blue circles with purple outlines.
+The evolution of the FT case in the left panels is shown as a thick orange line with a blue interior, and the corresponding TT case is shown as a blue star with a purple outline.
+We have additionally included some literature data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
+These experiments were conducted in a cylindrical geometry at a different Pr, and are not meant to be one-to-one-comparable, but are meant to guide the eye to the nature of the parameter space of rotating convection.
+The solid black line is the best-fit line for rotationally unconstrained simulations with Ra $\geq 10^{10}$ from ref.~\cite{cheng&all2015}.
+As expected, the scaling of Nu vs.~Ra is steep in the rotationally constrained regime \cite{julien&all2012, plumley&julien2019}, which these simulations trace through.
+As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT values of Nu are once again somewhat elevated above the comparable TT simulations.
 
-In the bottom right panels of Fig.~\ref{fig:rotating_panels}, we examine the evolution of dominant flow structures over the course of thermal relaxation.
-Shown is the vertically integrated vertical component of the vorticity.
-As shown in the left panel, a dominant LSV which is aligned with the global rotation forms at early times.
+In the bottom right three panels of Fig.~\ref{fig:rotating_panels}, we plot the vertically integrated vertical vorticity in the simulation at three different times.
+In the left panel, a dominant LSV which is aligned with the global rotation dominates the simulation at early times.
 Over thousands of freefall times, this LSV evolves into a long-lived vortex pair, displayed in the middle panel.
@@
 
-We note briefly that the transition from the unconstrained to rotationally constrained regime may be one area where the time evolution of FT simulations could be useful.
-The scaling of Nu vs Ra in the rotationally constrained regime is more complex than in unrotational convection due to first order dominance of geostrophy \citep{julien&all2012, plumley&julien2019}.
-A single FT simulation can trace through a large portion of this rotationally constrained parameter space, as shown in the upper right panel of Fig.~\ref{fig:rotating_panels}, so this approach may be one way to cleverly fill in this parameter space.
-However, it is probable that the best course of action is simply to run a large suite of TT simulations that cover the same track for two reasons:
-\begin{enumerate}
-\item The long thermal rundown has some short-lived memory of the higher-Ra$_{\Delta T}$ state that it was recently in.
-This is seen both in the post-transient bump of Pe in the bottom left panel of Fig.~\ref{fig:rotating_panels}, and also was found from a practical computing standpoint.
-In order to reduce the computational cost of this FT simulation, we reduced the vertical resolution from $512\times384^2$ to $256\times384^2$ (after about 100 freefall times) and then later to $128\times384^2$ (after about $3.3 \times 10^3$ freefall times).
+We suspect that the evolution of the dominant flow structures over time explains the strange behavior of Pe in the bottom left panel.
+At early times, the initially large value of Ra$_{\Delta T}$ in the FT case drives the displayed dominant LSV.
+This powerful driving injects energy into the LSV, causing Pe to grow.
+As Ra$_{\Delta T}$ and convective driving decrease over time, the LSV saturates and then starts to wind down, leading to the ``bump'' in the Pe trace.
+
+We once again find it important to briefly note the difference in computational cost between the FT and TT simulations conducted here.
+The TT simulation shown in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} only cost $2.6 \times 10^4$ cpu-hours.
+By comparison, the cost of the FT simulation shown in the same panels was \emph{two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
+The TT simulation's coefficient resolution was $128^3$.
+The FT simulation's initial resolution required to resolve the convective transient was $512\times384^2$ coefficients.
+We reduced the resolution to $256\times384^2$ after 100 freefall times, and then later to $128\times384^2$ after $\sim3.3 \times 10^3$ freefall times.
 At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduced the simulation solution with fidelity.
-For comparison, the TT simulation whose dynamics are identical to the evolved FT simulation was well resolved at a coefficient resolution of $128^3$.
-This suggests that small scale turbulent velocity structure injected by the vigorous transient is long lived throughout the thermal evolution of the simulation.
-\item The cost of running a turbulent FT simulation, compared to running its comparison TT simulation, is astounding.
-The FT case ran for roughly $1.4 \times 10^4$ freefall time units total, and the number of iterations achieved per cpu-hour was $\sim$0.733 at $512\times384^2$, $\sim$2.03 at $256\times384^2$, and $\sim$6.79 at $128\times384^2$.
-The simulation stepped through $1.59 \times 10^5$, $2.22 \times 10^6$, and $3.30 \times 10^6$ iterations at these resolutions, respectively, for a combined total of 2.32 million cpu-hours.
-For comparison, the TT simulation ran for $5 \times 10^3$ freefall units at $128^3$, took 56.4 iterations per cpu-hour, and ran for $1.46 \times 10^6$ iterations, for $\sim 2.6 \times 10^4$ cpu-hours.
-In other words, the computational cost of the FT simulation was \emph{two orders of magnitude} larger than its comparison TT case.
-\end{enumerate}
+This suggests that small scale turbulent velocity structures---which are injected by the vigorous transient and perhaps associated with the LSV---are long lived throughout the thermal evolution of the simulation.
 
@@
 \label{sec:discussion}
-In summary, we find that FT experiments experience a long thermal relaxation which is not experienced by TT simulations.
-Here we have studied the time evolution of \RB convection under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
+In short, we find that FT experiments experience a long thermal relaxation which is not experienced by TT simulations and, to first order, do not introduce important asymmetries into the solution.
+
+In this paper, we have studied the time evolution of \RB convection (RBC) under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
 Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
@@
 We find that the long relaxation of FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations due to the lack of evolution of the average domain temperature.
-On the other hand, RBC seems to restratify itself nearly instantaneously, as suggested by the rapid equilibration of our TT simulations.
-\item The thermal relaxation process of a FT simulation essentially performs a sweep through Ra$_{\Delta T}$ parameter space.
-We find that the heat transport (the Nusselt number) follows classical scaling laws through this parameter space sweep, but does so in the presence of increased turbulent velocities (quantified by the Reynolds number).
-\item Despite minor asymmetries in the instantaneously measured flows of FT simulations, we find no difference between the mean state of these simulations and the more classic TT simulations.
+The rapid evolution of our TT simulations suggests that RBC restratifies itself nearly instantaneously.
+\item Dynamical measurements taken during the thermal relaxation of a FT simulation may be misleading.
+Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
+\item The thermal relaxation process of a FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
+We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classical scaling laws along these parameter space sweeps.
 \item Great computational expense achieving thermal relaxation in a FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for a FT simulation.
-In other words, the proper choice of initial conditions can ensure that the initial and evolved energy reservoirs are not vastly different.
-\item If dynamical measurements are taken during the thermal relaxation of a FT simulation, they may be misleading.
-Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
+\item Despite minor asymmetries near the fixed-flux boundary, we find no meaningful difference between the mean state of FT and TT simulations.
 \end{enumerate}
+We now describe some lessons that should be applied from this work to astrophysical convection, and comment on some open areas of research.
 
-[NOTE: This is basically wild speculation and flailing. I need to get refs in here, maybe rearrange, maybe take stuff out. Open to suggestions. I find discussion sections difficult.]
+Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.
+In nature, convection is not always in an equilibrium state.
+For example, in the late stages of the lifetimes of stars, some core burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
+The use of FT boundaries or initial conditions that we have here consider to be ``bad'' choices may help in understanding these transient lifetime stages.
+However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
 
-In this work, we have studied the simplest possible case of convection: \RB convection; we will now comment on open avenues of research that should be investigated and some lessons to be learned for astrophysical convection.
-Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.
-This is not always true --- for example, in the late stages of the lifetimes of stars, some burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
-The use of FT boundaries or initial conditions that we consider to be ``poor'' may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, as in the TT or evolved FT cases here.
-
-One question which our study of RBC is not able to study is: how long does it take for a complex convective system to restratify?
+One question which our study of RBC is not able to address is: how long does it take for a complex convective system to restratify?
 Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains \citep{brummell&all2002, kapyla&all2019, pratt&all2017, korre&all2019} should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
-It is, however, probable that clever techniques could be used to rapidly restratify atmospheres \cite{anders&all2018}, and these techniques should be studied separately from cases where the thermal reservoir and stratification evolve simultaneously.
+It would be extremely helpful for future studies to examine relaxational timescales in systems where the energy reservoir is fixed, but where convection does not effectively mix the whole domain.
+Fortunately, clever techniques (e.g., as we explored in ref.~\cite{anders&all2018}) can likely be used to rapidly restratify atmospheres in such simulations.
 
 RBC is fundamentally symmetrical, but many natural convective processes occur in density-stratified domains in which the symmetries of the problem are fundamentally broken.
-In the present study, we observed that flux boundaries achieve more extreme values than temperature boundaries.
-In studies of overshooting or penetrative convection, these more extreme values could launch further into a stable layer, and so the choice of boundary condition on the plate that launches plumes into an adjacent radiative zone could change experimental outcomes.
-Some authors have aimed to quantify the statistical distribution of penetrative plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.
-This should be investigated in more detail.
+In the present study, we observed that flux boundaries produce more extreme thermodynamic events than temperature boundaries.
+In studies of overshooting convection, it is possible that plumes produced by a flux boundary layer could launch further into a stable layer than plumes produced by a temperature boundary.
+Some authors have aimed to quantify the nature of overshooting plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.
 
-Some of the most complex astrophysical experiments are dynamo simulations which aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains \cite{brown&all2010, yadav&all2016, strugarek&all2017, strugarek&all2018}.
+Some of the most complex astrophysical convection experiments aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains \cite{brown&all2010, yadav&all2016, strugarek&all2017, strugarek&all2018}.
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
-We found here in our FT rotating simulation that the early unrelaxed state generated a mean flow (large scale vortex, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
-If we had terminated our FT rotating simulation too early, we would not have seen this feature evolve as the simulation relaxed and progressed into a more rotationally constrained, lower Rossby number state.
+We found in our FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+If we had terminated our FT rotating simulation too early, we would not have seen the eventual destruction of this LSV or the later oscillatory behavior between jets and vortex pairs.
 Many dynamo simulations are performed in highly turbulent regimes at the cutting-edge of what is achievable using modern computational resources.
@@
 It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
-Some authors \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018, matilsky&all2019} employ FF boundary conditions, and our results here suggest that such a choice may be ideal.
+Some authors who study astrophysical convection \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018, matilsky&all2019} employ FF boundary conditions, and our results here suggest that such a choice may be ideal in those complex simulations.
 
-In conclusion, we note that our results here should provide astrophysical convection simulations with reason for caution and optimism.
-As a community of convection modellers, it is crucial that we understand the consequences that our choices of boundary conditions have on our experiments so that we do not misinterpret the evolved dynamics.
-However, through the proper setup of experiments (here, TT instead of FT boundary conditions), some of the problems that we face in numerics (thermal relaxation) can simply disappear.
+In conclusion, we note that our results here should provide astrophysical convection simulations with reason for optimism.
+Through a careful understanding of the setup of our numerical experiments, some problems that we encounter (e.g., long thermal rundown in FT simulations) can be completely avoided through a careful understanding of the system being solved.
 

### 2020-02-15 figures_and_data/rbc_1D_profiles.py

@@ -139,20 +139,19 @@ fig = plt.figure()
 fig = plt.figure(figsize=(7.5, 4))
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [( (0 , 0),         330,    250),
-            ( (330, 0),        330,    250),
-            ( (660, 0),        330,    250), 
-            ( (0 ,  350),      330,    250),
-            ( (330, 350),      330,    250),
-            ( (660, 350),      330,    250), 
-            ( (0 ,  700),      330,    250),
-            ( (330, 700),      330,    250),
-            ( (660, 700),      330,    250), 
+subplots = [( (0 , 0),         285,    400),
+            ( (330, 0),        285,    400),
+            ( (660, 0),        285,    400), 
+            ( (0 ,  500),      285,    250),
+            ( (330, 500),      285,    250),
+            ( (660, 500),      285,    250), 
+            ( (0 ,  750),      285,    250),
+            ( (330, 750),      285,    250),
+            ( (660, 750),      285,    250), 
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 axins_l = []
 axins_r = []
-axins_m = []
 
 
 bounds_out = 0.5
@@ -160,20 +159,16 @@ bounds_in  = 0.47
 
 #Row 1 - Temp
 k = 'T'
-axl, axm, axr= axs[0], axs[3], axs[6]
-for ax in [axl, axm, axr]:
+axf, axl, axr= axs[0], axs[3], axs[6]
+for ax in [axf, axl, axr]:
     ax.plot(fz, fixed_profs[fk][k][0,:],    c=fColor, label='TT', lw=2)
     ax.plot(mz, restarted_profs[mk][k][0,:]/dT, c=mColor, label='FT')
 #ax1.legend(loc='lower left', frameon=False, fontsize=7)
-axl.set_ylabel(r'$\bar{T}/\Delta T$')
-axm.legend(loc='lower center', ncol=2, frameon=False, fontsize=7)
+axf.set_ylabel(r'$\bar{T}/\Delta T$')
[…]

### 2020-02-15 figures_and_data/rbc_restart_description.py

@@ -88,9 +88,15 @@ mixed_pdfs = read_pdfs(mixed_ras, mixed_dirs)
 fixed_pdfs = read_pdfs(fixed_ras, fixed_dirs)
 restarted_pdfs = read_pdfs(restarted_ras, restarted_dirs)
 
-fk = '{:.4e}'.format(1.00e8)
-mk = '{:.4e}'.format(2.61e9)
-rk = '{:.4e}'.format(2.61e9)
+#fk = '{:.4e}'.format(1.00e8)
+#mk = '{:.4e}'.format(2.61e9)
+#rk = '{:.4e}'.format(2.61e9)
+
+fk = '{:.4e}'.format(1.00e9)
+mk = '{:.4e}'.format(4.83e10)
+rk = '{:.4e}'.format(4.83e10)
+
+Nu_approx=48.3
 
 # Get rolling averages of all data; Output is every 0.1 time units
 avg_window = 25 #time units
@@ -105,9 +111,9 @@ good_fixed_times = fixed_trace['sim_time'] <= partial_restarted_trace['sim_time'
 for k in fixed_trace.keys():
     fixed = fixed_trace[k][good_fixed_times]
     if k == 'left_flux' or k == 'right_flux':
-        restarted_trace[k] = np.concatenate((fixed/26.1**(3./2), partial_restarted_trace[k][1:])) 
+        restarted_trace[k] = np.concatenate((fixed/Nu_approx**(3./2), partial_restarted_trace[k][1:])) 
     elif 'T' in k:
-        restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:]*26.1)) 
+        restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:]*Nu_approx)) 
     else:
         restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:])) 
 
@@ -142,25 +148,25 @@ for i in [0, 1, 2]:
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-plt.plot(rolledr['sim_time'], rolledr['ra_flux']/2.61e9, color='black', lw=1, ls='-.', label=r'Ra$_{\partial_z T}/26.1$')#\langle\mathrm{Nu}\rangle$')
[…]

### 2020-02-15 figures_and_data/rotating_panels.py

@@ -95,14 +95,14 @@ gs = gridspec.GridSpec(1000, 1000)
 subplots = [( (50 , 0  ),       300,    430),
             ( (350, 0  ),       300,    430),
             ( (650, 0  ),       300,    430),
-            ( (100 , 530),      350,    540),
-            ( (600, 450),       350,    180),
-            ( (600, 630),       350,    180),
-            ( (600, 810),       350,    180),
+            ( (100 , 530),      350,    470),
+            ( (600, 460),       350,    180),
+            ( (600, 640),       350,    180),
+            ( (600, 820),       350,    180),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec((950, 580), 50, 280))
-caxEk = plt.subplot(gs.new_subplotspec((70, 560), 30, 510))
+caxEk = plt.subplot(gs.new_subplotspec((70, 560), 30, 440))
 
 
 #Show times of dynamics panels
@@ -116,12 +116,16 @@ for i in range(3):
 plt.sca(axs[0])
 ax = axs[0]
 #plt.grid(which='both')
-ax.plot([1, 1], [1,1], color=mColor, lw=2, label='FT')
+ax.plot([1, 1], [1,1], color=mColor, lw=1, label='FT')
+ax.plot([1, 1], [1,1], color=fColor, lw=1, label='TT')
+ax.plot([1, 1], [1,1], color='k', lw=1, label=r'Ra$_{\Delta T}$')
+ax.plot([1, 1], [1,1], color='k', lw=1, label=r'Ra$_{\partial_z T}$', dashes=(3,1,1,1))
+
 plt.axhline(np.mean(mixed_trace['ra_flux'])/2.75e9, color=mColor, lw=1, ls='-.')
 plt.axhline(np.mean(fixed_trace['ra_temp'])/2.75e9, color=fColor, lw=1)
 ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.75e9, color=mColor, lw=2, label='')
-ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.75e9, color=fColor, lw=1, ls='-.', label='TT')
-ax.legend(loc='center', frameon=True, fontsize=7)
[…]

### 2020-02-20 tex/mixedft_evolution_ms.tex
adds new Fig 1; swaps figs 2/3

@@
 Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection (RBC) to show that the use of these mixed (FT) thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain (TT).
+In this work, we study \RB convection (RBC) to understand how mixed (``FT'') thermal boundary conditions, which are often used in astrophysics, change the nature of the convective solution compared to the traditional choice of fixing the temperature at the top and bottom of the domain (``TT'').
+We find that FT boundaries impose a long thermal rundown on convective systems which is not experienced by experiments with TT boundaries.
 In the evolved state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries, and the fast evolution of TT simulations can be taken advantage of to rapidly relax FT simulations.
@@
 The scaling of the convective heat transport, quantified by the Nusselt number, as a function of increased convective driving, quantified by the Rayleigh number, has been shown to be equivalent for FF and TT boundaries \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
-However, FT boundaries introduce complexities into the convective solution which neither FF or TT boundaries are exposed to.
+However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
 First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time \cite{anders&all2018}.
@@
 
-\begin{figure}
+\begin{figure}[ht!]
+\includegraphics[width=\textwidth]{./figs/rbc_evolution_dynamics.pdf}
+\caption{ 
+	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation (bottom row).
+	The left column shows a TT case at Ra$_{\Delta T} = 10^{10}$ and the dynamics early in an FT simulation when its effective Ra$_{\Delta T} \approx 10^{10}$.
+	Despite similar flow structures (a large convective cell and plumes which break apart into small turbulent eddies), the temperature anomaly of the hot plume is distinctly smaller than the cold plume in the FT case.
+	The right column shows a TT case at Ra$_{\Delta T} = 10^9$, and the dynamics of the converged FT case when it has Ra$_{\Delta T} \approx 10^9$.
+	The dominant asymmetries observed in the early flow have vanished, and the FT and TT case are visually indistinguishable.
+	(Bottom four panels) Probability distribution functions of the temperature fields corresponding to the four simulations in the upper panels.
+	(Top row) In both cases, the TT temperature field has a mean value at $T = 0.5$ and a symmetric distribution around that peak. 
+	(Bottom left) At early times, A long tail reaching towards the cold (left) boundary is observed, but there is no clear mode of the PDF due to the constantly changing value of $\Delta T$ in this simulation (over time, the modal temperature moves from right to left).
+	(Bottom right) At late times, the temperature PDF from the mode to the fixed-temperature (cold) boundary is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
+	\label{fig:rbc_evolution_dynamics} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time-evolution of the temperature field of an FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
+As shown in the top four panels, in all simulations, we see a classical convective roll solution, as is anticipated for 2D RBC.
+Interestingly, at early times, we find that the dynamics of the FT simulation (bottom left) is highly asymmetrical compared to a comparable TT simulation (upper left), although the size of the turbulent convective structures is similar.
+In the early FT case, the temperature anomaly in the upper (cold) plume is much greater than the temperature anomaly in the warm plume.
+This excess of cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = 1$ to $\Delta T = \text{Nu}^{-1}$ in the final, equilibrated state.
+Eventually, the supply of warm material from the bottom boundary balances the supply of cold material from the top boundary, and the temperature profile of the simulation stops drifting.
+In this converged state, FT dynamics (bottom right) panel are indistinguishable from TT dynamics (top right).
+
+When we examine these temperature fields statistically (bottom four panels), we find a similar story.
+Both of the TT simulations (top row) have a mean temperature of 0.5  and some probability of hotter/colder material (mostly contained in the plumes), bounded by the fixed-temperature boundary values.
+At early times (lower left), the FT simulation shows an extreme tail to its PDF that characterizes the cold plume at the upper boundary.
+Furthermore, the early FT simulation has no distinct mode in its temperature PDF, but rather shows that migration of the modal temperature value from hot temperatures (on the right) toward colder temperatures.
+At late times (lower right), the  FT simulation's PDF is indistinguishable from the TT PDF between the cold (left) boudnary and the modal value.
+From the modal value towards warmer temperatures, we find that fixed-flux boundaries are capable of producing more extreme temperature events than fixed temperature boundaries.
+This is explored further in section \ref{sec:asymmetries}.
+
+\begin{figure}[b!]
 \includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
 \caption{ 
-	(left three panels) Time traces of rolling averages over 100 freefall times of a FT (orange) and a TT (purple) simulation.
+	(left three panels) Time traces of rolling averages over 100 freefall times of an FT (orange) and a TT (purple) simulation.
 	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation.
@@
 
-In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we display the evolution of a FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ (orange lines) and a TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
+In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we display the time evolution of scalar quantities from the FT simulation shown in Fig.~\ref{fig:rbc_evolution_dynamics} (orange lines) and compare it to the TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
 Simulation time in nondimensional freefall units is shown on the x-axis; each simulation's end time, $t_{\text{final}}$, is subtracted so that the final evolved states can be more directly compared, and so that $x = 0$ corresponds to the end of the simulation.
@@
 The orange lines show the evolution of the Ra$_{\partial_z T} = 4.83 \times 10^{10}$ case shown on the left, and the yellow lines show the evolution of a Ra$_{\partial_z T} = 2.61 \times 10^{9}$.
-The arrow give the sense of time in the simulations.
+The arrows give the sense of time in the simulations.
 For comparison, we have computed TT simulations throughout this parameter space (purple circles) and we have overplotted the reported results of ref.~\cite{zhu&all2018}.
@@
 We find that the FT simulations are more turbulent (higher Pe) and carry marginally more flux (higher Nu) than comparable TT simulations as they sweep through this parameter space.
-The dynamics in FT simulations evolve slowly during the rundown, and these traces demonstrate the importance of waiting until a FT simulation has reached its equilibrated state before sampling and analyzing the nonlinear convective state.
+The dynamics in FT simulations evolve slowly during the rundown, and these traces demonstrate the importance of waiting until an FT simulation has reached its equilibrated state before sampling and analyzing the nonlinear convective state.
 Furthermore, the heightened values of Nu and especially Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
+
+\subsection{Evolved Structure}
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
+\caption{ 
+	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
+	The boundary layer regions are separated from the bulk by thin vertical lines.
+	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
+	The insets show the \% difference between the FT and TT solutions.
+	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.
+\label{fig:rbc_1D_profiles} }
+\end{figure}
+
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally averaged, profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
+Time averages are taken over 500 nondimensional freefall time units, sampled once every 0.1 time units.
+The left three panels show (top) the mean temperature profile, (middle) the mean temperature profile in the upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$).
+Most of the interesting structure of these profiles is in the boundary layers, located between the edges of the plots and the thin vertical black lines.
+Zoomed in views of the bottom and top boundary layers are respectively shown in the middle and right columns.
+Inset panels show the percentage difference between the FT and TT solutions.
+In the case of the flux panels (bottom row), we do not show the \% difference in the conductive flux; the two cases agree to $\sim$1\% in the boundary layers, and the maximum deviation away from zero in the interior is less than 0.01.
+
+We find good ($\sim 1\%$) agreement between the temperature profiles throughout the full depth of the domain.
+When we examine the temperature in upflows and downflows respectively, we find similarly good agreement near the upper (fixed temperature) boundary, but differences of a few percent between the FT and TT case right near the bottom boundary layer.
+Specifically, we find that FT (upflows/downflows) are slightly (warmer/cooler) than their TT counterparts at the hot, bottom boundary.
+These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
+While there are very small differences between the condcutive fluxes, we do find differences between the convective fluxes of up to $\sim 3\%$ at most.
+We anticipate that these differences are merely a result of a small sample of convective dynamics in the FT case and do not point to appreciably differences in the heat transport.
+
+\subsection{TT-to-FT: Rapidly equilibrated FT simulations}
 
@@
 	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
-	(top left panel) The evolution of Ra over time is shown; Ra$_{\partial_z T}/(48.3\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
+	(top left panel) The evolution of Ra over time is shown; Ra$_{\partial_z T}/(4.83\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
 	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
@@
 The rundown in FT simulations is very costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state, and (2) thousands of freefall times must pass during relaxation.
-For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, with a modest Ra$_{\Delta T} = 10^9$, the full evolution of the FT simulation cost $4.75 \times 10^5$ cpu-hours, while the TT equivalent case cost $5.58 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
+For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, with a modest Ra$_{\Delta T} = 10^9$, the full evolution of the FT simulation costs $4.75 \times 10^5$ cpu-hours, while the TT equivalent case costs $5.58 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
 
 We now briefly describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
-In short, the evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for a FT simulation.
+In short, the evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for an FT simulation.
 Throughout this work, we will refer to simulations conducted this way as ``TT-to-FT'' simulations.
@@
 where $A$ is a flow quantity, $P(A)$ is the PDF of $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the discrete PDF bins, and $i$ is the index of the bin.
-The PDFs are very visually similar, and there is generally good agreement between the moments of the PDFs.
+The PDFs are qualitatively similar, and there is generally good agreement between the moments of the PDFs.
 The FT simulation here is not perfectly converged to many decimal places; the few \% difference between the modal values of the temperature PDFs is due to this lack of perfect convergence, and given infinite time the peak of the green FT PDF would shift left.
@@
 
-We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of a FT simulation.
+We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 As noted above in our TT-to-FT procedure, the velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
-This implies that every nondimensional freefall time in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in a FT simulation.
+This implies that every nondimensional freefall time in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
 This is on display in Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher frequency in the TT portion of the simulation than in the FT portion.
@@
 Thus, the \emph{thermal diffusion timescale}, which scales like $\sqrt{\text{Ra}_{\text{input}}}$, is also larger in FT simulations by a factor of $\sqrt{\text{Nu}}$.
-This means that one convective overturn timescale occurs over the same fraction of a nondimensional \emph{diffusion} timescale regardless of boundary condition or temperature nondimensionalization.
+This means that one convective overturn timescale occurs over the same fraction of a nondimensional \emph{diffusion} timescale regardless of boundary conditions or temperature nondimensionalization.
 These results suggest that comparisons of systems which are nondimensionalized on the flux and the temperature may be more straightforward in a thermal diffusion nondimensionalization \cite{goluskin2015} than the freefall nondimensionalization we have used throughout this work.
@@
 \label{sec:asymmetries}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
-\caption{ 
-	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
-	The boundary layer regions are separated from the bulk by thin vertical lines.
-	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
-	The insets show the \% difference between the FT and TT solutions.
-	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.
-\label{fig:rbc_1D_profiles} }
-\end{figure}
-
-We now study the asymmetries introduced into a solution by FT boundaries.
-We run a TT and TT-to-FT simulation at Ra$_{\Delta T} = 10^{10}$ and Ra$_{\partial_z T} = 9.51 \times 10^{11}$, respectively.
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally averaged, profiles of the temperature and fluxes in these two cases.
-Time averages are taken over 500 nondimensional freefall time units, sampled once every 0.1 time units (note, as per section \ref{sec:timescales}, that this means that roughly 10x more dynamics are sampled by the TT simulations).
-The left three panels show (top) the mean temperature profile, (middle) the mean temperature profile in the upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$).
-Most of the interesting structure of these profiles is in the boundary layers, located between the edges of the plots and the thin vertical black lines.
-Zoomed in views of the bottom and top boundary layers are respectively shown in the middle and right columns.
-Inset panels show the percentage difference between the FT and TT solutions.
-In the case of the flux panels (bottom row), we do not show the \% difference in the conductive flux; the two cases agree to $\sim$1\% in the boundary layers, and the maximum deviation away from zero in the interior is less than 0.01.
-
-We find remarkable ($< 1\%$) agreement between the temperature profiles throughout the full depth of the domain.
-When we examine the temperature in upflows and downflows respectively, we find similarly good agreement near the upper (fixed temperature) boundary, but differences of a few percent between the FT and TT case right near the bottom boundary layer.
-Specifically, we find that FT (upflows/downflows) are slightly (warmer/cooler) than their TT counterparts at the hot, bottom boundary.
-These differences are interesting, and are explored further in Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
-While there are very small differences between the condcutive fluxes, we do find differences between the convective fluxes of up to $\sim 6\%$ at most.
-We anticipate that these differences are merely a result of a small sample of convective dynamics in the FT case and do not point to appreciably differences in the heat transport.
 
@@
 
+We now study in more detail the asymmetries introduced into a solution by FT boundaries.
+We run a TT and TT-to-FT simulation at Ra$_{\Delta T} = 10^{10}$ and Ra$_{\partial_z T} = 9.51 \times 10^{11}$, respectively.
 In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation near the fixed-flux boundary.
@@
 	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
-	Data from our FT experiment are shown as a thick orange line with a blue interior, and the corresponding TT experiment's average is shown as a purple star with a blue interior.
-	Some comparison TT simulations through this parameter space are shown as purple circles with a blue interior.
+	Data from our FT experiment are shown as a thick orange line with a cyan interior, and the corresponding TT experiment's average is shown as a purple star with a cyan interior.
+	Some comparison TT simulations through this parameter space are shown as purple circles with a cyan interior.
 	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
@@
 In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot a parameter space cut of Nu vs.~Ra for rotating simulations.
-we have evolved select TT cases, and their values are plotted as blue circles with purple outlines.
-The evolution of the FT case in the left panels is shown as a thick orange line with a blue interior, and the corresponding TT case is shown as a blue star with a purple outline.
+We have evolved select TT cases, and their values are plotted as cyan circles with purple outlines (where here, the cyan shows the value of Ek for the simulations, per the colorbar).
+The evolution of the FT case in the left panels is shown as a thick orange line with a cyan interior, and the corresponding TT case is shown as a cyan star with a purple outline.
 We have additionally included some literature data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
@@
 We once again find it important to briefly note the difference in computational cost between the FT and TT simulations conducted here.
-The TT simulation shown in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} only cost $2.6 \times 10^4$ cpu-hours.
+The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.6 \times 10^4$ cpu-hours.
 By comparison, the cost of the FT simulation shown in the same panels was \emph{two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
@@
 We reduced the resolution to $256\times384^2$ after 100 freefall times, and then later to $128\times384^2$ after $\sim3.3 \times 10^3$ freefall times.
-At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduced the simulation solution with fidelity.
+At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduce the simulation solution with fidelity.
 This suggests that small scale turbulent velocity structures---which are injected by the vigorous transient and perhaps associated with the LSV---are long lived throughout the thermal evolution of the simulation.
@@
 The rapid evolution of our TT simulations suggests that RBC restratifies itself nearly instantaneously.
-\item Dynamical measurements taken during the thermal relaxation of a FT simulation may be misleading.
+\item Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading.
 Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
-\item The thermal relaxation process of a FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
+\item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
 We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classical scaling laws along these parameter space sweeps.
-\item Great computational expense achieving thermal relaxation in a FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for a FT simulation.
+\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation.
 \item Despite minor asymmetries near the fixed-flux boundary, we find no meaningful difference between the mean state of FT and TT simulations.
@@
 For example, in the late stages of the lifetimes of stars, some core burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
-The use of FT boundaries or initial conditions that we have here consider to be ``bad'' choices may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convecting system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
+The use of FT boundaries or initial conditions that we have here considered to be ``bad'' choices may help in understanding these transient lifetime stages.
+However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
 

### 2020-02-20 figures_and_data/rbc_1D_profiles.py

@@ -31,6 +31,8 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
                 partial_data[k] = []
@@ -108,20 +110,26 @@ mixed_asymms = read_asymms(mixed_ras, mixed_dirs)
 fixed_asymms = read_asymms(fixed_ras, fixed_dirs)
 restarted_asymms = read_asymms(restarted_ras, restarted_dirs)
 
+ra_dt = 1.00e8
+mk = '{:.4e}'.format(2.61e9)
+fk = '{:.4e}'.format(1.00e8)
+#mk = '{:.4e}'.format(4.83e10)
+#fk = '{:.4e}'.format(1.00e9)
+#mk = '{:.4e}'.format(9.51e11)
+#fk = '{:.4e}'.format(1.00e10)
 
-mk = '{:.4e}'.format(9.51e11)
-fk = '{:.4e}'.format(1.00e10)
-
-mz = restarted_profs[mk]['z']
+mz = mixed_profs[mk]['z']
 fz = fixed_profs[fk]['z']
 max_nz = np.max((len(mz), len(fz)))
 
 
-delta_T_mixed = restarted_scalars[mk]['delta_T']
-dT = np.mean(delta_T_mixed[-5000:])
+delta_T_mixed = mixed_scalars[mk]['delta_T']
+dT = np.mean(delta_T_mixed[-1000:])
 Nu_fixedT = fixed_scalars[fk]['Nu']
-Nu = np.mean(Nu_fixedT[-5000:])
-flux_scale = (np.sqrt(1e10)/Nu)**(-1)
+Nu = np.mean(Nu_fixedT[-1000:])
+flux_scale = (np.sqrt(ra_dt)/Nu)**(-1)
+
+print(dT, mixed_profs[mk]['T'][0,int(len(mz)/2)])
 
 
 z_basis = de.Chebyshev(  'z', max_nz, interval=[-1/2, 1/2], dealias=1)
@@ -155,14 +163,14 @@ axins_r = []
 
 
 bounds_out = 0.5
[…]

### 2020-02-20 figures_and_data/rbc_dynamics_asymmetries.py

@@ -26,6 +26,8 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
                 partial_data[k] = []

### 2020-02-20 figures_and_data/rbc_evolution_dynamics.py

@@ -1,0 +1,284 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+import dedalus.public as de
+
+mColor = 'darkorange'
+fColor = 'indigo'
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
[…]

### 2020-02-20 figures_and_data/rbc_restart_description.py

@@ -25,6 +25,8 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
                 partial_data[k] = []

### 2020-02-20 tex/mixedft_evolution_ms.tex
corrects fig 3 caption

@@
 \caption{ 
-	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
+	[NOTE: This is currently data from Ra$_{\Delta T} = 10^8$; $10^9$ is converging a bit further on Pleiades]
+	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for an FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{9}$.
 	The boundary layer regions are separated from the bulk by thin vertical lines.

### 2020-02-24 figures_and_data/rbc_1D_profiles.py
some improvements to Figs 2/3

@@ -110,13 +110,13 @@ mixed_asymms = read_asymms(mixed_ras, mixed_dirs)
 fixed_asymms = read_asymms(fixed_ras, fixed_dirs)
 restarted_asymms = read_asymms(restarted_ras, restarted_dirs)
 
-ra_dt = 1.00e8
-mk = '{:.4e}'.format(2.61e9)
-fk = '{:.4e}'.format(1.00e8)
-#mk = '{:.4e}'.format(4.83e10)
-#fk = '{:.4e}'.format(1.00e9)
-#mk = '{:.4e}'.format(9.51e11)
-#fk = '{:.4e}'.format(1.00e10)
+#ra_dt = 1.00e8
+#mk = '{:.4e}'.format(2.61e9)
+#fk = '{:.4e}'.format(1.00e8)
+
+ra_dt = 1.00e9
+mk = '{:.4e}'.format(4.83e10)
+fk = '{:.4e}'.format(1.00e9)
 
 mz = mixed_profs[mk]['z']
 fz = fixed_profs[fk]['z']

### 2020-02-24 figures_and_data/rbc_restart_description.py

@@ -187,11 +187,20 @@ ax.set_yticks((0.95, 1, 1.05))
 print(rolledr['left_T'])
 
 keys = ['T', 'enstrophy', 'enth_flux', 'w']
-labels = [r'$T/\Delta T$', r'$\omega^2 / 10^3$', r'$w T\cdot 10^3$', r'$w$']
+labels = [r'$T/\Delta T$', r'$\omega^2 / 10^2$', r'$w T\cdot 10^3$', r'$w$']
 for i, field in enumerate(keys):
     ax = axs[3+i] 
     mx, mp, mdx = [mixed_pdfs[mk][field][k] for k in ['xs', 'pdf', 'dx']]
     rx, rp, rdx = [restarted_pdfs[rk][field][k] for k in ['xs', 'pdf', 'dx']]
+
+    mcdf = np.zeros_like(mp)
+    rcdf = np.zeros_like(rp)
+    for j in range(len(mp)-1):
+        mcdf[j+1] = mcdf[j] + mp[j]*mdx
+    for j in range(len(rp)-1):
+        rcdf[j+1] = rcdf[j] + rp[j]*rdx
+    good_m = (mcdf > 0.0001)*(mcdf < 0.9999)*(mp > 0)
+    good_r = (rcdf > 0.0001)*(rcdf < 0.9999)*(rp > 0)
 
     ax.fill_between(mx, 1e-16, mp, color='olivedrab', alpha=0.5)
     ax.fill_between(rx, 1e-16, rp, color='black', alpha=0.5)
@@ -199,18 +208,27 @@ for i, field in enumerate(keys):
     ax.plot(rx, rp, label='TT-to-FT', color='black')
     ax.set_yscale('log')
     ax.set_xlabel(labels[i])
-    ax.set_ylim(np.min((mp[mp>0].min(), rp[rp>0].min())), np.max((mp.max(), rp.max())))
-    ax.set_xlim(np.min((mx.min(), rx.min())), np.max((mx.max(), rx.max())))
+
+
+
+
+    min_x_bounds = np.min((np.min(mx[good_m]), np.min(rx[good_r])))
+    max_x_bounds = np.max((np.max(mx[good_m]), np.max(rx[good_r])))
+
+    min_y_bounds = np.min((np.min(mp[good_m]), np.min(rp[good_r])))
+
[…]

### 2020-02-25 tex/mixedft_evolution_ms.tex
commits changes for near-final draft

--- 2020-02-20 tex/mixedft_evolution_ms.tex
@@
 \affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
-\author{Jeffrey S. Oishi}
-\affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
 
@@
 Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
-Numerical simulations are a commonly-used tool in studies into the nature of convection.
+Numerical simulations are a commonly-used tool in studies of geophysical or astrophysical convection.
 These studies range from examinations of convection in the simplified Boussinesq approximation \cite{spiegel&veronis1960, ahlers&all2009, plumley&julien2019} to highly complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
-In these simulations, convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
-One common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
-However, in Boussinesq studies of \RB convection, the most frequently-utilized choice of boundary conditions is to fix the temperature at both boundaries.
+Regardless of complexity, numerically simulated convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2016}.
+In studies of Boussinesq convection, the standard choice is to hold constant the temperature difference across the domain by fixing the temperature at the upper and lower boundaries.
+However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
 We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
@@
 In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
-We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT, FF, and FT are repsectively called RB1, RB2, and RB3.}.
-It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2015}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
-The scaling of the convective heat transport, quantified by the Nusselt number, as a function of increased convective driving, quantified by the Rayleigh number, has been shown to be equivalent for FF and TT boundaries \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
+We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are repsectively called RB1, RB2, and RB3.}.
+It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
+FF and TT boundaries exhibit the same scaling of convective heat transport, quantified by the Nusselt number (Nu), as a function of increased convective driving, quantified by the Rayleigh number (Ra) \cite{johnston&doering2009}.
+It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
-First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time \cite{anders&all2018}.
+First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve (``relax'') over time \cite{anders&all2018}.
 Second, FT boundary conditions are fundamentally asymmetric, and it is unclear if these asymmetries affect the evolved convective solution.
 
-In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed, and we compare evolved FT solutions to the most commonly studied TT solutions.
-We find that the thermal evolution and relaxation of FT systems is very long compared to TT systems, where it is nearly instantaneous.
-However, this long thermal evolution can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
-We also find that during their thermal relaxation, FT simulations simulations perform a sweep through parameter space, effectively sampling dynamics at various values of the Rayleigh number over their evolution.
-Finally, our results suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not importantly change the mean convective state when compared to TT siulations.
+In this paper, we investigate the thermal relaxation of and the asymmetries in RBC with FT boundary conditions.
+We also compare relaxed FT solutions to TT solutions.
+Our results suggest that the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+The thermal relaxation of FT simulations is analagous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
+We find that this long thermal relaxation can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
+Finally, FT boundaries create some asymmetries in the convective flows, but these asymmetries do not meaningfully change the mean convective state compared to TT simulations.
 
@@
 In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
-In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
+In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
 Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.
@@
 \label{sec:simulations}
-We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
-In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
+We study incompressible  under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
+In section \ref{sec:rotating_results}, we study convection in the presence of vertical global rotation \cite{julien&all1996}, and include the Coriolis term in the momentum equation for generality.
 The Boussinesq equations of motion are
 \begin{align}
-\Div{\bm{u}} &= 0
+\DivU &= 0
 	\label{eqn:incompressible}
@@
 \end{equation}
-where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale.
-These parameters set the freefall Reynolds and P\'{e}clet numbers, 
+where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
+These parameters set the freefall Reynolds (\Reff) and P\'{e}clet (\Peff) numbers, 
 \begin{equation}
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
+In nonrotating RBC (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
+
 The extent of our numerical domain is vertically $z = [-0.5, 0.5]$ and horizontally $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
 The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
-Depending on our choice of boundary condition, $\Delta$ is set by either the temperature jump across the domain or by the temperature gradient length scale.
-In the case of the former, Ra$_{\Delta T}$ is a temperature Rayleigh number; in the case of the latter, Ra$_{\partial_z T}$ is a flux Rayleigh number,
+The temperature scale, $\Delta$, is set by the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
+We respectively define a temperature (Ra$_{\Delta T}$) and a flux (Ra$_{\partial_z T}$) Rayleigh number for these cases,
 \begin{equation}
@@
 \end{equation}
-In this work, we study both FT and TT thermal boundary conditions,
+We impose FT and TT boundary conditions respectively as
 \begin{equation}
@@
 \end{equation}
-In the case of FT boundaries, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is Ra$_{\partial_z T}$, while for TT boundaries, $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is Ra$_{\Delta T}$.
 
@@
 \end{equation}
-The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}.
-For the cases studied here at Ek = $10^{-6}$, $\lambda_c(10^{-6}) = 4.81 \times 10^{-2}$.
-These rotating simulations employ stress-free, impenetrable boundaries,
+For this choice of boundary conditions, the critical value of the Rayleigh number is Ra$_{\partial_z T} = 1296$ for FT boundaries and Ra$_{\Delta T} = 1708$ for TT boundaries \cite{goluskin2016}.
+Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
+However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:2d_results}, we do not expect this difference in linear stability to be very important.
+
+The rotating cases in section \ref{sec:rotating_results} employ stress-free, impenetrable boundaries,
 \begin{equation}
@@
 \end{equation}
+We follow previous work  \cite{stellmach&all2014} and study three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek.
+For the cases studied here at Ek = $10^{-6}$, and for TT boundaries, $\lambda_c(10^{-6}) \approx 4.81 \times 10^{-2}$ and the critical Rayleigh number is Ra$_{\Delta T} \approx 9.2 \times 10^{8}$.
 
@@
 \end{equation}
-where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
-In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
+where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
+In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (-\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
 This implies that Nu is the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
@@
 \subsection{Time Evolution}
+\label{sec:time_evolution}
 
-\begin{figure}[ht!]
+\begin{figure}[p!]
 \includegraphics[width=\textwidth]{./figs/rbc_evolution_dynamics.pdf}
 \caption{ 
-	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation (bottom row).
-	The left column shows a TT case at Ra$_{\Delta T} = 10^{10}$ and the dynamics early in an FT simulation when its effective Ra$_{\Delta T} \approx 10^{10}$.
-	Despite similar flow structures (a large convective cell and plumes which break apart into small turbulent eddies), the temperature anomaly of the hot plume is distinctly smaller than the cold plume in the FT case.
-	The right column shows a TT case at Ra$_{\Delta T} = 10^9$, and the dynamics of the converged FT case when it has Ra$_{\Delta T} \approx 10^9$.
-	The dominant asymmetries observed in the early flow have vanished, and the FT and TT case are visually indistinguishable.
-	(Bottom four panels) Probability distribution functions of the temperature fields corresponding to the four simulations in the upper panels.
-	(Top row) In both cases, the TT temperature field has a mean value at $T = 0.5$ and a symmetric distribution around that peak. 
-	(Bottom left) At early times, A long tail reaching towards the cold (left) boundary is observed, but there is no clear mode of the PDF due to the constantly changing value of $\Delta T$ in this simulation (over time, the modal temperature moves from right to left).
-	(Bottom right) At late times, the temperature PDF from the mode to the fixed-temperature (cold) boundary is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
+	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation at early and late times (bottom row).
+	(Left two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^{10}$ and early in an FT simulation when Ra$_{\Delta T} \approx 10^{10}$.
+	To first order, both cases have similar flow structures: a large convective cell and plumes which break apart into small turbulent eddies.
+	However, in the FT case, the temperature anomaly of the cold plume is much larger than the hot plume, which does not appear on this colorscale.
+	(Right two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^9$ and in the relaxed state of the previously pictured FT simulation with Ra$_{\Delta T} \approx 10^9$.
+	The relaxed FT simulation is visually indistinguishable from its comparable TT simulation.
+\\	
+	(Bottom four panels) Probability distribution functions (PDFs) of the full temperature field in each of the four dynamical panels pictured above.
+	PDFs sample the dynamics in each simulation once every simulation freefall time unit over the course of 500 freefall time units.
+	The black vertical line shows the median value, and the grey outline shows the 68\% confidence interval, or where the cumulative distribution function (CDF)'s value ranges from 0.16 to 0.84.
+	(Top row) In both TT simulations, the temperature field has a mean value at $T = 0.5$ and a symmetric distribution around that peak with maxima at the fixed values of the boundaries. 
+	(Bottom left) At early times in the FT simulation, the modal value of the PDF constantly moves left (towards the cold fixed-temperature boundary).
+	(Bottom right) At late times, the temperature PDF from the cold fixed-temperature value (on the left) to the mode is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
 	\label{fig:rbc_evolution_dynamics} }
@@
 
-In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time-evolution of the temperature field of an FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
-As shown in the top four panels, in all simulations, we see a classical convective roll solution, as is anticipated for 2D RBC.
-Interestingly, at early times, we find that the dynamics of the FT simulation (bottom left) is highly asymmetrical compared to a comparable TT simulation (upper left), although the size of the turbulent convective structures is similar.
-In the early FT case, the temperature anomaly in the upper (cold) plume is much greater than the temperature anomaly in the warm plume.
-This excess of cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = 1$ to $\Delta T = \text{Nu}^{-1}$ in the final, equilibrated state.
-Eventually, the supply of warm material from the bottom boundary balances the supply of cold material from the top boundary, and the temperature profile of the simulation stops drifting.
-In this converged state, FT dynamics (bottom right) panel are indistinguishable from TT dynamics (top right).
+In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of an FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
+As shown in the top four panels, we see the expected convective roll solution in both TT simulations (top row) and at early and late times in the FT simulation (bottom row).
+Interestingly, we find highly asymmetrical dynamics at early times in the FT simulation (bottom left), in which the temperature anomaly in the cold plume is much greater than in the warm plume.
+This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
+In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).
 
-When we examine these temperature fields statistically (bottom four panels), we find a similar story.
-Both of the TT simulations (top row) have a mean temperature of 0.5  and some probability of hotter/colder material (mostly contained in the plumes), bounded by the fixed-temperature boundary values.
-At early times (lower left), the FT simulation shows an extreme tail to its PDF that characterizes the cold plume at the upper boundary.
-Furthermore, the early FT simulation has no distinct mode in its temperature PDF, but rather shows that migration of the modal temperature value from hot temperatures (on the right) toward colder temperatures.
-At late times (lower right), the  FT simulation's PDF is indistinguishable from the TT PDF between the cold (left) boudnary and the modal value.
-From the modal value towards warmer temperatures, we find that fixed-flux boundaries are capable of producing more extreme temperature events than fixed temperature boundaries.
-This is explored further in section \ref{sec:asymmetries}.
+In the bottom four panels, we examine these temperature fields statistically by displaying their probability distribution functions (PDFs).
+To create these PDFs, we sample the full simulation temperature field once every simulation freefall time unit over the span of 500 time units.
+We interpolate the (unevenly spaced) vertical Chebyshev gridpoints onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
 
-\begin{figure}[b!]
+We find that this statistical analysis of the simulations tells the same story as the dynamical images shown above.
+The temperature field in both of the TT simulations (top row) is dominated by the modal temperature of 0.5 in the bulk; a smaller fraction of the domain is filled with equal portions of hotter/colder material (mostly contained in the plumes), and the temperature field is rigidly bounded by the fixed-temperature boundary values.
+The story is more complex for the FT simulation.
+At early times (lower left), the FT simulation is characterized by two features: an extreme tail (to the left) that characterizes the cold plume at the upper boundary, and a migrating modal temperature that shifts from the right (hotter) to the left (cooler) as cold material mixes in the interior.
+At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold (left), fixed-tempertaure boundary and the modal value.
+From the modal value towards warmer temperatures, we find that fixed-flux (lower boundary) is capable of producing more extreme temperature events and results in a more extended PDF tail.
+This long tail is explored further in section \ref{sec:asymmetries}.
+
+In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we examine the time evolution of scalar quantities from the FT simulation shown in Fig.~\ref{fig:rbc_evolution_dynamics} (orange lines) and compare it to the TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
+Simulation time is shown in nondimensional freefall units on the x-axis; the latest time displayed for each simulation, $t_{\text{final}}$, is subtracted for direct comparison of the relaxed states.
+Traces of Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ are shown in the top-left panel.
+In the FT simulation, Ra$_{\Delta T}$ relaxes to its final value over thousands of simulation time units, and this final value is the input value of the equivalent TT case.
+In comparison, Ra$_{\partial_z T}$ for the TT case instantaneously reaches its final value, which is the input value for the FT simulation.
+This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of Nu (middle panel) and Pe (bottom panel).
+
+The right panels of Fig.~\ref{fig:rbc_scalar_comparisons} show that the relaxation of Ra$_{\Delta T}$ in FT simulations is akin to a sweep through Ra$_{\Delta T}$ parameter space.
+The orange (Ra$_{\partial_z T} = 4.83 \times 10^{10}$, as on the left) and yellow (Ra$_{\partial_z T} = 2.61 \times 10^{9}$) lines show the evolution of FT simulations, and the arrows give the sense of time in the simulations.
+For comparison, we plot results from TT simulations (purple circles) and the reported results of ref.~\cite{zhu&all2018} (black crosses).
+The purple circles filled with orange and yellow circles are comparison TT simulations for the relaxed states of the FT simulations.
+The top-right panel is a scaling plot for Nu vs.~Ra$_{\Delta T}$ compensated by the best fit reported in ref.~\cite{johnston&doering2009}.
+The bottom-right panel is a scaling plot of Pe vs~Ra$_{\Delta T}$ compensated by the expected scaling \cite{ahlers&all2009}.
+We find that FT simulations carry marginally more flux (higher Nu) and are more turbulent (higher Pe) than comparable TT simulations as they relax through this parameter space.
+These heightened values of Nu and Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
+
+FT simulation dynamics evolve slowly during thermal relaxation, and these images, PDFs, and traces demonstrate the importance of waiting for thermal relaxation to be achieved when conducting an FT simulation.
+
+\begin{figure}[t!]
 \includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
 \caption{ 
-	(left three panels) Time traces of rolling averages over 100 freefall times of an FT (orange) and a TT (purple) simulation.
-	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation.
-	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
-	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
-	The Nu vs Ra.~plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
-	The Re vs Ra.~plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of Pe \cite{ahlers&all2009}.
-	The orange trace shows the time evolution of the FT case from the left panels with the arrows showing the sense of time.
+	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) are shown.
+	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
+	We display evolutionary traces of Ra (top, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
+	(Right two panels) Compensated scaling plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
+	Nu vs.~Ra is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, the best-fit reported by ref.~\cite{johnston&doering2009}.
+	Re vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
+	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
 	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
-	Purple circles show our measured values of Nu in TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
+	Purple circles are the measured values of Nu and Pe in our TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
 	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
@@
 
-In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we display the time evolution of scalar quantities from the FT simulation shown in Fig.~\ref{fig:rbc_evolution_dynamics} (orange lines) and compare it to the TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
-Simulation time in nondimensional freefall units is shown on the x-axis; each simulation's end time, $t_{\text{final}}$, is subtracted so that the final evolved states can be more directly compared, and so that $x = 0$ corresponds to the end of the simulation.
-The lines shown are rolling averages taken over 100 freefall time units.
-In the top-left panel, the evolution of Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ is shown in each simulation.
-In the FT simulation, Ra$_{\Delta T}$ evolves towards its final value over thousands of simulation time units; this final value corresponds to the input value of the equivalent TT case.
-In comparison, Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
-This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of Nu (middle panel) and Pe (bottom panel).
-
-The right panels of Fig.~\ref{fig:rbc_scalar_comparisons} show that the evolution of Ra$_{\Delta T}$ in FT simulations is akin to a sweep through Ra$_{\Delta T}$ parameter space.
-The orange lines show the evolution of the Ra$_{\partial_z T} = 4.83 \times 10^{10}$ case shown on the left, and the yellow lines show the evolution of a Ra$_{\partial_z T} = 2.61 \times 10^{9}$.
-The arrows give the sense of time in the simulations.
-For comparison, we have computed TT simulations throughout this parameter space (purple circles) and we have overplotted the reported results of ref.~\cite{zhu&all2018}.
-The purple circles filled with orange and yellow circles respectively show the comparison TT simulations for the evolved FT simulations.
-In the upper panel, we show a compensated scaling plot for Nu vs.~Ra$_{\Delta T}$, compensated by the best fit reported in ref.~\cite{johnston&doering2009}.
-The lower panel is a compensated scaling plot of Pe vs~Ra$_{\Delta T}$, compensated by the expected scaling \cite{ahlers&all2009}.
-We find that the FT simulations are more turbulent (higher Pe) and carry marginally more flux (higher Nu) than comparable TT simulations as they sweep through this parameter space.
-The dynamics in FT simulations evolve slowly during the rundown, and these traces demonstrate the importance of waiting until an FT simulation has reached its equilibrated state before sampling and analyzing the nonlinear convective state.
-Furthermore, the heightened values of Nu and especially Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
-
 \subsection{Evolved Structure}
+\vspace{-0.5cm}
 \begin{figure}
@@
 \caption{ 
-	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
-	The boundary layer regions are separated from the bulk by thin vertical lines.
-	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
+	(Left three panels) We compare time- and horizontally-averaged profiles from an FT (orange) and TT (purple) simulation at Ra$_{\Delta T} = 10^{9}$.
+	Shown are the (top) temperature, (middle) temperature in upflows (solid) and downflows (dashed), and (bottom) enthalpy (solid) and conductive (dashed) fluxes.
+	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
+	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
 	The insets show the \% difference between the FT and TT solutions.
-	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.
+	There are slight (a few \%) differences between the two cases near the bottom boundary, but otherwise the two cases are nearly the same to within $\sim 1$\%.
 \label{fig:rbc_1D_profiles} }
+\vspace{0.5cm}
 \end{figure}
 
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally averaged, profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Time averages are taken over 500 nondimensional freefall time units, sampled once every 0.1 time units.
-The left three panels show (top) the mean temperature profile, (middle) the mean temperature profile in the upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$).
-Most of the interesting structure of these profiles is in the boundary layers, located between the edges of the plots and the thin vertical black lines.
-Zoomed in views of the bottom and top boundary layers are respectively shown in the middle and right columns.
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
+Time averages are taken over 500 nondimensional freefall time units for the TT case and over 2000 nondimensional freefall time units for the FT case, sampled once every 0.1 time units (the difference in averaging window is explained in Sec.~\ref{sec:timescales}).
+In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
+Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
+Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
 Inset panels show the percentage difference between the FT and TT solutions.
-In the case of the flux panels (bottom row), we do not show the \% difference in the conductive flux; the two cases agree to $\sim$1\% in the boundary layers, and the maximum deviation away from zero in the interior is less than 0.01.
+In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
+The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the largest deviations away from zero in the interior are O(0.01) in the plotted units.
 
-We find good ($\sim 1\%$) agreement between the temperature profiles throughout the full depth of the domain.
-When we examine the temperature in upflows and downflows respectively, we find similarly good agreement near the upper (fixed temperature) boundary, but differences of a few percent between the FT and TT case right near the bottom boundary layer.
-Specifically, we find that FT (upflows/downflows) are slightly (warmer/cooler) than their TT counterparts at the hot, bottom boundary.
+We find good ($\sim 1\%$) agreement between the FT and TT temperature profiles and enthalpy fluxes throughout the full depth of the domain, with slightly larger differences near the bottom boundary where the boundary conditions differ.
+When we split the profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
 These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
-While there are very small differences between the condcutive fluxes, we do find differences between the convective fluxes of up to $\sim 3\%$ at most.
-We anticipate that these differences are merely a result of a small sample of convective dynamics in the FT case and do not point to appreciably differences in the heat transport.
 
 \subsection{TT-to-FT: Rapidly equilibrated FT simulations}
+\label{sec:tt-to-ft}
 
@@
 \caption{ 
-	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
-	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
-	(top left panel) The evolution of Ra over time is shown; Ra$_{\partial_z T}/(4.83\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
-	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
+	(Left three panels) Time traces of scalar quantities, which have been averaged over a rolling time window of 25 simulation time units, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
+	The time of the change of boundary conditions is denoted by the vertical black line.
+	(Top panel) The evolution of Ra is shown; Ra$_{\partial_z T}/(4.83\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
+	The mean value of temperature gradient (middle panel) and temperature (bottom panel) at the bottom boundary are also shown.
 	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\text{Nu}$.
 	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
-	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown (the grey shaded region in the left three panels).
+	(right four panels) PDFs are shown which compare the dynamics during the grey time window in the left panels (black PDFs, TT-to-FT) to dynamics from a comparable time window in the FT case from Fig.~\ref{fig:rbc_scalar_comparisons}.
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
-	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}; green PDF) to the PDF of the TT-to-FT case (grey PDF).
 \label{fig:rbc_restart_description} }
+\vspace{-0.25cm}
 \end{figure}
 
-The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} between the FT and TT simulations suggests that, in a volume-averaged sense, there is a comparable TT experiment for each FT experiment.
-It should therefore be possible to take advantage of the fast evolution of TT simulations to achieve rapidly equilibrated FT simulations, which would save a great deal of computing time in solving FT simulations.
-The rundown in FT simulations is very costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state, and (2) thousands of freefall times must pass during relaxation.
-For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, with a modest Ra$_{\Delta T} = 10^9$, the full evolution of the FT simulation costs $4.75 \times 10^5$ cpu-hours, while the TT equivalent case costs $5.58 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
+Achieving thermal relaxation in pure FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
+For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
+In the previous sections, we have shown that relaxed FT and TT simulations are very similar.
+It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.
 
@@
 \end{enumerate}
-At the end of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, we change the boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$ and restart the simulation using the above procedure.
-In the left panels of Fig.~\ref{fig:rbc_restart_description}, we show the temporal behavior of Ra (top panel), the flux at the bottom boundary (middle panel), and the temperature difference between the top and bottom boundaries (bottom panel).
-The change from TT to FT boundaries is shown by the thin vertical line.
-Unlike in the FT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no long thermal rundown in the FT state, due to the rapid relaxation achieved during the TT portion of the simulation.
+We show this prcedure in practice in Fig.~\ref{fig:rbc_restart_description}.
+In the left three panels, we display the temporal behavior of (top) Ra, (middle) the flux at the bottom boundary, and (bottom) the temperature difference between the top and bottom boundaries.
+We take the full evolution of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, then change its boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$ and restart the simulation using the above procedure.
+The change from TT to FT boundaries occurs at the time denoted by the thin vertical line.
+Unlike in the FT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no thermal rundown in the FT state, due to the rapid relaxation achieved during the TT portion of the simulation.
 
-In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare probability distribution functions (PDFs) of flow fields in this TT-to-FT simulation and the comparable FT simulation shown in Fig.~\ref{fig:rbc_restart_description}.
-To create these PDFs, we sample the full simulation flow field once every simulation freefall time unit over the final 500 time units of each simulation (e.g., the grey shaded region in the left panels of Fig.~\ref{fig:rbc_restart_description}).
-We interpolate the (unevenly spaced) vertical Chebyshev gridpoints onto an evenly spaced grid before histogramming the flow values.
+In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable FT simulation which we timestepped through thermal relaxation.
 Shown are PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
@@
 The PDFs are qualitatively similar, and there is generally good agreement between the moments of the PDFs.
-The FT simulation here is not perfectly converged to many decimal places; the few \% difference between the modal values of the temperature PDFs is due to this lack of perfect convergence, and given infinite time the peak of the green FT PDF would shift left.
 The remaining discrepancies between the PDFs are small and seem to primarily be due to the randomness of the flows in the time windows over which we sampled the simulations.
 
-\begin{table}[t!]
+\begin{table}[b!]
+\vspace{-0.5cm}
 \caption{ 
@@
 }
+\vspace{-0.25cm}
 \setlength{\tabcolsep}{12pt}
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{c c c c c c}
+\begin{tabular}{c c c c c c}
 \hline																	
@@
 \hline
-$T$				&	FT			&		$1.11 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.179		&	26.5 \\
+$T$				&	FT			&		$1.03 \times 10^{-2}$	&	$1.49 \times 10^{-3}$	&	0.656		&	27.0 \\
 				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
 \hline
-$\omega^2$		&	FT			&		$20.2$					&	$9.66$					&	71.4		&	$9.65\times 10^3$ \\
-				&	TT-to-FT	&		$28.6$					&	$10.0$					&	96.8		&	$1.97 \times 10^4$ \\
+$\omega^2$		&	FT			&		$16.7$					&	$10.3$					&	96.2		&	$2.72 \times 10^4$ \\
+				&	TT-to-FT	&		$11.7$					&	$10.6$					&	86.0		&	$1.63 \times 10^4$ \\
 \hline
-$wT$			&	FT			&		$4.51 \times 10^{-6}$	&	$5.43 \times 10^{-4}$	&	0.0437	&	$2.99$ \\
-				&	TT-to-FT	&		$4.40 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0114	&	$3.07$ \\
+$wT$			&	FT			&		$4.50 \times 10^{-6}$	&	$4.87 \times 10^{-4}$	&	0.0133	&	$3.06$ \\
+				&	TT-to-FT	&		$4.47 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0110	&	$3.06$ \\
 \hline
-$w$				&	FT			&		$1.56 \times 10^{-5}$	&	$4.86 \times 10^{-2}$	&	0.0133	&	$2.92$ \\
-				&	TT-to-FT	&		$-1.74 \times 10^{-5}$	&	$4.82 \times 10^{-2}$	&	-0.0174	&	$3.02$ \\
+$w$				&	FT			&		$3.62 \times 10^{-6}$	&	$4.70 \times 10^{-2}$	&	-0.0211	&	$3.00$ \\
+				&	TT-to-FT	&		$4.22 \times 10^{-6}$	&	$4.82 \times 10^{-2}$	&	-0.0187	&	$3.02$ \\
 \hline																	
-\end{tabularx}
+\end{tabular}
 \end{center}
@@
 
-We note briefly that this mechanism that we describe here is not the only mechanism for accelerating the thermal relaxation of an FT simulation.
+We note briefly that this TT-to-FT mechanism is only one of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
-We note however that the TT-to-FT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified \RB convection setup that we are aware of.
+We note however that the TT-to-FT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified RBC setup that we are aware of.
 The successful degree with which this mechanism reproduces the evolved dynamics suggests that thermal relaxation occurs in two parts:
@@
 \end{enumerate}
-The rapid evolution of TT runs, whose energy reservoir does not change between the initial and final state, suggests that experimental restratification occurs rapidly in RBC. 
+The thermal energy reservoir of TT simulations does not change between the initial and final state.
+The rapid relaxation of TT simulations therefore suggests that experimental restratification occurs rapidly in RBC. 
 The long rundown of FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
-Put differently, the classic \RB setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
+Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
 
@@
 As noted above in our TT-to-FT procedure, the velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
-This implies that every nondimensional freefall time in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
-This is on display in Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher frequency in the TT portion of the simulation than in the FT portion.
-However, we note briefly that in FT simulations, Ra$_{\partial_z T}$ is the input Ra, and it is larger than Ra$_{\Delta T}$ by a factor of $\text{Nu}$.
-Thus, the \emph{thermal diffusion timescale}, which scales like $\sqrt{\text{Ra}_{\text{input}}}$, is also larger in FT simulations by a factor of $\sqrt{\text{Nu}}$.
-This means that one convective overturn timescale occurs over the same fraction of a nondimensional \emph{diffusion} timescale regardless of boundary conditions or temperature nondimensionalization.
-These results suggest that comparisons of systems which are nondimensionalized on the flux and the temperature may be more straightforward in a thermal diffusion nondimensionalization \cite{goluskin2015} than the freefall nondimensionalization we have used throughout this work.
+As a result, every simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
+This is on display in the left panels of Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher temporal frequency in the TT portion of the simulation than in the FT portion.
+
+These results imply that the true nondimensional freefall time of an FT simulation is $\tau_{\text{ff}} = \sqrt{\text{Nu}}$ in simulation freefall time units.
+However, we note that Ra$_{\partial_z T}$ is the input value of Ra for an FT simulations, and that Ra$_{\partial_z T}/$Ra$_{\Delta T} = \text{Nu}$.
+The thermal diffusion timescale, $\tau_{\text{th}}$, which scales like $\tau_{\text{th}} \propto \sqrt{\text{Ra}_{\text{input}}}$, is also larger in an FT simulation than in a comparable TT simulation by a factor of $\sqrt{\text{Nu}}$.
+One convective freefall timescale therefore occurs over the same fraction of a diffusion timescale regardless of boundary conditions or temperature nondimensionalization, $\tau_{\text{ff}}/\tau_{\text{th}} \neq f(\text{Nu})$.
+These findings suggest that comparisons of systems which are nondimensionalized on the flux and the temperature may be more straightforward in a thermal diffusion nondimensionalization \cite{goluskin2016} than the freefall nondimensionalization we have used throughout this work.
 
@@
 \caption{ 
-	(left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
+	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
 	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
-	(middle panel) A snapshot of the temperature anomaly in the FT simulation.
-	The black outline boxes around the roots of the plumes are zoomed in in the right two panels.
-	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes near the boundary, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
+	(Middle panel) A snapshot of the temperature anomaly in the FT simulation.
+	Zoomed in views of the regions outlined in black boxes are shown in the right two panels.
+	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
 \label{fig:rbc_dynamics_asymmetries} }
@@
 \label{sec:rotating_results}
-\begin{figure}
-\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
-\caption{ 
-	(left three panels) Time traces of rolling averages over 50 freefall times of a rotating FT simulation (green) and a TT (orange) simulation.
-	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
-	(middle left panel) Ro evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally constrained state to a heavily constrained state, while the TT simulation is in this latter state through its full evolution.
-	(bottom left panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
-	(right upper panel) Parameter space plots of Nu vs.~Ra$_{\Delta T}$.
-	Circlular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
-	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
-	Data from our FT experiment are shown as a thick orange line with a cyan interior, and the corresponding TT experiment's average is shown as a purple star with a cyan interior.
-	Some comparison TT simulations through this parameter space are shown as purple circles with a cyan interior.
-	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
-	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
-	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
-	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
-	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
-	The three vertical black lines in the left panels signify the times at which this snapshots are taken.
-\label{fig:rotating_panels} }
-\end{figure}
 
@@
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
-Even in the presence of strong rotation, the TT case's fluxes immediately equilibrate, but the FT case takes thousands of freefall times to achieve thermal relaxation.
-In the middle panel, we show the evolution of Ro; the evolved flows in both simulations exhibit rotationally constrained dynamics with Ro $\,\approx 0.1$, the flows in the FT simulation initially experience weak rotational influence (Ro $\,\approx 1$).
+Even in the presence of strong rotation, the TT immediately equilibrates, but the FT case takes thousands of freefall times to achieve thermal relaxation.
+In the middle panel, we show the evolution of Ro; the evolved flows in both simulations exhibit rotationally constrained dynamics with Ro $\,\approx 0.1$, but the flows in the FT simulation relax to this state from an initially unconstrained state (Ro $\,\approx 1$).
+This implies that the thermal relaxation process can walk through the parameter space of flow balances (e.g., the balance between Inertial and Coriolis forces) in addition to the Ra$_{\Delta T}$ parameter space.
 In the bottom panel, we display the evolution of Pe over time.
 Strangely, the peak value of Pe occurs a few hundred freefall times after the convective transient.
-After achieving this peak value, Pe monotonically decreases toward its equilibrium state.
+After achieving this peak value, Pe monotonically decreases toward its relaxed state.
 
-In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot a parameter space cut of Nu vs.~Ra for rotating simulations.
-We have evolved select TT cases, and their values are plotted as cyan circles with purple outlines (where here, the cyan shows the value of Ek for the simulations, per the colorbar).
-The evolution of the FT case in the left panels is shown as a thick orange line with a cyan interior, and the corresponding TT case is shown as a cyan star with a purple outline.
+In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot Nu vs.~Ra for rotating simulations.
+Select TT cases are plotted as cyan circles with purple outlines (where the cyan color denotes the value of Ek$\,=\,10^{-6}$ according to the colorbar).
+The evolution of the FT case in the left panels is shown as a thick orange line with a cyan interior and the black arrows show the direction of time.
+The TT case that corresponds to the FT case is a purple star with a cyan interior.
 We have additionally included some literature data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
@@
 
-We suspect that the evolution of the dominant flow structures over time explains the strange behavior of Pe in the bottom left panel.
+We suspect that the strange behavior of Pe in the bottom left panel can be explained by the evolution of the dominant flow structures over time.
 At early times, the initially large value of Ra$_{\Delta T}$ in the FT case drives the displayed dominant LSV.
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
+\caption{ 
+	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) are shown.
+	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
+	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
+	(Middle panel) Ro evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
+	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
+	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
+	Circlular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
+	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
+	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
+	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
+	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
+	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
+	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
+	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
+	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
+	The three vertical black lines in the left panels signify the times at which this snapshots are taken.
+\label{fig:rotating_panels} }
+\end{figure}
+
 %%%%%%%%%%%%
@@
 \label{sec:discussion}
-In short, we find that FT experiments experience a long thermal relaxation which is not experienced by TT simulations and, to first order, do not introduce important asymmetries into the solution.
+In short, we find that FT simulations experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
 
@@
 We find that the long relaxation of FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations due to the lack of evolution of the average domain temperature.
-The rapid evolution of our TT simulations suggests that RBC restratifies itself nearly instantaneously.
+The rapid evolution of our TT simulations suggests that RBC restratifies itself instantaneously.
 \item Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading.
-Dynamics during the relaxation are in a more turbulent state than in the evolved state, and can even feel different flow balances in the equation of motion (as quantified by e.g., the Rossby number).
+Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
 \item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
@@
 We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
+We'd also like to thank Jeff Oishi, who encouraged us to pursue the differences between early and late FT dynamics and who graciously saved the reader from reading ``mixedFT'' (instead of FT) and ``fixedT'' (instead of TT).
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
@@
 \label{app:table}
+Input and output information for the simulations in this work are shown in Table~\ref{table:simulations}.
+The code used to run these simulations can be found online in the repository of supplemental materials \cite{anders&all2020a_supp}.
 
@@
 	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
-	The ``Nu comp'' values are comparison Nusselt number values reported in \cite{zhu&all2018}.
-	Values of Nu and Re are the sample mean; the standard deviation of the sample mean is shown for Nu measurements, and is smaller than the number of significant figures reported for Re measurements.
+	Input quantities are the boundary conditions (BCs), Rayleigh number (Ra), coefficient resolution (nz$\times$nx$\times$ny), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
+	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
+	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units.
+	Reported uncertainties are the standard deviation of the sample mean; when the uncertainty is not reported, it is smaller than the number of reported digits.
+	The ``Nu comp'' values are comparison Nu values reported in ref.~\cite{zhu&all2018}.
 	Resolutions marked by a $*$ show the initial, highest resolution utilized in the simulation.
@@
 	The rotating FT case's resolution was reduced to $256\times384^2$ about one hundred freefall time units after transient, and was further reduced to $128\times384^2$ about $3.3\times 10^3$ freefall times after transient.
-	``TT-to-FT'' simulations are FT simulations which use an evolved TT simulation as initial conditions, and their cpu-hour cost does not include the cost of the TT transient.
 }
 \setlength{\tabcolsep}{8pt}
-\label{table:speed}
+\label{table:simulations}
 \begin{center}
-\begin{tabularx}{\textwidth}{c c c c c c c c}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{c c c c c c c c c}
 \hline																	
-BCs	&	Ra	&	nz$\times$nx$\times$ny	&	cpu-hours &	Nu	&	Nu comp	&	Pe  & Ro \\
+BCs	&	Ra	&	nz$\times$nx$\times$ny	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline
-TT			&	$1.00 \times 10^8$		&	512x1024	&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
-FT			&	$2.61 \times 10^9$		&	1024x2048	&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
-TT-to-FT	&	$2.61 \times 10^9$		&	512x1024	&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
-TT			&	$2.15 \times 10^8$		&	512x1024	&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
-TT			&	$4.64 \times 10^8$		&	1024x2048	&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
-TT			&	$1.00 \times 10^9$		&	1024x2048	&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
-FT			&	$4.83 \times 10^{10}$	&	2048x4096*	&	$4.75 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
-TT-to-FT	&	$4.83 \times 10^{10}$	&	1024x2048	&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
-TT			&	$2.15 \times 10^9$		&	1024x2048	&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
-TT			&	$4.64 \times 10^9$		&	1536x3072	&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
-TT			&	$1.00 \times 10^{10}$	&	2048x4096	&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
-TT-to-FT	&	$9.51 \times 10^{11}$	&	2048x4096	&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
+TT			&	$1.00 \times 10^8$		&	512x1024	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
+FT			&	$2.61 \times 10^9$		&	1024x2048	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
+TT-to-FT	&	$2.61 \times 10^9$		&	512x1024	&	1000		&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
+TT			&	$2.15 \times 10^8$		&	512x1024	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
+TT			&	$4.64 \times 10^8$		&	1024x2048	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
+TT			&	$1.00 \times 10^9$		&	1024x2048	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
+FT			&	$4.83 \times 10^{10}$	&	2048x4096*	&	16230		&	$5.36 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
+TT-to-FT	&	$4.83 \times 10^{10}$	&	1024x2048	&	1000		&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
+TT			&	$2.15 \times 10^9$		&	1024x2048	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
+TT			&	$4.64 \times 10^9$		&	1536x3072	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
+TT			&	$1.00 \times 10^{10}$	&	2048x4096	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
+TT-to-FT	&	$9.51 \times 10^{11}$	&	2048x4096	&	1000		&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
 \hline																	
@@
 \hline																	
-TT	&	$1.38 \times 10^9$		&	128$\times$64$^2$	&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
-TT	&	$1.83 \times 10^9$		&	128$\times$64$^2$	&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
-TT	&	$2.29 \times 10^9$		&	128$^3$				&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
-TT	&	$2.75 \times 10^9$		&	128$^3$				&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
-FT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
-TT	&	$3.67 \times 10^9$		&	128$^3$				&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
-TT	&	$4.58 \times 10^9$		&	128$^3$				&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
-TT	&	$5.50 \times 10^9$		&	192$^3$				&	---					&	$22.6$			&	---		&	$6.36 \times 10^3$  & $(2.95 \pm 0.11) \times 10^{-1}$ \\
-TT	&	$6.42 \times 10^9$		&	192$^3$				&	---					&	$29.3$			&	---		&	$7.84 \times 10^3$  & $(3.64 \pm 0.15) \times 10^{-1}$ \\
-TT	&	$7.33 \times 10^9$		&	256$^3$				&	---					&	$36.1$			&	---		&	$9.11 \times 10^3$  & $(4.31 \pm 0.16) \times 10^{-1}$ \\
-TT	&	$8.25 \times 10^9$		&	256$^3$				&	---					&	$43.0$			&	---		&	$*1.03 \times 10^4$ & $(4.98 \pm 0.21) \times 10^{-1}$ \\
-TT	&	$9.17 \times 10^9$		&	256$^3$				&	---					&	$48.9$			&	---		&	$*1.15 \times 10^4$ & $(5.60 \pm 0.23) \times 10^{-1}$ \\
-TT	&	$1.834 \times 10^{10}$	&	256$^3$				&	---					&	---				&	---		&	--- & --- \\
+TT	&	$1.38 \times 10^9$		&	128$\times$64$^2$	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
+TT	&	$1.83 \times 10^9$		&	128$\times$64$^2$	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
+TT	&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
+TT	&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
+FT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	13950		&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
+TT	&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
+TT	&	$4.58 \times 10^9$		&	128$^3$				&	2530		&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
+TT	&	$5.50 \times 10^9$		&	192$^3$				&	2402		&	$7.35 \times 10^4$	&	$22.8$			&	---		&	$6.38 \times 10^3$  & $(2.96 \pm 0.11) \times 10^{-1}$ \\
+TT	&	$6.42 \times 10^9$		&	192$^3$				&	2226		&	$7.35 \times 10^4$	&	$29.5$			&	---		&	$7.86 \times 10^3$  & $(3.65 \pm 0.16) \times 10^{-1}$ \\
+TT	&	$7.33 \times 10^9$		&	256$^3$				&	1147		&	$1.47 \times 10^5$	&	$36.2$			&	---		&	$9.52 \times 10^3$  & $(4.33 \pm 0.17) \times 10^{-1}$ \\
+TT	&	$8.25 \times 10^9$		&	256$^3$				&	1079		&	$1.47 \times 10^5$	&	$43.0$			&	---		&	$1.10 \times 10^4$  & $(5.01 \pm 0.20) \times 10^{-1}$ \\
+TT	&	$9.17 \times 10^9$		&	256$^3$				&	1030		&	$1.47 \times 10^5$	&	$48.9$			&	---		&	$1.24 \times 10^4$  & $(5.63 \pm 0.26) \times 10^{-1}$ \\
+TT	&	$1.834 \times 10^{10}$	&	256$^3$				&	971.9		&	$1.84 \times 10^5$	&	$111$			&	---		&	$2.21 \times 10^4$  & $1.18 \pm 0.09$ \\
 \hline																	
-\end{tabularx}
+\end{tabular}
+}
 \end{center}

### 2020-02-25 figures_and_data/rbc_1D_profiles.py

@@ -197,8 +197,8 @@ for ax, loc in [(axl, 'upper right'), (axr, 'lower left')]:
     if ax is axl: 
         axins.set_ylabel('% diff', fontsize=8, labelpad=0)
         axins_l.append(axins)
-        axins.set_ylim(0, 2)
-        axins.set_yticks((0, 1, 2))
+        axins.set_ylim(0, 3)
+        axins.set_yticks((0, 1.5, 3))
 #        axins.set_ylim(0, 0.5)
 #        axins.set_yticks((0, 0.25, 0.5))
     elif ax is axr: 
@@ -256,8 +256,8 @@ for ax, loc in [(axl, 'upper right'), (axr, 'lower left')]:
         this_err = err[(this_z < xlim[-1])*(this_z > xlim[0])]
         bounds = this_err.min()/2, this_err.max()*2
         if ax is axl:
-            axins.set_ylim(0, 4)#this_err.min()/2, this_err.max()*2)
-            axins.set_yticks((0, 2, 4))
+            axins.set_ylim(0, 3)#this_err.min()/2, this_err.max()*2)
+            axins.set_yticks((0, 1.5, 3))
         else:
             axins.set_ylim(0, 2)#this_err.min()/2, this_err.max()*2)
             axins.set_yticks((0, 1, 2))
@@ -294,7 +294,7 @@ for ax, loc in [(axl, 'center right'), (axr, 'center left')]:
     elif ax is axr: 
         axins_r.append(axins)
 
-    for k, ls in [(k1, '-')]:
+    for k, ls in [(k2, '-')]:
         p_mixed.set_scales(len(mixed_profs[mk][k][0,:])/max_nz)
         p_fixed.set_scales(len(fixed_profs[fk][k][0,:])/max_nz)
         p_mixed['g'] = mixed_profs[mk][k][0,:]/dT**(3/2)/flux_scale
@@ -304,6 +304,7 @@ for ax, loc in [(axl, 'center right'), (axr, 'center left')]:
 
         this_z = z
         err = 100*np.abs((p_fixed['g'] - p_mixed['g'])/p_fixed['g'])
+#        print(np.max(np.abs(p_fixed['g'][(this_z <= 0.45)*(this_z >= -0.45)])))
         z_bounds = (this_z <= xlim[-1])*(this_z >= xlim[0])
         good = (p_fixed['g'][z_bounds] >  0.1)
 
[…]

### 2020-02-25 figures_and_data/rbc_dynamics_asymmetries.py

@@ -117,8 +117,8 @@ dT = np.mean(delta_T_mixed[-5000:])
 plt.plot(mx/dT, mp*dT, label='FT', c=mColor)
 plt.plot(fx, fp, label='TT', c=fColor)
 plt.yscale('log')
-ax.set_ylabel(r'$P(T/\Delta T)$', labelpad=-1)
-ax.set_xlabel(r'$T/\Delta T$', labelpad=-1)
+ax.set_ylabel(r'$P(T/\Delta T)$', labelpad=0)
+ax.set_xlabel(r'$T/\Delta T$', labelpad=0)
 ax.legend(loc='upper right', frameon=False, fontsize=7, markerfirst=False, borderpad=0.1)
 
 ax.fill_between(mx/dT, 1e-16, mp*dT, color=mColor, alpha=0.5)
@@ -166,16 +166,17 @@ c = ax.pcolormesh(xx_b, zz_b, T_field['g'], cmap='RdBu_r', rasterized=True, vmin
 top_plume_bounds = [(-0.72, -0.65, -0.65, -0.72, -0.72),  (0.5, 0.5, 0.45, 0.45, 0.5)]
 bot_plume_bounds = [(0.53, 0.6, 0.6, 0.53, 0.53), (-0.45, -0.45, -0.5, -0.5, -0.45)]
 for i in range(4):
-    plt.plot(top_plume_bounds[0][i:i+2], top_plume_bounds[1][i:i+2], c='k', lw=0.5)
-    plt.plot(bot_plume_bounds[0][i:i+2], bot_plume_bounds[1][i:i+2], c='k', lw=0.5)
+    plt.plot(top_plume_bounds[0][i:i+2], top_plume_bounds[1][i:i+2], c='k', lw=1)
+    plt.plot(bot_plume_bounds[0][i:i+2], bot_plume_bounds[1][i:i+2], c='k', lw=1)
 
 ax.set_xlim(-1, 1)
 ax.set_ylim(-0.5, 0.5)
 ax.set_ylabel('z', labelpad=-1)
 ax.set_xlabel('x', labelpad=-1)
 
-ax.text(0.02, 0.02, 'Fixed Flux (bottom)', transform = ax.transAxes)
-ax.text(0.51, 0.92, 'Fixed Temp (top)', transform = ax.transAxes)
+bbox_props = dict(boxstyle="round", fc="w", ec="0.5", alpha=0.75)
[…]

### 2020-02-25 figures_and_data/rbc_evolution_dynamics.py

@@ -16,6 +16,7 @@ import h5py
 
 import pandas as pd
 import dedalus.public as de
+from scipy.interpolate import interp1d
 
 mColor = 'darkorange'
 fColor = 'indigo'
@@ -102,17 +103,17 @@ fke = '{:.4e}'.format(1.00e10)
 fkl = '{:.4e}'.format(1.00e9)
 
 # Set up figure subplots
-fig = plt.figure(figsize=(7.5, 7))
+fig = plt.figure(figsize=(7.5, 8))
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [( (50  ,   0),          250,    500),
-            ( (300 ,   0),          250,    500),
-            ( (650 ,   0),          175,    500),
-            ( (50  , 500),          250,    500),
-            ( (300 , 500),          250,    500),
-            ( (650 , 500),          175,    500),
-            ( (825 , 0),            175,    500),
-            ( (825 , 500),          175,    500),
+subplots = [( (50  ,   0),          225,    500),
+            ( (275 ,   0),          225,    500),
+            ( (600 ,   0),          200,    500),
+            ( (50  , 500),          225,    500),
+            ( (275 , 500),          225,    500),
+            ( (600 , 500),          200,    500),
+            ( (800 , 0),            200,    500),
+            ( (800 , 500),          200,    500),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 
@@ -194,9 +195,27 @@ axtt = axs[2]
 axft = axs[6]
 mx, mp, mdx = [mixed_data[mke]['T'][k] for k in ['xs', 'pdf', 'dx']]
 fx, fp, fdx = [fixed_data[fke]['T'][k] for k in ['xs', 'pdf', 'dx']]
+fdx = float(fdx)
+mdx = float(mdx)
 
[…]

### 2020-02-25 figures_and_data/rbc_restart_description.py

@@ -199,13 +199,18 @@ for i, field in enumerate(keys):
         mcdf[j+1] = mcdf[j] + mp[j]*mdx
     for j in range(len(rp)-1):
         rcdf[j+1] = rcdf[j] + rp[j]*rdx
-    good_m = (mcdf > 0.0001)*(mcdf < 0.9999)*(mp > 0)
-    good_r = (rcdf > 0.0001)*(rcdf < 0.9999)*(rp > 0)
+    if i == 1:
+        good_m = (mcdf < 0.9999)*(mp > 0)
+        good_r = (rcdf < 0.9999)*(rp > 0)
+    else:
+        good_m = (mcdf > 0.0001)*(mcdf < 0.9999)*(mp > 0)
+        good_r = (rcdf > 0.0001)*(rcdf < 0.9999)*(rp > 0)
 
-    ax.fill_between(mx, 1e-16, mp, color='olivedrab', alpha=0.5)
-    ax.fill_between(rx, 1e-16, rp, color='black', alpha=0.5)
-    ax.plot(mx, mp, label='FT', color='olivedrab')
-    ax.plot(rx, rp, label='TT-to-FT', color='black')
+    factor = 1
+    ax.fill_between(mx, 1e-16, factor*mp, color='olivedrab', alpha=0.5)
+    ax.fill_between(rx, 1e-16, factor*rp, color='black', alpha=0.5)
+    ax.plot(mx, factor*mp, label='FT', color='olivedrab')
+    ax.plot(rx, factor*rp, label='TT-to-FT', color='black')
     ax.set_yscale('log')
     ax.set_xlabel(labels[i])
 
@@ -218,7 +223,7 @@ for i, field in enumerate(keys):
     min_y_bounds = np.min((np.min(mp[good_m]), np.min(rp[good_r])))
 
     ax.set_xlim(min_x_bounds, max_x_bounds)
-    ax.set_ylim(min_y_bounds, 1.5*np.max((mp[good_m].max(), rp[good_r].max())))
+    ax.set_ylim(factor*min_y_bounds, factor*1.5*np.max((mp[good_m].max(), rp[good_r].max())))
     if field == 'enstrophy':
         ax.legend(loc='best', frameon=False)
 

### 2020-02-25 figures_and_data/rbc_scalar_comparisons.py

@@ -79,6 +79,10 @@ restarted_data = read_data(restarted_ras, restarted_dirs)
 avg_window = 100 #time units
 fixed_trace = fixed_data['{:.4e}'.format(1.00e9)]
 mixed_trace = mixed_data['{:.4e}'.format(4.83e10)]
+
+good = mixed_trace['sim_time'] <= 1e4
+for k in mixed_trace:
+    mixed_trace[k] = mixed_trace[k][good]
 dff = pd.DataFrame(data=fixed_trace)
 rolledf = dff.rolling(window=avg_window*10, min_periods=avg_window*10).mean()
 dfm = pd.DataFrame(data=mixed_trace)

### 2020-02-25 figures_and_data/rotating_panels.py

@@ -29,7 +29,7 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
-            numbered_dirs  = [(r, int(r.split('run')[-1].split('_')[0])) for r in sub_runs]
+            numbered_dirs  = [(r, int(r.split('run')[-1].split('/')[0].split('_')[0])) for r in sub_runs]
             sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
@@ -105,13 +105,6 @@ cax = plt.subplot(gs.new_subplotspec((950, 580), 50, 280))
 caxEk = plt.subplot(gs.new_subplotspec((70, 560), 30, 440))
 
 
-#Show times of dynamics panels
-for i in range(3):
-    axs[i].axvline(100   - mixed_trace['sim_time'][-1], c='k', lw=0.5)
-    axs[i].axvline(5380  - mixed_trace['sim_time'][-1], c='k', lw=0.5)
-    axs[i].axvline(13215 - mixed_trace['sim_time'][-1], c='k', lw=0.5)
-
-
 #Panel 1, Ra evolution
 plt.sca(axs[0])
 ax = axs[0]
@@ -125,7 +118,7 @@ plt.axhline(np.mean(mixed_trace['ra_flux'])/2.75e9, color=mColor, lw=1, ls='-.')
 plt.axhline(np.mean(fixed_trace['ra_temp'])/2.75e9, color=fColor, lw=1)
 ax.plot(rolledm['sim_time']-mixed_trace['sim_time'][-1], rolledm['ra_temp']/2.75e9, color=mColor, lw=2, label='')
 ax.plot(rolledf['sim_time']-fixed_trace['sim_time'][-1], rolledf['ra_flux']/2.75e9, color=fColor, lw=1, ls='-.', label='')
-ax.legend(loc='center', frameon=True, fontsize=7, ncol=2)
+ax.legend(loc='center right', frameon=True, fontsize=7, ncol=2)
[…]

### 2020-02-27 tex/mixedft_evolution_ms.tex
near-final ms changes

@@
 
-\title{Thermal relaxation is important in convective simulations: \\
-on the time evolution of flows and how to avoid unnecessary thermal rundown}
+\title{Convective dynamics with mixed temperature boundary conditions: \\
+why thermal relaxation matters and how to accelerate it}
 
@@
 Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection (RBC) to understand how mixed (``FT'') thermal boundary conditions, which are often used in astrophysics, change the nature of the convective solution compared to the traditional choice of fixing the temperature at the top and bottom of the domain (``TT'').
-We find that FT boundaries impose a long thermal rundown on convective systems which is not experienced by experiments with TT boundaries.
-In the evolved state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries, and the fast evolution of TT simulations can be taken advantage of to rapidly relax FT simulations.
+In this work, we study \RB convection (RBC) with mixed (``FT'') temperature boundary conditions.
+We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of fixing the temperature at the top and bottom of the domain (``TT'').
+We find that simulations with FT boundaries experience a long thermal rundown while simulations with TT boundaries do not.
+In the relaxed state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries.
+The fast evolution of TT simulations can therefore be taken advantage of to rapidly relax FT simulations.
 We show that these findings carry over to more complicated problems through a brief examination of rotating convection.
@@
 In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
-We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are repsectively called RB1, RB2, and RB3.}.
+We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
 It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
-FF and TT boundaries exhibit the same scaling of convective heat transport, quantified by the Nusselt number (Nu), as a function of increased convective driving, quantified by the Rayleigh number (Ra) \cite{johnston&doering2009}.
+FF and TT boundaries exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
 It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
@@
 Our results suggest that the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
-The thermal relaxation of FT simulations is analagous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
+The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
 We find that this long thermal relaxation can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
@@
 \label{sec:simulations}
-We study incompressible  under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
+We study incompressible RBC under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
 In section \ref{sec:rotating_results}, we study convection in the presence of vertical global rotation \cite{julien&all1996}, and include the Coriolis term in the momentum equation for generality.
@@
 \begin{equation}
-\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \frac{\nu}{2\Omega L_z^2},
+\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,u_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \frac{\nu}{2\Omega L_z^2},
 \end{equation}
-where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
+where $u_{\text{ff}}$ is the freefall velocity, $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
 These parameters set the freefall Reynolds (\Reff) and P\'{e}clet (\Peff) numbers, 
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In nonrotating RBC (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
+In non rotating RBC (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
 
-The extent of our numerical domain is vertically $z = [-0.5, 0.5]$ and horizontally $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
+The extent of our numerical domain vertically is $z = [-0.5, 0.5]$ and horizontally is $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
 The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
@@
 	To first order, both cases have similar flow structures: a large convective cell and plumes which break apart into small turbulent eddies.
-	However, in the FT case, the temperature anomaly of the cold plume is much larger than the hot plume, which does not appear on this colorscale.
+	However, in the FT case, the temperature anomaly of the cold plume is much larger than the hot plume, which does not appear on this color scale.
 	(Right two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^9$ and in the relaxed state of the previously pictured FT simulation with Ra$_{\Delta T} \approx 10^9$.
@@
 To create these PDFs, we sample the full simulation temperature field once every simulation freefall time unit over the span of 500 time units.
-We interpolate the (unevenly spaced) vertical Chebyshev gridpoints onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
+We interpolate the (unevenly spaced) vertical Chebyshev grid points onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
 
@@
 At early times (lower left), the FT simulation is characterized by two features: an extreme tail (to the left) that characterizes the cold plume at the upper boundary, and a migrating modal temperature that shifts from the right (hotter) to the left (cooler) as cold material mixes in the interior.
-At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold (left), fixed-tempertaure boundary and the modal value.
-From the modal value towards warmer temperatures, we find that fixed-flux (lower boundary) is capable of producing more extreme temperature events and results in a more extended PDF tail.
+At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold (left), fixed-temperature boundary and the modal value.
+From the modal value towards warmer temperatures, we find that the fixed-flux (lower boundary) is capable of producing more extreme temperature events and results in a more extended PDF tail.
 This long tail is explored further in section \ref{sec:asymmetries}.
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) are shown.
+	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
 	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
@@
 
+\vspace{-0.25cm}
 \subsection{Evolved Structure}
@@
 We find good ($\sim 1\%$) agreement between the FT and TT temperature profiles and enthalpy fluxes throughout the full depth of the domain, with slightly larger differences near the bottom boundary where the boundary conditions differ.
-When we split the profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
+When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
 These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
@@
 \end{enumerate}
-We show this prcedure in practice in Fig.~\ref{fig:rbc_restart_description}.
+We show this procedure in practice in Fig.~\ref{fig:rbc_restart_description}.
 In the left three panels, we display the temporal behavior of (top) Ra, (middle) the flux at the bottom boundary, and (bottom) the temperature difference between the top and bottom boundaries.
@@
 Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
-%\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-%\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
 \hline
@@
 One convective freefall timescale therefore occurs over the same fraction of a diffusion timescale regardless of boundary conditions or temperature nondimensionalization, $\tau_{\text{ff}}/\tau_{\text{th}} \neq f(\text{Nu})$.
-These findings suggest that comparisons of systems which are nondimensionalized on the flux and the temperature may be more straightforward in a thermal diffusion nondimensionalization \cite{goluskin2016} than the freefall nondimensionalization we have used throughout this work.
+These findings suggest that comparing FT and TT dynamics may be more straightforward under a thermal diffusion nondimensionalization \cite{goluskin2016} than the freefall nondimensionalization we have used throughout this work.
 
@@
 However, the FT PDF has a much longer tail and the FT solution achieves fluid parcels which are hotter than the average bottom boundary value by more than 50\%.
-In order to understand how this is possible, we examine a snapshot of the full temperature field.
-In the middle panel, we plot the temperature anomaly, or the temperature field with the mean vertical profile subtracted from it.
+In order to understand how this is possible, we examine a snapshot of the FT simulation's temperature anomaly in the middle panel.
 We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
@@
 In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot Nu vs.~Ra for rotating simulations.
-Select TT cases are plotted as cyan circles with purple outlines (where the cyan color denotes the value of Ek$\,=\,10^{-6}$ according to the colorbar).
+Select TT cases are plotted as cyan circles with purple outlines (where the cyan color denotes the value of Ek$\,=\,10^{-6}$ according to the color bar).
 The evolution of the FT case in the left panels is shown as a thick orange line with a cyan interior and the black arrows show the direction of time.
@@
 Finally, in the evolved state, this vortex pair solution begins to oscillate with domain-wide jets, such as those displayed in the right panel.
-We find that the the TT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 frefall timescales of evolution that we simulated.
+We find that the TT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 freefall timescales of evolution that we simulated.
 
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) are shown.
+	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
 	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
@@
 	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
-	Circlular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
-	The color of the data points signifies the Ekman number of the points, and black points are nonrotating.
+	Circular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
+	The color of the data points signifies the Ekman number of the points, and black points are non rotating.
 	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
@@
 	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
-	The three vertical black lines in the left panels signify the times at which this snapshots are taken.
+	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
 \label{fig:rotating_panels} }
@@
 In conclusion, we note that our results here should provide astrophysical convection simulations with reason for optimism.
-Through a careful understanding of the setup of our numerical experiments, some problems that we encounter (e.g., long thermal rundown in FT simulations) can be completely avoided through a careful understanding of the system being solved.
+Some problems that we encounter (e.g., long thermal rundown in FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.
 

### 2020-02-27 figures_and_data/rbc_dynamics_asymmetries.py
plot files point towards smaller slice files

@@ -134,14 +134,10 @@ ax.set_xlim(0, np.max(mx/dT))
 plt.sca(axs[1])
 ax = axs[1]
 
-#with h5py.File('./data/rbc/mixedFT_2d/ra2.61e9/slice_file.h5', 'r') as f:
-with h5py.File('./data/rbc/restarted_mixed_T2m/ra9.51e11/slices_s47.h5', 'r') as f:
-    x = f['scales/x/1.0'][()].flatten()
-    z = f['scales/z/1.0'][()].flatten()
-    T = f['tasks/T'][()][15,:]
-
-with h5py.File('./data/rbc/mixedFT_2d/ra2.61e9/avg_profs/averaged_avg_profs.h5', 'r') as f:
-    T_prof = f['T'][()][0,:]
+with h5py.File('./data/rbc/restarted_mixed_T2m/ra9.51e11/temp_slice.h5', 'r') as f:
+    x = f['x'][()]
+    z = f['z'][()]
+    T = f['T'][()]
 
 delta_T_mixed = restarted_scalars['{:.4e}'.format(9.51e11)]['delta_T']
 dT = np.mean(delta_T_mixed[-5000:])
@@ -154,7 +150,7 @@ base_scale=1
 highres_n = 4096
 big_scale=int(highres_n/len(x))
 T_field = domain.new_field()
-T_field['g'] = T - T.mean(axis=0)#T_prof
+T_field['g'] = T - T.mean(axis=0)
 
 x_big = domain.grid(0, scales=big_scale)
 z_big = domain.grid(1, scales=big_scale)

### 2020-02-27 figures_and_data/rbc_evolution_dynamics.py

@@ -120,26 +120,26 @@ axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec((0, 650), 50, 200))
 
 #Dynamics files
-ra1e9_TT  = './data/rbc/fixedT_2d/ra1.00e9/slices_s50.h5'
-ra1e10_TT = './data/rbc/fixedT_2d/ra1.00e10/run07/slices_s1.h5'
-ra1e9_FT  = './data/rbc/mixedFT_2d/ra4.83e10/run03/slices_s416.h5'
-ra1e10_FT = './data/rbc/mixedFT_2d/ra4.83e10/run03/slices_s22.h5' 
+ra1e9_TT  = './data/rbc/fixedT_2d/ra1.00e9/temp_slice.h5'#slices_s50.h5'
+ra1e10_TT = './data/rbc/fixedT_2d/ra1.00e10/temp_slice.h5'#run07/slices_s1.h5'
+ra1e9_FT  = './data/rbc/mixedFT_2d/ra4.83e10/temp_slice_late.h5'#run03/slices_s416.h5'
+ra1e10_FT = './data/rbc/mixedFT_2d/ra4.83e10/temp_slice_early.h5'#run03/slices_s22.h5' 
 
-loop =  (   (axs[0], ra1e10_TT, 7,  np.mean(fixed_scalars[fke]['delta_T'][-5000:]) ),
-            (axs[1], ra1e10_FT, 10,   np.mean(mixed_scalars[mk]['delta_T'][7500:12500])   ),
-            (axs[3], ra1e9_TT,  10,  np.mean(fixed_scalars[fkl]['delta_T'][-5000:]) ),
-            (axs[4], ra1e9_FT,  10,   np.mean(mixed_scalars[mk]['delta_T'][-5000:])  )
+loop =  (   (axs[0], ra1e10_TT,   np.mean(fixed_scalars[fke]['delta_T'][-5000:]) ),
+            (axs[1], ra1e10_FT,    np.mean(mixed_scalars[mk]['delta_T'][7500:12500])   ),
+            (axs[3], ra1e9_TT,    np.mean(fixed_scalars[fkl]['delta_T'][-5000:]) ),
+            (axs[4], ra1e9_FT,     np.mean(mixed_scalars[mk]['delta_T'][-5000:])  )
         )
 
-for ax, filen, writen, dT in loop:
+for ax, filen, dT in loop:
     print('writing from file {}'.format(filen))
[…]

### 2020-02-27 figures_and_data/rotating_panels.py

@@ -255,15 +255,15 @@ plt.ylim(1, 7e2)
 
 #Panel 5-7, Colormaps
 
-early_slice_f = 'data/rotation/mixedFT/ra2.1e10/slices/slices_t100_512x384x384_s1.h5'
-mid_slice_f = 'data/rotation/mixedFT/ra2.1e10/slices/slices_t5380_128x384x384_s1.h5'
-late_slice_f = 'data/rotation/mixedFT/ra2.1e10/slices/slices_t13215_128x384x384_s1.h5'
+early_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_early.h5'#slices/slices_t100_512x384x384_s1.h5'
+mid_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_mid.h5'#slices/slices_t5380_128x384x384_s1.h5'
+late_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_late.h5'#slices/slices_t13215_128x384x384_s1.h5'
 for i, filename, t in [(4, early_slice_f, r'100'), (5, mid_slice_f, r'5400'), (6, late_slice_f, r'13,200')]:
     plt.sca(axs[i])
     ax = axs[i]
     with h5py.File(filename, 'r') as f:
-        vorticity = f['tasks']['vort_z integ'][0,:].squeeze()
-        x, y = f['scales/x/1.0'], f['scales/y/1.0']
+        vorticity = f['vort_z integ'][()]
+        x, y = f['x'], f['y']
         yy, xx = np.meshgrid(y, x)
         maxv = np.abs(vorticity.max())
         c = plt.pcolormesh(xx, yy, vorticity, cmap='PiYG_r', vmin=-maxv, vmax=maxv, rasterized=True)

### 2020-02-27 code/join_data.py
adds code to repo

@@ -1,0 +1,47 @@
+'''
+Join distributed dedalus output data.
+
+Usage:
+      join_data.py <case>... [--data_type=<data_type> --cleanup]
+
+Options:
+      --data_type=<data_type>      Type of data to join; if provided join a single data.
+      --cleanup                    Cleanup after join
+
+'''
+
+import os
+import sys
+import logging
+logger = logging.getLogger(__name__)
+
+import dedalus.public
+from dedalus.tools  import post
+
+from docopt import docopt
+import glob
+
+args = docopt(__doc__)
+
+data_dir = args['<case>'][0]
+for d in glob.glob(data_dir):
+    base_path = os.path.abspath(d)+'/'
+
+    cleanup = args['--cleanup']
+
+    logger.info("joining data from Dedalus run {:s}".format(d))
+
+    if args['--data_type'] is not None:
+        data_types=[args['--data_type']]
+    else:
+        data_types = ['slices', 'profiles', 'final_checkpoint', 'checkpoint', 'volumes', 'scalar']
+
+    for data_type in data_types:
+        logger.info("merging {}".format(data_type))
+        try:
+            print(base_path+data_type)
+            post.merge_process_files('{:s}/{:s}/'.format(base_path,data_type), cleanup=cleanup)
+        except:
+            logger.info("missing {}".format(data_type))
+            
+    logger.info("done join operation for {:s}".format(d))

### 2020-02-27 code/logic/ae_tools.py

@@ -1,0 +1,345 @@
+from collections import OrderedDict
+import logging
+logger = logging.getLogger(__name__)
+
+from mpi4py import MPI
+import numpy as np
+
+from dedalus import public as de
+from dedalus.extras.flow_tools import GlobalFlowProperty
+
+class BoussinesqAESolver:
+    """
+    Logic for coupling into a Dedalus IVP solve of Boussinesq, Rayleigh-Benard Convection.
+    Currently only implemented for mixed thermal boundary conditions (fixed-flux at bottom,
+    fixed-temp at top).
+
+    Attributes:
+    -----------
+    (first_/curr_)ae_wait_time: float
+        Freefall times to wait before collecting averages on (first/current) AE solve
+    (first_/curr_)ae_avg_time: float
+        Minimum number of freefall times over which to take averages on (first/current) AE solve
+    (first_/curr_)ae_avg_thresh: float
+        Convergence criterion, in % diff, of profiles before (first/current) AE BVP solve triggers
+    AE_basis : Dedalus Chebyshev
+        1D z-basis for AE solve
+    AE_domain : Dedalus Domain
+        Domain object for AE solve
+    ae_fields : list
+        Strings of variables whose profiles must converge on AE solves
+    avg_profiles : OrderedDict
+        Contains time-averaged profiles
+    dist_ivp : Dedalus Distributor
+        MPI distributor from convection DNS
+    doing_ae : bool
+        If True, profiles are actively being averaged for an AE solve
+    elapsed_avg_time : float
+        Total sim time that has passed over the averaging window
+    extra_fields : list
+        Fields to track the instantaneous vertical profile of from the DNS.
+    finished_ae : bool
+        If True, AE has converged within ivp_convergence_thresh
+    flow : Dedalus GlobalFlowProperty
+        Tracks instantaneous profiles in the DNS
+    ivp_convergence_thresh: float
+        When AE changes the current simulation's temp profile by this % or lower, consider solution converged.
+    local_l2 : OrderedDict
+        Contains info about change in profile from previous to current average.
+    measured_profiles : OrderedDict
+        Contains info about the current and previous instantaneous profile values
+    measured_times : NumPy Array
[…]

### 2020-02-27 code/logic/extras.py

@@ -1,0 +1,45 @@
+import logging
+import numpy as np
+
+logger = logging.getLogger(__name__)
+
+def filter_field(field, frac=0.25):
+    """
+    Filter a field in coefficient space by cutting off all coefficient above
+    a given threshold.  This is accomplished by changing the scale of a field,
+    forcing it into coefficient space at that small scale, then coming back to
+    the original scale.
+
+    Inputs:
+        field   - The dedalus field to filter
+        frac    - The fraction of coefficients to KEEP POWER IN.  If frac=0.25,
+                    The upper 75% of coefficients are set to 0.
+    """
+    dom = field.domain
+    logger.info("filtering field {} with frac={} using a set-scales approach".format(field.name,frac))
+    orig_scale = field.scales
+    field.set_scales(frac, keep_data=True)
+    field['c']
+    field['g']
+    field.set_scales(orig_scale, keep_data=True)
+
+
+def global_noise(domain, seed=42, **kwargs):
+    """
+    Create a field fielled with random noise of order 1.  Modify seed to
+    get varying noise, keep seed the same to directly compare runs.
+    """
+    # Random perturbations, initialized globally for same results in parallel
+    gshape = domain.dist.grid_layout.global_shape(scales=domain.dealias)
+    slices = domain.dist.grid_layout.slices(scales=domain.dealias)
+    rand = np.random.RandomState(seed=seed)
+    noise = rand.standard_normal(gshape)[slices]
+
+    # filter in k-space
+    noise_field = domain.new_field()
+    noise_field.set_scales(domain.dealias, keep_data=False)
+    noise_field['g'] = noise
+    filter_field(noise_field, **kwargs)
+    return noise_field
+
+

### 2020-02-27 code/logic/output.py

@@ -1,0 +1,133 @@
+"""
+    This file is a partial driving script for boussinesq dynamics.  Here,
+    formulations of the boussinesq equations are handled in a clean way using
+    classes.
+"""
+import logging
+from collections import OrderedDict
+logger = logging.getLogger(__name__.split('.')[-1])
+
+def initialize_output(solver, data_dir, aspect, threeD=False, volumes=False,
+                      max_writes=20, output_dt=0.1, slice_output_dt=1, vol_output_dt=10,
+                      mode="overwrite", **kwargs):
+    """
+    Sets up output from runs.
+    """
+
+    Ly = Lx = aspect
+    Lz = 1
+
+    # Analysis
+    analysis_tasks = OrderedDict()
+    profiles = solver.evaluator.add_file_handler(data_dir+'profiles', sim_dt=output_dt, max_writes=max_writes*10, mode=mode)
+    profiles.add_task("plane_avg(T1+T0)", name="T")
+    profiles.add_task("plane_avg(dz(T1+T0))", name="Tz")
+    profiles.add_task("plane_avg(T1)", name="T1")
+    profiles.add_task("plane_avg(u)", name="u")
+    profiles.add_task("plane_avg(w)", name="w")
+    profiles.add_task("plane_avg(enstrophy)", name="enstrophy")
+    profiles.add_task('plane_avg(Oy)', name="y_vorticity")
+    profiles.add_task("plane_avg(Nu)", name="Nu")
+    profiles.add_task("plane_avg(Re)", name="Re")
+    profiles.add_task("plane_avg(Pe)", name="Pe")
+    profiles.add_task("plane_avg(enth_flux)", name="enth_flux")
+    profiles.add_task("plane_avg(cond_flux)", name="kappa_flux")
+    profiles.add_task("plane_avg(cond_flux + enth_flux)", name="tot_flux")
+
+    analysis_tasks['profiles'] = profiles
+
+    scalar = solver.evaluator.add_file_handler(data_dir+'scalar', sim_dt=output_dt, max_writes=max_writes*100, mode=mode)
+    scalar.add_task("vol_avg(T1)", name="IE")
+    scalar.add_task("vol_avg(0.5*vel_rms**2)", name="KE")
+    scalar.add_task("vol_avg(T1) + vol_avg(0.5*vel_rms**2)", name="TE")
+    scalar.add_task("vol_avg(Nu)", name="Nu")
[…]

### 2020-02-27 code/onset/rayleigh_benard.py

@@ -1,0 +1,160 @@
+"""
+Dedalus script for calculating the maximum growth rates in no-slip
+Rayleigh Benard convection over a range of horizontal wavenumbers.
+
+This script can be ran serially or in parallel, and produces a plot of the
+highest growth rate found for each horizontal wavenumber.
+
+To run using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+"""
+
+import time
+import numpy as np
+import matplotlib.pyplot as plt
+import dedalus.public as de
+from mpi4py import MPI
+CW = MPI.COMM_WORLD
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Global parameters
+Nz = 64
+Nk = 200
+zoom = 0.1
+
+data = {}
+
+for case in [0,1,2,3]:
+
+    if case == 0:
+        velocity_bc    = "stress-free"
+        temperature_bc = "TT"
+        kc = 2.22
+
+    if case == 1:
+        velocity_bc    = "no-slip"
+        temperature_bc = "TT"
+        kc = 3.12
+
+    if case == 2:
+        velocity_bc    = "stress-free"
+        temperature_bc = "FT"
+        kc = 1.76
+
+    if case == 3:
+        velocity_bc    = "no-slip"
+        temperature_bc = "FT"
+        kc = 2.55
+
+    kx_global = np.linspace(kc*(1-zoom),kc*(1+zoom), Nk)
+
+    # Create bases and domain
+    # Use COMM_SELF so keep calculations independent between processes
+    z_basis = de.Chebyshev('z', Nz, interval=(-1/2, 1/2))
+    domain = de.Domain([z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
+
+    # 2D Boussinesq hydrodynamics, with various boundary conditions
+    # Use substitutions for x derivatives
+    problem = de.EVP(domain, variables=['p','T','u','w','F','ω'], eigenvalue='Ra')
+    problem.parameters['kx'] = 1
+    problem.substitutions['dx(A)'] = "1j*kx*A"
+
+    problem.add_equation("  dx(u) + dz(w) = 0")
+    problem.add_equation("  dx(dx(T)) - dz(F) + w  = 0")
+    problem.add_equation("   dz(ω) + dx(p)         = 0")
[…]

### 2020-02-27 code/plotting/plot_3d_slices.py

@@ -1,0 +1,57 @@
+"""
+Script for plotting 2D slices of the evolution of a 3D dedalus simulation.  
+This script plots time evolution of the fields specified in 'fig_type'
+
+Usage:
+    plot_slices.py <root_dir> [options]
+
+Options:
+    --fig_name=<fig_name>               Name of figure output directory & base name of saved figures [default: snapshots]
+    --start_fig=<fig_start_num>         Number of first figure file [default: 1]
+    --start_file=<file_start_num>       Number of Dedalus output file to start plotting at [default: 1]
+    --n_files=<num_files>               Number of files to plot
+    --static_cbar                       If flagged, don't evolve the cbar with time
+    --dpi=<dpi>                         Image pixel density [default: 200]
+
+    --col_inch=<in>                     Number of inches / column [default: 3]
+    --row_inch=<in>                     Number of inches / row [default: 3]
+
+    --fig_type=<fig_type>               Type of figure to plot
+                                            1 - T (y = 0, near top, midplane)
+                                        [default: 1]
+"""
+from docopt import docopt
+args = docopt(__doc__)
+from plot_logic.slices import SlicePlotter
+import logging
+logger = logging.getLogger(__name__)
+
+
+start_fig = int(args['--start_fig'])
+n_files     = args['--n_files']
+if n_files is not None: n_files = int(n_files)
+start_file  = int(args['--start_file'])
+
+root_dir    = args['<root_dir>']
+if root_dir is None:
+    logger.error('No dedalus output dir specified, exiting')
+    import sys
+    sys.exit()
+fig_name   = args['--fig_name']
+
+plotter = SlicePlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
+
+plotter_kwargs = { 'col_in' : int(args['--col_inch']), 'row_in' : int(args['--row_inch']) }
+
+if int(args['--fig_type']) == 1:
+    plotter.setup_grid(2, 3, **plotter_kwargs)
+    plotter.grid.full_row_ax(0)
+    fnames = [(('T',), {'remove_x_mean' : True}), (('T near top',), {'remove_mean':True, 'y_basis':'y'}), (('T midplane',), {'remove_mean':True, 'y_basis':'y'}), (('vort_z integ',), {'y_basis':'y'})]
+
+
+
+
+for tup in fnames:
+    plotter.add_colormesh(*tup[0], **tup[1])
+
+plotter.plot_colormeshes(start_fig=start_fig, dpi=int(args['--dpi']))

### 2020-02-27 code/plotting/plot_logic/pdfs.py

@@ -1,0 +1,243 @@
+import os
+import logging
+from collections import OrderedDict
+from sys import stdout
+from sys import path
+
+import numpy as np
+import h5py
+from mpi4py import MPI
+from scipy.interpolate import RegularGridInterpolator
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+matplotlib.rcParams.update({'font.size': 9})
+
+from dedalus.tools.parallel import Sync
+
+path.insert(0, './plot_logic')
+from plot_logic.file_reader import SingleFiletypePlotter
+from plot_logic.plot_grid import PlotGrid
+
+logger = logging.getLogger(__name__.split('.')[-1])
+
+
+class PdfPlotter(SingleFiletypePlotter):
+    """
+    A class for plotting probability distributions of a dedalus output.
+    PDF plots are currently only implemented for 2D slices. When one axis is
+    represented by polynomials that exist on an uneven basis (e.g., Chebyshev),
+    that basis is evenly interpolated to avoid skewing of the distribution by
+    uneven grid sampling.
+
+    Additional Attributes:
+    -----------
+    pdfs : OrderedDict
+        Contains PDF data (x, y, dx)
+    pdf_stats : OrderedDict
+        Contains scalar stats for the PDFS (mean, stdev, skew, kurtosis)
+    """
+
+    def __init__(self, *args, **kwargs):
+        """
+        Initializes the PDF plotter.
+
+        Attributes:
+        -----------
+        *args, **kwargs : Additional keyword arguments for super().__init__() 
+        """
+        super(PdfPlotter, self).__init__(*args, distribution='even', **kwargs)
+        self.pdfs = OrderedDict()
+        self.pdf_stats = OrderedDict()
+
+
+    def _calculate_pdf_statistics(self):
+        """ Calculate statistics of the PDFs stored in self.pdfs. Store results in self.pdf_stats. """
+        for k, data in self.pdfs.items():
+            pdf, x_vals, dx = data
+
+            mean = np.sum(x_vals*pdf*dx)
+            stdev = np.sqrt(np.sum((x_vals-mean)**2*pdf*dx))
+            skew = np.sum((x_vals-mean)**3*pdf*dx)/stdev**3
+            kurt = np.sum((x_vals-mean)**4*pdf*dx)/stdev**4
+            self.pdf_stats[k] = (mean, stdev, skew, kurt)
+
+    
[…]

### 2020-02-27 code/plotting/plot_logic/plot_grid.py

@@ -1,0 +1,137 @@
+import matplotlib
+matplotlib.use('Agg')
+import numpy as np
+import matplotlib.gridspec as gridspec
+import matplotlib.pyplot as plt
+from collections import OrderedDict
+
+def fl_int(num):
+    return int(np.floor(num))
+
+
+class PlotGrid:
+    """
+    Sets up an even plot grid with a given number of rows and columns.
+    Axes objects are stored in self.axes, with keys like 'ax_0-1', where
+    the numbers refer to the column, then row of the plot (so they go
+    left to right, then top to bottom)
+
+    Attributes:
+    -----------
+    axes : OrderedDict
+        Contains matplotlib axes objects for plotting
+    fig : matplotlib figure
+        The figure object on which the grid is split up
+    gs : matplotlib Gridspec object
+        Object used for splitting up the grid
+    col_size, row_size : ints
+        The size of columns, and rows, in grid units
+    nrows, ncols : ints
+        Number of rows and columns, respectively, in the image
+    padding : int
+        spacing to leave between rows and columns 
+        (padding = 10 means 1% of the image space horizontally and vertically should be blank between rows/columns)
+    width, height : floats
+        The width and height of the figure in inches
+    """
+
+    def __init__(self, nrows, ncols, padding=50, col_in=3, row_in=3):
+        """
+        Initialize and create the plot grid.
+
+        Arguments:
+        ----------
+        nrows, ncols : ints
+            As in class-level docstring
+        padding : int
+            As in class-level docstring
+        col_in, row_in : floats
+            The number of inches taken up by each column's width or row's height.
+        """
+        self.nrows     = nrows
+        self.ncols     = ncols
+        self.width     = float(ncols*col_in)
+        self.height    = float(nrows*row_in)
+        self.padding   = padding
+        self.fig       = plt.figure(figsize=(self.width, self.height))
+        self.gs        = gridspec.GridSpec(1000,1000) #height units, then width units
+        self.col_size       = fl_int((1000 - padding*(self.ncols-1))/self.ncols) 
+        self.row_size       = fl_int((1000 - padding*(self.nrows-1))/self.nrows) 
+        self.axes      = OrderedDict()
+        self._make_subplots()
+
+
+    def _make_subplots(self):
+        """ Makes the subplots. """
+        for i in range(self.ncols):
+            for j in range(self.nrows):
+                self.axes['ax_{}-{}'.format(i,j)] = plt.subplot(self.gs.new_subplotspec(
[…]

### 2020-02-27 code/plotting/plot_logic/slices.py

@@ -1,0 +1,296 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+matplotlib.rcParams.update({'font.size': 9})
+
+import os
+from sys import stdout
+from sys import path
+
+
+from dedalus.tools.parallel import Sync
+
+path.insert(0, './plot_logic')
+from plot_logic.file_reader import SingleFiletypePlotter
+from plot_logic.plot_grid import ColorbarPlotGrid
+
+import numpy as np
+
+import logging
+logger = logging.getLogger(__name__.split('.')[-1])
+
+
+class Colormesh:
+    """
+    A struct containing information about a slice colormesh plot
+
+    Attributes:
+    -----------
+    field : string
+        The profile task name
+    x_basis, y_basis : strings
+        The dedalus basis names that the profile spans in the x- and y- direction of the plot
+    remove_mean : bool
+        If True, remove the mean value of the profile at each time
+    remove_x_mean : bool
+        If True, remove the mean value over the axis plotted in the x- direction
+    remove_y_mean : bool
+        If True, remove the mean value over the axis plotted in the y- direction
+    cmap  : string
+        The matplotlib colormap to plot the colormesh with
+    pos_def : bool
+        If True, profile is positive definite and colormap should span from max/min to zero.
+    """
+
+    def __init__(self, field, x_basis='x', y_basis='z', remove_mean=False, remove_x_mean=False, remove_y_mean=False, cmap='RdBu_r', pos_def=False):
+        self.field = field
+        self.x_basis = x_basis
+        self.y_basis = y_basis
+        self.remove_mean = remove_mean
+        self.remove_x_mean = remove_x_mean
+        self.remove_y_mean = remove_y_mean
+        self.cmap = cmap
+        self.pos_def = pos_def
+        self.xx, self.yy = None, None
+
+class SlicePlotter(SingleFiletypePlotter):
+    """
+    A class for plotting colormeshes of 2D slices of dedalus data.
+
+    Attributes:
+    -----------
+    colormeshes : list
+        A list of Colormesh objects
+    """
+
+    def __init__(self, *args, **kwargs):
+        """
+        Initializes the slice plotter.
+
+        Attributes:
+        -----------
+        *args, **kwargs : Additional keyword arguments for super().__init__() 
+        """
+        super(SlicePlotter, self).__init__(*args, distribution='even', **kwargs)
+        self.colormeshes = []
+
[…]

### 2020-02-27 code/plotting/plot_pdfs.py

@@ -1,0 +1,32 @@
+"""
+Script for plotting probability distribution functions of 2D quantities.
+
+Usage:
+    plot_pdfs.py <root_dir> [options]
+
+Options:
+    --fig_name=<fig_name>               Output directory for figures [default: pdfs]
+    --start_file=<start_file>           Dedalus output file to start at [default: 1]
+    --n_files=<num_files>               Number of files to plot [default: 100000]
+    --dpi=<dpi>                         Image pixel density [default: 150]
+    --bins=<bins>                       Number of bins per pdf [default: 100]
+"""
+import logging
+logger = logging.getLogger(__name__)
+from docopt import docopt
+args = docopt(__doc__)
+from plot_logic.pdfs import PdfPlotter
+
+root_dir = args['<root_dir>']
+fig_name  = args['--fig_name']
+start_file = int(args['--start_file'])
+n_files     = args['--n_files']
+if n_files is not None: n_files = int(n_files)
+
+pdfs_to_plot = ['T', 'enstrophy', 'enth_flux', 'w']
+
+
+# Load in figures and make plots
+plotter = PdfPlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
+plotter.calculate_pdfs(pdfs_to_plot, bins=int(args['--bins']), uneven_basis='z')
+plotter.plot_pdfs(dpi=int(args['--dpi']), row_in=5, col_in=8.5)

### 2020-02-27 code/rayleigh_benard.py

@@ -1,0 +1,469 @@
+"""
+Dedalus script for Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the horizontal direction(s) with periodic boundary
+conditions. The vertical direction is represented as Chebyshev coefficients.
+The equations are scaled in units of the buoyancy time (Fr = 1).
+
+By default, the boundary conditions are:
+    Velocity: Impenetrable, no-slip at both the top and bottom
+    Thermal:  Fixed flux (bottom), fixed temp (top)
+
+Usage:
+    rayleigh_benard.py [options] 
+
+Options:
+    --Rayleigh=<Rayleigh>      Rayleigh number [default: 1e4]
+    --Prandtl=<Prandtl>        Prandtl number = nu/kappa [default: 1]
+    --nz=<nz>                  Vertical resolution [default: 32]
+    --nx=<nx>                  Horizontal resolution [default: 64]
+    --ny=<nx>                  Horizontal resolution [default: 64]
+    --aspect=<aspect>          Aspect ratio of problem [default: 2]
+
+    --fixed_f                  Fixed flux boundary conditions top/bottom (FF)
+    --fixed_t                  Fixed temperature boundary conditions top/bottom (TT)
+    --stress_free              Stress free boundary conditions top/bottom 
+
+    --3D                       Run in 3D
+    --mesh=<mesh>              Processor mesh if distributing 3D run in 2D 
+    
+    --run_time_wall=<time>     Run time, in hours [default: 23.5]
+    --run_time_buoy=<time>     Run time, in buoyancy times
+    --run_time_therm=<time_>   Run time, in thermal times [default: 1]
+
+    --restart=<file>           Restart from checkpoint file
+    --restart_T2m=<file>       Restart from checkpoint file, going from TT to FT BCs 
+    --restart_T2m_Nu=<Nu>      Nusselt number of fixed-T run being restarted from [default: 1]
+    --overwrite                If flagged, force file mode to overwrite
+    --seed=<seed>              RNG seed for initial conditoins [default: 42]
+
[…]

### 2020-02-27 code/rotating_rayleigh_benard.py

@@ -1,0 +1,421 @@
+"""
+Dedalus script for 3D rotating Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the horizontal direction(s) with periodic boundary
+conditions. The vertical direction is represented as Chebyshev coefficients.
+The equations are scaled in units of the buoyancy time (Fr = 1).
+
+By default, the boundary conditions are:
+    Velocity: Impenetrable, stress-free at both the top and bottom
+    Thermal:  Fixed flux (bottom), fixed temp (top)
+
+Usage:
+    rotating_rayleigh_benard.py [options] 
+
+Options:
+    --Rayleigh=<Rayleigh>      Rayleigh number [default: 1e5]
+    --Prandtl=<Prandtl>        Prandtl number = nu/kappa [default: 1]
+    --Ekman=<Ekman>            Ekman number [default: 1e-2]
+    --nz=<nz>                  Vertical resolution [default: 32]
+    --nx=<nx>                  Horizontal resolution [default: 64]
+    --ny=<nx>                  Horizontal resolution [default: 64]
+    --aspect=<aspect>          Aspect ratio of problem [default: 2]
+
+    --fixed_f                  Fixed flux boundary conditions top/bottom (FF)
+    --fixed_t                  Fixed temperature boundary conditions top/bottom (TT)
+    --no_slip                  Stress free boundary conditions top/bottom
+
+    --mesh=<mesh>              Processor mesh if distributing 3D run in 2D 
+    
+    --run_time_wall=<time>     Run time, in hours [default: 23.5]
+    --run_time_buoy=<time>     Run time, in buoyancy times
+    --run_time_therm=<time_>   Run time, in thermal times [default: 1]
+
+    --restart=<file>           Restart from checkpoint file
+    --overwrite                If flagged, force file mode to overwrite
+    --seed=<seed>              RNG seed for initial conditoins [default: 42]
+
+    --label=<label>            Optional additional case name label
+    --verbose                  Do verbose output (e.g., sparsity patterns of arrays)
[…]

### 2020-02-27 tex/mixedft_evolution_ms.tex
ready for submission

@@
 Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D rotating simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
-The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
+The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using v1.0.0 of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
@@
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
+LK acknowledges support from the George Ellery Hale Post-Doctoral Fellowship.
 This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 

### 2020-02-28 tex/mixedft_evolution_ms.tex
fixes some typos iregarding the coefficient resolution of simulations in the table

@@
 	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
-	Input quantities are the boundary conditions (BCs), Rayleigh number (Ra), coefficient resolution (nz$\times$nx$\times$ny), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
+	Input quantities are the boundary conditions (BCs), Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
 	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
@@
 	The 2D FT Ra = $4.83 \times 10^{10}$ simulation's resolution was changed to $1024\times2048$ about 500 freefall time units after transient.
-	The rotating FT case's resolution was reduced to $256\times384^2$ about one hundred freefall time units after transient, and was further reduced to $128\times384^2$ about $3.3\times 10^3$ freefall times after transient.
+	The rotating FT case's resolution was reduced to $384^2\times256$ about one hundred freefall time units after transient, and was further reduced to $384^2\times128$ about $3.3\times 10^3$ freefall times after transient.
 }
@@
 \hline																	
-BCs	&	Ra	&	nz$\times$nx$\times$ny	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
+BCs	&	Ra	&	nx$\times$ny$\times$nz	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
@@
 \hline																	
-TT	&	$1.38 \times 10^9$		&	128$\times$64$^2$	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
-TT	&	$1.83 \times 10^9$		&	128$\times$64$^2$	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
+TT	&	$1.38 \times 10^9$		&	64$^2\times$128 	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
+TT	&	$1.83 \times 10^9$		&	64$^2\times$128 	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
 TT	&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
 TT	&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
-FT	&	$2.1 \times 10^{10}$	&	512$\times$384$^2$*	&	13950		&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
+FT	&	$2.1 \times 10^{10}$	&	384$^2\times$512*	&	13950		&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
 TT	&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\

### 2020-04-30 tex/mixedft_evolution_ms.tex
adds changes from thesis work

@@
 It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
+Indeed, \citet{calkins&all2015b} have found a dynamical equivalence between FT and TT boundaries in rapidly rotating RBC.
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
+	Note that the coefficient resolution of the evolved FT simulation and the TT-to-FT simulation are the same (nz, nx) = (1024, 2048).
 }
@@
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \cite{couston&all2019}.
+\footnote{At these parameters, we would be in the cellular convection regime of \citet{stellmach&all2014}, but our dynamics are different due to our choice of stress free boundary conditions.
+}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}.
 

### 2020-04-30 tex/mixedft_evolution_ms.tex
colors edits from thesis; expands bibliography with new lit review papers

--- 2020-02-28 tex/mixedft_evolution_ms.tex
@@
 \newcommand{\Peff}{\ensuremath{\text{Pe}_{\text{ff}}}}
+
+\newcommand{\ea}[1]{{\color{red} #1}}
 
@@
 It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
+\ea{Indeed, \citet{calkins&all2015b} have found a dynamical equivalence between FT and TT boundaries in rapidly rotating RBC.}
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
+	\ea{Note that the coefficient resolution of the evolved FT simulation and the TT-to-FT simulation are the same (nz, nx) = (1024, 2048).}
 }
@@
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \cite{couston&all2019}.
+\footnote{\ea{At these parameters, we would be in the cellular convection regime of \citet{stellmach&all2014}, but our dynamics are different due to our choice of stress free boundary conditions.
+}}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
 

### 2020-04-30 tex/mixedft_evolution_ms.tex
added initial conditions discussion. reworked general format of simulation details secton

@@
 It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
-\ea{Indeed, \citet{calkins&all2015b} have found a dynamical equivalence between FT and TT boundaries in rapidly rotating RBC.}
+\ea{Indeed, \citet{calkins&all2015} have found a dynamical equivalence between FF and TT boundaries in rapidly rotating RBC.}
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 %%%%%%%%%%%%
-
 \section{Simulation Details}
 \label{sec:simulations}
+\ea{
+\subsection{Equations, Control Parameters, Boundary Conditions, and Numerics}
+}
 We study incompressible RBC under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
@@
 \end{equation}
-For this choice of boundary conditions, the critical value of the Rayleigh number is Ra$_{\partial_z T} = 1296$ for FT boundaries and Ra$_{\Delta T} = 1708$ for TT boundaries \cite{goluskin2016}.
+For this choice of \ea{aspect ratio and} boundary conditions, the critical value of the Rayleigh number is Ra$_{\partial_z T} = 1296$ for FT boundaries and Ra$_{\Delta T} = 1708$ for TT boundaries \cite{goluskin2016}.
 Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
@@
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.
-We fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
-We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Ra & Nu arguments
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Nondimensional Output Quantities}
+\ea{
+\subsection{Output Quantities \& Mapping Between Temperature Nondimensionalizations}
+}
 \label{sec:ra_nu_relations}
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
-In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (-\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
-This implies that Nu is the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
+\ea{In an evolved, statistically stationary state \cite{calkins&all2015}, 
 \begin{equation}
-\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu}.
+\text{Nu} = \frac{\beta L_z}{\Delta T}, \,\,\text{where}\,\,
+\beta \begin{cases}
+< -1 & \text{(TT)} \\
+= -1 & \text{(FT/FF)},
+\end{cases},
+\qquad
+\Delta T \begin{cases}
+= -1 & \text{(TT)} \\
+\in [-1, 0) & \text{(FT/FF)}
+\end{cases},
+\label{eqn:evolved_nu}
+\end{equation}
+and where $\beta$ is the temperature gradient achieved at the domain boundaries.
+Nu is therefore the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
+\begin{equation}
+\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu},
+\qquad
+T_{\text{TT}} = \text{Nu} T_{\text{FT}},
+\qquad
+\bm{u}_{\text{TT}} = \sqrt{\text{Nu}} \bm{u}_{\text{FT}}.
 \label{eqn:ra_relation}
 \end{equation}
+This mapping is presented by ref.~\cite{calkins&all2015} for a diffusion timescale nondimensionalization, and we have expanded it here for a freefall timescale nondimensionalization.}
 
@@
 where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.
+
+\ea{
+\subsection{Initial Conditions}
+The time evolution of FT simulations is sensitive to the choice of initial conditions made due to the fact that the evolved, nonlinear convective dynamics determine the mean temperature for this choice of boudnary conditions.
+For this reason, we will study FT simulations which employ three different formulations of the initial temperature field.
+
+\paragraph{Classical ICs} 
+Our first set of initial conditions are the ``classical'' initial conditions on which the system was nondimensionalized,
+\begin{equation}
+T_c(z) = 0.5 - z.
+\end{equation}
+Simulations which employ these initial conditions will be simply denoted as ``FT'' simulations.
+
+\paragraph{Nu-based ICs} 
+Our second set of initial conditions are ``Nusselt-based'' initial conditions.
+As we will show in sections \ref{sec:results}, the evolved state of each FT simulation corresponds to an equivalent TT simulation.
+As a result, Nu~vs.~Ra scaling laws derived for TT simulations can be expected to hold for FT simulations.
+According to Eqn.~\ref{eqn:ra_relation}, we can rearrange a given scaling law,
+\begin{equation}
+\text{Nu} = A \text{Ra}_{\Delta T}^{\alpha} \rightarrow \text{Nu} = (A \text{Ra}_{\partial_z T}^{\alpha})^{1/(1+\alpha)},
+\end{equation}
+and use this law along with Eqn.~\ref{eqn:evolved_nu} to predict the evolved temperature jump in an FT simulation,
+\begin{equation}
+\Delta T = \frac{\beta L_z}{\text{Nu}} = -(A \text{Ra}_{\partial_z T}^{\alpha})^{-1/(1+\alpha)}.
+\end{equation}
+Our ``Nusselt-based'' initial conditions construct an initial temperature profile which is consistent with the bottom fixed-flux boundary condition but whose initial $\Delta T$ is determined by a specific Nu~vs.~Ra scaling law.
+The vertical temperature derivative is,
+\begin{equation}
+\frac{\partial T_N}{\partial z} = \grad_{\text{interior}} + w(z)(-1 - \grad_{\text{interior}}),
+\end{equation}
+where $w(z)$ is a windowing function which sets the temperature gradient to $-1$ near the boundaries,
+$$
+w(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_w)}{0.5\delta_w}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_w)}{0.5\delta_w}\right]\right),
+$$
+Here, $\delta_w = -\Delta T / 2$, an estimate of the boundary layer width, and $\grad_{\text{interior}}$, the temperature gradient in the interior of the domain, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+%why do we choose erf? why don't we specify a "right" bl shape?
+
+\paragraph{TT-to-FT}
+In some experiments, the proper Nu~vs.~Ra law is not well-known, or is not agreed upon by the community (see e.g.,~Sec.\ref{sec:rotation}).
+For such cases, it may still be numerically useful to be able to study converged FT simulations without having to resort to classical ICs.
+We will therefore examine ``TT-to-FT'' initial conditions, in which we run a TT simulation through its convective transient to statistical equilibrium, then use the full evolved nonlinear state as initial conditions for an FT simulation.
+}
+To achieve this, we perform these steps:
+\begin{enumerate}
+\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
+Measure $\text{Nu}$ in that state.
+\item Re-nondimensionalize from TT to FT according to Eqn.~\ref{eqn:ra_relation}.
+\item Restart the simulation with FT boundaries and continue timestepping.
+\end{enumerate}
+
+\ea{\paragraph{Additional ICs}
+In all cases, we assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
+We assume zero velocity in the initial state, except in the case of TT-to-FT simulations.
+For classical and Nu-based ICs,
+}
+we fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
+We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.
+
+\ea{
+\subsection{Evolutionary Timescales}
+
+}
 

### 2020-05-01 tex/mixedft_evolution_ms.tex
adds initial text on timescale evolution.

@@
 \ea{
-\subsection{Evolutionary Timescales}
+\subsection{Timescales}
+\label{sec:timescales}
+}
+\paragraph{Dynamical Timescales}
+One \ea{result of the mapping in Eqn.~\ref{eqn:ra_relation}} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
+The velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
+As a result, every simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
+\ea{To ensure that comparisons between TT and FT simulations are accurate, measurements in FT simulations will be taken over time windows longer by a factor of $\sqrt{\text{Nu}}$ than comparable windows in TT simulations.}
+
+\ea{
+\paragraph{Evolutionary Timescales}
+The thermal energy reservoir of our 2D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
+\begin{equation}
+E = \iint T\,dx\,dz = \Gamma \int T\,dz,
+\qquad
+\frac{dE}{dt} = -\iint \grad\cdot F_{\text{cond}}\,dx\,dz = -\Gamma F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\end{equation}
+where the conductive flux is $F_{\text{cond}} = -\Peff^{-1}\grad T$, $F_{\text{cond,z}}$ is its z-component, and where $\int T dz = \Delta T / 2$ in RBC.
+The thermal relaxation time of a \RB convection experiment is therefore
+\begin{equation}
+\tau_{\text{th}} = \frac{\Delta E}{dE/dt},
+\,\,\text{with}\,\,
+\Delta E = E(t=\infty) - E(t=0).
+\end{equation}
+In the case of TT boundary conditions, we expect $\Delta E = 0$, as the initial and final state have the same mean temperature.
+The goal of our ``Nu-based'' and TT-to-FT initial conditions is to create FT systems in which $\Delta E = 0$ is also true, creating a system with a negligible relaxational timescale.
+
+For the case of classical ICs in an FT system, $\Delta T(t=0) = -1$ and $\Delta T(t=\infty) = -\text{Nu}^{-1}$, and the temperature gradient at the bottom boundary is fixed at a value of -1.
+The thermal relaxation timescale is therefore
+\begin{equation}
+\tau_{\text{th, FT-classical}} = \Peff \frac{\text{Nu}^{-1} - 1}{\partial_z T(z=0.5) + 1} \sim \frac{\sqrt{\text{Ra Pr}}}{|\partial_z T(z = 0.5)| - 1}.
+\end{equation}
+Where the final expression is for the large Ra case where Nu$^{-1} \rightarrow 0$.
+The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but monotonically decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
+However, it is reasonable to assume that the evolutionary timescale lies within the window $\tau_{\text{th, FT-classical}} \in [\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1}, \sqrt{\text{Ra Pr}}]$.
 
@@
 Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
-
-\subsubsection{Changing Timescales}
-\label{sec:timescales}
-One surprising result of our FT simulations is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
-As noted above in our TT-to-FT procedure, the velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
-As a result, every simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
-This is on display in the left panels of Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher temporal frequency in the TT portion of the simulation than in the FT portion.
-
-These results imply that the true nondimensional freefall time of an FT simulation is $\tau_{\text{ff}} = \sqrt{\text{Nu}}$ in simulation freefall time units.
-However, we note that Ra$_{\partial_z T}$ is the input value of Ra for an FT simulations, and that Ra$_{\partial_z T}/$Ra$_{\Delta T} = \text{Nu}$.
-The thermal diffusion timescale, $\tau_{\text{th}}$, which scales like $\tau_{\text{th}} \propto \sqrt{\text{Ra}_{\text{input}}}$, is also larger in an FT simulation than in a comparable TT simulation by a factor of $\sqrt{\text{Nu}}$.
-One convective freefall timescale therefore occurs over the same fraction of a diffusion timescale regardless of boundary conditions or temperature nondimensionalization, $\tau_{\text{ff}}/\tau_{\text{th}} \neq f(\text{Nu})$.
-These findings suggest that comparing FT and TT dynamics may be more straightforward under a thermal diffusion nondimensionalization \cite{goluskin2016} than the freefall nondimensionalization we have used throughout this work.
 

### 2020-05-04 tex/mixedft_evolution_ms.tex
minor reworkings throughout MS. Sets up skeleton of new section structure.

@@
 However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
+%Mention mantle studies here
 We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
@@
 In this work, we examine how the choice of using ``mixed'' boundaries affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
-In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
+In RBC, temperature is the only thermodynamic quantity and throughout this work we will \ea{adopt the gnomenclature of past authors including ref.~\cite{ishiwatari&all1994} and} refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
 We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
-It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
+%Need to talk about: FF/TT differences in flow morphologies (aspect ratio) near onset. FT looks more like TT
+%Need to add something like this after that statement:\ea{Indeed, \citet{calkins&all2015} have found a dynamical equivalence between FF and TT boundaries in rapidly rotating RBC.}
+It is generally assumed that FT and FF boundaries should fundamentally behave similarly \ea{in their statistically stationary states} \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
 FF and TT boundaries exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
 It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
-\ea{Indeed, \citet{calkins&all2015} have found a dynamical equivalence between FF and TT boundaries in rapidly rotating RBC.}
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 We also compare relaxed FT solutions to TT solutions.
-Our results suggest that the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+\ea{When classical initial conditions which are in hydrostatic and thermal equilibrium are employed,} the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We find that this long thermal relaxation can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
+We find that this long thermal relaxation can be bypassed by \ea{constructing smarter initial conditions based on the expected evolved Nusselt number, or by simply} using the results of TT simulations as initial conditions for FT simulations.
 Finally, FT boundaries create some asymmetries in the convective flows, but these asymmetries do not meaningfully change the mean convective state compared to TT simulations.
@@
 In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
-In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
-In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
+In section \ref{sec:results_timescales}, we describe our findings \ea{regarding} the time evolution of FT systems.
+\ea{In section \ref{sec:results_dynamics}, we study dynamics and asymmetries in FT systems and compare them to TT systems.}
+In section \ref{sec:results_rotating}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
 Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.
@@
 We study incompressible RBC under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
-In section \ref{sec:rotating_results}, we study convection in the presence of vertical global rotation \cite{julien&all1996}, and include the Coriolis term in the momentum equation for generality.
+In section \ref{sec:results_rotating}, we study convection in the presence of vertical global rotation \cite{julien&all1996}, and include the Coriolis term in the momentum equation for generality.
 The Boussinesq equations of motion are
@@
 \end{align}
-where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is \ea{a background linearly unstable temperature profile} and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
 The dimensionless control parameters are the Rayleigh (Ra), Prandtl (Pr), and Ekman (Ek) numbers, defined respectively as
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In non rotating RBC (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
+In non rotating RBC (section\ea{s} \ref{sec:results_timescales}\ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
 
 The extent of our numerical domain vertically is $z = [-0.5, 0.5]$ and horizontally is $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
-The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
-The temperature scale, $\Delta$, is set by the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
+The \ea{background} temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
+The temperature scale, $\Delta$, is set by \ea{either} the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
 We respectively define a temperature (Ra$_{\Delta T}$) and a flux (Ra$_{\partial_z T}$) Rayleigh number for these cases,
@@
 
-In section \ref{sec:2d_results}, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
+In section\ea{s} \ref{sec:results_timescales}\ea{\& \ref{sec:results_dynamics}}, we study \ea{non rotating convection}.
 For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
 \begin{equation}
-u = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
+u = \ea{v =} w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
 \label{eqn:vel_bcs}
@@
 Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
-However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:2d_results}, we do not expect this difference in linear stability to be very important.
+However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:results_timescales}, we do not expect this difference in linear stability to be very important.
+\ea{Many of these simulations are restricted to} two-dimensional (2D) convection \ea{by setting} $\partial_y = v = 0$.
 
-The rotating cases in section \ref{sec:rotating_results} employ stress-free, impenetrable boundaries,
+The rotating cases in section \ref{sec:results_rotating} employ stress-free, impenetrable boundaries,
 \begin{equation}
@@
 We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
-Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D rotating simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
-The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using v1.0.0 of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
+Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the \ea{IMEX}, second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
+The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using \ea{v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and} v1.0.0 \ea{(for all other cases)} of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.
@@
 < -1 & \text{(TT)} \\
-= -1 & \text{(FT/FF)},
+= -1 & \text{(FT)},
 \end{cases},
@@
 = -1 & \text{(TT)} \\
-\in [-1, 0) & \text{(FT/FF)}
+\in [-1, 0) & \text{(FT)}
 \end{cases},
@@
 and where $\beta$ is the temperature gradient achieved at the domain boundaries.
-Nu is therefore the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
+Nu is therefore the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by both a Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
 \begin{equation}
-\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu},
+\text{Ra}_{\partial_z T} =\text{Nu}\, \text{Ra}_{\Delta T},
 \qquad
-T_{\text{TT}} = \text{Nu} T_{\text{FT}},
+T_{\text{TT}} = \text{Nu}\, T_{\text{FT}},
 \qquad
-\bm{u}_{\text{TT}} = \sqrt{\text{Nu}} \bm{u}_{\text{FT}}.
+\bm{u}_{\text{TT}} = \sqrt{\text{Nu}}\, \bm{u}_{\text{FT}}.
 \label{eqn:ra_relation}
@@
 
-Throughout this work, we will also measure the evolved P\'{e}clet number (Pe) and in section \ref{sec:rotating_results} we will measure the Rossby number (Ro).
+Throughout this work, we will also measure the evolved P\'{e}clet number (Pe) and in section \ref{sec:results_rotating} we will measure the Rossby number (Ro).
 These nondimensional quantities are defined as
@@
 The time evolution of FT simulations is sensitive to the choice of initial conditions made due to the fact that the evolved, nonlinear convective dynamics determine the mean temperature for this choice of boudnary conditions.
-For this reason, we will study FT simulations which employ three different formulations of the initial temperature field.
+For this reason, we will study FT simulations which employ three different initial states.
 
@@
 \begin{equation}
-T_c(z) = 0.5 - z.
+T_c(z) = T_0(z) = 0.5 - z.
 \end{equation}
@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = \grad_{\text{interior}} + w(z)(-1 - \grad_{\text{interior}}),
+\frac{\partial T_N}{\partial z} = \grad_{\text{interior}} + w(z)(-1 - \grad_{\text{interior}}).
 \end{equation}
-where $w(z)$ is a windowing function which sets the temperature gradient to $-1$ near the boundaries,
+Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $w(z)$, to set the temperature gradient to $-1$ near the boundaries,
 $$
-w(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_w)}{0.5\delta_w}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_w)}{0.5\delta_w}\right]\right),
+w(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_w)}{0.5\delta_w}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_w)}{0.5\delta_w}\right]\right).
 $$
 Here, $\delta_w = -\Delta T / 2$, an estimate of the boundary layer width, and $\grad_{\text{interior}}$, the temperature gradient in the interior of the domain, is determined by setting $\int \partial_z T_N dz = \Delta T$.
-%why do we choose erf? why don't we specify a "right" bl shape?
 
 \paragraph{TT-to-FT}
-In some experiments, the proper Nu~vs.~Ra law is not well-known, or is not agreed upon by the community (see e.g.,~Sec.\ref{sec:rotation}).
+In some experiments, the ``proper'' Nu~vs.~Ra law is not well-known, or is not agreed upon by the community (see e.g.,~Sec.\ref{sec:rotation}).
 For such cases, it may still be numerically useful to be able to study converged FT simulations without having to resort to classical ICs.
@@
 \ea{\paragraph{Additional ICs}
-In all cases, we assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
-We assume zero velocity in the initial state, except in the case of TT-to-FT simulations.
+In all cases, we modify the initial temperature profile by specifying the value of $T_1$, rather than through modifications to the linearly unstable reference profile, $T_0$.
+We furthermore assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
+We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
 For classical and Nu-based ICs,
@@
 \paragraph{Evolutionary Timescales}
-The thermal energy reservoir of our 2D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
+The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
 \begin{equation}
-E = \iint T\,dx\,dz = \Gamma \int T\,dz,
+E = \iiint T\,dx\,dy\,dz = \Gamma^2 \int T\,dz,
 \qquad
-\frac{dE}{dt} = -\iint \grad\cdot F_{\text{cond}}\,dx\,dz = -\Gamma F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\iiint \grad\cdot F_{\text{cond}}\,dx\,dy\,dz = -\Gamma^^22 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
@@
 Where the final expression is for the large Ra case where Nu$^{-1} \rightarrow 0$.
-The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but monotonically decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
+The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
 However, it is reasonable to assume that the evolutionary timescale lies within the window $\tau_{\text{th, FT-classical}} \in [\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1}, \sqrt{\text{Ra Pr}}]$.
@@
 %%%%%%%%%%%%
-\section{Results}
-\label{sec:2d_results}
+\section{Results: How initial conditions influence evolutionary timescales}
+\label{sec:results_timescales}
 
-\subsection{Time Evolution}
-\label{sec:time_evolution}
+\subsection{Classical initial conditions: long thermal relaxation}
+\label{sec:time_evolution_classic_ICs}
 
@@
 In the bottom four panels, we examine these temperature fields statistically by displaying their probability distribution functions (PDFs).
-To create these PDFs, we sample the full simulation temperature field once every simulation freefall time unit over the span of 500 time units.
+To create these PDFs, we sample the full simulation temperature field once every freefall time unit\footnote{\ea{For TT simulations, a freefall time unit is one simulation time unit.
+For FT simulations, a freefall time unit is $\sqrt{\text{Nu}}$ simulation time units.}} over the span of 500 time units.
 We interpolate the (unevenly spaced) vertical Chebyshev grid points onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
@@
 We find that FT simulations carry marginally more flux (higher Nu) and are more turbulent (higher Pe) than comparable TT simulations as they relax through this parameter space.
+\ea{(TODO)}
+%TODO: report scaling laws.
 These heightened values of Nu and Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
 
+Achieving thermal relaxation in pure FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
+For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
 FT simulation dynamics evolve slowly during thermal relaxation, and these images, PDFs, and traces demonstrate the importance of waiting for thermal relaxation to be achieved when conducting an FT simulation.
@@
 
-\vspace{-0.25cm}
-\subsection{Evolved Structure}
-\vspace{-0.5cm}
-\begin{figure}
-\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
-\caption{ 
-	(Left three panels) We compare time- and horizontally-averaged profiles from an FT (orange) and TT (purple) simulation at Ra$_{\Delta T} = 10^{9}$.
-	Shown are the (top) temperature, (middle) temperature in upflows (solid) and downflows (dashed), and (bottom) enthalpy (solid) and conductive (dashed) fluxes.
-	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
-	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
-	The insets show the \% difference between the FT and TT solutions.
-	There are slight (a few \%) differences between the two cases near the bottom boundary, but otherwise the two cases are nearly the same to within $\sim 1$\%.
-\label{fig:rbc_1D_profiles} }
-\vspace{0.5cm}
-\end{figure}
+\ea{
+\subsection{Nu-based initial conditions: rapid equilibration in \RB convection}
+\label{sec:time_evolution_classic_ICs}
 
-In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Time averages are taken over 500 nondimensional freefall time units for the TT case and over 2000 nondimensional freefall time units for the FT case, sampled once every 0.1 time units (the difference in averaging window is explained in Sec.~\ref{sec:timescales}).
-In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
-Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
-Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
-Inset panels show the percentage difference between the FT and TT solutions.
-In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
-The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the largest deviations away from zero in the interior are O(0.01) in the plotted units.
+}
 
-We find good ($\sim 1\%$) agreement between the FT and TT temperature profiles and enthalpy fluxes throughout the full depth of the domain, with slightly larger differences near the bottom boundary where the boundary conditions differ.
-When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
-These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
-
-\subsection{TT-to-FT: Rapidly equilibrated FT simulations}
+\subsection{TT-to-FT: arbitrary rapidly equilibrated FT simulations}
 \label{sec:tt-to-ft}
@@
 
-Achieving thermal relaxation in pure FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
-For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
-In the previous sections, we have shown that relaxed FT and TT simulations are very similar.
+\ea{Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
 It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.
-
-We now briefly describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
-In short, the evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for an FT simulation.
-Throughout this work, we will refer to simulations conducted this way as ``TT-to-FT'' simulations.
-To achieve this, we perform these steps:
-\begin{enumerate}
-\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
-Measure $\text{Nu}$ in that state.
-\item Re-nondimensionalize from $\Delta = \Delta T \rightarrow \partial_z T$, and from Ra$_{\Delta T}\rightarrow$Ra$_{\partial_z T}$, as in Eqn.~\ref{eqn:ra_relation}.
-In our freefall nondimensionalization, this means setting the velocities in the FT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{TT}} / \sqrt{\text{Nu}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{TT}} / \text{Nu}$.
-\item Restart the simulation with FT boundaries and continue timestepping.
-\end{enumerate}
-We show this procedure in practice in Fig.~\ref{fig:rbc_restart_description}.
+We show \ea{the results of using our TT-to-FT initial conditions procedure} in practice in Fig.~\ref{fig:rbc_restart_description}.
 In the left three panels, we display the temporal behavior of (top) Ra, (middle) the flux at the bottom boundary, and (bottom) the temperature difference between the top and bottom boundaries.
-We take the full evolution of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, then change its boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$ and restart the simulation using the above procedure.
+We take the full evolution of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, then change its boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$.
 The change from TT to FT boundaries occurs at the time denoted by the thin vertical line.
@@
 
-We note briefly that this TT-to-FT mechanism is only one of many ways of accelerating the thermal relaxation of an FT simulation.
+We note briefly that \ea{Nu-based ICs and} this TT-to-FT mechanism \ea{are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
+
+\subsection{3D verification of 2D results}
+
+\section{Results: Evolved dynamics and asymmetries in FT simulations}
+\label{sec:results_dynamics}
+
+\subsection{Evolved Structure}
+\begin{figure}
+\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
+\caption{ 
+	(Left three panels) We compare time- and horizontally-averaged profiles from an FT (orange) and TT (purple) simulation at Ra$_{\Delta T} = 10^{9}$.
+	Shown are the (top) temperature, (middle) temperature in upflows (solid) and downflows (dashed), and (bottom) enthalpy (solid) and conductive (dashed) fluxes.
+	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
+	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
+	The insets show the \% difference between the FT and TT solutions.
+	There are slight (a few \%) differences between the two cases near the bottom boundary, but otherwise the two cases are nearly the same to within $\sim 1$\%.
+\label{fig:rbc_1D_profiles} }
+\vspace{0.5cm}
+\end{figure}
+
+In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
+Time averages are taken over 500 nondimensional freefall time units for the TT case and over 2000 nondimensional freefall time units for the FT case, sampled once every 0.1 time units (the difference in averaging window is explained in Sec.~\ref{sec:timescales}).
+In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
+Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
+Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
+Inset panels show the percentage difference between the FT and TT solutions.
+In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
+The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the largest deviations away from zero in the interior are O(0.01) in the plotted units.
+
+We find good ($\sim 1\%$) agreement between the FT and TT temperature profiles and enthalpy fluxes throughout the full depth of the domain, with slightly larger differences near the bottom boundary where the boundary conditions differ.
+When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
+These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
 
@@
 
-\section{Rotating \RB Convection}
-\label{sec:rotating_results}
+\section{Results: Rotating \RB Convection}
+\label{sec:results_rotating}
 
@@
 \hline
-TT			&	$1.00 \times 10^8$		&	512x1024	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
-FT			&	$2.61 \times 10^9$		&	1024x2048	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
-TT-to-FT	&	$2.61 \times 10^9$		&	512x1024	&	1000		&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
-TT			&	$2.15 \times 10^8$		&	512x1024	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
-TT			&	$4.64 \times 10^8$		&	1024x2048	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
-TT			&	$1.00 \times 10^9$		&	1024x2048	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
-FT			&	$4.83 \times 10^{10}$	&	2048x4096*	&	16230		&	$5.36 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
-TT-to-FT	&	$4.83 \times 10^{10}$	&	1024x2048	&	1000		&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
-TT			&	$2.15 \times 10^9$		&	1024x2048	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
-TT			&	$4.64 \times 10^9$		&	1536x3072	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
-TT			&	$1.00 \times 10^{10}$	&	2048x4096	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
-TT-to-FT	&	$9.51 \times 10^{11}$	&	2048x4096	&	1000		&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
+TT			&	$1.00 \times 10^8$		&	1024x512	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
+FT			&	$2.61 \times 10^9$		&	2048x1024	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
+TT-to-FT	&	$2.61 \times 10^9$		&	1024x512	&	1000		&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
+TT			&	$2.15 \times 10^8$		&	1024x512	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
+TT			&	$4.64 \times 10^8$		&	2048x1024	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
+TT			&	$1.00 \times 10^9$		&	2048x1024	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
+FT			&	$4.83 \times 10^{10}$	&	4096x2048*	&	16230		&	$5.36 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
+TT-to-FT	&	$4.83 \times 10^{10}$	&	2048x1024	&	1000		&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
+TT			&	$2.15 \times 10^9$		&	2048x1024	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
+TT			&	$4.64 \times 10^9$		&	3072x1536	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
+TT			&	$1.00 \times 10^{10}$	&	4096x2048	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
+TT-to-FT	&	$9.51 \times 10^{11}$	&	4096x2048	&	1000		&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
 \hline																	

### 2020-05-11 figures_and_data/rbc_1D_profiles.py
updated FT PDFs (longer run time). Restructures rbc directory names

@@ -90,14 +90,14 @@ def read_asymms(ra_list, dir_list):
     return full_data
 
 
-mixed_dirs = glob.glob("./data/rbc/mixedFT_2d/ra*/")
-fixed_dirs = glob.glob("./data/rbc/fixedT_2d/ra*/")
-restarted_dirs = glob.glob("./data/rbc/restarted_mixed_T2m/ra*/")
-numbered_dirs  = [(f, float(f.split("./data/rbc/mixedFT_2d/ra")[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("./data/rbc/classic_FT_2D/ra*/")
+fixed_dirs = glob.glob("./data/rbc/TT_2D/ra*/")
+restarted_dirs = glob.glob("./data/rbc/TT-to-FT_2D/ra*/")
+numbered_dirs  = [(f, float(f.split("./data/rbc/classic_FT_2D/ra")[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/fixedT_2d/ra")[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT_2D/ra")[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/restarted_mixed_T2m/ra")[-1].split("/")[0])) for f in restarted_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT-to-FT_2D/ra")[-1].split("/")[0])) for f in restarted_dirs]
 restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_profs = read_profs(mixed_ras, mixed_dirs)

### 2020-05-11 figures_and_data/rbc_dynamics_asymmetries.py

@@ -70,14 +70,14 @@ def read_pdfs(ra_list, dir_list):
             full_data['{:.4e}'.format(ra)] = data
     return full_data
 
-mixed_dirs = glob.glob("./data/rbc/mixedFT_2d/ra*/")
-fixed_dirs = glob.glob("./data/rbc/fixedT_2d/ra*/")
-restarted_dirs = glob.glob("./data/rbc/restarted_mixed_T2m/ra*/")
-numbered_dirs  = [(f, float(f.split("./data/rbc/mixedFT_2d/ra")[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("./data/rbc/classic_FT_2D/ra*/")
+fixed_dirs = glob.glob("./data/rbc/TT_2D/ra*/")
+restarted_dirs = glob.glob("./data/rbc/TT-to-FT_2D/ra*/")
+numbered_dirs  = [(f, float(f.split("./data/rbc/classic_FT_2D/ra")[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/fixedT_2d/ra")[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT_2D/ra")[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/restarted_mixed_T2m/ra")[-1].split("/")[0])) for f in restarted_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT-to-FT_2D/ra")[-1].split("/")[0])) for f in restarted_dirs]
 restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_pdfs(mixed_ras, mixed_dirs)
@@ -134,7 +134,7 @@ ax.set_xlim(0, np.max(mx/dT))
 plt.sca(axs[1])
 ax = axs[1]
 
-with h5py.File('./data/rbc/restarted_mixed_T2m/ra9.51e11/temp_slice.h5', 'r') as f:
[…]

### 2020-05-11 figures_and_data/rbc_evolution_dynamics.py

@@ -71,14 +71,14 @@ def read_pdfs(ra_list, dir_list):
             full_data['{:.4e}'.format(ra)] = data
     return full_data
 
-mixed_dirs = glob.glob("./data/rbc/mixedFT_2d/ra*/")
-fixed_dirs = glob.glob("./data/rbc/fixedT_2d/ra*/")
-restarted_dirs = glob.glob("./data/rbc/restarted_mixed_T2m/ra*/")
-numbered_dirs  = [(f, float(f.split("./data/rbc/mixedFT_2d/ra")[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("./data/rbc/classic_FT_2D/ra*/")
+fixed_dirs = glob.glob("./data/rbc/TT_2D/ra*/")
+restarted_dirs = glob.glob("./data/rbc/TT-to-FT_2D/ra*/")
+numbered_dirs  = [(f, float(f.split("./data/rbc/classic_FT_2D/ra")[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/fixedT_2d/ra")[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT_2D/ra")[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("./data/rbc/restarted_mixed_T2m/ra")[-1].split("/")[0])) for f in restarted_dirs]
+numbered_dirs  = [(f, float(f.split("./data/rbc/TT-to-FT_2D/ra")[-1].split("/")[0])) for f in restarted_dirs]
 restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_pdfs(mixed_ras, mixed_dirs)
@@ -88,7 +88,7 @@ mixed_scalars = read_data(mixed_ras, mixed_dirs)
 fixed_scalars = read_data(fixed_ras, fixed_dirs)
[…]

### 2020-05-11 figures_and_data/rbc_restart_description.py

@@ -73,14 +73,14 @@ def read_pdfs(ra_list, dir_list):
 
 # Get data from files
 base_dir = './data/rbc/'
-mixed_dirs = glob.glob("{:s}mixedFT_2d/ra*/".format(base_dir))
-fixed_dirs = glob.glob("{:s}fixedT_2d/ra*/".format(base_dir))
-restarted_dirs = glob.glob("{:s}restarted_mixed_T2m/ra*/".format(base_dir))
-numbered_dirs  = [(f, float(f.split("{:s}mixedFT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("{:s}classic_FT_2D/ra*/".format(base_dir))
+fixed_dirs = glob.glob("{:s}TT_2D/ra*/".format(base_dir))
+restarted_dirs = glob.glob("{:s}TT-to-FT_2D/ra*/".format(base_dir))
+numbered_dirs  = [(f, float(f.split("{:s}classic_FT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("{:s}fixedT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("{:s}TT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("{:s}restarted_mixed_T2m/ra".format(base_dir))[-1].split("/")[0])) for f in restarted_dirs]
+numbered_dirs  = [(f, float(f.split("{:s}TT-to-FT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in restarted_dirs]
 restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_data(mixed_ras, mixed_dirs)

### 2020-05-11 figures_and_data/rbc_scalar_comparisons.py

@@ -61,14 +61,14 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
 
 # Get data from files
 base_dir = './data/rbc/'
-mixed_dirs = glob.glob("{:s}mixedFT_2d/ra*/".format(base_dir))
-fixed_dirs = glob.glob("{:s}fixedT_2d/ra*/".format(base_dir))
-restarted_dirs = glob.glob("{:s}restarted_mixed_T2m/ra*/".format(base_dir))
-numbered_dirs  = [(f, float(f.split("{:s}mixedFT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("{:s}classic_FT_2D/ra*/".format(base_dir))
+fixed_dirs = glob.glob("{:s}TT_2D/ra*/".format(base_dir))
+restarted_dirs = glob.glob("{:s}TT-to-FT_2D/ra*/".format(base_dir))
+numbered_dirs  = [(f, float(f.split("{:s}classic_FT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("{:s}fixedT_2d/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("{:s}TT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("{:s}restarted_mixed_T2m/ra".format(base_dir))[-1].split("/")[0])) for f in restarted_dirs]
+numbered_dirs  = [(f, float(f.split("{:s}TT-to-FT_2D/ra".format(base_dir))[-1].split("/")[0])) for f in restarted_dirs]
 restarted_dirs, restarted_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_data(mixed_ras, mixed_dirs)

### 2020-05-11 figures_and_data/rbc_3D_panels.py
adds script for 3D movie

@@ -1,0 +1,181 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+import dedalus.public as de
+
+
+mColor = 'darkorange'#olivedrab'
+fColor = 'indigo'
+colors = [fColor, mColor]
+
+# Get data from files
+base_dir = './data/rbc/3D/'
+TT_dir   = 'TT/ra1e8'
+FT_dir   = 'Nu_based_FT/ra2.61e9'
+
+data = OrderedDict()
+for label, dr in zip(['TT', 'FT'], [base_dir+TT_dir, base_dir+FT_dir]):
+    ra = float(dr.split('/')[-1].split('ra')[-1])
+
+    #Scalar Data
+    data[label] = OrderedDict()
+    with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+        for k in f.keys():
+            data[label][k] = f[k][()]
+
+    Nu = np.mean(data[label]['Nu'][-3500:])
+    data[label]['Nu_mean'] = Nu
+    if label == 'TT':
+        data[label]['t_ff'] = 1
+    else:
+        data[label]['t_ff'] = np.sqrt(Nu)
+    data[label]['ra_temp'] = ra*data[label]['delta_T']
+    data[label]['ra_flux'] = ra**(3./2)*data[label]['left_flux']
+
+    deltaT = np.mean(data[label]['delta_T'][-3500:])
+    data[label]['delta_T_mean'] = deltaT
+
+    #PDF data
+    with h5py.File('{:s}/pdfs/pdf_data.h5'.format(dr), 'r') as f:
+        for k in f.keys():
+            for sk in f[k].keys():
[…]

### 2020-05-11 figures_and_data/rotating_panels.py

@@ -61,11 +61,11 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
 
 # Get data from files
 base_dir = './data/rotation/'
-mixed_dirs = glob.glob("{:s}mixedFT/ra*/".format(base_dir))
-fixed_dirs = glob.glob("{:s}fixedT/ra*/".format(base_dir))
-numbered_dirs  = [(f, float(f.split("{:s}mixedFT/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
+mixed_dirs = glob.glob("{:s}classic_FT/ra*/".format(base_dir))
+fixed_dirs = glob.glob("{:s}TT/ra*/".format(base_dir))
+numbered_dirs  = [(f, float(f.split("{:s}classic_FT/ra".format(base_dir))[-1].split("/")[0])) for f in mixed_dirs]
 mixed_dirs, mixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
-numbered_dirs  = [(f, float(f.split("{:s}fixedT/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
+numbered_dirs  = [(f, float(f.split("{:s}TT/ra".format(base_dir))[-1].split("/")[0])) for f in fixed_dirs]
 fixed_dirs, fixed_ras = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
 
 mixed_data = read_data(mixed_ras, mixed_dirs)
@@ -255,9 +255,9 @@ plt.ylim(1, 7e2)
 
 #Panel 5-7, Colormaps
 
-early_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_early.h5'#slices/slices_t100_512x384x384_s1.h5'
-mid_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_mid.h5'#slices/slices_t5380_128x384x384_s1.h5'
-late_slice_f = 'data/rotation/mixedFT/ra2.1e10/vort_slice_late.h5'#slices/slices_t13215_128x384x384_s1.h5'
+early_slice_f = 'data/rotation/classic_FT/ra2.1e10/vort_slice_early.h5'#slices/slices_t100_512x384x384_s1.h5'
[…]

### 2020-05-11 tex/mixedft_evolution_ms.tex
expanded PDF moment table

@@
 \begin{center}
-\begin{tabular}{c c c c c c}
+\begin{tabular}{c c c c c c c}
 \hline																	
-Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
+Quantity 				&	BCs	& ICs	    &	$\mu$					&	$\sigma$				&	Skewness	&	Kurtosis \\
 \hline
-$T$				&	FT			&		$1.03 \times 10^{-2}$	&	$1.49 \times 10^{-3}$	&	0.656		&	27.0 \\
-				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
+$T/\Delta T$			&	TT	& Classic	&	$5.00 \times 10^{-1}$	&	$7.11 \times 10^{-2}$	&	$-1.53 \times 10^{-2}$	&	$2.01 \times 10^{1}$ \\
+						&	FT	& Classic	&	$5.07 \times 10^{-1}$	&	$7.37 \times 10^{-2}$	&	$7.31 \times 10^{-1}$	&	$2.70 \times 10^{1}$ \\
+						&	FT	& TT-to-FT	&	$5.08 \times 10^{-1}$	&	$7.34 \times 10^{-2}$	&	$7.18 \times 10^{-1}$	&	$2.70 \times 10^{1}$ \\
+						&	FT	& Nu-based	&	$5.06 \times 10^{-1}$	&	$7.36 \times 10^{-2}$	&	$7.63 \times 10^{-1}$	&	$2.70 \times 10^{1}$ \\
 \hline                                                                                                                      
-$\omega^2$		&	FT			&		$16.7$					&	$10.3$					&	96.2		&	$2.72 \times 10^4$ \\
-				&	TT-to-FT	&		$11.7$					&	$10.6$					&	86.0		&	$1.63 \times 10^4$ \\
+$\omega^2/\Delta T$		&	TT	& Classic	&	$3.99 \times 10^{2}$	&	$4.73 \times 10^{2}$	&	$5.87 \times 10^{1}$	&	$6.68 \times 10^{3}$ \\
+						&	FT	& Classic	&	$9.30 \times 10^{2}$	&	$4.79 \times 10^{2}$	&	$8.13 \times 10^{1}$	&	$1.76 \times 10^{4}$ \\
+						&	FT	& TT-to-FT	&	$6.37 \times 10^{2}$	&	$5.02 \times 10^{2}$	&	$6.56 \times 10^{1}$	&	$8.69 \times 10^{3}$ \\
+						&	FT	& Nu-based	&	$6.94 \times 10^{2}$	&	$4.84 \times 10^{2}$	&	$7.27 \times 10^{1}$	&	$1.20 \times 10^{4}$ \\
 \hline                                                                                                                      
-$wT$			&	FT			&		$4.50 \times 10^{-6}$	&	$4.87 \times 10^{-4}$	&	0.0133	&	$3.06$ \\
-				&	TT-to-FT	&		$4.47 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0110	&	$3.06$ \\
+$wT/(\Delta T)^{3/2}$	&	TT	& Classic	&	$1.46 \times 10^{-3}$	&	$1.63 \times 10^{-1}$	&	$5.14 \times 10^{-2}$	&	3.06 \\
+						&	FT	& Classic	&	$1.53 \times 10^{-3}$	&	$1.69 \times 10^{-1}$	&	$3.28 \times 10^{-2}$	&	2.92 \\
+						&	FT	& TT-to-FT	&	$1.51 \times 10^{-3}$	&	$1.67 \times 10^{-1}$	&	$3.63 \times 10^{-2}$	&	3.13 \\
+						&	FT	& Nu-based	&	$1.50 \times 10^{-3}$	&	$1.70 \times 10^{-1}$	&	$4.37 \times 10^{-2}$	&	3.20 \\
 \hline                                                                                                                    
-$w$				&	FT			&		$3.62 \times 10^{-6}$	&	$4.70 \times 10^{-2}$	&	-0.0211	&	$3.00$ \\
-				&	TT-to-FT	&		$4.22 \times 10^{-6}$	&	$4.82 \times 10^{-2}$	&	-0.0187	&	$3.02$ \\
+$w/(\Delta T)^{1/2}$ 	&	TT	& Classic	&	$-3.11 \times 10^{-5}$	&	$3.25 \times 10^{-1}$	&	$1.64 \times 10^{-2}$	&	2.99 \\
+						&	FT	& Classic	&	$-3.80 \times 10^{-5}$	&	$3.33 \times 10^{-1}$	&	$1.75 \times 10^{-3}$	&	2.85 \\
+						&	FT	& TT-to-FT	&	$2.66  \times 10^{-5}$	&	$3.29 \times 10^{-1}$	&	$-1.21 \times 10^{-3}$	&	3.08 \\
+						&	FT	& Nu-based	&	$2.41  \times 10^{-5}$	&	$3.35 \times 10^{-1}$	&	$1.08 \times 10^{-2}$	&	3.14 \\
 \hline																	

### 2020-05-11 figures_and_data/report_pdf_values.py

@@ -1,0 +1,149 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+#matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'left_T', 'right_T']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
[…]

### 2020-05-11 tex/mixedft_evolution_ms.tex
draft of revamp of 3D figure

--- 2020-05-04 tex/mixedft_evolution_ms.tex
@@
 \begin{center}
-\begin{tabular}{c c c c c c}
+\begin{tabular}{c c c c c c c}
 \hline																	
-Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
+Quantity 				&	BCs	& ICs	    &	$\mu$					&	$\sigma$				&	Skewness	&	Excess Kurtosis \\
 \hline
-$T$				&	FT			&		$1.03 \times 10^{-2}$	&	$1.49 \times 10^{-3}$	&	0.656		&	27.0 \\
-				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
+$T/\Delta T$			&	TT	& Classic	&	$5.00 \times 10^{-1}$	&	$7.11 \times 10^{-2}$	&	$-1.53 \times 10^{-2}$	&	$1.71 \times 10^{1}$ \\
+						&	FT	& Classic	&	$5.07 \times 10^{-1}$	&	$7.37 \times 10^{-2}$	&	$7.31 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
+						&	FT	& TT-to-FT	&	$5.08 \times 10^{-1}$	&	$7.34 \times 10^{-2}$	&	$7.18 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
+						&	FT	& Nu-based	&	$5.06 \times 10^{-1}$	&	$7.36 \times 10^{-2}$	&	$7.63 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
 \hline                                                                                                                      
-$\omega^2$		&	FT			&		$16.7$					&	$10.3$					&	96.2		&	$2.72 \times 10^4$ \\
-				&	TT-to-FT	&		$11.7$					&	$10.6$					&	86.0		&	$1.63 \times 10^4$ \\
+$\omega^2/\Delta T$		&	TT	& Classic	&	$3.99 \times 10^{2}$	&	$4.73 \times 10^{2}$	&	$5.87 \times 10^{1}$	&	$6.68 \times 10^{3}$ \\
+						&	FT	& Classic	&	$9.30 \times 10^{2}$	&	$4.79 \times 10^{2}$	&	$8.13 \times 10^{1}$	&	$1.76 \times 10^{4}$ \\
+						&	FT	& TT-to-FT	&	$6.37 \times 10^{2}$	&	$5.02 \times 10^{2}$	&	$6.56 \times 10^{1}$	&	$8.69 \times 10^{3}$ \\
+						&	FT	& Nu-based	&	$6.94 \times 10^{2}$	&	$4.84 \times 10^{2}$	&	$7.27 \times 10^{1}$	&	$1.20 \times 10^{4}$ \\
 \hline                                                                                                                      
-$wT$			&	FT			&		$4.50 \times 10^{-6}$	&	$4.87 \times 10^{-4}$	&	0.0133	&	$3.06$ \\
-				&	TT-to-FT	&		$4.47 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0110	&	$3.06$ \\
+$wT/(\Delta T)^{3/2}$	&	TT	& Classic	&	$1.46 \times 10^{-3}$	&	$1.63 \times 10^{-1}$	&	$5.14 \times 10^{-2}$	&	$5.85  \times 10^{-2}$ \\
+						&	FT	& Classic	&	$1.53 \times 10^{-3}$	&	$1.69 \times 10^{-1}$	&	$3.28 \times 10^{-2}$	&	$-8.19 \times 10^{-2}$ \\
+						&	FT	& TT-to-FT	&	$1.51 \times 10^{-3}$	&	$1.67 \times 10^{-1}$	&	$3.63 \times 10^{-2}$	&	$1.29  \times 10^{-1}$ \\
+						&	FT	& Nu-based	&	$1.50 \times 10^{-3}$	&	$1.70 \times 10^{-1}$	&	$4.37 \times 10^{-2}$	&	$1.95  \times 10^{-1}$ \\
 \hline                                                                                                                    
-$w$				&	FT			&		$3.62 \times 10^{-6}$	&	$4.70 \times 10^{-2}$	&	-0.0211	&	$3.00$ \\
-				&	TT-to-FT	&		$4.22 \times 10^{-6}$	&	$4.82 \times 10^{-2}$	&	-0.0187	&	$3.02$ \\
+$w/(\Delta T)^{1/2}$ 	&	TT	& Classic	&	$-3.11 \times 10^{-5}$	&	$3.25 \times 10^{-1}$	&	$1.64 \times 10^{-2}$	&	$-1.16 \times 10^{-2}$ \\
+						&	FT	& Classic	&	$-3.80 \times 10^{-5}$	&	$3.33 \times 10^{-1}$	&	$1.75 \times 10^{-3}$	&	$-1.48 \times 10^{-1}$ \\
+						&	FT	& TT-to-FT	&	$2.66  \times 10^{-5}$	&	$3.29 \times 10^{-1}$	&	$-1.21 \times 10^{-3}$	&	$7.89  \times 10^{-2}$ \\
+						&	FT	& Nu-based	&	$2.41  \times 10^{-5}$	&	$3.35 \times 10^{-1}$	&	$1.08 \times 10^{-2}$	&	$1.37  \times 10^{-1}$ \\
 \hline																	

### 2020-05-11 figures_and_data/rbc_3D_panels.py

@@ -56,6 +56,17 @@ for label, dr in zip(['TT', 'FT'], [base_dir+TT_dir, base_dir+FT_dir]):
             for sk in f[k].keys():
                 data[label]['pdf_{:s}_{:s}'.format(k, sk)] = f[k][sk][()]
 
+    with h5py.File('{:s}/pdfs_xy/pdf_data.h5'.format(dr), 'r') as f:
+        for k in f.keys():
+            for sk in f[k].keys():
+                data[label]['pdf_xy_{:s}_{:s}'.format(k, sk)] = f[k][sk][()]
+
+    with h5py.File('{:s}/pdfs_xz/pdf_data.h5'.format(dr), 'r') as f:
+        for k in f.keys():
+            for sk in f[k].keys():
+                data[label]['pdf_xz_{:s}_{:s}'.format(k, sk)] = f[k][sk][()]
+
+
     #slice data
     with h5py.File('{:s}/temp_slice.h5'.format(dr), 'r') as f:
         for k in f.keys():
@@ -66,45 +77,22 @@ for k in data['TT']: print(k)
 
 
 # Set up figure subplots
-fig = plt.figure(figsize=(7.5, 3))
+fig = plt.figure(figsize=(7.5, 8))
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [( (0  , 0  ),       450,    250),
-            ( (550, 0  ),       450,    250),
-            ( (50 , 280),       450,    360),
-            ( (50 , 640),       450,    180),
-            ( (50 , 820),       450,    180),
-            ( (500, 280),       450,    360),
-            ( (500, 640),       450,    180),
-            ( (500, 820),       450,    180),
+subplots = [( (0 , 100),      165,    352),
+            ( (175, 100),     330,    352),
+            ( (515, 100),     330,    352),
+            ( (0,  500),      165,    352),
+            ( (175, 500),     330,    352),
+            ( (515, 500),     330,    352),
+            ( (860, 0),       140,    200),
+            ( (860, 267),     140,    200),
+            ( (860, 533),     140,    200),
[…]

### 2020-05-12 figures_and_data/rbc_3D_panels.py
rearranges vertical slice to middle, fills up white space with labels a bit

@@ -80,16 +80,16 @@ for k in data['TT']: print(k)
 fig = plt.figure(figsize=(7.5, 8))
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [( (0 , 100),      165,    352),
-            ( (175, 100),     330,    352),
-            ( (515, 100),     330,    352),
-            ( (0,  500),      165,    352),
-            ( (175, 500),     330,    352),
-            ( (515, 500),     330,    352),
-            ( (860, 0),       140,    200),
-            ( (860, 267),     140,    200),
-            ( (860, 533),     140,    200),
-            ( (860, 800),     140,    200),
+subplots = [( (0 ,  175),     330,    352),
+            ( (340, 175),     165,    352),
+            ( (515, 175),     330,    352),
+            ( (0,   575),      330,    352),
+            ( (340, 575),     165,    352),
+            ( (515, 575),     330,    352),
+            ( (860, 0),       140,    180),
+            ( (860, 273),     140,    180),
+            ( (860, 547),     140,    180),
+            ( (860, 820),     140,    180),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec((150, 950), 500, 50))
@@ -120,37 +120,39 @@ for i, bc in enumerate(data.keys()):
     vert_map = data[bc]['slice_T'] - np.mean(data[bc]['slice_T'], axis=0)
     maxval = data[bc]['delta_T_mean']/3
 
+    horiz_field.set_scales(1)
+    horiz_field['g'] = top_map
+    horiz_field.set_scales(horiz_scales, keep_data=True)
+    c = axs[0+3*i].pcolormesh(xx_tb,  yy_tb,  horiz_field['g'],  vmin=-maxval, vmax=maxval, cmap='RdBu_r')
+
+
     vert_field.set_scales(1)
     vert_field['g'] = vert_map
     vert_field.set_scales(vert_scales, keep_data=True)
[…]

### 2020-05-12 referee_responses/submission1/referee_response.tex
draft of referee response

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Emmanuel,
$\,$\newline

\begin{singlespace}
We return our revised manuscript, ``Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it.'' 
We have addressed the questions and concerns of the referees, and we rebut the claim of referee 2 that our results are not novel.
We would like to point out a few major changes in this version of the manuscript:
\begin{enumerate}
\item The ``Simulation Details'' section has been broken up into subsections, and two new subsections have been added. These discuss:
\begin{enumerate}
\item The different initial conditions used in the simulations in this work.
The description of our TT-to-FT procedure has been moved here.
Per the advice of referee 1, we have also added and studied new ``Nu-based'' boundary conditions.
\item Evolutionary and dynamical timescales.
The text of the ``changing timescales'' section, previously in the results, has been moved here.
\end{enumerate}
\item The ``Results'' section has been broken up into two major sections.
The first focuses on the time evolution of FT simulations which employ different initial conditions, and it compares their equilibrated states.
The second focuses on asymmetries in the flows introduced by the boundary conditions.
\item Our non-rotating 2D results have been verified with a 3D case.
\end{enumerate}
Aside from these major changes, we have cleaned up the text throughout the paper for clarity, including in the abstract.
We have included a ``redlined'' version of the manuscript in this resubmission which highlights the changes we have made to the text of the manuscript.

We feel that the clarity and scientific content of the paper have been greatly improved by the report of referee 1, and we thank that referee for their honest critiques and attention to detail. 
Below we include our responses to both referee reports; the original text of the reports is included in italics, and our responses follow inline in unitalicized blocks.

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Geoffrey M. Vasil, Benjamin P. Brown, and Lydia Korre

\newpage
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
This is an interesting paper presenting numerical simulations of convection (Rayleigh-B\'{e}nard and rotating Rayleigh-B\'{e}nard) with specific boundary conditions relevant for astrophysical fluid dynamics. 
2 objectives are pursued: (i) a scientific one, i.e. describing the typical behaviour and scaling laws of convection with mixed, imposed flux / imposed temperature, boundaries; (ii) a technical / numerical one, i.e. finding a rapid and easy way to reach statistical equilibrium in such simulations. 
Presented results are new and successfully fulfill both objectives. 
I recommend the publication of the paper providing the following comments are accounted for and the following questions are answered.
\end{myquotation}

We would like to thank the referee for the care with which they read our manuscript, and for their excellent constructive criticism.
We hope that the changes to the manuscript, including those described in our inline responses below, have answered all questions that have been raised.

\begin{myquotation}
Questions

All the discussions about the time necessary to reach statistical equilibrium obviously depend on the chose initial conditions: that should be made crystal clear each time (see e.g. in conclusion, bottom of page 10… see also introduction p.1 : ``the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature'').
\end{myquotation}
This is an excellent point, and we have restructured the paper to try to make this abundantly clear.
Section 2 (``Simulation Details'') now contains a subsection dedicated to initial conditions, and throughout the paper we have tried to clarify that thermal relaxation timescales depend on initial conditions.

\begin{myquotation}
Your chosen initial conditions are a linear temperature from 1 at the bottom to 0 at the top, and I guess, zero velocity everywhere and matching hydrostatic pressure (that should be mentioned in the text). 
\end{myquotation}
This has now been clarified in section II.C (see the ``Additional ICs'' paragraph).
The linear temperature profile is now also referred to as ``Classical ICs''.

\begin{myquotation}
Those initial conditions are obviously wrong for the FT simulations whose overall temperature contrast is much smaller than 1. 
This FT equilibrium temperature contrast can be estimated using your results showing that FT final state is comparable to TT final state, hence using classical scaling law for Nusselt (I like Nu=(Ra/Rac)$^(1/3)$, but what follows can be easily adapted to your favorite one):
\begin{itemize}
\item One can define an effective Rayleigh number Ra$_e$, based on the real temperature contrast deltaT rather than the initial (wrong) DeltaT: then Ra$_e$ = Ra * deltaT/DeltaT.
\item The final heat flux follows the classical scaling law for Nu, considering Ra$_e$ and the non-dimensionalisation by deltaT. 
Hence the final, dimensional, heat flux is F=(Ra$_e$/Rac)$^{1/3}$*k*deltaT/Lz.
\item But this heat flux is also equal to the imposed one at the bottom, equal by definition to F=k*DeltaT/Lz.
\item Hence equating the two, one find deltaT=DeltaT*(Rac/Ra)$^{1/4}$. So several questions there: 
\begin{itemize}
	\item Does this scaling hold in your simulation? It does in the rapid tests I ran. It also seems ~OK with the temperature range in your figure 1, bottom right.
	\item Instead of using your strategy to define initial conditions for FT simulation derived from TT simulation, which still requires to compute the FT solution, wouldn’t it be easier and more efficient to use as the initial conditions zero velocity everywhere, plus a linear temperature profile from deltaT/DeltaT at the bottom to 0 at the top, eventually with some local regularization to match the imposed flux at the bottom? 
	Then you would start from a solution much closer to the final one, without even having to compute a TT solution.
\end{itemize}
\end{itemize}
\end{myquotation}
There are two questions here, and we'll respond to each bullet in order:
\begin{enumerate}
\item We agree with the logic of the math here, and that if you have a given law, Nu $\propto$ Ra$_e^{\alpha}$, you can retrieve a law for deltaT$\propto Ra^{-\alpha/(1+\alpha)}$ (where this exponent is 1/4 for $\alpha = 1/3$).
This is now shown in the paper (see eqn 15).
We have presented this in its general form so that people can chose their favorite or best-fit scaling law.
Due to its excellent agreement with the simulations we ran, we have chosen to stick with the $\alpha = 0.285$ law that we have used previously in this work.
This means that a Ra$^{-0.22}$ law is a better fit for our data than Ra$^{-1/4}$, but those are pretty hard to distinguish between; so -- yes, this scaling roughly holds in our simulations.
\item For the specific case of classical RBC, the initial conditions that you describe here are probably simpler to use than our TT-to-FT initial conditions.
See section II.C for a description of these ``Nu-based'' initial conditions, and section III.(TODO) for a description of evolution in these systems.
One difficulty of using Nu-based initial conditions is that they are sensitive to the Nu vs.~Ra law that is used.
For more complex simulations (e.g., rotationally- or magnetically- constrained RBC) where the Nu vs.~Ra laws are more contentious and less universally agreed-upon in the community, Nu-based ICs which presume the answer may be less reliable than TT-to-FT simulations.
\end{enumerate}

\begin{myquotation}
With this estimate, we can also quantify the amount of energy (the reservoir) that has to be evacuated before reaching steady state: it is E$\sim$rhoCp(DeltaT-deltaT)*Lz/2 per unit surface. 
This must be evacuated by the top/bottom flux F=kDeltaT/Lz. 
Hence the ratio gives us a typical timescale for reaching equilibrium: t$_{eq}$ = E/F = 0.5*Lz$^2$/Kappa*(1-deltaT/DeltaT), i.e. a diffusive time…
Does this scaling law hold? It seems not completely crazy according to your figure 2 left.
\end{myquotation}
Deriving the equilibration time is a bit trickier than this estimate because the difference between the flux leaving through the top of the domain constantly evolves over time.
We've added a derivation of this timescale and a discussion of this subtlety to a new section II.D.
(TODO: Does this scaling law hold?)

\begin{myquotation}
Comments:

-       The abstract is not fully self-consistent and might lead to misunderstanding.
For instance, you do no clearly define the meaning of FT. 
Also, you mention astrophysical simulations, meaning for me (and others I guess) compressible convection: you should mention that your work is in the Boussinesq framework.
\end{myquotation}
TODO: We have rewritten the abstract for self-consistency and clarity.
\begin{myquotation}
-       P.3, lettering and numbering: it is strange to suddenly have a subsection A at the end of section II, while all the beginning was not labelled.
\end{myquotation}
We have rearranged section II so that it has a few distinct subsections to help assist reader navigation.
\begin{myquotation}
-       Figure 1: how did you chose the scales for the temperature axis of the bottom figures? 
I would e.g. align the median values with the top figures (not done on the left).
\end{myquotation}
For the right two PDFs, we chose scales so as to align median values.
For the left two PDFs, we chose scales which tried to show the shape of the PDFs and avoid excess white space.
TODO: We have adjusted the scale of the the bottom left PDF so that its median value is aligned with the top left panel.
\begin{myquotation}
-       P.5 and figure 3: how do you define the boundary layers?
\end{myquotation}
We have defined the boundary layers as the parts of the domain where conduction carries more than $20\%$ of the flux.
TODO: Do we do something more traditional or do we at least say this in the text?
\begin{myquotation}
-       P.9, lettering and numbering: it is strange to suddenly have a subsubsection “1. Changing Timescales” at the very end of this subsection C.
\end{myquotation}
Agreed.
The info in this subsection has been relocated to the section II.D.
Section III has been split into a few sections (one each for the different IC choices, and one for 3D).

\begin{myquotation}
-       P.10: you don’t prove the validity of your results in 3D in the non-rotating case. 
I don’t see any reason why it would be different from 2D, but is it impossible to run one case to show it?
\end{myquotation}
TODO: We have added section III.D and Fig.~4 to show that 3D results are in line with 2D results.

\begin{myquotation}
Typo:
p.3: The codeS used to run simulations and to create the figures...
Caption of figure 2: “Re vs. Ra is compensated…” -> Pe vs. Ra
\end{myquotation}
TODO: These typos have been fixed.

\newpage
\noindent
\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
\begin{myquotation}
In this manuscript the authors focus on the different equilibration times required by simulations of Rayleigh-B\'{e}nard flows with fixed temperature boundaries (referred to as T-T) or with one fixed temperature and one fixed heat flux wall (F-T). 
They investigate mostly 2D cases although they consider also 3D configurations but in a rotating environment and with free slip boundaries. 
\end{myquotation}
We have now verified our results in a 3D case with no-slip boundaries, analagous to our 2D setup, in section III.D.
The introduction to the rotating case now provides more context to show that rotating RBC is a good testing bed for our TT-to-FT method.

\begin{myquotation}
The claims of the paper are well known among people studying these problems and I do not see any novelty in the results of this paper. 
\end{myquotation}
We disagree.
Through discussions with numerous colleagues and a deeper literature review, we are convinced that our results are novel.
We have rewritten the abstract of the paper, restructured the Simulation Details and Results sections, and added a few references throughout the manuscript.
These changes have aimed to improve the clarity and logical flow of our paper, and also have tried to better place our results in the context of the literature.

If these results are truly well-known in the community, provide us with references.

\begin{myquotation}
In a flow with imposed boundary conditions (T-T) the mean temperature is known a-priori and, if the initial condition has that average temperature, the flow needs only to equilibrate through the boundary layer that, being much thinner that the boundary distance, take much less time.

On the other hand, when the heat flux is assigned, the mean temperature is unknown and equilibrating the bulk takes a time $\sim\sqrt{Ra/Pr}/Nu$. 
\end{myquotation}
Section II.C and II.D now discusses how initial conditions affect thermal relaxation timescales.

\begin{myquotation}
Also, imposing a boundary temperature entails the flow to develop any temperature gradient, while imposing the gradient at the wall limits the peaks. 
What the authors call "energy reservoir" is nothing but the heat capacity of the fluid volume that, of course, takes more time to thermally equilibrate than the thin boundary layers.
\end{myquotation}
TODO: I don't even know how to respond to this.

\begin{myquotation}
The analysis of the rotating Rayleigh-B\'{e}nard cases is very qualitative and it overlooks most of the relevant literature.
\end{myquotation}
Our goal is not to robustly examine rotating RBC.
Our goal is to show that:
\begin{enumerate}
\item Timescale lessons in non-rotating convection apply to rotating convection (unsurprising), and therefore
\item our TT-to-FT initial conditions can save a great deal of time in the rotating case where Nu vs.~Ra powerlaws are less well agreed-upon by the community, and the evolved Delta T is truly unknown.
\end{enumerate}
We have also added additional references to the literature.

\begin{myquotation}
The paper, finally, does not read well, with many imprecise, naive or bold statements: I report in the following a couple of examples. 
"For this choice of boundary conditions, the critical value of the Rayleigh number is Ra∂z T = 1296 for FT boundaries and Ra∆T = 1708 for TT boundaries" is true only for horizontally infinite domains but not for finite aspect-ratio boxes.
\end{myquotation}
The unstable band of wavenumbers for FT and TT boundaries near the critical values reported is narrow and is captured by our numerical domains.
We have added the clarification ``For this choice of \emph{aspect ratio and} boundary conditions...".

FT boundaries do not have the same instability properties as FF boundaries in which the $k = 0$ mode is unstable.

\begin{myquotation}
"Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading." is not clear at all; if one investigates a transient phase studying the thermal relaxation phase is perfectly fine while, if one is interested in the statistical steady state, considering the thermal relaxation phase is wrong (not misleading). 
\end{myquotation}
We agree that there may be cases in which studying transient phases can be interesting.
In fact, we made this caveat and grounded it in a physical example in the following paragraph of the discussion section in our original manuscript.

\begin{myquotation}
I do not recommend the publication of this paper.
\end{myquotation}

\end{singlespace}

\bibliography{../../biblio.bib}
\end{document}

### 2020-05-12 tex/mixedft_evolution_ms.tex
skeleton of changes to the paper inserted. Tomorrow = clean-up and tightening text.

@@
 \usepackage{xcolor}
+\usepackage{placeins}
 \hypersetup{
@@
 We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
-%Need to talk about: FF/TT differences in flow morphologies (aspect ratio) near onset. FT looks more like TT
-%Need to add something like this after that statement:\ea{Indeed, \citet{calkins&all2015} have found a dynamical equivalence between FF and TT boundaries in rapidly rotating RBC.}
-It is generally assumed that FT and FF boundaries should fundamentally behave similarly \ea{in their statistically stationary states} \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
-FF and TT boundaries exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
-It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
+
+\ea{Early studies of FF convection often focused on flow morphologies, as large-to-infinite aspect ratio convective rolls are linearly unstable at the critical value of the Rayleigh number (see e.g., ref.~\cite{chapman&proctor1980}).
+However, the onset properties and resultant flow morphologies in FT simulations more strongly resemble TT dynamics than FF dynamics \cite{ishiwatari&all1994}.}
+\ea{More recently,} FF and TT boundaries \ea{have been shown to} exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
+It is generally assumed that, \ea{in their statistically stationary states, simulations with} FT boundaries should behave similarly to FF boundaries \cite{goluskin2016, otero&all2002}.
+%It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 We present these findings as follows.
-In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
+In section \ref{sec:simulations}, we describe our simulation setup, numerical methods, \ea{initial conditions, and timescales in the convective systems}.
 In section \ref{sec:results_timescales}, we describe our findings \ea{regarding} the time evolution of FT systems.
@@
 \subsection{Initial Conditions}
-The time evolution of FT simulations is sensitive to the choice of initial conditions made due to the fact that the evolved, nonlinear convective dynamics determine the mean temperature for this choice of boudnary conditions.
+The time evolution of FT simulations is sensitive to the choice of initial conditions made due to the fact that the evolved, nonlinear convective dynamics determine the mean temperature for this choice of boundary conditions.
 For this reason, we will study FT simulations which employ three different initial states.
@@
 \end{equation}
-Simulations which employ these initial conditions will be simply denoted as ``FT'' simulations.
 
+\paragraph{TT-to-FT}
+As Eqn.~\ref{eqn:ra_relation} suggests, and as we will show in section \ref{sec:results_timescales}, the evolved state of each FT simulation corresponds to an equivalent TT simulation.
+As a result, we will examine ``TT-to-FT'' initial conditions, in which we run a TT simulation through its convective transient to statistical equilibrium, then use the full evolved nonlinear state as initial conditions for an FT simulation.
+}
+To achieve this, we perform these steps:
+\begin{enumerate}
+\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
+Measure $\text{Nu}$ in that state.
+\item Re-nondimensionalize from TT to FT according to Eqn.~\ref{eqn:ra_relation}.
+\item Restart the simulation with FT boundaries and continue timestepping.
+\end{enumerate}
+
+\ea{
 \paragraph{Nu-based ICs} 
-Our second set of initial conditions are ``Nusselt-based'' initial conditions.
-As we will show in sections \ref{sec:results}, the evolved state of each FT simulation corresponds to an equivalent TT simulation.
-As a result, Nu~vs.~Ra scaling laws derived for TT simulations can be expected to hold for FT simulations.
+The similarity of TT and FT simulations in the statistically stationary state suggests that Nu~vs.~Ra scaling laws derived for TT simulations can be expected to hold for FT simulations.
 According to Eqn.~\ref{eqn:ra_relation}, we can rearrange a given scaling law,
@@
 
-\paragraph{TT-to-FT}
-In some experiments, the ``proper'' Nu~vs.~Ra law is not well-known, or is not agreed upon by the community (see e.g.,~Sec.\ref{sec:rotation}).
-For such cases, it may still be numerically useful to be able to study converged FT simulations without having to resort to classical ICs.
-We will therefore examine ``TT-to-FT'' initial conditions, in which we run a TT simulation through its convective transient to statistical equilibrium, then use the full evolved nonlinear state as initial conditions for an FT simulation.
-}
-To achieve this, we perform these steps:
-\begin{enumerate}
-\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
-Measure $\text{Nu}$ in that state.
-\item Re-nondimensionalize from TT to FT according to Eqn.~\ref{eqn:ra_relation}.
-\item Restart the simulation with FT boundaries and continue timestepping.
-\end{enumerate}
-
-\ea{\paragraph{Additional ICs}
+\paragraph{Additional ICs}
 In all cases, we modify the initial temperature profile by specifying the value of $T_1$, rather than through modifications to the linearly unstable reference profile, $T_0$.
@@
 \qquad
-\frac{dE}{dt} = -\iiint \grad\cdot F_{\text{cond}}\,dx\,dy\,dz = -\Gamma^^22 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\iiint \grad\cdot F_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
@@
 The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
-However, it is reasonable to assume that the evolutionary timescale lies within the window $\tau_{\text{th, FT-classical}} \in [\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1}, \sqrt{\text{Ra Pr}}]$.
+However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} < \tau_{\text{th, FT-classical}} < \sqrt{\text{Ra Pr}}$.
 
@@
 
-\ea{
-\subsection{Nu-based initial conditions: rapid equilibration in \RB convection}
-\label{sec:time_evolution_classic_ICs}
-
-}
-
-\subsection{TT-to-FT: arbitrary rapidly equilibrated FT simulations}
+\subsection{TT-to-FT \& Nu-based ICs: rapidly equilibrated FT simulations}
 \label{sec:tt-to-ft}
@@
 where $A$ is a flow quantity, $P(A)$ is the PDF of $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the discrete PDF bins, and $i$ is the index of the bin.
-The PDFs are qualitatively similar, and there is generally good agreement between the moments of the PDFs.
-The remaining discrepancies between the PDFs are small and seem to primarily be due to the randomness of the flows in the time windows over which we sampled the simulations.
+\ea{We specifically report the Excess Kurtosis = Kurtosis $- 3$, to show how the Kurtosis of our PDFs differs from the Kurtosis of Normal Distributions.
+The PDFs of all FT simulations agree well regardless of initial conditions, suggesting that all initial conditions do achieve a similar statistically stationary state.
+
+From the moments of these PDFs, we conclude that the primary difference between FT and TT simulations is in the temperature field, and that the vertical velocities and nonlinear transport is the same regardless of boundary conditions.
+The temperature PDF of the TT simulation unsurprisingly has a mean of 0.5, a Skewness close to zero (no asymmetry between upflows and downflows), and an appreciable Excess Kurtosis (the tails, which primarily sample the plumes, are more important than they are in a Normal Distribution).
+The FT temperature PDF, on the other hand, has a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more excess Kurtosis.
+Furthermore, the mean temperature is slightly larger in the FT case.
+Outside of the temperature field, we find that the vertical velocity, $w$, and the vertical heat transport, $wT$, are well-described by normal distributions  aside from the area near their peak of zero (which is dominated by the boundary layers).
+}
 
@@
 
+\ea{
+While we do not show a time trace, here's a 1-paragraph description of Nu-based ICs.
+TODO: Write this, include max Re.
+}
+
 We note briefly that \ea{Nu-based ICs and} this TT-to-FT mechanism \ea{are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
@@
 
+\begin{figure}[p!]
+\includegraphics[width=\textwidth]{./figs/rbc_3D_panels.pdf}
+\caption{ 
+	words
+	words
+	\label{fig:rbc_3D_panels} }
+\end{figure}
+
+\ea{
 \subsection{3D verification of 2D results}
+We note briefly that these results hold in 3D.
+The thermal relaxation of systems with classical ICs is prohibitively expensive, and so here we have aimed to compare the statistically stationary state of a TT simulation and an FT simulation (with TT-to-FT initial conditions).
+Dynamical slices from these simulations are shown in Fig.~\ref{fig:rbc_3D_panels}.
+We find that the two simulations are nearly identical aside from their temperature fields, and so have focused on the temperature fields in this figure.
+Near the top boundary and in the interior, the TT and FT dynamics are quite similar.
+However, near the bottom boundary, the warm upflows in FT simulations are hotter relative to their counterparts in TT simulations.
+At the bottom of the figure, we compare PDFs of the full temperature field to PDFs of the temperature field in each of the shown slices (near the top boundary layer, a vertical slice of the interior, and near the bottom boundary layer).
+}
+
+\FloatBarrier
 

### 2020-05-12 figures_and_data/rbc_3D_panels.py

@@ -123,19 +123,19 @@ for i, bc in enumerate(data.keys()):
     horiz_field.set_scales(1)
     horiz_field['g'] = top_map
     horiz_field.set_scales(horiz_scales, keep_data=True)
-    c = axs[0+3*i].pcolormesh(xx_tb,  yy_tb,  horiz_field['g'],  vmin=-maxval, vmax=maxval, cmap='RdBu_r')
+    c = axs[0+3*i].pcolormesh(xx_tb,  yy_tb,  horiz_field['g'],  vmin=-maxval, vmax=maxval, cmap='RdBu_r', rasterized=True)
 
 
     vert_field.set_scales(1)
     vert_field['g'] = vert_map
     vert_field.set_scales(vert_scales, keep_data=True)
-    c = axs[1+3*i].pcolormesh(xx_mid, zz_mid, vert_field['g'], vmin=-maxval, vmax=maxval, cmap='RdBu_r')
+    c = axs[1+3*i].pcolormesh(xx_mid, zz_mid, vert_field['g'], vmin=-maxval, vmax=maxval, cmap='RdBu_r', rasterized=True)
 
 
     horiz_field.set_scales(1)
     horiz_field['g'] = bot_map
     horiz_field.set_scales(horiz_scales, keep_data=True)
-    c = axs[2+3*i].pcolormesh(xx_tb,  yy_tb,  horiz_field['g'],  vmin=-maxval, vmax=maxval, cmap='RdBu_r')
+    c = axs[2+3*i].pcolormesh(xx_tb,  yy_tb,  horiz_field['g'],  vmin=-maxval, vmax=maxval, cmap='RdBu_r', rasterized=True)
 
 bar = plt.colorbar(c, cax=cax, orientation='vertical')
 cax.set_xticklabels(())
@@ -173,21 +173,24 @@ for i, c in zip((0, 3, 7, 1, 4, 8, 2, 5, 9), ('orange', 'orange', 'orange', 'gre
 #PDF plots
 for i, bc in enumerate(data.keys()):
     axs[6].plot(        data[bc]['pdf_T_xs'] /data[bc]['delta_T_mean'],               data[bc]['pdf_T_pdf']*data[bc]['delta_T_mean'],         c=colors[i], label=bc)
[…]

### 2020-05-13 figures_and_data/rbc_3D_panels.py
3D fig now with TT-to-FT and different border colors

@@ -23,10 +23,16 @@ mColor = 'darkorange'#olivedrab'
 fColor = 'indigo'
 colors = [fColor, mColor]
 
+top_border_color    = 'darkblue'
+middle_border_color = 'seagreen'
+bottom_border_color = 'firebrick'
+
+
 # Get data from files
 base_dir = './data/rbc/3D/'
 TT_dir   = 'TT/ra1e8'
-FT_dir   = 'Nu_based_FT/ra2.61e9'
+#FT_dir   = 'Nu_based_FT/ra2.61e9'
+FT_dir   = 'TT-to-FT/ra3.1e9'
 
 data = OrderedDict()
 for label, dr in zip(['TT', 'FT'], [base_dir+TT_dir, base_dir+FT_dir]):
@@ -161,12 +167,12 @@ for i in range(6):
     axs[i].set_yticks(())
 
 for i in [0, 2, 3, 5]:
-    axs[i].axhline(0, c='g', lw=1, ls='--')
+    axs[i].axhline(0, c=middle_border_color, lw=1.5, ls='--')
 
-for i, c in zip((0, 3, 7, 1, 4, 8, 2, 5, 9), ('orange', 'orange', 'orange', 'green', 'green', 'green', 'blue', 'blue', 'blue')):
+for i, c in zip((0, 3, 7, 1, 4, 8, 2, 5, 9), (*[top_border_color]*3, *[middle_border_color]*3, *[bottom_border_color]*3)):
     for k in axs[i].spines.keys():
         axs[i].spines[k].set_color(c)
-        axs[i].spines[k].set_linewidth(1)
+        axs[i].spines[k].set_linewidth(1.5)
 
 
 

### 2020-05-13 referee_responses/submission1/referee_response.tex
many small changes for refereeing

@@
 \item For the specific case of classical RBC, the initial conditions that you describe here are probably simpler to use than our TT-to-FT initial conditions.
-See section II.C for a description of these ``Nu-based'' initial conditions, and section III.(TODO) for a description of evolution in these systems.
+See section II.C for a description of these ``Nu-based'' initial conditions, and section III.B for a brief description of evolution in these systems.
 One difficulty of using Nu-based initial conditions is that they are sensitive to the Nu vs.~Ra law that is used.
@@
 We've added a derivation of this timescale and a discussion of this subtlety to a new section II.D.
-(TODO: Does this scaling law hold?)
+In practice, we find that this definition of an equilibration time far \emph{over}estimates the relaxational timescale.
+We find that the relaxational time is $(\text{a few})\cdot(\sqrt{\text{Ra Pr}}/\text{Nu})$, and have said so at the end of section III.C.
 
@@
 \end{myquotation}
-For the right two PDFs, we chose scales so as to align median values.
-For the left two PDFs, we chose scales which tried to show the shape of the PDFs and avoid excess white space.
-TODO: We have adjusted the scale of the the bottom left PDF so that its median value is aligned with the top left panel.
+For the right two PDFs, we chose scales so as to align median values (and show the range of the FT PDF).
+For the left two PDFs, we previously chose scales which tried to show the shape of the PDFs and avoid excess white space.
+We have adjusted the scale of the the bottom left PDF so that its median value is aligned with the top left panel.
 \begin{myquotation}
@@
 \end{myquotation}
-TODO: We have added section III.D and Fig.~4 to show that 3D results are in line with 2D results.
+We have added section III.D and Fig.~4 to show that 3D results are in line with 2D results.
 
@@
 p.3: The codeS used to run simulations and to create the figures...
-Caption of figure 2: “Re vs. Ra is compensated…” -> Pe vs. Ra
+Caption of figure 2:``Re vs. Ra is compensated…'' $\rightarrow$ Pe vs. Ra
 \end{myquotation}
-TODO: These typos have been fixed.
+These typos have been fixed.
 

### 2020-05-13 tex/mixedft_evolution_ms.tex
many small changes for refereeing

@@
 \frac{\partial T_N}{\partial z} = \grad_{\text{interior}} + w(z)(-1 - \grad_{\text{interior}}).
+\label{eqn:nu_based_gradT}
 \end{equation}
@@
 	Nu vs.~Ra is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, the best-fit reported by ref.~\cite{johnston&doering2009}.
-	Re vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
+	Pe vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
 	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
@@
 
-\ea{Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
+\ea{\paragraph{TT-to-FT} Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
 It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.
@@
 
+\paragraph{Statistical Comparison of BCs and ICs}
 From the moments of these PDFs, we conclude that the primary difference between FT and TT simulations is in the temperature field, and that the vertical velocities and nonlinear transport is the same regardless of boundary conditions.
@@
 \ea{
-While we do not show a time trace, here's a 1-paragraph description of Nu-based ICs.
-TODO: Write this, include max Re.
+\paragraph{Nu-based ICs}
+The time evolution of Nu-based ICs is similar to the time evolution of TT simulations with classical ICs, with a few caveats.
+The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
+During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classical roll solution is achieved.
+This behavior is quite different from classical ICs in TT simulations, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
+Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classical ICs.
+Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classical ICs are very similar.
 }
 
-We note briefly that \ea{Nu-based ICs and} this TT-to-FT mechanism \ea{are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
+\subsection{\ea{Discussion of 2D results}} We note briefly that \ea{Nu-based ICs and} this TT-to-FT mechanism \ea{are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
+\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classical ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
+
+\ea{
+As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$\,\gtrsim 10^{8.67}$ .
+This velocity field relaxation happens despite instant \emph{thermal} equilibration of the temperature field for these simulations.
+We find that the kinetic energy increases by less than a factor of two from its initial post-transient value to its final value in the equilibrated state.
+}
 
@@
 \caption{ 
-	words
-	words
+	(top six panels) Snapshots of the temperature anomaly are shown for select slices through 3D domains.
+	The left column shows data from TT simulations with Ra$_{\Delta T} = 10^{8}$, the right column shows data for FT simulations with Ra$_{\partial_z T} = 3.1 \times 10^{9}$.
+	The top and bottom rows respectively show horizontal slices 1\% of the domain depth away from the top and bottom boundaries, while the middle row shows a vertical slice at $y = 0$.
+	Visually, TT and FT dynamics are indistinguishable aside from the warm upflows near the bottom boundary.
+	(Bottom four panels) PDFs of the temperature field are shown.
+	From left to right, these PDFs are shown for the full 3D domain, the upper boundary layer slice, the vertical slice, and the bottom boundary layer slice.
+	The extreme temperature events which stand out visually near the bottom boundary layer can be clearly seen in all PDFs except for the one near the upper boundary.
 	\label{fig:rbc_3D_panels} }
@@
 \subsection{3D verification of 2D results}
-We note briefly that these results hold in 3D.
-The thermal relaxation of systems with classical ICs is prohibitively expensive, and so here we have aimed to compare the statistically stationary state of a TT simulation and an FT simulation (with TT-to-FT initial conditions).
-Dynamical slices from these simulations are shown in Fig.~\ref{fig:rbc_3D_panels}.
-We find that the two simulations are nearly identical aside from their temperature fields, and so have focused on the temperature fields in this figure.
+We note briefly that our results from 2D hold in 3D: classical ICs exhibit a prohibitively long thermal rundown, but equilibrated FT and TT simulations are analogous in a volume-averaged sense.
+In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from a 3D TT and TT-to-FT simulation.
+As in 2D, we find that the two simulations are nearly identical aside from their temperature fields, and so have focused on the temperature fields in this figure.
 Near the top boundary and in the interior, the TT and FT dynamics are quite similar.
@@
 At the bottom of the figure, we compare PDFs of the full temperature field to PDFs of the temperature field in each of the shown slices (near the top boundary layer, a vertical slice of the interior, and near the bottom boundary layer).
+The PDF of the full volume of these simulations is indistinguishable between the two cases except near the hot bottom boundary.
+Indeed, we find that the two cases have indistinguishable PDFs in a horizontal slice near the top boundary, and that temperature events which range from the fixed boundary temperature ($T = 0$) to the temperature achieved in the interior $T = 0.5\Delta T$) are all equally probable.
+The story is the same for the TT case near the bottom boundary, but the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
+Unsurprisingly, we find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is similar, but not identical, to the PDFs of the temperature field of the full volume, suggesting that this one slice does not capture the full range of possible dynamics which occur in the domain over our sampling window.
 }
@@
 Input and output information for the simulations in this work are shown in Table~\ref{table:simulations}.
-The code used to run these simulations can be found online in the repository of supplemental materials \cite{anders&all2020a_supp}.
+The codes used to run these simulations can be found online in the repository of supplemental materials \cite{anders&all2020a_supp}.
 

### 2020-05-13 figures_and_data/rbc_3D_panels.py

@@ -206,6 +206,9 @@ for i in [6, 8]:
 for i in [7, 9]:
     axs[i].set_ylim(1e-3, 10)
 axs[6].set_xlim(0, 1.5)
+axs[8].set_xlim(0, 1.5)
+axs[7].set_xlim(0, 0.75)
+axs[9].set_xlim(0.25, 1.5)
 
 
 fig.savefig('rbc_3D_panels.png', dpi=300, bbox_inches='tight')

### 2020-05-13 figures_and_data/rbc_evolution_dynamics.py

@@ -174,11 +174,11 @@ axs[0].xaxis.set_ticks_position('top')
 axs[0].xaxis.set_label_position('top')
 
 
-bbox_props = dict(boxstyle="round", fc="w", ec="0.5", alpha=0.75)
-axs[0].text(0.18, 0.11, r"TT, Ra$_{\Delta T}\,=\,10^{10}$", ha="center", va="center", size=8, bbox=bbox_props, transform=axs[0].transAxes)
-axs[1].text(0.25, 0.89, r"FT (early), Ra$_{\Delta T}\,\approx\,10^{10}$", ha="center", va="center", size=8, bbox=bbox_props, transform=axs[1].transAxes)
-axs[3].text(0.83, 0.11, r"TT, Ra$_{\Delta T}\,=\,10^{9}$", ha="center", va="center", size=8, bbox=bbox_props, transform=axs[3].transAxes)
-axs[4].text(0.77, 0.89, r"FT (late), Ra$_{\Delta T}\,\approx\,10^{9}$", ha="center", va="center", size=8, bbox=bbox_props, transform=axs[4].transAxes)
+bbox_props = dict(boxstyle="round", fc="w", ec="0.5", alpha=0.5)
+axs[0].text(0.03, 0.11, r"TT, Ra$_{\Delta T}\,=\,{10}^{10}$",               ha="left",  va="center", size=9, bbox=bbox_props, transform=axs[0].transAxes)
+axs[1].text(0.03, 0.89, r"FT (early), Ra$_{\Delta T}\,\approx\,{10}^{10}$", ha="left",  va="center", size=9, bbox=bbox_props, transform=axs[1].transAxes)
+axs[3].text(0.97, 0.11, r"TT, Ra$_{\Delta T}\,=\,{10}^{9}$",                ha="right", va="center", size=9, bbox=bbox_props, transform=axs[3].transAxes)
+axs[4].text(0.97, 0.89, r"FT (late), Ra$_{\Delta T}\,\approx\,{10}^{9}$",   ha="right", va="center", size=9, bbox=bbox_props, transform=axs[4].transAxes)
 
 #Colorbar
 bar = plt.colorbar(c, cax=cax, orientation='horizontal')#, rasterized=True)
@@ -186,8 +186,8 @@ cax.set_xticklabels(())
[…]

### 2020-05-13 figures_and_data/report_scaling_laws.py
adds file for calculating scaling laws; need to add TT calculation to it.

@@ -1,0 +1,111 @@
+import glob
+from collections import OrderedDict
+
+import h5py
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+from scipy.optimize import curve_fit
+def line(x, a, b):
+    return a + b*x
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'left_T', 'right_T']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
+                    data[k][start_ind:start_ind+len(arr)] = arr
+                    start_ind += len(arr)
+        else:
+            with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                for k in keys:
+                    data[k] = f[k][()]
+
+        data['ra_temp'] = ra*data['delta_T']
+        data['ra_flux'] = ra**(3./2)*data['left_flux']
+        full_data['{:.4e}'.format(ra)] = data
+    return full_data
+
[…]

### 2020-05-13 figures_and_data/report_scaling_laws.py
adds Pe and TT scaling laws to report file

@@ -64,20 +64,17 @@ fixed_data = read_data(fixed_ras, fixed_dirs)
 N = 10
 for k, data in mixed_data.items():
     fig = plt.figure()
-    plt.grid(which='both')
-    Nu = data['Nu'][400:]
     ra_dz = float(k)
     ra_dT = ra_dz*data['delta_T'][400:]
     finite = np.isfinite(ra_dT)
-    Nu = Nu[finite]
     ra_dT = ra_dT[finite]
 
+    #Set up Ra bins
     ra_ranges = np.zeros((N,2))
     if '4.83' in k:
         max_dT = 2.5e10
     else:
         max_dT = ra_dT.max()
-#    ra_points = np.linspace(ra_dT.min(), max_dT, N)
     ra_points = np.logspace(np.log10(ra_dT.min()), np.log10(max_dT), N)
     ra_ranges[0][0] = ra_dT.min()
     ra_ranges[-1][-1] = max_dT
@@ -85,27 +82,61 @@ for k, data in mixed_data.items():
     for i in range(N-1):
         ra_ranges[i][1] = ra_points[i] + dra[i]/2
         ra_ranges[i+1][0] = ra_points[i+1] - dra[i]/2
+    
+    for i, fd in enumerate(['Nu', 'Pe']):
+        ax = fig.add_subplot(1, 2, 1+i)
+        plt.grid(which='both')
+        values  = data[fd][400:]
+        values  = values[finite]
 
-    ras, nus, err = np.zeros(N), np.zeros(N), np.zeros(N)
-    for i in range(N):
-        good = (ra_dT > ra_ranges[i][0] ) * (ra_dT <= ra_ranges[i][1])
-        mean_ra = np.mean(ra_dT[good])
-        mean_nu = np.mean(Nu[good])
-        std_nu  = np.std(Nu[good])
-        plt.plot(ra_dT[good], Nu[good])
-        ras[i] = mean_ra
-        nus[i] = mean_nu
-        err[i] = std_nu/np.sqrt(np.sum(good))
-    plt.errorbar(ras, nus, yerr=err, zorder=1e2, ms=4, marker='o', c='k', capsize=1, elinewidth=1, lw=0) 
-    fit = curve_fit(line, np.log10(ras), np.log10(nus), (-1, 1/3), err)
-    print('best fit: {:.2e} * ra ^ {:.3g}'.format(10**fit[0][0], fit[0][1]))
[…]

### 2020-05-14 figures_and_data/rbc_1D_profiles.py
minor updates to 1D profile figure

@@ -163,7 +163,31 @@ axins_r = []
 
 
 bounds_out = 0.5
-bounds_in  = 0.45
+
+#find true BL width
+k = 'kappa_flux'
+m_flux = mixed_profs[mk][k][0,:]/dT**(3/2)/flux_scale
+f_flux = fixed_profs[fk][k][0,:]/flux_scale
+
+m_bl_bot = mz[(m_flux > 0.05)*(mz < 0)][-1]
+f_bl_bot = fz[(f_flux > 0.05)*(fz < 0)][-1]
+m_bl_top = mz[(m_flux > 0.05)*(mz > 0)][0]
+f_bl_top = fz[(f_flux > 0.05)*(fz > 0)][0]
+
+print('boundary layers (mixed): {:.3g} / {:.3g}'.format(m_bl_bot, m_bl_top))
+print('boundary layers (fixed): {:.3g} / {:.3g}'.format(f_bl_bot, f_bl_top))
+
+avg_bl = np.mean((0.5+m_bl_bot, 0.5+f_bl_bot, 0.5-m_bl_top, 0.5-f_bl_top))
+
+bounds_in = bounds_out - 3*avg_bl #show 3 * bl width
+
+#plt.figure()
+#interior = (mz >= -0.5+avg_bl)*(mz <= 0.5-avg_bl)
+#plt.plot(mz[interior], (f_flux - m_flux)[interior])
+#plt.xlim(-0.5+avg_bl, 0.5-avg_bl)
+#plt.show()
+
+                               
 
 #Row 1 - Temp
 k = 'T'
@@ -172,7 +196,7 @@ for ax in [axf, axl, axr]:
     ax.plot(fz, fixed_profs[fk][k][0,:],    c=fColor, label='TT', lw=2)
     ax.plot(mz, mixed_profs[mk][k][0,:]/dT, c=mColor, label='FT')
 #ax1.legend(loc='lower left', frameon=False, fontsize=7)
-axf.set_ylabel(r'$\bar{T}/\Delta T$')
+axf.set_ylabel(r'$\overline{T}/\Delta T$')
 axf.legend(loc='lower center', ncol=2, frameon=False, fontsize=8)
 
 axf.set_ylim(0, 1)
@@ -203,8 +227,10 @@ for ax, loc in [(axl, 'upper right'), (axr, 'lower left')]:
 #        axins.set_yticks((0, 0.25, 0.5))
     elif ax is axr: 
         axins_r.append(axins)
[…]

### 2020-05-14 referee_responses/submission1/referee_response.tex
many small improvements

@@
 \end{myquotation}
-TODO: We have rewritten the abstract for self-consistency and clarity.
+We have rewritten the abstract in an attempt to make it self-consistent and to make it more clearly speak to our results.
 \begin{myquotation}
@@
 \end{myquotation}
-We have defined the boundary layers as the parts of the domain where conduction carries more than $20\%$ of the flux.
-TODO: Do we do something more traditional or do we at least say this in the text?
+We have defined the boundary layers as the parts of the domain where conduction carries more than $5\%$ of the flux.
+We have specified this in the text.
 \begin{myquotation}

### 2020-05-14 tex/mixedft_evolution_ms.tex
many small improvements

@@
 Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
-In this work, we study \RB convection (RBC) with mixed (``FT'') temperature boundary conditions.
-We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of fixing the temperature at the top and bottom of the domain (``TT'').
-We find that simulations with FT boundaries experience a long thermal rundown while simulations with TT boundaries do not.
-In the relaxed state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries.
-The fast evolution of TT simulations can therefore be taken advantage of to rapidly relax FT simulations.
-We show that these findings carry over to more complicated problems through a brief examination of rotating convection.
-We furthermore find that FT boundaries introduce minor asymmetries into the flow fields, with the fixed flux boundary producing more extreme events than the fixed temperature boundary, but that these asymmetries do not appreciably affect the bulk flows.
-We conclude that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
-Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
+In this work, we study \RB convection (RBC) \ea{under the Boussinesq approximation}.
+\ea{We examine simulations with mixed ``FT'' boundary conditions in which the flux is fixed at the bottom boundary and the temperature is fixed at the top.}
+We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of \ea{``TT'' boundaries, in which the temperature is fixed} at the top and bottom of the domain.
+\ea{We demonstrate that the timescale of thermal relaxation for FT simulations is dependent upon the initial conditions.
+``Classic'' initial conditions which employ a hydrostatically- and thermally- balanced linear temperature profile exhibit a long thermal relaxation.
+This long relaxation timescale can be skipped by either using a TT simulation's nonlinear state as initial conditions for an FT simulation, or by choosing initial conditions which more accurately guess the temperature difference between the top and bottom plates in the evolved state.}
+In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries.
+\ea{FT boundaries are fundamentally asymmetric, and we examine the asymmetries that these boundaries produce in the flow.
+We find that the fixed-flux boundary produces more extreme temperature events than the fixed-temperature boundary.
+However, these near-boundary asymmetries do not measurably break the symmetry in the convective interior.
+We briefly explore rotating RBC to demonstrate that our findings with respect to thermal relaxation carry over to this more complex case.}
 \end{abstract}
@@
 We find that FT simulations carry marginally more flux (higher Nu) and are more turbulent (higher Pe) than comparable TT simulations as they relax through this parameter space.
-\ea{(TODO)}
-%TODO: report scaling laws.
+\ea{By binning Ra$_{\Delta T}(t)$, Nu$(t)$, and Pe$(t)$ into ten bins over the evolution of our FT simulations, we can quantify the path through parameter space that our FT simulations trace out.
+By performing a least-squares fit to this data, the best-fit paths for Ra$_{\partial_z T} = 4.83 \times 10^{10}$ are $\text{Nu} = 0.0618\,\text{Ra}_{\Delta T}^{0.322}$ and $\text{Pe} = (5.73 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.597}$.
+At Ra$_{\partial_z T} = 2.61 \times 10^{9}$, our best-fit paths are $\text{Nu} = 0.0845\,\text{Ra}_{\Delta T}^{0.310}$ and $\text{Pe} = (4.05 \times 10^{-3})\,\text{Ra}_{\Delta T}^{0.739}$.
+By comparison, the best fit scaling laws for our TT cases are $\text{Nu} = 0.141\,\text{Ra}_{\Delta T}^{0.282}$ (very similar to the law reported in ref.~\cite{johnston&doering2009}), $\text{Pe} = (0.303)\,\text{Ra}_{\Delta T}^{0.516}$ (for Ra$_{\Delta T} \geq 10^9$), and $\text{Pe} = (2.41 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.64}$.
+}
 These heightened values of Nu and Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
 
-Achieving thermal relaxation in pure FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
+Achieving thermal relaxation in \ea{classic} FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
 For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
@@
 In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Time averages are taken over 500 nondimensional freefall time units for the TT case and over 2000 nondimensional freefall time units for the FT case, sampled once every 0.1 time units (the difference in averaging window is explained in Sec.~\ref{sec:timescales}).
+Time averages are taken over 500 freefall time units for the \ea{evolved flows}, sampled once every 0.1 time units.
 In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
 Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
+\ea{Here, we define the boundary layers as the heights above or below which conduction carries 95\% of the flux.
+We find a boundary layer depth of $\sim 0.024$ at Ra$_{\Delta T} = 10^9$, and show three times this depth in the zoomed in panels}
 Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
@@
 In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
-The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the largest deviations away from zero in the interior are O(0.01) in the plotted units.
+The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the \ea{FT and TT cases differ by no more than 0.0025 in the plotted units} in the interior.
 
@@
 After achieving this peak value, Pe monotonically decreases toward its relaxed state.
+\ea{We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}}/\text{Nu}$ nondimensional freefall time units.}
 
@@
 As expected, the scaling of Nu vs.~Ra is steep in the rotationally constrained regime \cite{julien&all2012, plumley&julien2019}, which these simulations trace through.
-As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT values of Nu are once again somewhat elevated above the comparable TT simulations.
+\ea{We find that at values of Ra$_{\Delta T} \gtrsim 8 \times 10^9$, scaling laws start to flatten towards the unconstrained regime.
+The FT simulation at all times when Ra$_{\Delta T} < 8 \times 10^9$ traces out $\text{Nu} = (1.08 \times 10^{-18})\,\text{Ra}_{\Delta T}^{2}$ and $\text{Pe} = (4.26 \times 10^{-20})\,\text{Ra}_{\Delta T}^{2.4}$.
+The TT simulation with Ra$_{\Delta T} < 8 \times 10^9$ trace out $\text{Nu} = (9.36 \times 10^{-17})\,\text{Ra}_{\Delta T}^{1.79}$ and $\text{Pe} = (4.78 \times 10^{-19})\,\text{Ra}_{\Delta T}^{2.27}$.}
+As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT \ea{scaling laws} are once again \ea{steeper than} the comparable TT \ea{laws}.
 
@@
 	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
-	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units.
+	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units \ea{for all rotating cases and all 2D cases except the Ra$_{\partial_z T} = 9.51\times10^{11}$ TT-to-FT case, where samples were taken over 200 evolved freefall time units; samples were taken over 350 freefall time units for 3D nonrotating cases}.
 	Reported uncertainties are the standard deviation of the sample mean; when the uncertainty is not reported, it is smaller than the number of reported digits.
@@
 \resizebox{\textwidth}{!}{
-\begin{tabular}{c c c c c c c c c}
+\begin{tabular}{c c c c c c c c c c}
 \hline																	
-BCs	&	Ra	&	nx$\times$ny$\times$nz	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
+BCs	&	ICs	&	Ra	&	nx$\times$ny$\times$nz	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
 \hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
-\multicolumn{7}{c}{\vspace{0.1cm}2D Runs ($\Gamma = 2$, no-slip)} \\
+\multicolumn{7}{c}{\vspace{0.1cm}Non-rotating Runs ($\Gamma = 2$, no-slip, Ek$\,=\,\infty$)} \\
 \hline
-TT			&	$1.00 \times 10^8$		&	1024x512	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
-FT			&	$2.61 \times 10^9$		&	2048x1024	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
-TT-to-FT	&	$2.61 \times 10^9$		&	1024x512	&	1000		&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
-TT			&	$2.15 \times 10^8$		&	1024x512	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
-TT			&	$4.64 \times 10^8$		&	2048x1024	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
-TT			&	$1.00 \times 10^9$		&	2048x1024	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
-FT			&	$4.83 \times 10^{10}$	&	4096x2048*	&	16230		&	$5.36 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
-TT-to-FT	&	$4.83 \times 10^{10}$	&	2048x1024	&	1000		&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
-TT			&	$2.15 \times 10^9$		&	2048x1024	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
-TT			&	$4.64 \times 10^9$		&	3072x1536	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
-TT			&	$1.00 \times 10^{10}$	&	4096x2048	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
-TT-to-FT	&	$9.51 \times 10^{11}$	&	4096x2048	&	1000		&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
+TT			&	Classic		&	$1.00 \times 10^8$		&	384$^2$x256	&	482			&	$1.95 \times 10^5$	&	$31.4$			&	---		&	$1.78 \times 10^3$ & --- \\
+FT			&	TT-to-FT	&	$3.10 \times 10^9$		&	384$^2$x256	&	2221		&	$1.95 \times 10^5$	&	$31.9$			&	---		&	$1.78 \times 10^3$ & --- \\
+TT			&	Classic		&	$1.00 \times 10^8$		&	1024x512	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
+FT			&	Classic		&	$2.61 \times 10^9$		&	2048x1024	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
+FT			&	TT-to-FT	&	$2.61 \times 10^9$		&	1024x512	&	5040		&	$3.21 \times 10^3$	&	$26.0 \pm 0.1$	&	26.1	&	$3.17 \times 10^3$ & --- \\
+TT			&	Classic		&	$2.15 \times 10^8$		&	1024x512	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
+TT			&	Classic		&	$4.64 \times 10^8$		&	2048x1024	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
+TT			&	Classic		&	$1.00 \times 10^9$		&	2048x1024	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
+FT			&	Classic		&	$4.83 \times 10^{10}$	&	4096x2048*	&	19702		&	$5.56 \times 10^5$	&	$48.8 \pm 0.4$	&	48.3	&	$1.36 \times 10^4$ & --- \\
+FT			&	TT-to-FT	&	$4.83 \times 10^{10}$	&	2048x1024	&	6136		&	$3.64 \times 10^4$	&	$49.0 \pm 0.4$	&	48.3	&	$1.32 \times 10^4$ & --- \\
+FT			&	Nu-based	&	$4.83 \times 10^{10}$	&	2048x1024	&	6877		&	$3.64 \times 10^4$	&	$49.0 \pm 0.4$	&	48.3	&	$1.34 \times 10^4$ & --- \\
+TT			&	Classic		&	$2.15 \times 10^9$		&	2048x1024	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
+TT			&	Classic		&	$4.64 \times 10^9$		&	3072x1536	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
+TT			&	Classic		&	$1.00 \times 10^{10}$	&	4096x2048	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
+FT			&	TT-to-FT	&	$9.51 \times 10^{11}$	&	4096x2048	&	2142		&	$1.22 \times 10^5$	& 	$95.3 \pm 1.0$ 	&	95.1	&	$4.29 \times 10^4$ & --- \\
 \hline																	
-\multicolumn{7}{c}{\vspace{0.1cm}3D Rotating Runs (Ek = $10^{-6}$, $\Gamma = 0.481$, stress-free)} \\
+\multicolumn{7}{c}{\vspace{0.1cm}Rotating Runs ($\Gamma = 0.481$, stress-free, Ek = $10^{-6}$)} \\
 \hline																	
-TT	&	$1.38 \times 10^9$		&	64$^2\times$128 	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
-TT	&	$1.83 \times 10^9$		&	64$^2\times$128 	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
-TT	&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
-TT	&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
-FT	&	$2.1 \times 10^{10}$	&	384$^2\times$512*	&	13950		&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
-TT	&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
-TT	&	$4.58 \times 10^9$		&	128$^3$				&	2530		&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
-TT	&	$5.50 \times 10^9$		&	192$^3$				&	2402		&	$7.35 \times 10^4$	&	$22.8$			&	---		&	$6.38 \times 10^3$  & $(2.96 \pm 0.11) \times 10^{-1}$ \\
-TT	&	$6.42 \times 10^9$		&	192$^3$				&	2226		&	$7.35 \times 10^4$	&	$29.5$			&	---		&	$7.86 \times 10^3$  & $(3.65 \pm 0.16) \times 10^{-1}$ \\
-TT	&	$7.33 \times 10^9$		&	256$^3$				&	1147		&	$1.47 \times 10^5$	&	$36.2$			&	---		&	$9.52 \times 10^3$  & $(4.33 \pm 0.17) \times 10^{-1}$ \\
-TT	&	$8.25 \times 10^9$		&	256$^3$				&	1079		&	$1.47 \times 10^5$	&	$43.0$			&	---		&	$1.10 \times 10^4$  & $(5.01 \pm 0.20) \times 10^{-1}$ \\
-TT	&	$9.17 \times 10^9$		&	256$^3$				&	1030		&	$1.47 \times 10^5$	&	$48.9$			&	---		&	$1.24 \times 10^4$  & $(5.63 \pm 0.26) \times 10^{-1}$ \\
-TT	&	$1.834 \times 10^{10}$	&	256$^3$				&	971.9		&	$1.84 \times 10^5$	&	$111$			&	---		&	$2.21 \times 10^4$  & $1.18 \pm 0.09$ \\
+TT	&	Classic		&	$1.38 \times 10^9$		&	64$^2\times$128 	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
+TT	&	Classic		&	$1.83 \times 10^9$		&	64$^2\times$128 	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
+TT	&	Classic		&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
+TT	&	Classic		&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
+FT	&	Classic		&	$2.1 \times 10^{10}$	&	384$^2\times$512*	&	13950		&	$2.3 \times 10^6$	&	$7.90 \pm 0.01$	&	---		&	$1.70 \times 10^3$  & $(1.15 \pm 0.06) \times 10^{-1}$ \\
+FT	&	TT-to-FT	&	$2.1 \times 10^{10}$	&	128$^3$				&	2775		&	$4.34 \times 10^4$	&	$7.83 \pm 0.01$	&	---		&	$1.65 \times 10^3$  & $(1.14 \pm 0.05) \times 10^{-1}$ \\
+TT	&	Classic		&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
+TT	&	Classic		&	$4.58 \times 10^9$		&	128$^3$				&	2530		&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
+TT	&	Classic		&	$5.50 \times 10^9$		&	192$^3$				&	2402		&	$7.35 \times 10^4$	&	$22.8$			&	---		&	$6.38 \times 10^3$  & $(2.96 \pm 0.11) \times 10^{-1}$ \\
+TT	&	Classic		&	$6.42 \times 10^9$		&	192$^3$				&	2226		&	$7.35 \times 10^4$	&	$29.5$			&	---		&	$7.86 \times 10^3$  & $(3.65 \pm 0.16) \times 10^{-1}$ \\
+TT	&	Classic		&	$7.33 \times 10^9$		&	256$^3$				&	1147		&	$1.47 \times 10^5$	&	$36.2$			&	---		&	$9.52 \times 10^3$  & $(4.33 \pm 0.17) \times 10^{-1}$ \\
+TT	&	Classic		&	$8.25 \times 10^9$		&	256$^3$				&	1079		&	$1.47 \times 10^5$	&	$43.0$			&	---		&	$1.10 \times 10^4$  & $(5.01 \pm 0.20) \times 10^{-1}$ \\
+TT	&	Classic		&	$9.17 \times 10^9$		&	256$^3$				&	1030		&	$1.47 \times 10^5$	&	$48.9$			&	---		&	$1.24 \times 10^4$  & $(5.63 \pm 0.26) \times 10^{-1}$ \\
+TT	&	Classic		&	$1.834 \times 10^{10}$	&	256$^3$				&	971.9		&	$1.84 \times 10^5$	&	$111$			&	---		&	$2.21 \times 10^4$  & $1.18 \pm 0.09$ \\
 \hline																	

### 2020-05-14 figures_and_data/rbc_dynamics_asymmetries.py

@@ -126,8 +126,8 @@ ax.fill_between(fx, 1e-16, fp, color=fColor, alpha=0.5)
 
 minv = np.min((np.min(mp[mp > 0]*dT), np.min(fp[fp > 0])))
 maxv = np.max((np.max(mp[mp > 0]*dT), np.max(fp[fp > 0])))
-ax.set_ylim(minv, maxv)
-ax.set_xlim(0, np.max(mx/dT))
+ax.set_ylim(3e-5, maxv)
+ax.set_xlim(0, 1.55)#np.max(mx/dT))
 
 
 # Panel 2, Dynamics
@@ -199,7 +199,7 @@ bar = plt.colorbar(c, cax=cax, orientation='horizontal')#, rasterized=True)
 cax.set_xticklabels(())
 bar.set_ticks(())
 cax.text(0.5, -0.55, r'$\pm\Delta T / 3$', transform=ax.transAxes, ha='center')
-cax.text(0.5, -0.21, r'$T - \bar{T}$', transform=ax.transAxes, ha='center')
+cax.text(0.5, -0.21, r'$T - \overline{T}$', transform=ax.transAxes, ha='center')
 #cax.annotate(r'$-|S| \times 10^{-5}$', fontsize=8,  xy=(-0.37, 0.5), va='center', annotation_clip=False)
 #cax.annotate(r'$|S| \times 10^{-5}$', fontsize=8,  xy=(1.02, 0.5),  va='center',  annotation_clip=False)
 

### 2020-05-14 figures_and_data/report_rotating_scalars.py

@@ -1,0 +1,115 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+
+mColor = 'darkorange'#olivedrab'
+fColor = 'indigo'
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux', 'Ro']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(r, int(r.split('run')[-1].split('/')[0].split('_')[0])) for r in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
+                for arr in partial_data[k]:
[…]

### 2020-05-14 figures_and_data/report_scalars.py

@@ -1,0 +1,184 @@
+import glob
+import matplotlib
+from collections import OrderedDict
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import h5py
+
+import pandas as pd
+
+mColor  = 'darkorange'#olivedrab'
+mColor2 = 'gold'
+fColor  = 'indigo'
+
+def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 'left_flux', 'right_flux']):
+    """
+    Reads scalar data in from a folder containing a series of subfolders of different Ra values.
+    """
+    full_data = OrderedDict()
+    for ra, dr in zip(ra_list, dir_list):
+        data = OrderedDict()
+        sub_runs = glob.glob('{:s}/run*/'.format(dr))
+        if len(sub_runs) > 0:
+            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
+            partial_data = OrderedDict()
+            for k in keys:
+                partial_data[k] = []
+
+            N_tot = 0
+            for i, dr in enumerate(sub_runs):
+                with h5py.File('{:s}/traces/full_traces.h5'.format(dr), 'r') as f:
+                    N_tot += len(f['Nu'])
+                    for k in keys:
+                        partial_data[k].append(f[k][()])
+
+            data = OrderedDict()
+            for k in keys:
+                data[k] = np.zeros(N_tot)
+                start_ind=0
[…]

### 2020-05-14 figures_and_data/report_scaling_laws.py

@@ -19,7 +19,10 @@ def read_data(ra_list, dir_list, keys=['Nu', 'delta_T', 'sim_time', 'Pe', 'KE', 
         data = OrderedDict()
         sub_runs = glob.glob('{:s}/run*/'.format(dr))
         if len(sub_runs) > 0:
-            numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            try: 
+                numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0])) for f in sub_runs]
+            except:
+                numbered_dirs  = [(f, float(f.split("run")[-1].split("/")[0].split('_')[0])) for f in sub_runs]
             sub_runs, run_num = zip(*sorted(numbered_dirs, key=lambda x: x[1]))
             partial_data = OrderedDict()
             for k in keys:
@@ -115,13 +118,14 @@ for k, data in mixed_data.items():
         fig.savefig('FT_scalings_{}_vs_time.png'.format(k), dpi=200, bbox_inches='tight')
 
 fig = plt.figure()
-for i, fd in enumerate(['Nu', 'Pe']):
-    ax = fig.add_subplot(1,2, 1+i)
+for i, fd in enumerate(['Nu', 'Pe', 'Pe']):
+    ax = fig.add_subplot(1,3, 1+i)
     fixed_ra = []
     fixed_val = []
     fixed_err = []
     for k in fixed_data.keys():
-        if fd == 'Pe' and float(k) < 1e9: continue
+        if i == 1 and float(k) < 1e9: continue
+        if i == 2 and float(k) >= 1e9: continue
         fixed_ra.append(float(k))
         fixed_val.append(np.mean(fixed_data[k][fd][-5000:]))
         fixed_err.append(np.std(fixed_data[k][fd][-5000:])/np.sqrt(5000))
@@ -140,3 +144,101 @@ for i, fd in enumerate(['Nu', 'Pe']):
 
 
 fig.savefig('TT_scalings.png', dpi=200, bbox_inches='tight')
+
+
+# Get data from files
+base_dir = './data/rotation/'
+fixed_dirs = glob.glob("{:s}TT/ra*/".format(base_dir))
[…]

### 2020-05-14 tex/mixedft_evolution_ms.tex
updates to abstract, intro, and sim details text

@@
 This long relaxation timescale can be skipped by either using a TT simulation's nonlinear state as initial conditions for an FT simulation, or by choosing initial conditions which more accurately guess the temperature difference between the top and bottom plates in the evolved state.}
-In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries.
+In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries\ea{, and time- and volume-averaged flow statistics like the Nusselt number and P\'{e}clet number are indistinguishable between FT and TT simulations}.
 \ea{FT boundaries are fundamentally asymmetric, and we examine the asymmetries that these boundaries produce in the flow.
@@
 However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
-%Mention mantle studies here
-We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
+We are unaware of any study which has examined the consequences of imposing these ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
 
-In this work, we examine how the choice of using ``mixed'' boundaries affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
+In this work, we examine how the choice of using ``mixed'' \ea{thermodynamic boundary conditions} affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
 In RBC, temperature is the only thermodynamic quantity and throughout this work we will \ea{adopt the gnomenclature of past authors including ref.~\cite{ishiwatari&all1994} and} refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
@@
 
-\ea{Early studies of FF convection often focused on flow morphologies, as large-to-infinite aspect ratio convective rolls are linearly unstable at the critical value of the Rayleigh number (see e.g., ref.~\cite{chapman&proctor1980}).
-However, the onset properties and resultant flow morphologies in FT simulations more strongly resemble TT dynamics than FF dynamics \cite{ishiwatari&all1994}.}
-\ea{More recently,} FF and TT boundaries \ea{have been shown to} exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
-It is generally assumed that, \ea{in their statistically stationary states, simulations with} FT boundaries should behave similarly to FF boundaries \cite{goluskin2016, otero&all2002}.
-%It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
+It is generally assumed that, \ea{in their statistically stationary states, simulations with} FT boundaries should behave similarly to \ea{those with} FF boundaries \cite{goluskin2016, otero&all2002}.
+\ea{Early studies of FF convection often focused on flow morphologies, because large-to-infinite aspect ratio convective rolls are linearly unstable for this choice of boundary condition (see e.g., ref.~\cite{chapman&proctor1980}).
+However, the onset properties and resultant flow morphologies in FT simulations more strongly resemble TT dynamics \cite{ishiwatari&all1994}, in that both are linearly unstable at a well-defined, finite aspect ratio.}
+\ea{Despite these differences near convective onset,} FF and TT boundaries \ea{have been shown to} exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We find that this long thermal relaxation can be bypassed by \ea{constructing smarter initial conditions based on the expected evolved Nusselt number, or by simply} using the results of TT simulations as initial conditions for FT simulations.
-Finally, FT boundaries create some asymmetries in the convective flows, but these asymmetries do not meaningfully change the mean convective state compared to TT simulations.
+We find that this long thermal relaxation can be bypassed by \ea{constructing smarter initial conditions based on the expected evolved value of Nu, or by simply} using the results of TT simulations as initial conditions for FT simulations.
+Finally, FT boundaries create some asymmetries in the convective flows, \ea{particularly in the boundary layers,} but these asymmetries do not meaningfully change the \ea{bulk} convective state compared to TT simulations.
 
@@
 In section \ref{sec:results_timescales}, we describe our findings \ea{regarding} the time evolution of FT systems.
-\ea{In section \ref{sec:results_dynamics}, we study dynamics and asymmetries in FT systems and compare them to TT systems.}
+\ea{In section \ref{sec:results_dynamics}, we study asymmetries in FT systems and compare them to TT systems.}
 In section \ref{sec:results_rotating}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
@@
 \end{equation}
-We impose FT and TT boundary conditions respectively as
+We respectively impose FT and TT boundary conditions as
 \begin{equation}
@@
 \begin{equation}
-u = \ea{v =} w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
+u = \ea{v =}\, w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
 \label{eqn:vel_bcs}
@@
 Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the \ea{IMEX}, second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
-The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using \ea{v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and} v1.0.0 \ea{(for all other cases)} of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
+The codes used to run the simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using \ea{v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and} v1.0.0 \ea{(for all other cases)} of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.
@@
 \subsection{Initial Conditions}
-The time evolution of FT simulations is sensitive to the choice of initial conditions made due to the fact that the evolved, nonlinear convective dynamics determine the mean temperature for this choice of boundary conditions.
+The time evolution of FT simulations is sensitive to the initial conditions due to the fact that the evolved, nonlinear convective dynamics determine the magnitude of the temperature jump across the domain.
 For this reason, we will study FT simulations which employ three different initial states.
 
-\paragraph{Classical ICs} 
-Our first set of initial conditions are the ``classical'' initial conditions on which the system was nondimensionalized,
+\paragraph{Classic ICs} 
+Our first set of initial conditions are the ``classic'' initial conditions on which the system was nondimensionalized,
 \begin{equation}
@@
 $$
-Here, $\delta_w = -\Delta T / 2$, an estimate of the boundary layer width, and $\grad_{\text{interior}}$, the temperature gradient in the interior of the domain, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width, and the temperature gradient in the interior of the domain, $\grad_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
 
@@
 The velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
-As a result, every simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
-\ea{To ensure that comparisons between TT and FT simulations are accurate, measurements in FT simulations will be taken over time windows longer by a factor of $\sqrt{\text{Nu}}$ than comparable windows in TT simulations.}
+As a result, every nondimensional simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a time unit in an FT simulation.
+\ea{We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
+To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.}
 
@@
 \end{equation}
-where the conductive flux is $F_{\text{cond}} = -\Peff^{-1}\grad T$, $F_{\text{cond,z}}$ is its z-component, and where $\int T dz = \Delta T / 2$ in RBC.
-The thermal relaxation time of a \RB convection experiment is therefore
+where $F_{\text{cond,z}}$ is the z-component of the conductive flux, $F_{\text{cond}} = -\Peff^{-1}\grad T$, and where $\int T dz = \Delta T / 2$ in RBC.
+The thermal relaxation time of an RBC experiment is therefore
 \begin{equation}
@@
 \end{equation}
-In the case of TT boundary conditions, we expect $\Delta E = 0$, as the initial and final state have the same mean temperature.
-The goal of our ``Nu-based'' and TT-to-FT initial conditions is to create FT systems in which $\Delta E = 0$ is also true, creating a system with a negligible relaxational timescale.
+In the case of TT boundary conditions, we expect $\Delta E = 0$, as the initial and final state have the same $\Delta T$.
+The goal of our ``Nu-based'' and TT-to-FT initial conditions is to create FT systems in which $\Delta E \approx 0$, creating a system with a negligible relaxational timescale.
 
@@
 \begin{acknowledgments}
+\ea{We'd like to thank the anonymous referee who suggested the idea of Nu-based ICs, and whose careful and thoughtful comments greatly improved both the quality and clarity of this manuscript.}
 We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
@@
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
-LK acknowledges support from the George Ellery Hale Post-Doctoral Fellowship.
+LK acknowledges support from the George Ellery Hale Post-Doctoral Fellowship and from NASA grant 80NSSC17K0008.
 This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 

### 2020-05-14 tex/mixedft_evolution_ms.tex
some edits through section 3

@@
 We also compare relaxed FT solutions to TT solutions.
-\ea{When classical initial conditions which are in hydrostatic and thermal equilibrium are employed,} the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+\ea{When classic initial conditions which are in hydrostatic and thermal equilibrium are employed,} the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
@@
 We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
-For classical and Nu-based ICs,
+For classic and Nu-based ICs,
 }
@@
 
-For the case of classical ICs in an FT system, $\Delta T(t=0) = -1$ and $\Delta T(t=\infty) = -\text{Nu}^{-1}$, and the temperature gradient at the bottom boundary is fixed at a value of -1.
+For the case of classic ICs in an FT system, $\Delta T(t=0) = -1$ and $\Delta T(t=\infty) = -\text{Nu}^{-1}$, and the temperature gradient at the bottom boundary is fixed at a value of -1.
 The thermal relaxation timescale is therefore
 \begin{equation}
-\tau_{\text{th, FT-classical}} = \Peff \frac{\text{Nu}^{-1} - 1}{\partial_z T(z=0.5) + 1} \sim \frac{\sqrt{\text{Ra Pr}}}{|\partial_z T(z = 0.5)| - 1}.
+\tau_{\text{th, FT-classic}} = \Peff \frac{\text{Nu}^{-1} - 1}{\partial_z T(z=0.5) + 1} \sim \frac{\sqrt{\text{Ra Pr}}}{|\partial_z T(z = 0.5)| - 1}.
 \end{equation}
@@
 The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
-However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} < \tau_{\text{th, FT-classical}} < \sqrt{\text{Ra Pr}}$.
+However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} < \tau_{\text{th, FT-classic}} < \sqrt{\text{Ra Pr}}$.
 
@@
 
-\subsection{Classical initial conditions: long thermal relaxation}
+\subsection{Classic initial conditions: long thermal relaxation}
 \label{sec:time_evolution_classic_ICs}
@@
 In the bottom four panels, we examine these temperature fields statistically by displaying their probability distribution functions (PDFs).
-To create these PDFs, we sample the full simulation temperature field once every freefall time unit\footnote{\ea{For TT simulations, a freefall time unit is one simulation time unit.
-For FT simulations, a freefall time unit is $\sqrt{\text{Nu}}$ simulation time units.}} over the span of 500 time units.
+To create these PDFs, we sample the full simulation temperature field once every \ea{evolved} freefall time, \ea{$\tau_{\text{ff, ev}}$}, over the span of 500\ea{$\tau_{\text{ff, ev}}$}.
 We interpolate the (unevenly spaced) vertical Chebyshev grid points onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
@@
 At early times (lower left), the FT simulation is characterized by two features: an extreme tail (to the left) that characterizes the cold plume at the upper boundary, and a migrating modal temperature that shifts from the right (hotter) to the left (cooler) as cold material mixes in the interior.
-At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold (left), fixed-temperature boundary and the modal value.
-From the modal value towards warmer temperatures, we find that the fixed-flux (lower boundary) is capable of producing more extreme temperature events and results in a more extended PDF tail.
+At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold fixed-temperature boundary and the modal value.
+From the modal value towards warmer temperatures, we find that the hot fixed-flux boundary is capable of producing more extreme temperature events and results in a more extended PDF tail.
 This long tail is explored further in section \ref{sec:asymmetries}.
@@
 
-In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable FT simulation which we timestepped through thermal relaxation.
+In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable \ea{classic} FT simulation.
 Shown are PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
@@
 The temperature PDF of the TT simulation unsurprisingly has a mean of 0.5, a Skewness close to zero (no asymmetry between upflows and downflows), and an appreciable Excess Kurtosis (the tails, which primarily sample the plumes, are more important than they are in a Normal Distribution).
-The FT temperature PDF, on the other hand, has a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more excess Kurtosis.
+The FT temperature PDF, on the other hand, has a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis.
 Furthermore, the mean temperature is slightly larger in the FT case.
-Outside of the temperature field, we find that the vertical velocity, $w$, and the vertical heat transport, $wT$, are well-described by normal distributions  aside from the area near their peak of zero (which is dominated by the boundary layers).
+Aside from the temperature field, we find that the vertical velocity, $w$, and the vertical heat transport, $wT$, are well-described by normal distributions  aside from the area near their peak of zero (which is dominated by the boundary layers).
 }
@@
 \paragraph{Nu-based ICs}
-The time evolution of Nu-based ICs is similar to the time evolution of TT simulations with classical ICs, with a few caveats.
+The time evolution of Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
-During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classical roll solution is achieved.
-This behavior is quite different from classical ICs in TT simulations, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
-Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classical ICs.
-Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classical ICs are very similar.
+During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classic roll solution is achieved.
+This behavior is quite different from classic ICs in TT simulations, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
+Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classic ICs.
+Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classic ICs are very similar.
 }
@@
 The thermal energy reservoir of TT simulations does not change between the initial and final state.
-The rapid relaxation of TT simulations therefore suggests that experimental restratification occurs rapidly in RBC. 
-The long rundown of FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
-Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.
-\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classical ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
+The rapid relaxation of TT simulations\ea{, as well as FT simulations with Nu-based and TT-to-FT ICs}, therefore suggests that experimental restratification occurs rapidly in RBC. 
+The long rundown of \ea{classic} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
+\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classic ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
 
 \ea{
-As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$\,\gtrsim 10^{8.67}$ .
+As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$ .
 This velocity field relaxation happens despite instant \emph{thermal} equilibration of the temperature field for these simulations.
@@
 \subsection{3D verification of 2D results}
-We note briefly that our results from 2D hold in 3D: classical ICs exhibit a prohibitively long thermal rundown, but equilibrated FT and TT simulations are analogous in a volume-averaged sense.
-In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from a 3D TT and TT-to-FT simulation.
+We note briefly that our results from 2D hold in 3D: classic ICs exhibit a prohibitively long thermal rundown, but equilibrated FT and TT simulations are analogous in a volume-averaged sense.
+In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from 3D TT and TT-to-FT simulations.
 As in 2D, we find that the two simulations are nearly identical aside from their temperature fields, and so have focused on the temperature fields in this figure.
@@
 At the bottom of the figure, we compare PDFs of the full temperature field to PDFs of the temperature field in each of the shown slices (near the top boundary layer, a vertical slice of the interior, and near the bottom boundary layer).
-The PDF of the full volume of these simulations is indistinguishable between the two cases except near the hot bottom boundary.
-Indeed, we find that the two cases have indistinguishable PDFs in a horizontal slice near the top boundary, and that temperature events which range from the fixed boundary temperature ($T = 0$) to the temperature achieved in the interior $T = 0.5\Delta T$) are all equally probable.
+The PDF of the temperature field over the full volume of these simulations is indistinguishable between the two cases except near the hot bottom boundary.
+Indeed, we find that the two cases have indistinguishable PDFs in a horizontal slice near the top boundary, and that temperature events which range from the fixed boundary temperature ($T = 0$) to the temperature achieved in the interior ($T = 0.5\Delta T$) are all equally probable.
 The story is the same for the TT case near the bottom boundary, but the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
@@
 \item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
-We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classical scaling laws along these parameter space sweeps.
+We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classic scaling laws along these parameter space sweeps.
 \item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation.

### 2020-05-14 referee_responses/submission1/referee_response.tex
adds paper to repo at end of zoom call status

@@
 \noindent
-\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent
+\Large{\textbf{Response to first report:}}\newline$\,$\newline\indent
 
@@
 This is an excellent point, and we have restructured the paper to try to make this abundantly clear.
-Section 2 (``Simulation Details'') now contains a subsection dedicated to initial conditions, and throughout the paper we have tried to clarify that thermal relaxation timescales depend on initial conditions.
+Section II (``Simulation Details'') now contains a subsection dedicated to initial conditions (II.C), and throughout the paper we have tried to clarify that thermal relaxation timescales depend on initial conditions.
 
@@
 \end{myquotation}
-This has now been clarified in section II.C (see the ``Additional ICs'' paragraph).
+This has now been clarified in section II.D see the ``Additional ICs'' paragraph).
 The linear temperature profile is now also referred to as ``Classical ICs''.
@@
 Those initial conditions are obviously wrong for the FT simulations whose overall temperature contrast is much smaller than 1. 
-This FT equilibrium temperature contrast can be estimated using your results showing that FT final state is comparable to TT final state, hence using classical scaling law for Nusselt (I like Nu=(Ra/Rac)$^(1/3)$, but what follows can be easily adapted to your favorite one):
+This FT equilibrium temperature contrast can be estimated using your results showing that FT final state is comparable to TT final state, hence using classical scaling law for Nusselt (I like Nu=(Ra/Rac)$^{1/3}$, but what follows can be easily adapted to your favorite one):
 \begin{itemize}
@@
 \end{myquotation}
-There are two questions here, and we'll respond to each bullet in order:
-\begin{enumerate}
-\item We agree with the logic of the math here, and that if you have a given law, Nu $\propto$ Ra$_e^{\alpha}$, you can retrieve a law for deltaT$\propto Ra^{-\alpha/(1+\alpha)}$ (where this exponent is 1/4 for $\alpha = 1/3$).
+We agree with the logic of the math here, and that if you have a given law, Nu $\propto$ Ra$_e^{\alpha}$, you can retrieve a law for deltaT$\propto Ra^{-\alpha/(1+\alpha)}$ (where this exponent is 1/4 for $\alpha = 1/3$).
 This is now shown in the paper (see eqn 15).
 We have presented this in its general form so that people can chose their favorite or best-fit scaling law.
-Due to its excellent agreement with the simulations we ran, we have chosen to stick with the $\alpha = 0.285$ law that we have used previously in this work.
-This means that a Ra$^{-0.22}$ law is a better fit for our data than Ra$^{-1/4}$, but those are pretty hard to distinguish between; so -- yes, this scaling roughly holds in our simulations.
-\item For the specific case of classical RBC, the initial conditions that you describe here are probably simpler to use than our TT-to-FT initial conditions.
-See section II.C for a description of these ``Nu-based'' initial conditions, and section III.B for a brief description of evolution in these systems.
+Now we will respond to each of the two posed questions in order.
+\begin{enumerate}
+\item 
+Yes, this scaling does seem to hold in our simulations.
+For us, the scaling law is closer to $\alpha = 0.285$ rather than $\alpha = 1/3$.
+This means that a Ra$^{-0.22}$ law is a better fit for our data than Ra$^{-1/4}$, but those are pretty hard to distinguish between.
+\item 
+We now conduct a series of test with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.C (TODO)).
+\vspace{0.5cm}
+\\
 One difficulty of using Nu-based initial conditions is that they are sensitive to the Nu vs.~Ra law that is used.
 For more complex simulations (e.g., rotationally- or magnetically- constrained RBC) where the Nu vs.~Ra laws are more contentious and less universally agreed-upon in the community, Nu-based ICs which presume the answer may be less reliable than TT-to-FT simulations.
+We highlight this in section V. (TODO)
 \end{enumerate}
@@
 \end{myquotation}
-Deriving the equilibration time is a bit trickier than this estimate because the difference between the flux leaving through the top of the domain constantly evolves over time.
+Deriving the equilibration time is a bit tricky, because the flux leaving through the top of the domain constantly evolves over time.
 We've added a derivation of this timescale and a discussion of this subtlety to a new section II.D.
-In practice, we find that this definition of an equilibration time far \emph{over}estimates the relaxational timescale.
-We find that the relaxational time is $(\text{a few})\cdot(\sqrt{\text{Ra Pr}}/\text{Nu})$, and have said so at the end of section III.C.
+In practice, we find that this definition of an equilibration time \emph{over}estimates the relaxational timescale.
+We find that the relaxational time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so at the end of section III.C.
 
@@
 \end{myquotation}
+Thank you.
 We have rewritten the abstract in an attempt to make it self-consistent and to make it more clearly speak to our results.
@@
 \end{myquotation}
-We have added section III.D and Fig.~4 to show that 3D results are in line with 2D results.
+Thank you.
+We have now run a non-rotating 3D case.
+We have added section III.D and Fig.~4, and have confirmed that the 3D results are in line with 2D results.
 
@@
 These typos have been fixed.
+\\
+
+\vspace{0.5cm}
+We would again like to thank the referee for the care with which they read our manuscript, and for their excellent constructive criticism.
+We feel that these comments have measurably improved our understanding of the problem being studied and have vastly improved the quality of the science being presented in our paper.
 
@@
 \noindent
-\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
+\Large{\textbf{Response to second report:}}\newline$\,$\newline\indent
 \begin{myquotation}
@@
 \end{myquotation}
-We have now verified our results in a 3D case with no-slip boundaries, analagous to our 2D setup, in section III.D.
-The introduction to the rotating case now provides more context to show that rotating RBC is a good testing bed for our TT-to-FT method.
+We thank the referee for their report.
+We agree that it was confusing to have a rotating 3D case with different boundary conditions.
+We have now conducted a non-rotating 3D case with no-slip boundaries, analagous to our 2D setup.
+The results of this are presented in section III.D and confirm the prior 2D results.
+In section V, for the rotating case, we provide more context to show that rotating RBC is a testbed for the TT-to-FT method.
 
@@
 We disagree.
-Through discussions with numerous colleagues and a deeper literature review, we are convinced that our results are novel.
-We have rewritten the abstract of the paper, restructured the Simulation Details and Results sections, and added a few references throughout the manuscript.
-These changes have aimed to improve the clarity and logical flow of our paper, and also have tried to better place our results in the context of the literature.
-
-If these results are truly well-known in the community, provide us with references.
+Through further discussions with numerous colleagues and a deeper literature review, we remain convinced that our results are novel.
+We have made various revisions to the structure of the paper, and have included further references to better place our results in the context of the literature.
+After doing so, we remain convinced that our results are novel.
+If we are incorrect, we would welcome references.
 
@@
 \end{myquotation}
-Section II.C and II.D now discusses how initial conditions affect thermal relaxation timescales.
+Thank you.
+We find that the relaxational time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so in section II.D.
+Sections II.C and II.D now discusses how initial conditions affect thermal relaxation timescales.
 
@@
 Also, imposing a boundary temperature entails the flow to develop any temperature gradient, while imposing the gradient at the wall limits the peaks. 
-What the authors call "energy reservoir" is nothing but the heat capacity of the fluid volume that, of course, takes more time to thermally equilibrate than the thin boundary layers.
+What the authors call ``energy reservoir'' is nothing but the heat capacity of the fluid volume that, of course, takes more time to thermally equilibrate than the thin boundary layers.
 \end{myquotation}
-TODO: I don't even know how to respond to this.
+Yes.
+But it turns out that the timescale of equilibration is complicated by the fact that the flux through one of the walls is constantly evolving and changing, and that has made this an interesting problem.
+We discuss this in section II.D.
 
@@
 \end{myquotation}
-Our goal is not to robustly examine rotating RBC.
-Our goal is to show that:
-\begin{enumerate}
-\item Timescale lessons in non-rotating convection apply to rotating convection (unsurprising), and therefore
-\item our TT-to-FT initial conditions can save a great deal of time in the rotating case where Nu vs.~Ra powerlaws are less well agreed-upon by the community, and the evolved Delta T is truly unknown.
-\end{enumerate}
-We have also added additional references to the literature.
+Our narrow goal in including the rotating example is to show that timescale lessons in non-rotating convection apply to rotating convection.
+Therefore, our TT-to-FT initial conditions can save a great deal of time in the rotating case where Nu vs.~Ra powerlaws are less well agreed-upon by the community, and the evolved Delta T is truly unknown.
+We have expanded our references to the rotating RBC literature.
 
@@
 The paper, finally, does not read well, with many imprecise, naive or bold statements: I report in the following a couple of examples. 
-"For this choice of boundary conditions, the critical value of the Rayleigh number is Ra∂z T = 1296 for FT boundaries and Ra∆T = 1708 for TT boundaries" is true only for horizontally infinite domains but not for finite aspect-ratio boxes.
+``For this choice of boundary conditions, the critical value of the Rayleigh number is Ra∂z T = 1296 for FT boundaries and Ra∆T = 1708 for TT boundaries'' is true only for horizontally infinite domains but not for finite aspect-ratio boxes.
 \end{myquotation}
-The unstable band of wavenumbers for FT and TT boundaries near the critical values reported is narrow and is captured by our numerical domains.
-We have added the clarification ``For this choice of \emph{aspect ratio and} boundary conditions...".
-
-FT boundaries do not have the same instability properties as FF boundaries in which the $k = 0$ mode is unstable.
+Thank you.
+We have computed the convective onset, and the critical wavenumber at Ra$_{\partial_z T} = 1296$ is $k \approx 2.5$, whereas the smallest $k$ that fits in our aspect ratio 2 domain is $\pi$.
+At $k = \pi$, the critical value is slightly higher, it is TODO, which is a small difference.
+It is true that in FF boundary conditions, there is a long and broad minimum extending to $k = 0$, and there is a band instability.
+But, for these FT and TT boundary conditions, the critical curve has a well-defined minimum, and wavelength associated with that minimum is close to the minimum wavelength obtainable in our finite aspect ratio boxes.
+We have made this caveat in the paper.
 
 \begin{myquotation}
-"Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading." is not clear at all; if one investigates a transient phase studying the thermal relaxation phase is perfectly fine while, if one is interested in the statistical steady state, considering the thermal relaxation phase is wrong (not misleading).
+``Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading.'' is not clear at all; if one investigates a transient phase studying the thermal relaxation phase is perfectly fine while, if one is interested in the statistical steady state, considering the thermal relaxation phase is wrong (not misleading).
 \end{myquotation}
-We agree that there may be cases in which studying transient phases can be interesting.
-In fact, we made this caveat and grounded it in a physical example in the following paragraph of the discussion section in our original manuscript.
+We don't disagree.
 
@@
 \end{myquotation}
+We thank the referee for their report.
+We think that our revised version has significantly clarified the results and narrative.
+We remain convinced that this work is novel.
 

### 2020-05-14 tex/mixedft_evolution_ms.tex
adds paper to repo at end of zoom call status

@@
 However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:results_timescales}, we do not expect this difference in linear stability to be very important.
+%TODO: Mention that our finite aspect ratio has a minimum wavenumber $\geq \pi$, so the critical values of Ra at those things is ___
 \ea{Many of these simulations are restricted to} two-dimensional (2D) convection \ea{by setting} $\partial_y = v = 0$.
@@
 \subsection{Initial Conditions}
+
+\subsubsection{Temperature Initial Conditions}
+
 The time evolution of FT simulations is sensitive to the initial conditions due to the fact that the evolved, nonlinear convective dynamics determine the magnitude of the temperature jump across the domain.
@@
 
-\paragraph{Additional ICs}
+\subsubsection{Additional Initial Conditions}
 In all cases, we modify the initial temperature profile by specifying the value of $T_1$, rather than through modifications to the linearly unstable reference profile, $T_0$.
@@
 }
-\paragraph{Dynamical Timescales}
+\subsubsection{Dynamical Timescales}
 One \ea{result of the mapping in Eqn.~\ref{eqn:ra_relation}} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
@@
 \ea{
-\paragraph{Evolutionary Timescales}
+\subsubsection{Evolutionary Timescales}
 The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
@@
 The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
-However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} < \tau_{\text{th, FT-classic}} < \sqrt{\text{Ra Pr}}$.
+However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} \lesssim \tau_{\text{th, FT-classic}} \lesssim \sqrt{\text{Ra Pr}}$.
+In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units(see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
 
@@
 FT simulation dynamics evolve slowly during thermal relaxation, and these images, PDFs, and traces demonstrate the importance of waiting for thermal relaxation to be achieved when conducting an FT simulation.
+\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classic ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
 
@@
 The long rundown of \ea{classic} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
-\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classic ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
 
@@
 The rapid evolution of our TT simulations suggests that RBC restratifies itself instantaneously.
-\item Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading.
+\item Dynamical measurements taken during thermal relaxation may be misleading.
 Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
+\ea{This is principly a concern in systems like FT which can have very long relaxational times compared to dynamical times.}
 \item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.

### 2020-05-15 tex/mixedft_evolution_ms.tex
adds TT-to-FT discussion to rotation section.

@@
 These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
+\ea{
+Rotating convection is an excellent testbed for our TT-to-FT method.
+In rotating convection, at a fixed value of Ek, as Ra increases, flows transition from the rotationally constrained to the rotationally unconstrained regime.
+The scaling of Nu~vs.~Ra changes drastically between these two regimes, and is some blend of the two in the intermediary, marginally constrained regime.
+Furthermore, the precise scaling law attained in the rotationally constrained regime differs as Ek changes, and these scaling laws are less straightforward and well-understood than their non-rotationally-constrained counterparts \cite{king&all2009, schmitz&tilgner2009, zhong&ahlers2010, julien&all2012, stevens&all2013, ecke2015, grooms2015, grooms&whitehead2015,  plumley&julien2019}.
+As a result, the powerlaw used for Nu-based ICs would have to be a complex function of Ek, Ra, and boundary conditions for rotating RBC.
+However, TT-to-FT should work generally for all parameters, so long as a TT simulation can be performed.
+}
 
@@
 
+\ea{
+We performed a TT-to-FT simulation starting from the evolved state of the TT simulation, and its time evolution matched that see in Fig.~\ref{fig:rbc_restart_description}.
+There was no long thermal evolutionary timescale.
+In the equilibrated classic FT simulation, we measured Nu$=7.90 \pm 0.01$, Pe$=1.70 \times 10^3$, and Ro$=0.115 \pm 0.006$.
+In the TT-to-FT simulation, we measured Nu$=7.83 \pm 0.01$, Pe$=1.65 \times 10^3$, and Ro=$0.114 \pm 0.005$.
+These Ro measurements are indistinguishable, Nu measurements are within 1\% of each other, and Pe measurements are within 3\% of each other, representing excellent agreement.
+}
+
 We once again find it important to briefly note the difference in computational cost between the FT and TT simulations conducted here.
 The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.6 \times 10^4$ cpu-hours.
-By comparison, the cost of the FT simulation shown in the same panels was \emph{two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
-The TT simulation's coefficient resolution was $128^3$.
+\ea{The TT-to-FT simulation cost an additional $4.34 \times 10^4$ cpu-hours.}
+By comparison, the cost of the FT simulation shown in the same panels was \emph{nearly two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
+The TT \ea{and TT-to-FT} simulations \ea{had a} coefficient resolution \ea{of} $128^3$.
 The FT simulation's initial resolution required to resolve the convective transient was $512\times384^2$ coefficients.

### 2020-05-15 tex/mixedft_evolution_ms.tex
adds estimate of FT runddown time for 3D case; adds in true critical values

@@
 \end{equation}
-For this choice of \ea{aspect ratio and} boundary conditions, the critical value of the Rayleigh number is Ra$_{\partial_z T} = 1296$ for FT boundaries and Ra$_{\Delta T} = 1708$ for TT boundaries \cite{goluskin2016}.
+For this choice of boundary conditions, the critical values of the Rayleigh number \ea{and wavenumber are (Ra$_{\partial_z T}, k) = (1295.78, 2.5519)$} for FT boundaries and \ea{(Ra$_{\Delta T}, k) = (1707.76, 3.1163)$} for TT boundaries \cite{goluskin2016}.
+\ea{In our $\Gamma = 2$ box, the smallest wavenumber permitted is $k = \pi$, and at that wavenumber the critical values of are Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which are slightly larger than the classical onset values}.
 Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
 However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:results_timescales}, we do not expect this difference in linear stability to be very important.
-%TODO: Mention that our finite aspect ratio has a minimum wavenumber $\geq \pi$, so the critical values of Ra at those things is ___
 \ea{Many of these simulations are restricted to} two-dimensional (2D) convection \ea{by setting} $\partial_y = v = 0$.
@@
 \subsection{3D verification of 2D results}
-We note briefly that our results from 2D hold in 3D: classic ICs exhibit a prohibitively long thermal rundown, but equilibrated FT and TT simulations are analogous in a volume-averaged sense.
+Timestepping through the thermal relaxation of a classic FT simulation is prohibatively expensive in 3D, even for our least turbulent Ra$_{\partial_z T} = 2.61 \times 10^9$ case.
+In order to timestep through the intense, early convective transient, we anticipate that such a simulation would require a coefficient resolution of $\gtrsim 512^3$, a factor of 64 times more coefficients than our comparable 2D case at 2048x1024.
+This classic FT 2D case took $1.21 \times 10^5$ cpu-hours, so we estimate that a classic FT case in 3D at this value of Ra$_{\partial_z T}$ would take O(10 million) cpu-hours.
+We found previously \cite{anders&all2018} at lower Ra$_{\partial_z T}$ that 3D classic FT cases exhibited the same thermal rundown as 2D cases.
+As a result, we will focus here on comparisons of FT and TT simulations in the evolved state through the use of TT-to-FT initial conditions.
+
+We find that equilibrated FT and TT simulations are analogous in a volume-averaged sense: measurements of Nu (31.4 for TT, 31.9 for FT) and Pe ($1.78 \times 10^3$ for both) are nearly indistinguishable.
 In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from 3D TT and TT-to-FT simulations.

### 2020-05-15 tex/mixedft_evolution_ms.tex
some paragraphs-> subsections

@@
 
-\ea{\paragraph{TT-to-FT} Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
+\ea{\subsubsection{TT-to-FT} Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
 It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.
@@
 
-\paragraph{Statistical Comparison of BCs and ICs}
+\subsubsection{Statistical Comparison of BCs and ICs}
 From the moments of these PDFs, we conclude that the primary difference between FT and TT simulations is in the temperature field, and that the vertical velocities and nonlinear transport is the same regardless of boundary conditions.
@@
 \ea{
-\paragraph{Nu-based ICs}
+\subsubsection{Nu-based ICs}
 The time evolution of Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.

### 2020-05-15 referee_responses/submission1/referee_response.tex
finishes off TODOs in referee response

@@
 \item 
-We now conduct a series of test with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.C (TODO)).
+We now conduct a series of test with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.B).
 \vspace{0.5cm}
@@
 For more complex simulations (e.g., rotationally- or magnetically- constrained RBC) where the Nu vs.~Ra laws are more contentious and less universally agreed-upon in the community, Nu-based ICs which presume the answer may be less reliable than TT-to-FT simulations.
-We highlight this in section V. (TODO)
+We highlight this in section V.
 \end{enumerate}
@@
 Thank you.
-We have computed the convective onset, and the critical wavenumber at Ra$_{\partial_z T} = 1296$ is $k \approx 2.5$, whereas the smallest $k$ that fits in our aspect ratio 2 domain is $\pi$.
-At $k = \pi$, the critical value is slightly higher, it is TODO, which is a small difference.
+We have computed the convective onset, and the FT critical wavenumber at Ra$_{\partial_z T} = 1295.78$ is $k = 2.5519$, the TT critical wavenumber is Ra$_{\Delta T} = 1707.76$ at $k = 3.1163$, but the smallest $k$ that fits in our aspect ratio 2 domain is $k = \pi$.
+At $k = \pi$, the critical value is slightly higher, Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which is a small difference.
+We have made this caveat in the text.
 It is true that in FF boundary conditions, there is a long and broad minimum extending to $k = 0$, and there is a band instability.
 But, for these FT and TT boundary conditions, the critical curve has a well-defined minimum, and wavelength associated with that minimum is close to the minimum wavelength obtainable in our finite aspect ratio boxes.
-We have made this caveat in the paper.
 

### 2020-05-15 referee_responses/submission1/referee_response.tex
rough v2 of paper done. Rough referee response done. Ready for co-author review.

@@
 We return our revised manuscript, ``Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it.'' 
+We thank the referees for their time and effort in reviewing our work; we would like to particularly thank referee 1 for their careful and thoughtful comments.
 We have addressed the questions and concerns of the referees, and we rebut the claim of referee 2 that our results are not novel.
+
+This version of the manuscript has been substantially edited and logically reorganized compared to the previous version.
+However, the main results, conclusions, and figures are largely the same.
 We would like to point out a few major changes in this version of the manuscript:
 \begin{enumerate}
+\item The abstract has been largely rewritten for clarity.
 \item The ``Simulation Details'' section has been broken up into subsections, and two new subsections have been added. These discuss:
@@
 \item The different initial conditions used in the simulations in this work.
-The description of our TT-to-FT procedure has been moved here.
+The description of our TT-to-FT procedure has been moved here and expanded.
 Per the advice of referee 1, we have also added and studied new ``Nu-based'' boundary conditions.
@@
 \item The ``Results'' section has been broken up into two major sections.
-The first focuses on the time evolution of FT simulations which employ different initial conditions, and it compares their equilibrated states.
-The second focuses on asymmetries in the flows introduced by the boundary conditions.
-\item Our non-rotating 2D results have been verified with a 3D case.
+Section III focuses on the time evolution of FT simulations which employ different initial conditions, and it compares their equilibrated states to TT simulations.
+Section IV focuses on asymmetries in the flows introduced by the boundary conditions.
+\item We have computed a 3D, non rotating case.
+Its results are presented in section III.D, along with a new figure, Fig.~4.
 \end{enumerate}
-Aside from these major changes, we have cleaned up the text throughout the paper for clarity, including in the abstract.
+Aside from these major changes and reorganizations, we have cleaned up the text throughout the paper for clarity, including in the abstract.
 We have included a ``redlined'' version of the manuscript in this resubmission which highlights the changes we have made to the text of the manuscript.
 
-We feel that the clarity and scientific content of the paper have been greatly improved by the report of referee 1, and we thank that referee for their honest critiques and attention to detail. 
+We feel that the clarity and scientific content of the paper have been greatly improved by the referee process. 
 Below we include our responses to both referee reports; the original text of the reports is included in italics, and our responses follow inline in unitalicized blocks.

### 2020-05-15 tex/mixedft_evolution_ms.tex
adds Ra_DeltaT clarification to fig 1 caption
rough v2 of paper done. Rough referee response done. Ready for co-author review.

@@
 In studies of Boussinesq convection, the standard choice is to hold constant the temperature difference across the domain by fixing the temperature at the upper and lower boundaries.
-However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
+However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019, matilsky&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
 We are unaware of any study which has examined the consequences of imposing these ``mixed'' boundaries that are frequently favored in astrophysical convection studies.
@@
 
-In this paper, we investigate the thermal relaxation of and the asymmetries in RBC with FT boundary conditions.
+In this paper, we investigate the thermal relaxation of, and the asymmetries in, RBC with FT boundary conditions.
 We also compare relaxed FT solutions to TT solutions.
@@
 \end{equation}
-where $u_{\text{ff}}$ is the freefall velocity, $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
+where $u_{\text{ff}}$ is the freefall velocity, $g$ is the gravitational acceleration, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
 These parameters set the freefall Reynolds (\Reff) and P\'{e}clet (\Peff) numbers, 
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In non rotating RBC (section\ea{s} \ref{sec:results_timescales}\ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
+In non rotating RBC (section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
 
@@
 \begin{equation}
-(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5};\qquad\qquad
+(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5},\qquad\qquad
 (\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
@@
 
-In section\ea{s} \ref{sec:results_timescales}\ea{\& \ref{sec:results_dynamics}}, we study \ea{non rotating convection}.
+In section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}, we study \ea{non rotating convection}.
 For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
@@
 For this choice of boundary conditions, the critical values of the Rayleigh number \ea{and wavenumber are (Ra$_{\partial_z T}, k) = (1295.78, 2.5519)$} for FT boundaries and \ea{(Ra$_{\Delta T}, k) = (1707.76, 3.1163)$} for TT boundaries \cite{goluskin2016}.
-\ea{In our $\Gamma = 2$ box, the smallest wavenumber permitted is $k = \pi$, and at that wavenumber the critical values of are Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which are slightly larger than the classical onset values}.
-Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
-However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:results_timescales}, we do not expect this difference in linear stability to be very important.
+\ea{In our $\Gamma = 2$ box, the smallest wavenumber permitted is $k = \pi$, and at that wavenumber the critical values are Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which are slightly larger than the classical onset values}.
+It is reasonable to expect important differences between FT and TT solutions at low supercriticalities due to the difference in onset.
+However, for the supercriticalities of O($10^{5+}$) studied here, we do not expect this difference in linear stability to be very important.
 \ea{Many of these simulations are restricted to} two-dimensional (2D) convection \ea{by setting} $\partial_y = v = 0$.
@@
 \end{equation}
+We set the initial temperature field by integrating Eqn.~\ref{eqn:nu_based_gradT} according to the top (fixed-temperature) boundary condition.
 Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $w(z)$, to set the temperature gradient to $-1$ near the boundaries,
@@
 $$
-Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width, and the temperature gradient in the interior of the domain, $\grad_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $\grad_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
 In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
@@
 \end{equation}
-Where the final expression is for the large Ra case where Nu$^{-1} \rightarrow 0$.
+Where the final expression is for the large Ra case where Nu$^{-1} \ll 1$.
 The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
 However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} \lesssim \tau_{\text{th, FT-classic}} \lesssim \sqrt{\text{Ra Pr}}$.
-In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units(see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
+In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units(see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
 
@@
 
+In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of a \ea{classic-IC} FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
+As shown in the top four panels, we see the expected convective roll solution in both TT simulations (top row) and at early and late times in the FT simulation (bottom row).
+Interestingly, we find highly asymmetrical dynamics at early times in the FT simulation (bottom left), in which the temperature anomaly in the cold plume is much greater than in the warm plume.
+This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
+In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).
+
 \begin{figure}[p!]
@@
 \caption{ 
-	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation at early and late times (bottom row).
-	(Left two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^{10}$ and early in an FT simulation when Ra$_{\Delta T} \approx 10^{10}$.
+	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$ }at early and late times (bottom row).
+	(Left two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^{10}$ and early in the FT simulation when Ra$_{\Delta T} \approx 10^{10}$.
 	To first order, both cases have similar flow structures: a large convective cell and plumes which break apart into small turbulent eddies.
@@
 	The relaxed FT simulation is visually indistinguishable from its comparable TT simulation.
+	\ea{Note that Ra$_{\Delta T}$ is a measured \emph{output} quantity for the FT simulation at two different times in its evolution.}
 \\	
 	(Bottom four panels) Probability distribution functions (PDFs) of the full temperature field in each of the four dynamical panels pictured above.
-	PDFs sample the dynamics in each simulation once every simulation freefall time unit over the course of 500 freefall time units.
 	The black vertical line shows the median value, and the grey outline shows the 68\% confidence interval, or where the cumulative distribution function (CDF)'s value ranges from 0.16 to 0.84.
@@
 	(Bottom left) At early times in the FT simulation, the modal value of the PDF constantly moves left (towards the cold fixed-temperature boundary).
-	(Bottom right) At late times, the temperature PDF from the cold fixed-temperature value (on the left) to the mode is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
+	(Bottom right) At late times, the temperature PDF from the cold fixed-temperature value (on the left) to the modal value is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
 	\label{fig:rbc_evolution_dynamics} }
 \end{figure}
-
-In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of an FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
-As shown in the top four panels, we see the expected convective roll solution in both TT simulations (top row) and at early and late times in the FT simulation (bottom row).
-Interestingly, we find highly asymmetrical dynamics at early times in the FT simulation (bottom left), in which the temperature anomaly in the cold plume is much greater than in the warm plume.
-This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
-In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).
 
@@
 At Ra$_{\partial_z T} = 2.61 \times 10^{9}$, our best-fit paths are $\text{Nu} = 0.0845\,\text{Ra}_{\Delta T}^{0.310}$ and $\text{Pe} = (4.05 \times 10^{-3})\,\text{Ra}_{\Delta T}^{0.739}$.
-By comparison, the best fit scaling laws for our TT cases are $\text{Nu} = 0.141\,\text{Ra}_{\Delta T}^{0.282}$ (very similar to the law reported in ref.~\cite{johnston&doering2009}), $\text{Pe} = (0.303)\,\text{Ra}_{\Delta T}^{0.516}$ (for Ra$_{\Delta T} \geq 10^9$), and $\text{Pe} = (2.41 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.64}$.
+By comparison, the best fit scaling laws for our TT cases are $\text{Nu} = 0.141\,\text{Ra}_{\Delta T}^{0.282}$ (very similar to the law reported in ref.~\cite{johnston&doering2009}), $\text{Pe} = (0.303)\,\text{Ra}_{\Delta T}^{0.516}$ (for Ra$_{\Delta T} \geq 10^9$), and $\text{Pe} = (2.41 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.64}$ (for Ra$_{\Delta T} < 10^9$).
 }
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
+	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange\ea{, Ra$_{\partial_z T} = 4.81 \times 10^{10}$}) and TT (purple\ea{, Ra$_{\Delta T} = 10^9$}) simulation are shown.
 	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
-	We display evolutionary traces of Ra (top, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
+	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
 	(Right two panels) Compensated scaling plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities, which have been averaged over a rolling time window of 25 simulation time units, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
+	(Left three panels) Time traces of scalar quantities, which have been averaged over a rolling time window of 25 simulation time units, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$}.
 	The time of the change of boundary conditions is denoted by the vertical black line.
@@
 	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
-	(right four panels) PDFs are shown which compare the dynamics during the grey time window in the left panels (black PDFs, TT-to-FT) to dynamics from a comparable time window in the FT case from Fig.~\ref{fig:rbc_scalar_comparisons}.
+	(right four panels) PDFs are shown which compare TT-to-FT dynamics (black PDFs) to dynamics from \ea{the classic-IC} FT case from Fig.~\ref{fig:rbc_scalar_comparisons} (green PDFs).
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
@@
 \subsubsection{Statistical Comparison of BCs and ICs}
-From the moments of these PDFs, we conclude that the primary difference between FT and TT simulations is in the temperature field, and that the vertical velocities and nonlinear transport is the same regardless of boundary conditions.
+From the moments of the PDFs presented in table \ref{table:pdf_values}, we conclude that FT and TT simulations are indistinguishable outside of their temperature fields.
 The temperature PDF of the TT simulation unsurprisingly has a mean of 0.5, a Skewness close to zero (no asymmetry between upflows and downflows), and an appreciable Excess Kurtosis (the tails, which primarily sample the plumes, are more important than they are in a Normal Distribution).
-The FT temperature PDF, on the other hand, has a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis.
-Furthermore, the mean temperature is slightly larger in the FT case.
-Aside from the temperature field, we find that the vertical velocity, $w$, and the vertical heat transport, $wT$, are well-described by normal distributions  aside from the area near their peak of zero (which is dominated by the boundary layers).
+The FT temperature PDF, on the other hand, has a mean slightly larger than 0.5, a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis (implying more extreme plumes).
+It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
 }
@@
 \caption{ 
-	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
-	\ea{Note that the coefficient resolution of the evolved FT simulation and the TT-to-FT simulation are the same (nz, nx) = (1024, 2048).}
+	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below \ea{for the TT case with Ra$_{\Delta T} = 10^9$ and all FT cases with Ra$_{\partial_z T} = 4.83\times 10^{10}$}.
 }
@@
 \subsubsection{Nu-based ICs}
-The time evolution of Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.
+The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
@@
 
-\subsection{\ea{Discussion of 2D results}} We note briefly that \ea{Nu-based ICs and} this TT-to-FT mechanism \ea{are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
+\subsection{\ea{Discussion of 2D results}} 
+We note briefly that \ea{Nu-based and} TT-to-FT \ea{ICs are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 \caption{ 
-	(top six panels) Snapshots of the temperature anomaly are shown for select slices through 3D domains.
-	The left column shows data from TT simulations with Ra$_{\Delta T} = 10^{8}$, the right column shows data for FT simulations with Ra$_{\partial_z T} = 3.1 \times 10^{9}$.
+	\ea{
+	(top six panels) Snapshots of the temperature anomaly are shown for select slices through the 3D TT simulation at Ra$_{\Delta T} = 10^8$ (left column) and the TT-to-FT simulation at Ra$_{\partial_z T} = 3.1 \times 10^9$ (right column).
 	The top and bottom rows respectively show horizontal slices 1\% of the domain depth away from the top and bottom boundaries, while the middle row shows a vertical slice at $y = 0$.
 	Visually, TT and FT dynamics are indistinguishable aside from the warm upflows near the bottom boundary.
+	\\
 	(Bottom four panels) PDFs of the temperature field are shown.
-	From left to right, these PDFs are shown for the full 3D domain, the upper boundary layer slice, the vertical slice, and the bottom boundary layer slice.
+	From left to right, these PDFs are shown for the full 3D domain, the upper boundary layer slice at $z = 0.49$, the vertical slice at $y = 0$, and the bottom boundary layer slice at $z = -0.49$.
 	The extreme temperature events which stand out visually near the bottom boundary layer can be clearly seen in all PDFs except for the one near the upper boundary.
+	}
 	\label{fig:rbc_3D_panels} }
@@
 \subsection{3D verification of 2D results}
-Timestepping through the thermal relaxation of a classic FT simulation is prohibatively expensive in 3D, even for our least turbulent Ra$_{\partial_z T} = 2.61 \times 10^9$ case.
+Timestepping through the thermal relaxation of a classic FT simulation is prohibatively expensive in 3D, even for our least turbulent case with an evolved Ra$_{\Delta T} \approx 10^8$.
 In order to timestep through the intense, early convective transient, we anticipate that such a simulation would require a coefficient resolution of $\gtrsim 512^3$, a factor of 64 times more coefficients than our comparable 2D case at 2048x1024.
-This classic FT 2D case took $1.21 \times 10^5$ cpu-hours, so we estimate that a classic FT case in 3D at this value of Ra$_{\partial_z T}$ would take O(10 million) cpu-hours.
-We found previously \cite{anders&all2018} at lower Ra$_{\partial_z T}$ that 3D classic FT cases exhibited the same thermal rundown as 2D cases.
-As a result, we will focus here on comparisons of FT and TT simulations in the evolved state through the use of TT-to-FT initial conditions.
+This 2D, classic-IC, FT case took $1.21 \times 10^5$ cpu-hours, so we estimate that a classic FT case in 3D at this value of Ra$_{\partial_z T}$ would take O(10 million) cpu-hours.
+We found in previous work \cite{anders&all2018} at lower Ra$_{\partial_z T}$ that 3D classic FT cases exhibited the same thermal rundown as 2D cases.
+As a result, we will focus here on 3D comparisons of FT and TT simulations in the statistically-stationary state through the use of TT-to-FT initial conditions.
 
@@
 In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from 3D TT and TT-to-FT simulations.
-As in 2D, we find that the two simulations are nearly identical aside from their temperature fields, and so have focused on the temperature fields in this figure.
+As in 2D, we find no difference between the PDFs of evolved quantities like the nonlinear transport ($wT$) between TT and FT simulations.
+Therefore, we have focused on the temperature fields in this figure, which does display differences between the two sets of boundary conditions.
 Near the top boundary and in the interior, the TT and FT dynamics are quite similar.
 However, near the bottom boundary, the warm upflows in FT simulations are hotter relative to their counterparts in TT simulations.
-At the bottom of the figure, we compare PDFs of the full temperature field to PDFs of the temperature field in each of the shown slices (near the top boundary layer, a vertical slice of the interior, and near the bottom boundary layer).
-The PDF of the temperature field over the full volume of these simulations is indistinguishable between the two cases except near the hot bottom boundary.
-Indeed, we find that the two cases have indistinguishable PDFs in a horizontal slice near the top boundary, and that temperature events which range from the fixed boundary temperature ($T = 0$) to the temperature achieved in the interior ($T = 0.5\Delta T$) are all equally probable.
-The story is the same for the TT case near the bottom boundary, but the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
+
+At the bottom of Fig.~\ref{fig:rbc_3D_panels}, we compare PDFs of the full temperature field to PDFs of the temperature field in each of the shown slices (near the top boundary layer, a vertical slice of the interior, and near the bottom boundary layer).
+The PDF of the temperature field over the full volume of these simulations shows the same features as in 2D (see Fig.~\ref{fig:rbc_evolution_dynamics}).
+Interestingly, we find that within the upper boundary layer, the two cases have indistinguishable temperature fields, with temperature events ranging from the fixed boundary temperature ($T = 0$) to the temperature achieved in the interior ($T = 0.5\Delta T$) occuring with equal probability.
+However, near the bottom boundary, the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
 Unsurprisingly, we find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is similar, but not identical, to the PDFs of the temperature field of the full volume, suggesting that this one slice does not capture the full range of possible dynamics which occur in the domain over our sampling window.
@@
 
-\section{Results: Evolved dynamics and asymmetries in FT simulations}
+\section{Results: Evolved structure, dynamics, and asymmetries in FT simulations}
 \label{sec:results_dynamics}
@@
 In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Time averages are taken over 500 freefall time units for the \ea{evolved flows}, sampled once every 0.1 time units.
-In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
+Time averages are taken over 500\ea{$\tau_{\text{ff, ev}}$}, sampled once every 0.1\ea{$\tau_{\text{ff, ev}}$}.
+In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the vertical conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
 Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
-\ea{Here, we define the boundary layers as the heights above or below which conduction carries 95\% of the flux.
-We find a boundary layer depth of $\sim 0.024$ at Ra$_{\Delta T} = 10^9$, and show three times this depth in the zoomed in panels}
-Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
+Zoomed-in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
 Inset panels show the percentage difference between the FT and TT solutions.
@@
 The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the \ea{FT and TT cases differ by no more than 0.0025 in the plotted units} in the interior. 
+\ea{Here, we define the boundary layers as the heights above or below which conduction carries 95\% of the flux.
+By this definition, the boundary layer depth is $\sim 0.024$ at Ra$_{\Delta T} = 10^9$, and we show three times this depth in the zoomed-in panels.}
 
@@
 When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
-These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.
+These differences are interesting, \ea{can be seen visually in Fig.~\ref{fig:rbc_3D_panels},} and are explored further in \ea{the next section} (section \ref{sec:asymmetries}) and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do seem to affect the convective dynamics appreciably.
 
@@
 In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation near the fixed-flux boundary.
-In the left panel, we plot PDFs of the temperature fields in comparable TT and FT simulations.
+In the left panel, we plot PDFs of the temperature fields of the two cases.
 These PDFs agree remarkably well near the mean and for cold temperatures (near the fixed temperature boundary), but diverge in the tail of the PDF for hot temperatures where $T/\Delta T \gtrsim 0.8$, where the boundary conditions differ.
@@
 We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
-The TT upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
+The fixed-temperature upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
 The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area, thus allowing for the asymmetry in the tails of the temperature PDF.
@@
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-\footnote{\ea{At these parameters, we would be in the cellular convection regime of \citet{stellmach&all2014}, but our dynamics are different due to our choice of stress free boundary conditions.
-}}.
 These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
@@
 
-In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of the FT and TT cases.
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of \ea{a classic-IC} FT and TT case.
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
-Even in the presence of strong rotation, the TT immediately equilibrates, but the FT case takes thousands of freefall times to achieve thermal relaxation.
+Even in the presence of strong rotation, the TT simulation immediately equilibrates, but the FT case takes thousands of freefall times to achieve thermal relaxation.
 In the middle panel, we show the evolution of Ro; the evolved flows in both simulations exhibit rotationally constrained dynamics with Ro $\,\approx 0.1$, but the flows in the FT simulation relax to this state from an initially unconstrained state (Ro $\,\approx 1$).
@@
 \ea{We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}}/\text{Nu}$ nondimensional freefall time units.}
+
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
+\caption{ 
+	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange) and TT (purple) simulation are shown.
+	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
+	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
+	(Middle panel) Ro evolution of both simulations; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
+	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
+	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
+	Circular and diamond data points are respectively simulations and experimental data points from ref.~\cite{cheng&all2015}.
+	The color of the data points signifies the Ekman number of the points, and black points are non rotating.
+	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
+	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
+	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
+	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
+	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
+	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
+	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
+	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
+\label{fig:rotating_panels} }
+\end{figure}
 
@@
 The FT simulation at all times when Ra$_{\Delta T} < 8 \times 10^9$ traces out $\text{Nu} = (1.08 \times 10^{-18})\,\text{Ra}_{\Delta T}^{2}$ and $\text{Pe} = (4.26 \times 10^{-20})\,\text{Ra}_{\Delta T}^{2.4}$.
-The TT simulation with Ra$_{\Delta T} < 8 \times 10^9$ trace out $\text{Nu} = (9.36 \times 10^{-17})\,\text{Ra}_{\Delta T}^{1.79}$ and $\text{Pe} = (4.78 \times 10^{-19})\,\text{Ra}_{\Delta T}^{2.27}$.}
+The TT simulations with Ra$_{\Delta T} < 8 \times 10^9$ trace out $\text{Nu} = (9.36 \times 10^{-17})\,\text{Ra}_{\Delta T}^{1.79}$ and $\text{Pe} = (4.78 \times 10^{-19})\,\text{Ra}_{\Delta T}^{2.27}$.}
 As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT \ea{scaling laws} are once again \ea{steeper than} the comparable TT \ea{laws}.
@@
 \ea{
-We performed a TT-to-FT simulation starting from the evolved state of the TT simulation, and its time evolution matched that see in Fig.~\ref{fig:rbc_restart_description}.
+We performed a TT-to-FT simulation starting from the evolved state of the TT simulation, and its time evolution matched that seen in Fig.~\ref{fig:rbc_restart_description}.
 There was no long thermal evolutionary timescale.
@@
 
-We once again find it important to briefly note the difference in computational cost between the FT and TT simulations conducted here.
-The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.6 \times 10^4$ cpu-hours.
-\ea{The TT-to-FT simulation cost an additional $4.34 \times 10^4$ cpu-hours.}
-By comparison, the cost of the FT simulation shown in the same panels was \emph{nearly two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
+We once again find it important to briefly note the difference in computational cost between the \ea{classic-IC} FT, \ea{TT-to-FT,} and TT simulations conducted here.
+The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.2 \times 10^3$ cpu-hours to run 5000 freefall times.
+\ea{The TT-to-FT simulation cost an additional $1.28 \times 10^3$ cpu-hours to run 1000$\tau_{\text{ff, ev}}$.}
+By comparison, the cost of the FT simulation shown in the same panels was \emph{roughly three orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
 The TT \ea{and TT-to-FT} simulations \ea{had a} coefficient resolution \ea{of} $128^3$.
@@
 This suggests that small scale turbulent velocity structures---which are injected by the vigorous transient and perhaps associated with the LSV---are long lived throughout the thermal evolution of the simulation.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
-\caption{ 
-	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
-	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
-	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
-	(Middle panel) Ro evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
-	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
-	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
-	Circular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
-	The color of the data points signifies the Ekman number of the points, and black points are non rotating.
-	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
-	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
-	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
-	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
-	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
-	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
-	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
-	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
-\label{fig:rotating_panels} }
-\end{figure}
 
@@
 \label{sec:discussion}
-In short, we find that FT simulations experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
+In short, we find that FT simulations \ea{can} experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
 
 In this paper, we have studied the time evolution of \RB convection (RBC) under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
-Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
+\ea{In the case of FT boundaries, we studied three different sets of initial conditions and examined both the nature of thermal relaxation and the equilibrated, statistically stationary state.}
+Through studying this relaxation and the relaxed states simulations, we come to the following conclusions:
 \begin{enumerate}
 \item Thermal relaxation in RBC has two components: (a) changes in the energy reservoir and (b) changes in the stratification.
-We find that the long relaxation of FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations due to the lack of evolution of the average domain temperature.
-The rapid evolution of our TT simulations suggests that RBC restratifies itself instantaneously.
+We find that the long relaxation of \ea{classic-IC} FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations \ea{and FT simulations with Nu-based or TT-to-FT ICs} due to the lack of evolution of the \ea{temperature difference between the boundaries}.
+The rapid evolution of \ea{all of our simulations other than the classic-IC FC} simulations suggests that RBC \ea{thermally} restratifies itself instantaneously.
 \item Dynamical measurements taken during thermal relaxation may be misleading.
 Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
-\ea{This is principly a concern in systems like FT which can have very long relaxational times compared to dynamical times.}
-\item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
+\ea{This is principly a concern in systems like classic-IC FT simulations which can have very long relaxational times compared to dynamical times.}
+\item The thermal relaxation process of a \ea{classic-IC} FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
 We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classic scaling laws along these parameter space sweeps.
-\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation.
-\item Despite minor asymmetries near the fixed-flux boundary, we find no meaningful difference between the mean state of FT and TT simulations.
+\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation, \ea{or by constructing an initial state which is characterized by a temperature difference similar to the evolved one}.
+\item Despite minor asymmetries near the \ea{boundaries}, we find no meaningful difference between the mean state of FT and TT simulations.
 \end{enumerate}
@@
 It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
-Some authors who study astrophysical convection \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018, matilsky&all2019} employ FF boundary conditions, and our results here suggest that such a choice may be ideal in those complex simulations.
+Some authors who study astrophysical convection \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018} employ FF boundary conditions, and our results here suggest that such a choice may be ideal in those complex simulations.
+\ea{Indeed, convection in 3D spherical shells does seem to thermally converge faster with FF boundaries than FT boundaries (Matilsky 2020, private communication).
+However, FF boundaries have also been shown to drive different flow morphologies than FT or TT boundaries in rotating convection in spherical geometries \cite{matilsky&all2020, calkins&all2015}, so perhaps numericists should lean on the development of ``smarter'' initial conditions rather than changes to the boundary conditions to achieve faster relaxation for some cases.
+}
 
@@
 TT	&	Classic		&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
-TT	&	Classic		&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
+TT	&	Classic		&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.2 \times 10^3$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
 FT	&	Classic		&	$2.1 \times 10^{10}$	&	384$^2\times$512*	&	13950		&	$2.3 \times 10^6$	&	$7.90 \pm 0.01$	&	---		&	$1.70 \times 10^3$  & $(1.15 \pm 0.06) \times 10^{-1}$ \\
-FT	&	TT-to-FT	&	$2.1 \times 10^{10}$	&	128$^3$				&	2775		&	$4.34 \times 10^4$	&	$7.83 \pm 0.01$	&	---		&	$1.65 \times 10^3$  & $(1.14 \pm 0.05) \times 10^{-1}$ \\
+FT	&	TT-to-FT	&	$2.1 \times 10^{10}$	&	128$^3$				&	2775		&	$1.28 \times 10^3$	&	$7.83 \pm 0.01$	&	---		&	$1.65 \times 10^3$  & $(1.14 \pm 0.05) \times 10^{-1}$ \\
 TT	&	Classic		&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\

### 2020-05-15 figures_and_data/rbc_restart_description.py

@@ -116,6 +116,8 @@ for k in fixed_trace.keys():
         restarted_trace[k] = np.concatenate((fixed/Nu_approx**(3./2), partial_restarted_trace[k][1:])) 
     elif 'T' in k:
         restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:]*Nu_approx)) 
+    elif 'sim_time' in k:
+        restarted_trace[k] = np.concatenate((fixed, fixed[-1] + (partial_restarted_trace[k][1:] - partial_restarted_trace[k][1])/np.sqrt(Nu_approx))) 
     else:
         restarted_trace[k] = np.concatenate((fixed, partial_restarted_trace[k][1:])) 
 
@@ -135,14 +137,14 @@ gs = gridspec.GridSpec(1000, 1000)
 subplots = [( (50 , 0  ),       300,    330),
             ( (350, 0  ),       300,    330),
             ( (650, 0  ),       300,    330),
-            ( (50 , 400),       450,    300),
-            ( (50 , 700),       450,    300),
-            ( (500 , 400),       450,    300),
-            ( (500 , 700),       450,    300),
+            ( (50 , 450),       450,    275),
+            ( (50 , 725),       450,    275),
+            ( (500, 450),       450,    275),
+            ( (500, 725),       450,    275),
             ]
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 for i in [0, 1, 2]:
-    axs[i].fill_between([restarted_trace['sim_time'][-1]-500, restarted_trace['sim_time'][-1]], 1e-2, 10, alpha=0.2, color='grey')
+#    axs[i].fill_between([restarted_trace['sim_time'][-1]-500, restarted_trace['sim_time'][-1]], 1e-2, 10, alpha=0.2, color='grey')
     axs[i].axvline(partial_restarted_trace['sim_time'][0], c='k', lw=0.5)
 
 
@@ -209,7 +211,7 @@ for i, field in enumerate(keys):
     factor = 1
     ax.fill_between(mx, 1e-16, factor*mp, color='olivedrab', alpha=0.5)
     ax.fill_between(rx, 1e-16, factor*rp, color='black', alpha=0.5)
-    ax.plot(mx, factor*mp, label='FT', color='olivedrab')
[…]

### 2020-05-19 referee_responses/submission1/referee_response.tex
adds in Lydia's edits

@@
 Section IV focuses on asymmetries in the flows introduced by the boundary conditions.
-\item We have computed a 3D, non rotating case.
+\item We have computed a 3D, non-rotating case.
 Its results are presented in section III.D, along with a new figure, Fig.~4.
 \end{enumerate}
-Aside from these major changes and reorganizations, we have cleaned up the text throughout the paper for clarity, including in the abstract.
+Aside from these major changes and reorganizations, we have cleaned up the text throughout the paper for clarity, including the abstract.
 We have included a ``redlined'' version of the manuscript in this resubmission which highlights the changes we have made to the text of the manuscript.
@@
 \item 
-We now conduct a series of test with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.B).
+We now conduct a series of tests with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.B).
 \vspace{0.5cm}
@@
 We've added a derivation of this timescale and a discussion of this subtlety to a new section II.D.
-In practice, we find that this definition of an equilibration time \emph{over}estimates the relaxational timescale.
-We find that the relaxational time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so at the end of section III.C.
+In practice, we find that this definition of an equilibration time \emph{over}estimates the thermal relaxation timescale.
+We find that the thermal relaxation time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so at the end of section III.C.
 
@@
 Agreed.
-The info in this subsection has been relocated to the section II.D.
-Section III has been split into a few sections (one each for the different IC choices, and one for 3D).
+The information in this subsection has been relocated to the section II.D.
+Section III has been split into a few sections: classic-ICs, ``fast'' ICs (Nu-based and TT-to-FT), discussion of 2D results, and a brief exploration of 3D non-rotating results.
 
@@
 We have now conducted a non-rotating 3D case with no-slip boundaries, analagous to our 2D setup.
-The results of this are presented in section III.D and confirm the prior 2D results.
+The results of this non-rotating 3D case are presented in section III.D and confirm the prior 2D results.
 In section V, for the rotating case, we provide more context to show that rotating RBC is a testbed for the TT-to-FT method.
@@
 Thank you.
-We find that the relaxational time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so in section II.D.
+We find that the thermal relaxation time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so in section II.D.
 Sections II.C and II.D now discusses how initial conditions affect thermal relaxation timescales.
@@
 Our narrow goal in including the rotating example is to show that timescale lessons in non-rotating convection apply to rotating convection.
-Therefore, our TT-to-FT initial conditions can save a great deal of time in the rotating case where Nu vs.~Ra powerlaws are less well agreed-upon by the community, and the evolved Delta T is truly unknown.
+Therefore, our TT-to-FT initial conditions can save a great deal of time in the rotating case where Nu vs.~Ra power laws are less well agreed-upon by the community, and the evolved Delta T is truly unknown.
 We have expanded our references to the rotating RBC literature.
@@
 Thank you.
-We have computed the convective onset, and the FT critical wavenumber at Ra$_{\partial_z T} = 1295.78$ is $k = 2.5519$, the TT critical wavenumber is Ra$_{\Delta T} = 1707.76$ at $k = 3.1163$, but the smallest $k$ that fits in our aspect ratio 2 domain is $k = \pi$.
-At $k = \pi$, the critical value is slightly higher, Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which is a small difference.
+We have computed the convective onset, and the FT critical wavenumber at Ra$_{\partial_z T} = 1295.78$ is $k = 2.5519$, while the TT critical wavenumber at Ra$_{\Delta T} = 1707.76$ is $k = 3.1163$.
+But the smallest $k$ that fits in our aspect ratio 2 domain is $k = \pi$.
+At $k = \pi$, the critical Rayleigh is slightly higher, Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which is a small difference.
 We have made this caveat in the text.
 It is true that in FF boundary conditions, there is a long and broad minimum extending to $k = 0$, and there is a band instability.
-But, for these FT and TT boundary conditions, the critical curve has a well-defined minimum, and wavelength associated with that minimum is close to the minimum wavelength obtainable in our finite aspect ratio boxes.
+But, for these FT and TT boundary conditions, the critical curve has a well-defined minimum, and the wavelength associated with that minimum is close to the minimum wavelength obtainable in our finite aspect ratio boxes.
 

### 2020-05-19 tex/mixedft_evolution_ms.tex
adds in Lydia's edits

@@
 In this work, we study \RB convection (RBC) \ea{under the Boussinesq approximation}.
-\ea{We examine simulations with mixed ``FT'' boundary conditions in which the flux is fixed at the bottom boundary and the temperature is fixed at the top.}
-We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of \ea{``TT'' boundaries, in which the temperature is fixed} at the top and bottom of the domain.
+\ea{We examine simulations with mixed temperature boundary conditions in which the flux is fixed at the bottom boundary and the temperature is fixed at the top (``FT'').}
+We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of \ea{thermal boundaries, in which the temperature is fixed} at the top and bottom of the domain (``TT'').
 \ea{We demonstrate that the timescale of thermal relaxation for FT simulations is dependent upon the initial conditions.
@@
 This long relaxation timescale can be skipped by either using a TT simulation's nonlinear state as initial conditions for an FT simulation, or by choosing initial conditions which more accurately guess the temperature difference between the top and bottom plates in the evolved state.}
-In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries\ea{, and time- and volume-averaged flow statistics like the Nusselt number and P\'{e}clet number are indistinguishable between FT and TT simulations}.
+In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries\ea{, and time- and volume-averaged flow statistics like the Nusselt number and the P\'{e}clet number are indistinguishable between FT and TT simulations}.
 \ea{FT boundaries are fundamentally asymmetric, and we examine the asymmetries that these boundaries produce in the flow.
@@
 In this work, we examine how the choice of using ``mixed'' \ea{thermodynamic boundary conditions} affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
-In RBC, temperature is the only thermodynamic quantity and throughout this work we will \ea{adopt the gnomenclature of past authors including ref.~\cite{ishiwatari&all1994} and} refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
+In RBC, temperature is the only thermodynamic quantity and throughout this work we will \ea{adopt the gnomenclature of past authors (see e.g., ref.~\cite{ishiwatari&all1994}) and} refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
 We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
@@
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
-First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve (``relax'') over time \cite{anders&all2018}.
+First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve (``thermally relax'') over time \cite{anders&all2018}.
 Second, FT boundary conditions are fundamentally asymmetric, and it is unclear if these asymmetries affect the evolved convective solution.
@@
 We find that this long thermal relaxation can be bypassed by \ea{constructing smarter initial conditions based on the expected evolved value of Nu, or by simply} using the results of TT simulations as initial conditions for FT simulations.
-Finally, FT boundaries create some asymmetries in the convective flows, \ea{particularly in the boundary layers,} but these asymmetries do not meaningfully change the \ea{bulk} convective state compared to TT simulations.
+Finally, FT boundaries create some asymmetries in the convective flows, \ea{particularly in the boundary layers,} but these asymmetries do not \ea{appreciably} change the \ea{bulk} convective state compared to TT simulations.
 
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In non rotating RBC (section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
+In non-rotating RBC (section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
 
@@
 \end{equation}
-We respectively impose FT and TT boundary conditions as
+We respectively impose TT and FT boundary conditions as
 \begin{equation}
-(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5},\qquad\qquad
-(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
+(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}},\qquad\qquad
+(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5}.
 \end{equation}
 
-In section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}, we study \ea{non rotating convection}.
+In section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}, we study \ea{non-rotating convection}.
 For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
-\ea{In an evolved, statistically stationary state \cite{calkins&all2015}, 
+\ea{In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
 \begin{equation}
@@
 and where $\beta$ is the temperature gradient achieved at the domain boundaries.
-Nu is therefore the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by both a Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
+Nu is therefore the conversion between a temperature and flux nondimensionalization such that the thermally relaxed state of any convective solution is characterized by both a Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
 \begin{equation}
@@
 \begin{equation}
-\text{Nu} = A \text{Ra}_{\Delta T}^{\alpha} \rightarrow \text{Nu} = (A \text{Ra}_{\partial_z T}^{\alpha})^{1/(1+\alpha)},
+\text{Nu} = A \text{Ra}_{\Delta T}^{\alpha} \,\,\Rightarrow\,\, \text{Nu} = (A \text{Ra}_{\partial_z T}^{\alpha})^{1/(1+\alpha)},
 \end{equation}
@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = \grad_{\text{interior}} + w(z)(-1 - \grad_{\text{interior}}).
+\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} + w(z)[-1 - (\grad T)_{\text{interior}}].
 \label{eqn:nu_based_gradT}
@@
 $$
-Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $\grad_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
 In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
@@
 \end{equation}
-where $F_{\text{cond,z}}$ is the z-component of the conductive flux, $F_{\text{cond}} = -\Peff^{-1}\grad T$, and where $\int T dz = \Delta T / 2$ in RBC.
+where $F_{\text{cond}} = -\Peff^{-1}\grad T$ is the conductive flux whose z-component is $F_{\text{cond,z}}$, and where $\int T dz = \Delta T / 2$ in RBC.
 The thermal relaxation time of an RBC experiment is therefore
@@
 \begin{equation}
-\tau_{\text{th, FT-classic}} = \Peff \frac{\text{Nu}^{-1} - 1}{\partial_z T(z=0.5) + 1} \sim \frac{\sqrt{\text{Ra Pr}}}{|\partial_z T(z = 0.5)| - 1}.
+\tau_{\text{th, FT-classic}} = \Peff \frac{\text{Nu}^{-1} - 1}{\partial_z T(z=0.5) + 1} \sim \frac{\sqrt{\text{Ra Pr}}}{|\partial_z T(z = 0.5)| - 1},
 \end{equation}
-Where the final expression is for the large Ra case where Nu$^{-1} \ll 1$.
+where the final expression is for the large Ra case where Nu$^{-1} \ll 1$.
 The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
 However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} \lesssim \tau_{\text{th, FT-classic}} \lesssim \sqrt{\text{Ra Pr}}$.
-In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units(see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
+In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units (see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
 
@@
 \ea{
-As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$ .
+As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$.
 This velocity field relaxation happens despite instant \emph{thermal} equilibration of the temperature field for these simulations.
@@
 	The top and bottom rows respectively show horizontal slices 1\% of the domain depth away from the top and bottom boundaries, while the middle row shows a vertical slice at $y = 0$.
+	The $y = 0$ vertical slice intersects the two horizontal slices at the location indicated by the dashed green line.
 	Visually, TT and FT dynamics are indistinguishable aside from the warm upflows near the bottom boundary.
@@
 When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
-These differences are interesting, \ea{can be seen visually in Fig.~\ref{fig:rbc_3D_panels},} and are explored further in \ea{the next section} (section \ref{sec:asymmetries}) and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do seem to affect the convective dynamics appreciably.
+\ea{These (rather interesting) differences are illustrated in Fig.~\ref{fig:rbc_3D_panels}, and are explored further in the next section (also see Fig.~\ref{fig:rbc_dynamics_asymmetries}).
+However, these differences do vanish in the interior and do not seem to affect the convective dynamics appreciably.
+}
 
-\subsection{Asymmetries induced by mixed boundaries}
+\subsection{Asymmetries induced by mixed boundary conditions}
 \label{sec:asymmetries}
@@
 	Circular and diamond data points are respectively simulations and experimental data points from ref.~\cite{cheng&all2015}.
-	The color of the data points signifies the Ekman number of the points, and black points are non rotating.
+	The color of the data points signifies the Ekman number of the points, and black points are non-rotating.
 	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
@@
 We find that the long relaxation of \ea{classic-IC} FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations \ea{and FT simulations with Nu-based or TT-to-FT ICs} due to the lack of evolution of the \ea{temperature difference between the boundaries}.
-The rapid evolution of \ea{all of our simulations other than the classic-IC FC} simulations suggests that RBC \ea{thermally} restratifies itself instantaneously.
+The rapid evolution of \ea{all of our simulations other than the classic-IC FT} simulations suggests that RBC \ea{thermally} restratifies itself instantaneously.
 \item Dynamical measurements taken during thermal relaxation may be misleading.
 Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
-\ea{This is principly a concern in systems like classic-IC FT simulations which can have very long relaxational times compared to dynamical times.}
+\ea{This is principly a concern in systems like classic-IC FT simulations which can have very long thermal relaxation timescales compared to dynamical times.}
 \item The thermal relaxation process of a \ea{classic-IC} FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
@@
 	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
-	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units \ea{for all rotating cases and all 2D cases except the Ra$_{\partial_z T} = 9.51\times10^{11}$ TT-to-FT case, where samples were taken over 200 evolved freefall time units; samples were taken over 350 freefall time units for 3D nonrotating cases}.
+	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units \ea{for all rotating cases and all 2D cases except the Ra$_{\partial_z T} = 9.51\times10^{11}$ TT-to-FT case, where samples were taken over 200 evolved freefall time units; samples were taken over 350 freefall time units for 3D non-rotating cases}.
 	Reported uncertainties are the standard deviation of the sample mean; when the uncertainty is not reported, it is smaller than the number of reported digits.

### 2020-05-20 figures_and_data/rbc_3D_panels.py
switches PDF order on 3D fig

@@ -178,17 +178,17 @@ for i, c in zip((0, 3, 7, 1, 4, 8, 2, 5, 9), (*[top_border_color]*3, *[middle_bo
 
 #PDF plots
 for i, bc in enumerate(data.keys()):
-    axs[6].plot(        data[bc]['pdf_T_xs'] /data[bc]['delta_T_mean'],               data[bc]['pdf_T_pdf']*data[bc]['delta_T_mean'],         c=colors[i], label=bc)
-    axs[6].fill_between(data[bc]['pdf_T_xs'] /data[bc]['delta_T_mean'],        1e-16, data[bc]['pdf_T_pdf']*data[bc]['delta_T_mean'],         color=colors[i], alpha=0.5, rasterized=True)
+    axs[6].plot(        data[bc]['pdf_T_xs'] /data[bc]['delta_T_mean'],               data[bc]['pdf_T_pdf']*data[bc]['delta_T_mean'],         c=colors[i], label=bc, zorder=1-i)
+    axs[6].fill_between(data[bc]['pdf_T_xs'] /data[bc]['delta_T_mean'],        1e-16, data[bc]['pdf_T_pdf']*data[bc]['delta_T_mean'],         color=colors[i], alpha=0.5, rasterized=True, zorder=1-i)
 
-    axs[7].plot(        data[bc]['pdf_xy_T near top_xs'] /data[bc]['delta_T_mean'],               data[bc]['pdf_xy_T near top_pdf']*data[bc]['delta_T_mean'],         c=colors[i])
-    axs[7].fill_between(data[bc]['pdf_xy_T near top_xs'] /data[bc]['delta_T_mean'],        1e-16, data[bc]['pdf_xy_T near top_pdf']*data[bc]['delta_T_mean'],         color=colors[i], alpha=0.5, rasterized=True)
+    axs[7].plot(        data[bc]['pdf_xy_T near top_xs'] /data[bc]['delta_T_mean'],               data[bc]['pdf_xy_T near top_pdf']*data[bc]['delta_T_mean'],         c=colors[i], zorder=1-i)
+    axs[7].fill_between(data[bc]['pdf_xy_T near top_xs'] /data[bc]['delta_T_mean'],        1e-16, data[bc]['pdf_xy_T near top_pdf']*data[bc]['delta_T_mean'],         color=colors[i], alpha=0.5, rasterized=True, zorder=1-i)
 
[…]

### 2020-05-20 tex/mixedft_evolution_ms.tex
lots of small tweaks to the text

@@
 \begin{abstract}
-Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
+Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately model natural systems.
 In this work, we study \RB convection (RBC) \ea{under the Boussinesq approximation}.
@@
 ``Classic'' initial conditions which employ a hydrostatically- and thermally- balanced linear temperature profile exhibit a long thermal relaxation.
-This long relaxation timescale can be skipped by either using a TT simulation's nonlinear state as initial conditions for an FT simulation, or by choosing initial conditions which more accurately guess the temperature difference between the top and bottom plates in the evolved state.}
+This long relaxation is not seen in FT simulations which use a TT simulation's nonlinear state as initial conditions (``TT-to-FT'').}
 In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries\ea{, and time- and volume-averaged flow statistics like the Nusselt number and the P\'{e}clet number are indistinguishable between FT and TT simulations}.
@@
 However, these near-boundary asymmetries do not measurably break the symmetry in the convective interior.
-We briefly explore rotating RBC to demonstrate that our findings with respect to thermal relaxation carry over to this more complex case.}
+We briefly explore rotating RBC to demonstrate that our findings with respect to thermal relaxation carry over to this more complex case, and to show the power of TT-to-FT initial conditions.}
 \end{abstract}
@@
 }
-\subsubsection{Dynamical Timescales}
 One \ea{result of the mapping in Eqn.~\ref{eqn:ra_relation}} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
@@
 \ea{
-\subsubsection{Evolutionary Timescales}
 The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
@@
 \qquad
-\frac{dE}{dt} = -\iiint \grad\cdot F_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\iiint \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
-where $F_{\text{cond}} = -\Peff^{-1}\grad T$ is the conductive flux whose z-component is $F_{\text{cond,z}}$, and where $\int T dz = \Delta T / 2$ in RBC.
+where $\bm{F}_{\text{cond}} = -\Peff^{-1}\grad T$ is the conductive flux whose z-component is $F_{\text{cond,z}}$, and where $\int T dz = \Delta T / 2$ in RBC.
 The thermal relaxation time of an RBC experiment is therefore
@@
 where the final expression is for the large Ra case where Nu$^{-1} \ll 1$.
-The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in \cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
+The magnitude of the temperature derivative achieved at the top boundary is initially very large ($|\partial_z T(z=0.5)|_{\text{early}} > \text{Nu}(t=\infty)$; see e.g., Fig.~1b in ref.~\cite{anders&all2018}), but decreases in magnitude throughout the evolution of a simulation, making it difficult to estimate the true thermal relaxation time.
 However, it is reasonable to assume that the evolutionary timescale lies within the window $\sqrt{\text{Ra Pr}} \,\text{Nu}^{-1} \lesssim \tau_{\text{th, FT-classic}} \lesssim \sqrt{\text{Ra Pr}}$.
-In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units (see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ (see section \ref{sec:results_rotating}).
+In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units (see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ time units (see section \ref{sec:results_rotating}).
 
@@
 
+\newpage
 \subsection{TT-to-FT \& Nu-based ICs: rapidly equilibrated FT simulations}
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities, which have been averaged over a rolling time window of 25 simulation time units, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$}.
+	(Left three panels) Time traces \ea{(in units of $\tau_{\text{ff, ev}}$)} of scalar quantities, which have been averaged over a rolling time window of 25\ea{$\tau_{\text{ff, ev}}$}, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$}.
 	The time of the change of boundary conditions is denoted by the vertical black line.
@@
 During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classic roll solution is achieved.
-This behavior is quite different from classic ICs in TT simulations, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
+This behavior is quite different from classic ICs, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
 Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classic ICs.
@@
 The rapid relaxation of TT simulations\ea{, as well as FT simulations with Nu-based and TT-to-FT ICs}, therefore suggests that experimental restratification occurs rapidly in RBC. 
-The long rundown of \ea{classic} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
+The long rundown of \ea{classic-IC} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
 
@@
 As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$.
-This velocity field relaxation happens despite instant \emph{thermal} equilibration of the temperature field for these simulations.
-We find that the kinetic energy increases by less than a factor of two from its initial post-transient value to its final value in the equilibrated state.
+This velocity field relaxation happens despite instant \emph{thermal} relaxation of the temperature field for these simulations.
+We find that the kinetic energy increases by less than a factor of two from its initial post-transient value to its final value in the statistically-stationary state.
 }
@@
 \subsection{3D verification of 2D results}
-Timestepping through the thermal relaxation of a classic FT simulation is prohibatively expensive in 3D, even for our least turbulent case with an evolved Ra$_{\Delta T} \approx 10^8$.
-In order to timestep through the intense, early convective transient, we anticipate that such a simulation would require a coefficient resolution of $\gtrsim 512^3$, a factor of 64 times more coefficients than our comparable 2D case at 2048x1024.
-This 2D, classic-IC, FT case took $1.21 \times 10^5$ cpu-hours, so we estimate that a classic FT case in 3D at this value of Ra$_{\partial_z T}$ would take O(10 million) cpu-hours.
-We found in previous work \cite{anders&all2018} at lower Ra$_{\partial_z T}$ that 3D classic FT cases exhibited the same thermal rundown as 2D cases.
-As a result, we will focus here on 3D comparisons of FT and TT simulations in the statistically-stationary state through the use of TT-to-FT initial conditions.
+It would be prohibatively expensive to timestep through the thermal relaxation of a 3D classic-IC FT simulation, even for our least turbulent Ra$_{\Delta T} \approx 10^8$ case.
+We anticipate that the transient state would require a spectral coefficient resolution of $\gtrsim 512^3$ for adequate resolution, a factor of 64 times more coefficients than our comparable 2D case at 2048x1024.
+This 2D case cost $1.21 \times 10^5$ cpu-hours, so we estimate that comparable 3D case would cost O(10 million) cpu-hours.
+We found in previous work \cite{anders&all2018} at lower Ra$_{\partial_z T}$ that 3D classic-IC FT cases exhibited the same thermal rundown as 2D cases.
+Here, we will focus on 3D comparisons of FT and TT simulations in the statistically-stationary state through the use of TT-to-FT initial conditions.
 
-We find that equilibrated FT and TT simulations are analogous in a volume-averaged sense: measurements of Nu (31.4 for TT, 31.9 for FT) and Pe ($1.78 \times 10^3$ for both) are nearly indistinguishable.
-In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices from 3D TT and TT-to-FT simulations.
-As in 2D, we find no difference between the PDFs of evolved quantities like the nonlinear transport ($wT$) between TT and FT simulations.
-Therefore, we have focused on the temperature fields in this figure, which does display differences between the two sets of boundary conditions.
+We find that equilibrated FT and TT simulations are analogous in a volume-averaged sense: measurements of Nu (31.4 for TT, 31.9 for FT) and Pe ($1.78 \times 10^3$ for both) are nearly indistinguishable between the two cases.
+As in 2D, we find no difference between the PDFs of evolved quantities like the nonlinear transport ($wT$) between TT and FT simulations, but we do find differences between the evolved temperature fields ($T$).
+In Fig.~\ref{fig:rbc_3D_panels}, we show dynamical slices of $T$ from 3D TT and FT simulations.
 Near the top boundary and in the interior, the TT and FT dynamics are quite similar.
@@
 
-We now extend our study to a more complicated experiment: 3D rotating RBC with an Ekman number of $10^{-6}$.
-We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
 \ea{
 Rotating convection is an excellent testbed for our TT-to-FT method.
-In rotating convection, at a fixed value of Ek, as Ra increases, flows transition from the rotationally constrained to the rotationally unconstrained regime.
+In rotating convection, as Ra increases at a fixed value of the Ekman number (Ek), flows transition from the rotationally constrained to the rotationally unconstrained regime.
 The scaling of Nu~vs.~Ra changes drastically between these two regimes, and is some blend of the two in the intermediary, marginally constrained regime.
@@
 However, TT-to-FT should work generally for all parameters, so long as a TT simulation can be performed.
+Here we explore the parameter space that the classic-IC FT simulation explores as it thermally relaxes and demonstrate that the TT-to-FT approach leads to rapid convergence for a rotating simulation.
 }
+
+We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
+We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
+\ea{We then take the TT case, do a TT-to-FT simulation, and compare the results of the TT-to-FT simulation to the classic-IC FT case.}
 
@@
 After achieving this peak value, Pe monotonically decreases toward its relaxed state.
-\ea{We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}}/\text{Nu}$ nondimensional freefall time units.}
+\ea{We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}\text{ Pr}}/\text{Nu}$ nondimensional freefall time units.}
 
@@
 	Circular and diamond data points are respectively simulations and experimental data points from ref.~\cite{cheng&all2015}.
-	The color of the data points signifies the Ekman number of the points, and black points are non-rotating.
+	The color of the data points signifies the Ekman number of the points, and grey diamonds are non-rotating.
 	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
@@
 These Ro measurements are indistinguishable, Nu measurements are within 1\% of each other, and Pe measurements are within 3\% of each other, representing excellent agreement.
+
+The difference in computational cost between classic-IC FT simulations and the TT/TT-to-FT simulations are even more striking here than in our previous examples.
 }
-
-We once again find it important to briefly note the difference in computational cost between the \ea{classic-IC} FT, \ea{TT-to-FT,} and TT simulations conducted here.
 The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.2 \times 10^3$ cpu-hours to run 5000 freefall times.
@@
 \ea{In the case of FT boundaries, we studied three different sets of initial conditions and examined both the nature of thermal relaxation and the equilibrated, statistically stationary state.}
-Through studying this relaxation and the relaxed states simulations, we come to the following conclusions:
+Through studying this relaxation and the relaxed states, we come to the following conclusions:
 \begin{enumerate}
@@
 For example, in the late stages of the lifetimes of stars, some core burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
-The use of FT boundaries or initial conditions that we have here considered to be ``bad'' choices may help in understanding these transient lifetime stages.
+The use of \ea{classic-ICs with} FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
 However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
@@
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
-We found in our FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+We found in our \ea{classic-IC} FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
 If we had terminated our FT rotating simulation too early, we would not have seen the eventual destruction of this LSV or the later oscillatory behavior between jets and vortex pairs.
@@
 It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
-Some authors who study astrophysical convection \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018} employ FF boundary conditions, and our results here suggest that such a choice may be ideal in those complex simulations.
-\ea{Indeed, convection in 3D spherical shells does seem to thermally converge faster with FF boundaries than FT boundaries (Matilsky 2020, private communication).
-However, FF boundaries have also been shown to drive different flow morphologies than FT or TT boundaries in rotating convection in spherical geometries \cite{matilsky&all2020, calkins&all2015}, so perhaps numericists should lean on the development of ``smarter'' initial conditions rather than changes to the boundary conditions to achieve faster relaxation for some cases.
-}
 
 In conclusion, we note that our results here should provide astrophysical convection simulations with reason for optimism.
-Some problems that we encounter (e.g., long thermal rundown in FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.
+Some problems that we encounter (e.g., long thermal rundown in \ea{classic-IC} FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.
 
 \begin{acknowledgments}
-\ea{We'd like to thank the anonymous referee who suggested the idea of Nu-based ICs, and whose careful and thoughtful comments greatly improved both the quality and clarity of this manuscript.}
-We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
-We'd also like to thank Jeff Oishi, who encouraged us to pursue the differences between early and late FT dynamics and who graciously saved the reader from reading ``mixedFT'' (instead of FT) and ``fixedT'' (instead of TT).
+\ea{We thank the anonymous referee who suggested the idea of Nu-based ICs, and whose careful and thoughtful comments greatly improved both the quality and clarity of this manuscript.}
+We thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
+We'd especially like to thank Jeff Oishi, who encouraged us to pursue the differences between early and late FT dynamics and who graciously saved the reader from reading ``mixedFT'' (instead of FT) and ``fixedT'' (instead of TT).
 EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
 LK acknowledges support from the George Ellery Hale Post-Doctoral Fellowship and from NASA grant 80NSSC17K0008.
-This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 
+This work was additionally supported by NASA LWS grant NNX16AC92G and NASA SSW grant 80NSSC19K0026. 
 Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
@@
 	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
-	Input quantities are the boundary conditions (BCs), Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
+	Input quantities are the boundary conditions (BCs), \ea{initial conditions (ICs),} Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
 	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.

### 2020-05-20 tex/mixedft_evolution_ms.tex
minor fig caption updates

@@
 	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
-	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
+	The yellow trace shows the evolution of an FT case with Ra$_{\partial_z T} = 2.61 \times 10^9$.
 	Purple circles are the measured values of Nu and Pe in our TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
@@
 \caption{ 
-	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
+	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange, Ra$_{\partial_z T} = 9.51 \times 10^{11}$) and TT (purple, Ra$_{\Delta T} = 10^{10}$) simulation are displayed.
 	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange) and TT (purple) simulation are shown.
+	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange, $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 2.75\times 10^9$) simulation are shown.
 	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
-	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
+	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ of the TT simulation.
 	(Middle panel) Ro evolution of both simulations; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.

### 2020-05-20 referee_responses/submission1/referee_response.tex
nearly ready for resubmission

@@
 We thank the referees for their time and effort in reviewing our work; we would like to particularly thank referee 1 for their careful and thoughtful comments.
-We have addressed the questions and concerns of the referees, and we rebut the claim of referee 2 that our results are not novel.
+We have addressed the questions and concerns of the reports, and we rebut the claim of report 2 that our results are not novel.
 
-This version of the manuscript has been substantially edited and logically reorganized compared to the previous version.
-However, the main results, conclusions, and figures are largely the same.
+In addressing the questions within the reports, we have edited, expanded, and reorganized portions of the manuscript.
+The main results and conclusions are the same.
 We would like to point out a few major changes in this version of the manuscript:
 \begin{enumerate}
-\item The abstract has been largely rewritten for clarity.
 \item The ``Simulation Details'' section has been broken up into subsections, and two new subsections have been added. These discuss:
@@
 The description of our TT-to-FT procedure has been moved here and expanded.
-Per the advice of referee 1, we have also added and studied new ``Nu-based'' boundary conditions.
+Per the advice of report 1, we have also added and studied ``Nu-based'' initial conditions.
 \item Evolutionary and dynamical timescales.
@@
 Section IV focuses on asymmetries in the flows introduced by the boundary conditions.
-\item We have computed a 3D, non-rotating case.
+\item While reading the reports, we realized it was confusing to have a 3D case in which many things (rotation, boundary conditions) were different from the 2D non-rotating simulations.
+We have computed a 3D, non-rotating case which has the same boundary conditions as the 2D work, making this a direct comparison to the main body of the work.
 Its results are presented in section III.D, along with a new figure, Fig.~4.
+We continue to include the rotating case in section V, as the rotating system is an interesting use case for the TT-to-FT technique.
 \end{enumerate}
@@
 \end{myquotation}
-This has now been clarified in section II.D see the ``Additional ICs'' paragraph).
-The linear temperature profile is now also referred to as ``Classical ICs''.
+This has now been clarified in section II.D; temperature initial conditions are in II.D.1, and the additional initial conditions are in II.D.2.
+The linear temperature profile is now also referred to as ``Classic ICs''.
 
@@
 \item 
-We now conduct a series of tests with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.B).
+We now conduct select simulations with what we call ``Nu-based'' initial conditions, using our $\alpha = 0.285$ (see sections II.C and III.B).
 \vspace{0.5cm}
@@
 In practice, we find that this definition of an equilibration time \emph{over}estimates the thermal relaxation timescale.
-We find that the thermal relaxation time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so at the end of section III.C.
+We find that the thermal relaxation time is $C (\sqrt{\text{Ra Pr}}/\text{Nu})$, where $C$ is a constant of order 1, and have said so at the end of section II.D.
 
@@
 Agreed.
-The information in this subsection has been relocated to the section II.D.
+The information in this subsection has been relocated to section II.D.
 Section III has been split into a few sections: classic-ICs, ``fast'' ICs (Nu-based and TT-to-FT), discussion of 2D results, and a brief exploration of 3D non-rotating results.

### 2020-05-20 code/logic/output.py
updates paper repo code

@@ -64,13 +64,18 @@ def initialize_output(solver, data_dir, aspect, threeD=False, volumes=False,
         #Analysis
         slices = solver.evaluator.add_file_handler(data_dir+'slices', sim_dt=slice_output_dt, max_writes=max_writes, mode=mode)
         slices.add_task("interp(T1 + T0,         y={})".format(0), name='T')
-        slices.add_task("interp(T1 + T0,         z={})".format(0.45), name='T near top')
+        slices.add_task("interp(T1 + T0,         z={})".format(0.49), name='T near top')
+        slices.add_task("interp(T1 + T0,         z={})".format(-0.49), name='T near bot 1')
+        slices.add_task("interp(T1 + T0,         z={})".format(-0.48), name='T near bot 2')
+        slices.add_task("interp(T1 + T0,         z={})".format(-0.47), name='T near bot 3')
         slices.add_task("interp(T1 + T0,         z={})".format(0), name='T midplane')
         slices.add_task("interp(w,         y={})".format(0), name='w')
-        slices.add_task("interp(w,         z={})".format(0.45), name='w near top')
+        slices.add_task("interp(w,         z={})".format(0.49), name='w near top')
+        slices.add_task("interp(w,         z={})".format(-0.49), name='w near bot')
         slices.add_task("interp(w,         z={})".format(0), name='w midplane')
         slices.add_task("interp(enstrophy,         y={})".format(0),    name='enstrophy')
-        slices.add_task("interp(enstrophy,         z={})".format(0.45), name='enstrophy near top')
+        slices.add_task("interp(enstrophy,         z={})".format(0.49), name='enstrophy near top')
+        slices.add_task("interp(enstrophy,         z={})".format(-0.49), name='enstrophy near bot')
         slices.add_task("interp(enstrophy,         z={})".format(0),    name='enstrophy midplane')
         analysis_tasks['slices'] = slices
 
@@ -82,8 +87,9 @@ def initialize_output(solver, data_dir, aspect, threeD=False, volumes=False,
         analysis_tasks['scalar'].add_task("vol_avg(v)",  name="v")
 
         if volumes:
-            analysis_volume = solver.evaluator.add_file_handler(data_dir+'volumes', sim_dt=vol_output_dt, max_writes=max_writes, mode=mode)
+            analysis_volume = solver.evaluator.add_file_handler(data_dir+'volumes', sim_dt=vol_output_dt, max_writes=5, mode=mode)
[…]

### 2020-05-20 code/plotting/plot_3d_slices.py

@@ -17,7 +17,8 @@ Options:
     --row_inch=<in>                     Number of inches / row [default: 3]
 
     --fig_type=<fig_type>               Type of figure to plot
-                                            1 - T (y = 0, near top, midplane)
+                                            1 - T & vort (y = 0, near top, midplane)
+                                            2 - T (y = 0, near top, midplane)
                                         [default: 1]
 """
 from docopt import docopt
@@ -46,7 +47,18 @@ plotter_kwargs = { 'col_in' : int(args['--col_inch']), 'row_in' : int(args['--ro
 if int(args['--fig_type']) == 1:
     plotter.setup_grid(2, 3, **plotter_kwargs)
     plotter.grid.full_row_ax(0)
-    fnames = [(('T',), {'remove_x_mean' : True}), (('T near top',), {'remove_mean':True, 'y_basis':'y'}), (('T midplane',), {'remove_mean':True, 'y_basis':'y'}), (('vort_z integ',), {'y_basis':'y'})]
+    fnames = [(('T',), {'remove_x_mean' : True}), 
+              (('T near top',), {'remove_mean':True, 'y_basis':'y'}), 
+              (('T midplane',), {'remove_mean':True, 'y_basis':'y'}), 
+              (('vort_z integ',), {'y_basis':'y'})]
+elif int(args['--fig_type']) == 2:
+    plotter.setup_grid(2, 3, **plotter_kwargs)
+    plotter.grid.full_row_ax(0)
+    fnames = [(('T',), {'remove_x_mean' : True}), 
+              (('T near top',), {'remove_mean':True, 'y_basis':'y'}), 
+              (('T near bot 1',), {'remove_mean':True, 'y_basis':'y'}), 
+              (('T midplane',), {'remove_mean':True, 'y_basis':'y'})]
+
 
 
 

### 2020-05-20 code/plotting/plot_logic/pdfs.py

@@ -25,7 +25,7 @@ logger = logging.getLogger(__name__.split('.')[-1])
 class PdfPlotter(SingleFiletypePlotter):
     """
     A class for plotting probability distributions of a dedalus output.
-    PDF plots are currently only implemented for 2D slices. When one axis is
+    PDF plots are currently implemented for 2D slices and 3D volumes. When one axis is
     represented by polynomials that exist on an uneven basis (e.g., Chebyshev),
     that basis is evenly interpolated to avoid skewing of the distribution by
     uneven grid sampling.
@@ -65,7 +65,7 @@ class PdfPlotter(SingleFiletypePlotter):
     
     def _get_interpolated_slices(self, file_name, pdf_list, bases=['x', 'z'], uneven_basis=None):
         """
-        For data on an uneven grid, interpolates that data on to an evenly spaced grid.
+        For 2D data on an uneven grid, interpolates that data on to an evenly spaced grid.
 
         Attributes:
         ----------
@@ -93,16 +93,87 @@ class PdfPlotter(SingleFiletypePlotter):
 
         file_data = OrderedDict()
         for k in pdf_list: 
+            shape = tsk[k].squeeze().shape
+            if len(shape) == 2:
+                file_data[k] = np.zeros((1, *tsk[k].squeeze().shape))
+            else:
+                file_data[k] = np.zeros(tsk[k].squeeze().shape)
+            for i in range(file_data[k].shape[0]):
+                if self.reader.comm.rank == 0:
+                    print('interpolating {} ({}/{})...'.format(k, i+1, file_data[k].shape[0]))
+                    stdout.flush()
+                interp = RegularGridInterpolator((x.flatten(), y.flatten()), tsk[k][i,:].squeeze(), method='linear')
+                file_data[k][i,:] = interp((exx, eyy))
+
+        return file_data
+
+    def _get_interpolated_volumes(self, file_name, pdf_list, bases=['x', 'y', 'z'], uneven_basis=None):
+        """
+        For 3D data on an uneven grid, interpolates that data on to an evenly spaced grid.
+
+        Attributes:
+        ----------
+        pdf_list : list
+            list of strings of the Dedalus tasks to make PDFs of.
+        bases : list, optional
+            The names of the Dedalus bases on which the data exists
+        uneven_basis : string, optional
+            The basis on which the grid has uneven spacing.
+        """
+        #Read data
[…]

### 2020-05-20 code/plotting/plot_pdfs.py

@@ -7,9 +7,9 @@ Usage:
 Options:
     --fig_name=<fig_name>               Output directory for figures [default: pdfs]
     --start_file=<start_file>           Dedalus output file to start at [default: 1]
-    --n_files=<num_files>               Number of files to plot [default: 100000]
+    --n_files=<num_files>               Number of files to plot [default: 25]
     --dpi=<dpi>                         Image pixel density [default: 150]
-    --bins=<bins>                       Number of bins per pdf [default: 100]
+    --bins=<bins>                       Number of bins per pdf [default: 200]
 """
 import logging
 logger = logging.getLogger(__name__)
@@ -23,10 +23,38 @@ start_file = int(args['--start_file'])
 n_files     = args['--n_files']
 if n_files is not None: n_files = int(n_files)
 
-pdfs_to_plot = ['T', 'enstrophy', 'enth_flux', 'w']
 
 
 # Load in figures and make plots
-plotter = PdfPlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
-plotter.calculate_pdfs(pdfs_to_plot, bins=int(args['--bins']), uneven_basis='z')
+if '3D' in root_dir:
+    threeD = True
+    bases  = ['x', 'y', 'z']
+    pdfs_to_plot = ['T', 'wT']
+    plotter = PdfPlotter(root_dir, file_dir='volumes', fig_name=fig_name, start_file=start_file, n_files=n_files)
+
+
+    bases_2  = ['x', 'y']
+    pdfs_to_plot2 = ['T near top', 'T near bot 1']
+    plotter2 = PdfPlotter(root_dir, file_dir='slices', fig_name=fig_name+'_xy', start_file=start_file, n_files=n_files)
+
+
+    bases_3  = ['x', 'z']
+    pdfs_to_plot3 = ['T']
+    plotter3 = PdfPlotter(root_dir, file_dir='slices', fig_name=fig_name+'_xz', start_file=start_file, n_files=n_files)
+else:
+    threeD = False
+    bases  = ['x', 'z']
+    pdfs_to_plot = ['T', 'enstrophy', 'enth_flux', 'w']
+    plotter = PdfPlotter(root_dir, file_dir='slices', fig_name=fig_name, start_file=start_file, n_files=n_files)
+
+
[…]

### 2020-05-20 code/rayleigh_benard.py

@@ -20,9 +20,10 @@ Options:
     --ny=<nx>                  Horizontal resolution [default: 64]
     --aspect=<aspect>          Aspect ratio of problem [default: 2]
 
-    --fixed_f                  Fixed flux boundary conditions top/bottom (FF)
-    --fixed_t                  Fixed temperature boundary conditions top/bottom (TT)
-    --stress_free              Stress free boundary conditions top/bottom 
+    --FF                       Fixed flux boundary conditions top/bottom (default FT)
+    --TT                       Fixed temperature boundary conditions top/bottom (default FT)
+    --FS                       Free-slip/stress free boundary conditions (default No-slip, NS)
+    --smart_ICs                Use smarter static initial conditions for flux boundaries
 
     --3D                       Run in 3D
     --mesh=<mesh>              Processor mesh if distributing 3D run in 2D 
@@ -32,8 +33,9 @@ Options:
     --run_time_therm=<time_>   Run time, in thermal times [default: 1]
 
     --restart=<file>           Restart from checkpoint file
-    --restart_T2m=<file>       Restart from checkpoint file, going from TT to FT BCs 
-    --restart_T2m_Nu=<Nu>      Nusselt number of fixed-T run being restarted from [default: 1]
+    --restart_Nu=<Nu>          Nusselt number of run that is being restarted, for adjusting t_ff [default: 1]
+    --TT_to_FT=<file>          Restart from checkpoint file, going from TT to FT BCs 
+    --TT_to_FT_Nu=<Nu>         Nusselt number of fixed-T run being restarted from [default: 1]
     --overwrite                If flagged, force file mode to overwrite
     --seed=<seed>              RNG seed for initial conditoins [default: 42]
 
@@ -43,6 +45,7 @@ Options:
     --root_dir=<dir>           Root directory for output [default: ./]
     --safety=<s>               CFL safety factor [default: 0.5]
     --RK443                    Use RK443 instead of RK222
+
 
     --stat_wait_time=<t>       Time to wait before taking rolling averages of quantities like Nu [default: 20]
[…]

### 2020-05-20 code/rotating_rayleigh_benard.py

@@ -21,9 +21,10 @@ Options:
     --ny=<nx>                  Horizontal resolution [default: 64]
     --aspect=<aspect>          Aspect ratio of problem [default: 2]
 
-    --fixed_f                  Fixed flux boundary conditions top/bottom (FF)
-    --fixed_t                  Fixed temperature boundary conditions top/bottom (TT)
-    --no_slip                  Stress free boundary conditions top/bottom
+    --FF                       Fixed flux boundary conditions top/bottom (default FT)
+    --TT                       Fixed temperature boundary conditions top/bottom (default FT)
+    --NS                       Free-slip/stress free boundary conditions (default Free-slip, FS)
+    --smart_ICs                Use smarter static initial conditions for flux boundaries
 
     --mesh=<mesh>              Processor mesh if distributing 3D run in 2D 
     
@@ -32,6 +33,9 @@ Options:
     --run_time_therm=<time_>   Run time, in thermal times [default: 1]
 
     --restart=<file>           Restart from checkpoint file
+    --restart_Nu=<Nu>          Nusselt number of run that is being restarted, for adjusting t_ff [default: 1]
+    --TT_to_FT=<file>          Restart from checkpoint file, going from TT to FT BCs 
+    --TT_to_FT_Nu=<Nu>         Nusselt number of fixed-T run being restarted from [default: 1]
     --overwrite                If flagged, force file mode to overwrite
     --seed=<seed>              RNG seed for initial conditoins [default: 42]
 
@@ -40,6 +44,8 @@ Options:
     --no_join                  If flagged, don't join files at end of run
     --root_dir=<dir>           Root directory for output [default: ./]
     --safety=<s>               CFL safety factor [default: 0.5]
+    --RK443                    Use RK443 instead of RK222
+
 
     --stat_wait_time=<t>       Time to wait before taking rolling averages of quantities like Nu [default: 20]
     --stat_window=<t_w>        Max time to take rolling averages over [default: 100]
@@ -70,32 +76,41 @@ logger = logging.getLogger(__name__)
[…]

### 2020-05-20 submission1_tex/mixedft_evolution_ms.tex
tracks uploaded files for submission 1

\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography, superscriptaddress]{revtex4-1}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{D_{\text{KS}}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{D_\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\Reff}{\ensuremath{\text{Re}_{\text{ff}}}}
\newcommand{\Peff}{\ensuremath{\text{Pe}_{\text{ff}}}}

\newcommand\mnras{{MNRAS}}%
\newcommand\apjl{{The Astrophysical Journal Letters}}%

\begin{document}
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Geoffrey M. Vasil}
\affiliation{University of Sydney School of Mathematics and Statistics, Sydney, NSW 2006, Australia}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Lydia Korre}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}

\title{Convective dynamics with mixed temperature boundary conditions: \\
why thermal relaxation matters and how to accelerate it}

\begin{abstract}
Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
In this work, we study \RB convection (RBC) with mixed (``FT'') temperature boundary conditions.
We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of fixing the temperature at the top and bottom of the domain (``TT'').
We find that simulations with FT boundaries experience a long thermal rundown while simulations with TT boundaries do not.
In the relaxed state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries.
The fast evolution of TT simulations can therefore be taken advantage of to rapidly relax FT simulations.
We show that these findings carry over to more complicated problems through a brief examination of rotating convection.
We furthermore find that FT boundaries introduce minor asymmetries into the flow fields, with the fixed flux boundary producing more extreme events than the fixed temperature boundary, but that these asymmetries do not appreciably affect the bulk flows.
We conclude that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
\end{abstract}
\maketitle

%%%%%%%%%%%%
%%%%%%%%%%%
% INTRO
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
Numerical simulations are a commonly-used tool in studies of geophysical or astrophysical convection.
These studies range from examinations of convection in the simplified Boussinesq approximation \cite{spiegel&veronis1960, ahlers&all2009, plumley&julien2019} to highly complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
Regardless of complexity, numerically simulated convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2016}.
In studies of Boussinesq convection, the standard choice is to hold constant the temperature difference across the domain by fixing the temperature at the upper and lower boundaries.
However, a common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux entering the domain through the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.

In this work, we examine how the choice of using ``mixed'' boundaries affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2016}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
FF and TT boundaries exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
It is natural to assume that FT simulations should follow the same Nu vs.~Ra scaling laws as FF and TT boundary conditions.
However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve (``relax'') over time \cite{anders&all2018}.
Second, FT boundary conditions are fundamentally asymmetric, and it is unclear if these asymmetries affect the evolved convective solution.

In this paper, we investigate the thermal relaxation of and the asymmetries in RBC with FT boundary conditions.
We also compare relaxed FT solutions to TT solutions.
Our results suggest that the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
We find that this long thermal relaxation can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
Finally, FT boundaries create some asymmetries in the convective flows, but these asymmetries do not meaningfully change the mean convective state compared to TT simulations.

We present these findings as follows.
In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.

%%%%%%%%%%%%
%%%%%%%%%%%
% EXPERIMENT
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Simulation Details}
\label{sec:simulations}
We study incompressible RBC under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
In section \ref{sec:rotating_results}, we study convection in the presence of vertical global rotation \cite{julien&all1996}, and include the Coriolis term in the momentum equation for generality.
The Boussinesq equations of motion are
\begin{align}
\DivU &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh (Ra), Prandtl (Pr), and Ekman (Ek) numbers, defined respectively as
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,u_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \frac{\nu}{2\Omega L_z^2},
\end{equation}
where $u_{\text{ff}}$ is the freefall velocity, $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale (defined below).
These parameters set the freefall Reynolds (\Reff) and P\'{e}clet (\Peff) numbers, 
\begin{equation}
\Reff = \sqrt{\frac{\text{Ra}}{\text{Pr}}},\qquad
\Peff = \text{Pr }\Reff,
\end{equation}
and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
In non rotating RBC (section \ref{sec:2d_results}), we set Ek$\,= \infty$.

The extent of our numerical domain vertically is $z = [-0.5, 0.5]$ and horizontally is $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
The temperature scale, $\Delta$, is set by the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
We respectively define a temperature (Ra$_{\Delta T}$) and a flux (Ra$_{\partial_z T}$) Rayleigh number for these cases,
\begin{equation}
\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
\end{equation}
We impose FT and TT boundary conditions respectively as
\begin{equation}
(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5};\qquad\qquad
(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
\end{equation}

In section \ref{sec:2d_results}, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
\label{eqn:vel_bcs}
\end{equation}
For this choice of boundary conditions, the critical value of the Rayleigh number is Ra$_{\partial_z T} = 1296$ for FT boundaries and Ra$_{\Delta T} = 1708$ for TT boundaries \cite{goluskin2016}.
Due to this difference in onset, it is reasonable to expect important differences between FT and TT solutions at low supercriticalities.
However, for the supercriticalities of O($10^{5+}$) studied in Sec.~\ref{sec:2d_results}, we do not expect this difference in linear stability to be very important.

The rotating cases in section \ref{sec:rotating_results} employ stress-free, impenetrable boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
\label{eqn:vel_bcs}
\end{equation}
We follow previous work  \cite{stellmach&all2014} and study three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek. 
For the cases studied here at Ek = $10^{-6}$, and for TT boundaries, $\lambda_c(10^{-6}) \approx 4.81 \times 10^{-2}$ and the critical Rayleigh number is Ra$_{\Delta T} \approx 9.2 \times 10^{8}$.

We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D rotating simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}. 
The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using v1.0.0 of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
We fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ra & Nu arguments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nondimensional Output Quantities}
\label{sec:ra_nu_relations}
Throughout this work we will measure and report the evolved value of the Nusselt number (Nu).
We define and measure Nu instantaneously as
\begin{equation}
\text{Nu} \equiv \angles{\frac{w T - \Peff^{-1} \partial_z T}{-\Peff^{-1} \angles{\partial_z T}}}
= 1 + \Peff\frac{\angles{w T}}{-\Delta T},
\end{equation}
where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (-\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
This implies that Nu is the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
\begin{equation}
\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu}.
\label{eqn:ra_relation}
\end{equation}

Throughout this work, we will also measure the evolved P\'{e}clet number (Pe) and in section \ref{sec:rotating_results} we will measure the Rossby number (Ro).
These nondimensional quantities are defined as
\begin{equation}
\text{Pe} = \angles{|\bm{u}|}\Peff,\qquad \text{Ro} = \angles{|\bm{\omega}|}\text{Ek }\Reff,
\end{equation}
where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\section{Results}
\label{sec:2d_results}

\subsection{Time Evolution}
\label{sec:time_evolution}

\begin{figure}[p!]
\includegraphics[width=\textwidth]{./rbc_evolution_dynamics.pdf}
\caption{ 
	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation at early and late times (bottom row).
	(Left two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^{10}$ and early in an FT simulation when Ra$_{\Delta T} \approx 10^{10}$.
	To first order, both cases have similar flow structures: a large convective cell and plumes which break apart into small turbulent eddies.
	However, in the FT case, the temperature anomaly of the cold plume is much larger than the hot plume, which does not appear on this color scale.
	(Right two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^9$ and in the relaxed state of the previously pictured FT simulation with Ra$_{\Delta T} \approx 10^9$.
	The relaxed FT simulation is visually indistinguishable from its comparable TT simulation.
\\	
	(Bottom four panels) Probability distribution functions (PDFs) of the full temperature field in each of the four dynamical panels pictured above.
	PDFs sample the dynamics in each simulation once every simulation freefall time unit over the course of 500 freefall time units.
	The black vertical line shows the median value, and the grey outline shows the 68\% confidence interval, or where the cumulative distribution function (CDF)'s value ranges from 0.16 to 0.84.
	(Top row) In both TT simulations, the temperature field has a mean value at $T = 0.5$ and a symmetric distribution around that peak with maxima at the fixed values of the boundaries. 
	(Bottom left) At early times in the FT simulation, the modal value of the PDF constantly moves left (towards the cold fixed-temperature boundary).
	(Bottom right) At late times, the temperature PDF from the cold fixed-temperature value (on the left) to the mode is indistinguishable from the TT PDF, but from the mode to the fixed-flux boundary there is a large tail characterized by low-probability, hot elements.
	\label{fig:rbc_evolution_dynamics} }
\end{figure}

In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of an FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
As shown in the top four panels, we see the expected convective roll solution in both TT simulations (top row) and at early and late times in the FT simulation (bottom row).
Interestingly, we find highly asymmetrical dynamics at early times in the FT simulation (bottom left), in which the temperature anomaly in the cold plume is much greater than in the warm plume.
This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).

In the bottom four panels, we examine these temperature fields statistically by displaying their probability distribution functions (PDFs).
To create these PDFs, we sample the full simulation temperature field once every simulation freefall time unit over the span of 500 time units.
We interpolate the (unevenly spaced) vertical Chebyshev grid points onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.

We find that this statistical analysis of the simulations tells the same story as the dynamical images shown above.
The temperature field in both of the TT simulations (top row) is dominated by the modal temperature of 0.5 in the bulk; a smaller fraction of the domain is filled with equal portions of hotter/colder material (mostly contained in the plumes), and the temperature field is rigidly bounded by the fixed-temperature boundary values.
The story is more complex for the FT simulation.
At early times (lower left), the FT simulation is characterized by two features: an extreme tail (to the left) that characterizes the cold plume at the upper boundary, and a migrating modal temperature that shifts from the right (hotter) to the left (cooler) as cold material mixes in the interior.
At late times (lower right), the FT simulation's PDF is indistinguishable from the TT PDF between the cold (left), fixed-temperature boundary and the modal value.
From the modal value towards warmer temperatures, we find that the fixed-flux (lower boundary) is capable of producing more extreme temperature events and results in a more extended PDF tail.
This long tail is explored further in section \ref{sec:asymmetries}.

In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we examine the time evolution of scalar quantities from the FT simulation shown in Fig.~\ref{fig:rbc_evolution_dynamics} (orange lines) and compare it to the TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
Simulation time is shown in nondimensional freefall units on the x-axis; the latest time displayed for each simulation, $t_{\text{final}}$, is subtracted for direct comparison of the relaxed states.
Traces of Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ are shown in the top-left panel.
In the FT simulation, Ra$_{\Delta T}$ relaxes to its final value over thousands of simulation time units, and this final value is the input value of the equivalent TT case.
In comparison, Ra$_{\partial_z T}$ for the TT case instantaneously reaches its final value, which is the input value for the FT simulation.
This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of Nu (middle panel) and Pe (bottom panel).

The right panels of Fig.~\ref{fig:rbc_scalar_comparisons} show that the relaxation of Ra$_{\Delta T}$ in FT simulations is akin to a sweep through Ra$_{\Delta T}$ parameter space.
The orange (Ra$_{\partial_z T} = 4.83 \times 10^{10}$, as on the left) and yellow (Ra$_{\partial_z T} = 2.61 \times 10^{9}$) lines show the evolution of FT simulations, and the arrows give the sense of time in the simulations.
For comparison, we plot results from TT simulations (purple circles) and the reported results of ref.~\cite{zhu&all2018} (black crosses).
The purple circles filled with orange and yellow circles are comparison TT simulations for the relaxed states of the FT simulations.
The top-right panel is a scaling plot for Nu vs.~Ra$_{\Delta T}$ compensated by the best fit reported in ref.~\cite{johnston&doering2009}.
The bottom-right panel is a scaling plot of Pe vs~Ra$_{\Delta T}$ compensated by the expected scaling \cite{ahlers&all2009}.
We find that FT simulations carry marginally more flux (higher Nu) and are more turbulent (higher Pe) than comparable TT simulations as they relax through this parameter space.
These heightened values of Nu and Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.

FT simulation dynamics evolve slowly during thermal relaxation, and these images, PDFs, and traces demonstrate the importance of waiting for thermal relaxation to be achieved when conducting an FT simulation.

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./rbc_scalar_comparisons.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
	We display evolutionary traces of Ra (top, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
	(Right two panels) Compensated scaling plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	Nu vs.~Ra is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, the best-fit reported by ref.~\cite{johnston&doering2009}.
	Re vs.~Ra is compensated by a Ra$_{\Delta T}^{1/2}$ law, the anticipated scaling of Pe \cite{ahlers&all2009}.
	The orange trace is the time evolution of the FT case from the left panels with the arrows showing the sense of time.
	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
	Purple circles are the measured values of Nu and Pe in our TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
	Black crosses show comparison TT simulations as reported by ref.~\cite{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

\vspace{-0.25cm}
\subsection{Evolved Structure}
\vspace{-0.5cm}
\begin{figure}
\includegraphics[width=\textwidth]{./rbc_1D_profiles.pdf}
\caption{ 
	(Left three panels) We compare time- and horizontally-averaged profiles from an FT (orange) and TT (purple) simulation at Ra$_{\Delta T} = 10^{9}$.
	Shown are the (top) temperature, (middle) temperature in upflows (solid) and downflows (dashed), and (bottom) enthalpy (solid) and conductive (dashed) fluxes.
	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
	The insets show the \% difference between the FT and TT solutions.
	There are slight (a few \%) differences between the two cases near the bottom boundary, but otherwise the two cases are nearly the same to within $\sim 1$\%.
\label{fig:rbc_1D_profiles} }
\vspace{0.5cm}
\end{figure}

In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
Time averages are taken over 500 nondimensional freefall time units for the TT case and over 2000 nondimensional freefall time units for the FT case, sampled once every 0.1 time units (the difference in averaging window is explained in Sec.~\ref{sec:timescales}).
In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
Most of the interesting structure is in the boundary layers, located between the sides of the plots and the thin vertical black lines.
Zoomed in plots of the bottom and top boundary layers are respectively shown in the middle and right columns.
Inset panels show the percentage difference between the FT and TT solutions.
In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the largest deviations away from zero in the interior are O(0.01) in the plotted units.

We find good ($\sim 1\%$) agreement between the FT and TT temperature profiles and enthalpy fluxes throughout the full depth of the domain, with slightly larger differences near the bottom boundary where the boundary conditions differ.
When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
These differences are interesting, and are explored further in section \ref{sec:asymmetries} and Fig.~\ref{fig:rbc_dynamics_asymmetries}, but vanish in the interior and do not likely affect the convective dynamics appreciably.

\subsection{TT-to-FT: Rapidly equilibrated FT simulations}
\label{sec:tt-to-ft}

\begin{figure}
\includegraphics[width=\textwidth]{./rbc_restart_description.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities, which have been averaged over a rolling time window of 25 simulation time units, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
	The time of the change of boundary conditions is denoted by the vertical black line.
	(Top panel) The evolution of Ra is shown; Ra$_{\partial_z T}/(4.83\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
	The mean value of temperature gradient (middle panel) and temperature (bottom panel) at the bottom boundary are also shown.
	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\text{Nu}$.
	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
	(right four panels) PDFs are shown which compare the dynamics during the grey time window in the left panels (black PDFs, TT-to-FT) to dynamics from a comparable time window in the FT case from Fig.~\ref{fig:rbc_scalar_comparisons}.
	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
\label{fig:rbc_restart_description} }
\vspace{-0.25cm}
\end{figure}

Achieving thermal relaxation in pure FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
In the previous sections, we have shown that relaxed FT and TT simulations are very similar.
It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.

We now briefly describe a procedure which takes advantage of the fast evolution of TT simulations to achieve equilibrated FT simulations.
In short, the evolved flow fields in the TT simulation are properly re-nondimensionalized and used as initial conditions for an FT simulation.
Throughout this work, we will refer to simulations conducted this way as ``TT-to-FT'' simulations.
To achieve this, we perform these steps:
\begin{enumerate}
\item Run a TT simulation to its statistically stationary state ($\sim100+$ freefall time units). 
Measure $\text{Nu}$ in that state.
\item Re-nondimensionalize from $\Delta = \Delta T \rightarrow \partial_z T$, and from Ra$_{\Delta T}\rightarrow$Ra$_{\partial_z T}$, as in Eqn.~\ref{eqn:ra_relation}.
In our freefall nondimensionalization, this means setting the velocities in the FT simulation to $\bm{u}_{\text{FT}} = \bm{u}_{\text{TT}} / \sqrt{\text{Nu}}$, and setting the temperature field to $T_{\text{FT}} = T_{\text{TT}} / \text{Nu}$.
\item Restart the simulation with FT boundaries and continue timestepping.
\end{enumerate}
We show this procedure in practice in Fig.~\ref{fig:rbc_restart_description}.
In the left three panels, we display the temporal behavior of (top) Ra, (middle) the flux at the bottom boundary, and (bottom) the temperature difference between the top and bottom boundaries.
We take the full evolution of the Ra$_{\Delta T} = 10^9$ TT simulation shown in Fig.~\ref{fig:rbc_scalar_comparisons}, then change its boundary conditions to FT at Ra$_{\partial_z T} = 4.83\times 10^{10}$ and restart the simulation using the above procedure.
The change from TT to FT boundaries occurs at the time denoted by the thin vertical line.
Unlike in the FT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, there is no thermal rundown in the FT state, due to the rapid relaxation achieved during the TT portion of the simulation.

In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable FT simulation which we timestepped through thermal relaxation.
Shown are PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
In Table~\ref{table:pdf_values}, we display the first four moments of each of these distributions,
\begin{equation}
\begin{split}
&\mu(A) \equiv \sum_{i} A_i\,P(A_i)\,\Delta A,\qquad\qquad\qquad\qquad\qquad\qquad\,\,
\sigma(A) \equiv \sqrt{\sum_{i}[A_i-\mu(A)]^2 P(A_i) \Delta A},\\
&\text{Skewness}(A) \equiv \frac{1}{\sigma(A)^3}\sum_i [A_i-\mu(A)]^3 P(A_i) \Delta A,\qquad
\text{Kurtosis}(A) \equiv \frac{1}{\sigma(A)^4}\sum_i [A_i-\mu(A)]^4 P(A_i) \Delta A,
\end{split}
\label{eqn:pdf_moments}
\end{equation}
where $A$ is a flow quantity, $P(A)$ is the PDF of $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the discrete PDF bins, and $i$ is the index of the bin.
The PDFs are qualitatively similar, and there is generally good agreement between the moments of the PDFs.
The remaining discrepancies between the PDFs are small and seem to primarily be due to the randomness of the flows in the time windows over which we sampled the simulations.

\begin{table}[b!]
\vspace{-0.5cm}
\caption{ 
	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
}
\vspace{-0.25cm}
\setlength{\tabcolsep}{12pt}
\label{table:pdf_values}
\begin{center}
\begin{tabular}{c c c c c c}
\hline																	
Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
\hline
$T$				&	FT			&		$1.03 \times 10^{-2}$	&	$1.49 \times 10^{-3}$	&	0.656		&	27.0 \\
				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
\hline
$\omega^2$		&	FT			&		$16.7$					&	$10.3$					&	96.2		&	$2.72 \times 10^4$ \\
				&	TT-to-FT	&		$11.7$					&	$10.6$					&	86.0		&	$1.63 \times 10^4$ \\
\hline
$wT$			&	FT			&		$4.50 \times 10^{-6}$	&	$4.87 \times 10^{-4}$	&	0.0133	&	$3.06$ \\
				&	TT-to-FT	&		$4.47 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0110	&	$3.06$ \\
\hline
$w$				&	FT			&		$3.62 \times 10^{-6}$	&	$4.70 \times 10^{-2}$	&	-0.0211	&	$3.00$ \\
				&	TT-to-FT	&		$4.22 \times 10^{-6}$	&	$4.82 \times 10^{-2}$	&	-0.0187	&	$3.02$ \\
\hline																	
\end{tabular}
\end{center}
\end{table}

We note briefly that this TT-to-FT mechanism is only one of many ways of accelerating the thermal relaxation of an FT simulation.
We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
We note however that the TT-to-FT setup described here is likely the least complicated mechanism for achieving rapid relaxation in a simplified RBC setup that we are aware of.
The successful degree with which this mechanism reproduces the evolved dynamics suggests that thermal relaxation occurs in two parts:
\begin{enumerate}
\item Changes to the simulation energy reservoir, and
\item Restratification of the experiment.
\end{enumerate}
The thermal energy reservoir of TT simulations does not change between the initial and final state.
The rapid relaxation of TT simulations therefore suggests that experimental restratification occurs rapidly in RBC. 
The long rundown of FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the mean temperature) drifting over time.
Put differently, the classic RBC setup for $T_0(z)$ is a bad choice of initial conditions for FT boundaries, and TT-to-FT simulations use TT dynamics to choose a more ideal set of initial conditions.

\subsubsection{Changing Timescales}
\label{sec:timescales}
One surprising result of our FT simulations is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
As noted above in our TT-to-FT procedure, the velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
As a result, every simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a nondimensional freefall time in an FT simulation.
This is on display in the left panels of Fig~\ref{fig:rbc_restart_description}, where the flow variations occur at a higher temporal frequency in the TT portion of the simulation than in the FT portion.

These results imply that the true nondimensional freefall time of an FT simulation is $\tau_{\text{ff}} = \sqrt{\text{Nu}}$ in simulation freefall time units.
However, we note that Ra$_{\partial_z T}$ is the input value of Ra for an FT simulations, and that Ra$_{\partial_z T}/$Ra$_{\Delta T} = \text{Nu}$.
The thermal diffusion timescale, $\tau_{\text{th}}$, which scales like $\tau_{\text{th}} \propto \sqrt{\text{Ra}_{\text{input}}}$, is also larger in an FT simulation than in a comparable TT simulation by a factor of $\sqrt{\text{Nu}}$.
One convective freefall timescale therefore occurs over the same fraction of a diffusion timescale regardless of boundary conditions or temperature nondimensionalization, $\tau_{\text{ff}}/\tau_{\text{th}} \neq f(\text{Nu})$.
These findings suggest that comparing FT and TT dynamics may be more straightforward under a thermal diffusion nondimensionalization \cite{goluskin2016} than the freefall nondimensionalization we have used throughout this work.

\subsection{Asymmetries induced by mixed boundaries}
\label{sec:asymmetries}

\begin{figure}
\includegraphics[width=\textwidth]{./rbc_dynamics_asymmetries.pdf}
\caption{ 
	(Left panel) PDFs of temperature measurements of a TT-to-FT (orange) and TT (purple) case with Ra$_{\Delta T} = 10^{10}$ are displayed.
	The right tail of the distribution (near the hot fixed-flux boundary for the FT case) shows that fixed flux boundaries achieve more extreme temperature events than fixed temperature boundaries.
	(Middle panel) A snapshot of the temperature anomaly in the FT simulation.
	Zoomed in views of the regions outlined in black boxes are shown in the right two panels.
	Near the top (fixed temperature) boundary, the temperature anomaly at the root of the plume vanishes, but this does not happen near the bottom (fixed flux) boundary, allowing for more extreme instantaneous values.
\label{fig:rbc_dynamics_asymmetries} }
\end{figure}

We now study in more detail the asymmetries introduced into a solution by FT boundaries.
We run a TT and TT-to-FT simulation at Ra$_{\Delta T} = 10^{10}$ and Ra$_{\partial_z T} = 9.51 \times 10^{11}$, respectively.
In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation near the fixed-flux boundary.
In the left panel, we plot PDFs of the temperature fields in comparable TT and FT simulations.
These PDFs agree remarkably well near the mean and for cold temperatures (near the fixed temperature boundary), but diverge in the tail of the PDF for hot temperatures where $T/\Delta T \gtrsim 0.8$, where the boundary conditions differ.
Interestingly, there are no temperature fluctuations which exceed the specified boundary values in the convective domain for TT simulations.
However, the FT PDF has a much longer tail and the FT solution achieves fluid parcels which are hotter than the average bottom boundary value by more than 50\%.
In order to understand how this is possible, we examine a snapshot of the FT simulation's temperature anomaly in the middle panel.
We have outlined a portion of a cold plume near the upper (fixed-temperature) boundary and a portion of a hot plume near the lower (fixed-flux) boundary, and these regions are magnified in the rightmost panels.
The TT upper boundary suppresses temperature anomaly at the upper boundary and regulates the temperature minima which can be achieved.
The fixed-flux lower boundary does no such suppression and allows for extreme temperature values to be achieved in the plume-launching area, thus allowing for the asymmetry in the tails of the temperature PDF.

We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between FT and TT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
We explore this further in the discussion in section \ref{sec:discussion}.

\section{Rotating \RB Convection}
\label{sec:rotating_results}

We now extend our study to a more complicated experiment: 3D rotating RBC with an Ekman number of $10^{-6}$.
We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and an FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \cite{couston&all2019}.

In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of the FT and TT cases.
The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
Even in the presence of strong rotation, the TT immediately equilibrates, but the FT case takes thousands of freefall times to achieve thermal relaxation.
In the middle panel, we show the evolution of Ro; the evolved flows in both simulations exhibit rotationally constrained dynamics with Ro $\,\approx 0.1$, but the flows in the FT simulation relax to this state from an initially unconstrained state (Ro $\,\approx 1$).
This implies that the thermal relaxation process can walk through the parameter space of flow balances (e.g., the balance between Inertial and Coriolis forces) in addition to the Ra$_{\Delta T}$ parameter space.
In the bottom panel, we display the evolution of Pe over time.
Strangely, the peak value of Pe occurs a few hundred freefall times after the convective transient.
After achieving this peak value, Pe monotonically decreases toward its relaxed state.

In the upper right panel of Fig.~\ref{fig:rotating_panels}, we plot Nu vs.~Ra for rotating simulations.
Select TT cases are plotted as cyan circles with purple outlines (where the cyan color denotes the value of Ek$\,=\,10^{-6}$ according to the color bar).
The evolution of the FT case in the left panels is shown as a thick orange line with a cyan interior and the black arrows show the direction of time.
The TT case that corresponds to the FT case is a purple star with a cyan interior.
We have additionally included some literature data from numerical simulations (circles) and experiments (diamonds) as reported in the appendix tables of ref.~\cite{cheng&all2015}.
These experiments were conducted in a cylindrical geometry at a different Pr, and are not meant to be one-to-one-comparable, but are meant to guide the eye to the nature of the parameter space of rotating convection.
The solid black line is the best-fit line for rotationally unconstrained simulations with Ra $\geq 10^{10}$ from ref.~\cite{cheng&all2015}.
As expected, the scaling of Nu vs.~Ra is steep in the rotationally constrained regime \cite{julien&all2012, plumley&julien2019}, which these simulations trace through.
As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT values of Nu are once again somewhat elevated above the comparable TT simulations.

In the bottom right three panels of Fig.~\ref{fig:rotating_panels}, we plot the vertically integrated vertical vorticity in the simulation at three different times.
In the left panel, a dominant LSV which is aligned with the global rotation dominates the simulation at early times.
Over thousands of freefall times, this LSV evolves into a long-lived vortex pair, displayed in the middle panel.
Finally, in the evolved state, this vortex pair solution begins to oscillate with domain-wide jets, such as those displayed in the right panel.
We find that the TT solution shows this oscillatory behavior between vortex pairs and jets immediately and throughout the full 5000 freefall timescales of evolution that we simulated.

We suspect that the strange behavior of Pe in the bottom left panel can be explained by the evolution of the dominant flow structures over time.
At early times, the initially large value of Ra$_{\Delta T}$ in the FT case drives the displayed dominant LSV.
This powerful driving injects energy into the LSV, causing Pe to grow.
As Ra$_{\Delta T}$ and convective driving decrease over time, the LSV saturates and then starts to wind down, leading to the ``bump'' in the Pe trace.

We once again find it important to briefly note the difference in computational cost between the FT and TT simulations conducted here.
The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.6 \times 10^4$ cpu-hours.
By comparison, the cost of the FT simulation shown in the same panels was \emph{two orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
The TT simulation's coefficient resolution was $128^3$.
The FT simulation's initial resolution required to resolve the convective transient was $512\times384^2$ coefficients.
We reduced the resolution to $256\times384^2$ after 100 freefall times, and then later to $128\times384^2$ after $\sim3.3 \times 10^3$ freefall times.
At each of these times, we found that lowering the \emph{horizontal} coefficient resolution of the simulation did not reproduce the simulation solution with fidelity.
This suggests that small scale turbulent velocity structures---which are injected by the vigorous transient and perhaps associated with the LSV---are long lived throughout the thermal evolution of the simulation.

\begin{figure}
\includegraphics[width=\textwidth]{./rotating_panels.pdf}
\caption{ 
	(Left three panels) Time traces of scalar quantities in an FT (orange) and TT (purple) simulation are shown.
	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
	(Top panel) Ra, normalized by the input Ra$_{\Delta T}$ = 2.75$\,\times 10^9$ of the TT simulation.
	(Middle panel) Ro evolution of both simulation; the bulk flow of the FT simulation transitions from a marginally rotationally unconstrained state to a constrained state, while the TT simulation is always rotationally constrained.
	(Bottom panel) Pe evolution of the simulations is shown, normalized by the mean value measured over the last 500 freefall times of the TT simulation.
	(Upper right panel) Parameter space of Nu vs.~Ra$_{\Delta T}$ in rotating convection.
	Circular and diamond data points are respectively simulations and experimental data points from \cite{cheng&all2015}.
	The color of the data points signifies the Ekman number of the points, and black points are non rotating.
	Data from our Ek$\,=\,10^{-6}$ FT experiment are shown as a thick orange line with a cyan interior, where the black arrows give the direction of time.
	Some TT simulations are shown as purple circles with a cyan interior, and the TT case which corresponds to the relaxed state of the FT simulation is shown as a star.
	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
	In the converged state, we see oscillatory behavior between this vortex pair behavior and jets (right panel).
	The TT case exhibits the oscillatory behavior between vortex pairs and jets throughout its whole evolution.
	The three vertical black lines in the left panels signify the times at which these snapshots are taken.
\label{fig:rotating_panels} }
\end{figure}

%%%%%%%%%%%%
%%%%%%%%%%%
% CONCLUSION
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Conclusions \& Discussion}
\label{sec:discussion}
In short, we find that FT simulations experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.

In this paper, we have studied the time evolution of \RB convection (RBC) under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
Through studying this relaxation and the relaxed states of both simulations, we come to the following conclusions:
\begin{enumerate}
\item Thermal relaxation in RBC has two components: (a) changes in the energy reservoir and (b) changes in the stratification.
We find that the long relaxation of FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations due to the lack of evolution of the average domain temperature.
The rapid evolution of our TT simulations suggests that RBC restratifies itself instantaneously.
\item Dynamical measurements taken during the thermal relaxation of an FT simulation may be misleading.
Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
\item The thermal relaxation process of an FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classical scaling laws along these parameter space sweeps.
\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation.
\item Despite minor asymmetries near the fixed-flux boundary, we find no meaningful difference between the mean state of FT and TT simulations.
\end{enumerate}
We now describe some lessons that should be applied from this work to astrophysical convection, and comment on some open areas of research.

Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.
In nature, convection is not always in an equilibrium state.
For example, in the late stages of the lifetimes of stars, some core burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
The use of FT boundaries or initial conditions that we have here considered to be ``bad'' choices may help in understanding these transient lifetime stages.
However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.

One question which our study of RBC is not able to address is: how long does it take for a complex convective system to restratify?
Our fully convective domains restratified instantaneously, but it is likely that mixed convective-and-stably-stratified domains \citep{brummell&all2002, kapyla&all2019, pratt&all2017, korre&all2019} should have regions that are not turbulently mixed by convection which could also have long relaxation timescales.
It would be extremely helpful for future studies to examine relaxational timescales in systems where the energy reservoir is fixed, but where convection does not effectively mix the whole domain.
Fortunately, clever techniques (e.g., as we explored in ref.~\cite{anders&all2018}) can likely be used to rapidly restratify atmospheres in such simulations.

RBC is fundamentally symmetrical, but many natural convective processes occur in density-stratified domains in which the symmetries of the problem are fundamentally broken.
In the present study, we observed that flux boundaries produce more extreme thermodynamic events than temperature boundaries.
In studies of overshooting convection, it is possible that plumes produced by a flux boundary layer could launch further into a stable layer than plumes produced by a temperature boundary.
Some authors have aimed to quantify the nature of overshooting plumes from a convective region into a stable region \cite{pratt&all2017, korre&all2019}, and it is unclear if different choices of boundary conditions could change the observed distribution of overshooting plumes observed there.

Some of the most complex astrophysical convection experiments aim to understand self-consistently evolving magnetic dynamos in rotating, spherical, magnetohydrodynamical domains \cite{brown&all2010, yadav&all2016, strugarek&all2017, strugarek&all2018}.
These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
We found in our FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
If we had terminated our FT rotating simulation too early, we would not have seen the eventual destruction of this LSV or the later oscillatory behavior between jets and vortex pairs.
Many dynamo simulations are performed in highly turbulent regimes at the cutting-edge of what is achievable using modern computational resources.
As a result, timestepping through thousands of freefall timescales is not possible in these simulations.
It is therefore crucial that dynamo simulations be set up in such a manner as to avoid large changes to the system's energy reservoir such as those that we observed and studied here.
Some authors who study astrophysical convection \citep{featherstone&hindman2016a, strugarek&all2018, bordwell&all2018, matilsky&all2019} employ FF boundary conditions, and our results here suggest that such a choice may be ideal in those complex simulations.

In conclusion, we note that our results here should provide astrophysical convection simulations with reason for optimism.
Some problems that we encounter (e.g., long thermal rundown in FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.

\begin{acknowledgments}
We'd like to thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
We'd also like to thank Jeff Oishi, who encouraged us to pursue the differences between early and late FT dynamics and who graciously saved the reader from reading ``mixedFT'' (instead of FT) and ``fixedT'' (instead of TT).
EHA acknowledges that this work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
LK acknowledges support from the George Ellery Hale Post-Doctoral Fellowship.
This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
\end{acknowledgments}

\appendix
\section{Table of Simulations}
\label{app:table}
Input and output information for the simulations in this work are shown in Table~\ref{table:simulations}.
The code used to run these simulations can be found online in the repository of supplemental materials \cite{anders&all2020a_supp}.

\begin{table}[ht]
\caption{
	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
	Input quantities are the boundary conditions (BCs), Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units.
	Reported uncertainties are the standard deviation of the sample mean; when the uncertainty is not reported, it is smaller than the number of reported digits.
	The ``Nu comp'' values are comparison Nu values reported in ref.~\cite{zhu&all2018}.
	Resolutions marked by a $*$ show the initial, highest resolution utilized in the simulation.
	The 2D FT Ra = $4.83 \times 10^{10}$ simulation's resolution was changed to $1024\times2048$ about 500 freefall time units after transient.
	The rotating FT case's resolution was reduced to $384^2\times256$ about one hundred freefall time units after transient, and was further reduced to $384^2\times128$ about $3.3\times 10^3$ freefall times after transient.
}
\setlength{\tabcolsep}{8pt}
\label{table:simulations}
\begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{c c c c c c c c c}
\hline																	
BCs	&	Ra	&	nx$\times$ny$\times$nz	& $t_{\text{simulation}}$	&	cpu-hours 	&	Nu	&	Nu comp	&	Pe  & Ro \\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{7}{c}{\vspace{0.1cm}2D Runs ($\Gamma = 2$, no-slip)} \\
\hline
TT			&	$1.00 \times 10^8$		&	512x1024	&	1023		&	$5.57 \times 10^3$	&	$25.4 \pm 0.1$	&	26.1	&	$3.18 \times 10^3$ & --- \\
FT			&	$2.61 \times 10^9$		&	1024x2048	&	9410		&	$1.21 \times 10^5$	&	$25.3 \pm 0.2$	&	26.1	&	$3.31 \times 10^3$ & --- \\
TT-to-FT	&	$2.61 \times 10^9$		&	512x1024	&	1000		&	$1.88 \times 10^3$	&	$26.1 \pm 0.1$	&	26.1	&	$3.22 \times 10^3$ & --- \\
TT			&	$2.15 \times 10^8$		&	512x1024	&	1023		&	$5.73 \times 10^3$	&	$31.3 \pm 0.2$	&	31.2	&	$5.17 \times 10^3$ & --- \\
TT			&	$4.64 \times 10^8$		&	1024x2048	&	1024		&	$4.66 \times 10^4$	&	$38.4 \pm 0.3$	&	38.9	&	$8.60 \times 10^3$ & --- \\
TT			&	$1.00 \times 10^9$		&	1024x2048	&	1023		&	$5.58 \times 10^4$	&	$48.0 \pm 0.4$	&	48.3	&	$1.33 \times 10^4$ & --- \\
FT			&	$4.83 \times 10^{10}$	&	2048x4096*	&	16230		&	$5.36 \times 10^5$	&	$48.7 \pm 0.4$	&	48.3	&	$1.41 \times 10^4$ & --- \\
TT-to-FT	&	$4.83 \times 10^{10}$	&	1024x2048	&	1000		&	$1.11 \times 10^4$	&	$48.7 \pm 0.3$	&	48.3	&	$1.36 \times 10^4$ & --- \\
TT			&	$2.15 \times 10^9$		&	1024x2048	&	1029		&	$6.38 \times 10^4$	&	$60.4 \pm 0.5$	&	61.1	&	$1.99 \times 10^4$ & --- \\
TT			&	$4.64 \times 10^9$		&	1536x3072	&	1024		&	$3.29 \times 10^5$	&	$75.2 \pm 0.6$	&	76.3	&	$2.94 \times 10^4$ & --- \\
TT			&	$1.00 \times 10^{10}$	&	2048x4096	&	1039		&	$7.79 \times 10^5$	&	$95.3 \pm 0.7$	&	95.1	&	$4.30 \times 10^4$ & --- \\
TT-to-FT	&	$9.51 \times 10^{11}$	&	2048x4096	&	1000		&	$7.91 \times 10^4$	& 	$93.2 \pm 0.8$ 	&	95.1	&	$4.11 \times 10^4$ & --- \\
\hline																	
\multicolumn{7}{c}{\vspace{0.1cm}3D Rotating Runs (Ek = $10^{-6}$, $\Gamma = 0.481$, stress-free)} \\
\hline																	
TT	&	$1.38 \times 10^9$		&	64$^2\times$128 	&	2565		&	$2.98 \times 10^3$	&	$2.17$			&	---		&	$2.84 \times 10^2$  & $(3.38 \pm 0.17) \times 10^{-2}$ \\
TT	&	$1.83 \times 10^9$		&	64$^2\times$128 	&	2545		&	$3.54 \times 10^3$	&	$3.56$			&	---		&	$5.28 \times 10^2$  & $(5.67 \pm 0.33) \times 10^{-2}$ \\
TT	&	$2.29 \times 10^9$		&	128$^3$				&	2537		&	$1.08 \times 10^4$	&	$5.61$			&	---		&	$8.91 \times 10^2$  & $(8.56 \pm 0.44) \times 10^{-2}$ \\
TT	&	$2.75 \times 10^9$		&	128$^3$				&	5035		&	$2.6 \times 10^4$	&	$8.04 \pm 0.01$	&	---		&	$1.71 \times 10^3$  & $(1.17 \pm 0.06) \times 10^{-1}$ \\
FT	&	$2.1 \times 10^{10}$	&	384$^2\times$512*	&	13950		&	$2.3 \times 10^6$	&	$7.86 \pm 0.01$	&	---		&	$1.76 \times 10^3$  & $(1.14 \pm 0.06) \times 10^{-1}$ \\
TT	&	$3.67 \times 10^9$		&	128$^3$				&	2532		&	$1.55 \times 10^4$	&	$12.5$			&	---		&	$3.39 \times 10^3$  & $(1.74 \pm 0.08) \times 10^{-1}$ \\
TT	&	$4.58 \times 10^9$		&	128$^3$				&	2530		&	$1.69 \times 10^4$	&	$17.6$			&	---		&	$4.77 \times 10^3$  & $(2.35 \pm 0.08) \times 10^{-1}$ \\
TT	&	$5.50 \times 10^9$		&	192$^3$				&	2402		&	$7.35 \times 10^4$	&	$22.8$			&	---		&	$6.38 \times 10^3$  & $(2.96 \pm 0.11) \times 10^{-1}$ \\
TT	&	$6.42 \times 10^9$		&	192$^3$				&	2226		&	$7.35 \times 10^4$	&	$29.5$			&	---		&	$7.86 \times 10^3$  & $(3.65 \pm 0.16) \times 10^{-1}$ \\
TT	&	$7.33 \times 10^9$		&	256$^3$				&	1147		&	$1.47 \times 10^5$	&	$36.2$			&	---		&	$9.52 \times 10^3$  & $(4.33 \pm 0.17) \times 10^{-1}$ \\
TT	&	$8.25 \times 10^9$		&	256$^3$				&	1079		&	$1.47 \times 10^5$	&	$43.0$			&	---		&	$1.10 \times 10^4$  & $(5.01 \pm 0.20) \times 10^{-1}$ \\
TT	&	$9.17 \times 10^9$		&	256$^3$				&	1030		&	$1.47 \times 10^5$	&	$48.9$			&	---		&	$1.24 \times 10^4$  & $(5.63 \pm 0.26) \times 10^{-1}$ \\
TT	&	$1.834 \times 10^{10}$	&	256$^3$				&	971.9		&	$1.84 \times 10^5$	&	$111$			&	---		&	$2.21 \times 10^4$  & $1.18 \pm 0.09$ \\
\hline																	
\end{tabular}
}
\end{center}
\end{table}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (0) dotless jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (0) verbatim
%Control: production of eprint (0) enabled
\begin{thebibliography}{37}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {{Spiegel}}\ and\ \citenamefont
  {{Veronis}}(1960)}]{spiegel&veronis1960}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~A.}\ \bibnamefont
  {{Spiegel}}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {{Veronis}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On the
  Boussinesq Approximation for a Compressible Fluid.}}}\ }\href {\doibase
  10.1086/146849} {\bibfield  {journal} {\bibinfo  {journal} {\apj}\ }\textbf
  {\bibinfo {volume} {131}},\ \bibinfo {pages} {442} (\bibinfo {year}
  {1960})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Ahlers}\ \emph {et~al.}(2009)\citenamefont {Ahlers},
  \citenamefont {Grossmann},\ and\ \citenamefont {Lohse}}]{ahlers&all2009}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Guenter}\ \bibnamefont
  {Ahlers}}, \bibinfo {author} {\bibfnamefont {Siegfried}\ \bibnamefont
  {Grossmann}}, \ and\ \bibinfo {author} {\bibfnamefont {Detlef}\ \bibnamefont
  {Lohse}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Heat transfer and
  large scale dynamics in turbulent rayleigh-b\'enard convection},}\ }\href
  {\doibase 10.1103/RevModPhys.81.503} {\bibfield  {journal} {\bibinfo
  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
  {pages} {503--537} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Plumley}}\ and\ \citenamefont
  {{Julien}}(2019)}]{plumley&julien2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Meredith}\
  \bibnamefont {{Plumley}}}\ and\ \bibinfo {author} {\bibfnamefont {Keith}\
  \bibnamefont {{Julien}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Scaling Laws in Rayleigh-B{\'e}nard Convection}},}\ }\href {\doibase
  10.1029/2019EA000583} {\bibfield  {journal} {\bibinfo  {journal} {Earth and
  Space Science}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
  {1580--1592} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Charbonneau}}(2014)}]{charbonneau2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Paul}\ \bibnamefont
  {{Charbonneau}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Solar
  Dynamo Theory}},}\ }\href {\doibase 10.1146/annurev-astro-081913-040012}
  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Astronomy and
  Astrophysics}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages}
  {251--290} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Toomre}}(2019)}]{toomre2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Some travels
  in the land of nonlinear convection and magnetism}},}\ }in\ \href {\doibase
  10.1051/eas/1982027} {\emph {\bibinfo {booktitle} {EAS Publications
  Series}}},\ \bibinfo {series} {EAS Publications Series}, Vol.~\bibinfo
  {volume} {82}\ (\bibinfo {year} {2019})\ pp.\ \bibinfo {pages}
  {273--294}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Goluskin}}(2016)}]{goluskin2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {David}\ \bibnamefont
  {{Goluskin}}},\ }\href {\doibase 10.1007/978-3-319-23941-5} {\emph {\bibinfo
  {title} {{Internally heated convection and Rayleigh-B{\'e}nard
  convection}}}}\ (\bibinfo  {publisher} {Springer International Publishing},\
  \bibinfo {year} {2016})\ p.\ \bibinfo {pages} {arXiv:1506.01656},\ \Eprint
  {http://arxiv.org/abs/1506.01656} {arXiv:1506.01656 [physics.flu-dyn]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Glatzmaier}}\ and\ \citenamefont
  {{Gilman}}(1982)}]{glatzmaier&gilman1982}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~A.}\ \bibnamefont
  {{Glatzmaier}}}\ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
  {{Gilman}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Compressible
  convection in a rotating spherical shell. V - Induced differential rotation
  and meridional circulation}},}\ }\href {\doibase 10.1086/159909} {\bibfield
  {journal} {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {256}},\
  \bibinfo {pages} {316--330} (\bibinfo {year} {1982})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Hurlburt}}\ \emph {et~al.}(1986)\citenamefont
  {{Hurlburt}}, \citenamefont {{Toomre}},\ and\ \citenamefont
  {{Massaguer}}}]{hurlburt&all1986}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
  {{Hurlburt}}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {{Toomre}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
  {{Massaguer}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Nonlinear
  compressible convection penetrating into stable layers and producing internal
  gravity waves}},}\ }\href {\doibase 10.1086/164796} {\bibfield  {journal}
  {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {311}},\ \bibinfo
  {pages} {563--577} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Cattaneo}}\ \emph {et~al.}(1990)\citenamefont
  {{Cattaneo}}, \citenamefont {{Hurlburt}},\ and\ \citenamefont
  {{Toomre}}}]{cattaneo&all1990}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {{Cattaneo}}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
  {{Hurlburt}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Supersonic
  convection}},}\ }\href {\doibase 10.1086/185652} {\bibfield  {journal}
  {\bibinfo  {journal} {Astrophys. J. Lett.}\ }\textbf {\bibinfo {volume}
  {349}},\ \bibinfo {pages} {L63--L66} (\bibinfo {year} {1990})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {{Featherstone}}\ and\ \citenamefont
  {{Hindman}}(2016)}]{featherstone&hindman2016a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nicholas~A.}\
  \bibnamefont {{Featherstone}}}\ and\ \bibinfo {author} {\bibfnamefont
  {Bradley~W.}\ \bibnamefont {{Hindman}}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {{The Spectral Amplitude of Stellar Convection and Its
  Scaling in the High-Rayleigh-number Regime}},}\ }\href {\doibase
  10.3847/0004-637X/818/1/32} {\bibfield  {journal} {\bibinfo  {journal}
  {\apj}\ }\textbf {\bibinfo {volume} {818}},\ \bibinfo {eid} {32} (\bibinfo
  {year} {2016})},\ \Eprint {http://arxiv.org/abs/1511.02396} {arXiv:1511.02396
  [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Korre}}\ \emph {et~al.}(2019)\citenamefont
  {{Korre}}, \citenamefont {{Garaud}},\ and\ \citenamefont
  {{Brummell}}}]{korre&all2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {{Korre}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {{Garaud}}}, \
  and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {{Brummell}}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {{Convective overshooting and
  penetration in a Boussinesq spherical shell}},}\ }\href {\doibase
  10.1093/mnras/stz047} {\bibfield  {journal} {\bibinfo  {journal} {\mnras}\
  }\textbf {\bibinfo {volume} {484}},\ \bibinfo {pages} {1220--1237} (\bibinfo
  {year} {2019})},\ \Eprint {http://arxiv.org/abs/1810.06700} {arXiv:1810.06700
  [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Wood}}\ and\ \citenamefont
  {{Brummell}}(2018)}]{wood&brummell2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~S.}\ \bibnamefont
  {{Wood}}}\ and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
  {{Brummell}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{A
  Self-consistent Model of the Solar Tachocline}},}\ }\href {\doibase
  10.3847/1538-4357/aaa6d5} {\bibfield  {journal} {\bibinfo  {journal} {\apj}\
  }\textbf {\bibinfo {volume} {853}},\ \bibinfo {eid} {97} (\bibinfo {year}
  {2018})},\ \Eprint {http://arxiv.org/abs/1801.02565} {arXiv:1801.02565
  [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{K{\"a}pyl{\"a}}}\ \emph {et~al.}(2019)\citenamefont
  {{K{\"a}pyl{\"a}}}, \citenamefont {{Viviani}}, \citenamefont
  {{K{\"a}pyl{\"a}}}, \citenamefont {{Brandenburg}},\ and\ \citenamefont
  {{Spada}}}]{kapyla&all2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont
  {{K{\"a}pyl{\"a}}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {{Viviani}}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
  {{K{\"a}pyl{\"a}}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {{Brandenburg}}}, \ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {{Spada}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Effects of a
  subadiabatic layer on convection and dynamos in spherical wedge
  simulations}},}\ }\href {\doibase 10.1080/03091929.2019.1571584} {\bibfield
  {journal} {\bibinfo  {journal} {Geophysical and Astrophysical Fluid
  Dynamics}\ }\textbf {\bibinfo {volume} {113}},\ \bibinfo {pages} {149--183}
  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1803.05898}
  {arXiv:1803.05898 [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Otero}}\ \emph {et~al.}(2002)\citenamefont
  {{Otero}}, \citenamefont {{Wittenberg}}, \citenamefont {{Worthing}},\ and\
  \citenamefont {{Doering}}}]{otero&all2002}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {{Otero}}}, \bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont
  {{Wittenberg}}}, \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
  {{Worthing}}}, \ and\ \bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
  {{Doering}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Bounds on
  Rayleigh B{\'e}nard convection with an imposed heat flux}},}\ }\href
  {\doibase 10.1017/S0022112002002410} {\bibfield  {journal} {\bibinfo
  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {473}},\ \bibinfo
  {pages} {191--199} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Johnston}}\ and\ \citenamefont
  {{Doering}}(2009)}]{johnston&doering2009}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {{Johnston}}}\ and\ \bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
  {{Doering}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Comparison
  of Turbulent Thermal Convection between Conditions of Constant Temperature
  and Constant Flux}},}\ }\href {\doibase 10.1103/PhysRevLett.102.064501}
  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {eid} {064501} (\bibinfo {year}
  {2009})},\ \Eprint {http://arxiv.org/abs/0811.0401} {arXiv:0811.0401
  [physics.flu-dyn]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Anders}\ \emph {et~al.}(2018)\citenamefont {Anders},
  \citenamefont {Brown},\ and\ \citenamefont {Oishi}}]{anders&all2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
  {Anders}}, \bibinfo {author} {\bibfnamefont {Benjamin~P.}\ \bibnamefont
  {Brown}}, \ and\ \bibinfo {author} {\bibfnamefont {Jeffrey~S.}\ \bibnamefont
  {Oishi}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Accelerated
  evolution of convective simulations},}\ }\href {\doibase
  10.1103/PhysRevFluids.3.083502} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages}
  {083502} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Julien}}\ \emph {et~al.}(1996)\citenamefont
  {{Julien}}, \citenamefont {{Legg}}, \citenamefont {{McWilliams}},\ and\
  \citenamefont {{Werne}}}]{julien&all1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {{Julien}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {{Legg}}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{McWilliams}}}, \ and\
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{Werne}}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {{Rapidly rotating turbulent
  Rayleigh-Benard convection}},}\ }\href {\doibase 10.1017/S0022112096002789}
  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid Mechanics}\
  }\textbf {\bibinfo {volume} {322}},\ \bibinfo {pages} {243--273} (\bibinfo
  {year} {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Stellmach}}\ \emph {et~al.}(2014)\citenamefont
  {{Stellmach}}, \citenamefont {{Lischper}}, \citenamefont {{Julien}},
  \citenamefont {{Vasil}}, \citenamefont {{Cheng}}, \citenamefont {{Ribeiro}},
  \citenamefont {{King}},\ and\ \citenamefont {{Aurnou}}}]{stellmach&all2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {{Stellmach}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {{Lischper}}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {{Julien}}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {{Vasil}}},
  \bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont {{Cheng}}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {{Ribeiro}}}, \bibinfo {author}
  {\bibfnamefont {E.~M.}\ \bibnamefont {{King}}}, \ and\ \bibinfo {author}
  {\bibfnamefont {J.~M.}\ \bibnamefont {{Aurnou}}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {{Approaching the Asymptotic Regime of Rapidly
  Rotating Convection: Boundary Layers versus Interior Dynamics}},}\ }\href
  {\doibase 10.1103/PhysRevLett.113.254501} {\bibfield  {journal} {\bibinfo
  {journal} {\prl}\ }\textbf {\bibinfo {volume} {113}},\ \bibinfo {eid}
  {254501} (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1409.7432}
  {arXiv:1409.7432 [physics.flu-dyn]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2016)\citenamefont
  {{Burns}}, \citenamefont {{Vasil}}, \citenamefont {{Oishi}}, \citenamefont
  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {{Burns}}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {{Vasil}}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{Oishi}}}, \bibinfo
  {author} {\bibfnamefont {D.}~\bibnamefont {{Lecoanet}}}, \ and\ \bibinfo
  {author} {\bibfnamefont {B.}~\bibnamefont {{Brown}}},\ }\href@noop {}
  {\enquote {\bibinfo {title} {{Dedalus: Flexible framework for spectrally
  solving differential equations}},}\ }\bibinfo {howpublished} {Astrophysics
  Source Code Library} (\bibinfo {year} {2016}),\ \Eprint
  {http://arxiv.org/abs/1603.015} {ascl:1603.015} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2019)\citenamefont
  {{Burns}}, \citenamefont {{Vasil}}, \citenamefont {{Oishi}}, \citenamefont
  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Keaton~J.}\
  \bibnamefont {{Burns}}}, \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\
  \bibnamefont {{Vasil}}}, \bibinfo {author} {\bibfnamefont {Jeffrey~S.}\
  \bibnamefont {{Oishi}}}, \bibinfo {author} {\bibfnamefont {Daniel}\
  \bibnamefont {{Lecoanet}}}, \ and\ \bibinfo {author} {\bibfnamefont
  {Benjamin~P.}\ \bibnamefont {{Brown}}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {{Dedalus: A Flexible Framework for Numerical Simulations
  with Spectral Methods}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1905.10388}} (\bibinfo
  {year} {2019})},\ \Eprint {http://arxiv.org/abs/1905.10388} {arXiv:1905.10388
  [astro-ph.IM]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Ascher}}\ \emph {et~al.}(1997)\citenamefont
  {{Ascher}}, \citenamefont {{Ruuth}},\ and\ \citenamefont
  {{Spiteri}}}]{ascher&all1997}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.~M.}\ \bibnamefont
  {{Ascher}}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
  {{Ruuth}}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
  {{Spiteri}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Implicit-explicit Runge-Kutta methods for time-dependent partial
  differential equations}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Applied Numerical Mathematics}\ }\textbf {\bibinfo {volume}
  {25}},\ \bibinfo {pages} {151--167} (\bibinfo {year} {1997})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {{Anders}}\ \emph {et~al.}(2020)\citenamefont
  {{Anders}}, \citenamefont {{Vasil}}, \citenamefont {{Brown}},\ and\
  \citenamefont {{Korre}}}]{anders&all2020a_supp}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
  {{Anders}}}, \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\ \bibnamefont
  {{Vasil}}}, \bibinfo {author} {\bibfnamefont {Benjamin~P.}\ \bibnamefont
  {{Brown}}}, \ and\ \bibinfo {author} {\bibfnamefont {Lydia}\ \bibnamefont
  {{Korre}}},\ }\href {\doibase 10.5281/zenodo.3691954} {\enquote {\bibinfo
  {title} {{Supplemental Materials for "Convective dynamics with mixed
  temperature boundary conditions: why thermal relaxation matters and how to
  accelerate it"}},}\ } (\bibinfo {year} {2020})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Anders}}(2020)}]{code:boussinesq_convection}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
  {{Anders}}},\ }\href {\doibase 10.5281/zenodo.3690215} {\enquote {\bibinfo
  {title} {{evanhanders/boussinesq\_convection: Version of Code released with
  FT / TT paper (Anders+ 2020) submission.}}}\ } (\bibinfo {year}
  {2020})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Zhu}}\ \emph {et~al.}(2018)\citenamefont {{Zhu}},
  \citenamefont {{Mathai}}, \citenamefont {{Stevens}}, \citenamefont
  {{Verzicco}},\ and\ \citenamefont {{Lohse}}}]{zhu&all2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Xiaojue}\ \bibnamefont
  {{Zhu}}}, \bibinfo {author} {\bibfnamefont {Varghese}\ \bibnamefont
  {{Mathai}}}, \bibinfo {author} {\bibfnamefont {Richard J.~A.~M.}\
  \bibnamefont {{Stevens}}}, \bibinfo {author} {\bibfnamefont {Roberto}\
  \bibnamefont {{Verzicco}}}, \ and\ \bibinfo {author} {\bibfnamefont {Detlef}\
  \bibnamefont {{Lohse}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Transition to the Ultimate Regime in Two-Dimensional Rayleigh-B{\'e}nard
  Convection}},}\ }\href {\doibase 10.1103/PhysRevLett.120.144502} {\bibfield
  {journal} {\bibinfo  {journal} {\prl}\ }\textbf {\bibinfo {volume} {120}},\
  \bibinfo {eid} {144502} (\bibinfo {year} {2018})},\ \Eprint
  {http://arxiv.org/abs/1804.03914} {arXiv:1804.03914 [physics.flu-dyn]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Couston}}\ \emph {et~al.}(2019)\citenamefont
  {{Couston}}, \citenamefont {{Lecoanet}}, \citenamefont {{Favier}},\ and\
  \citenamefont {{Le Bars}}}]{couston&all2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Louis-Alexandre}\
  \bibnamefont {{Couston}}}, \bibinfo {author} {\bibfnamefont {Daniel}\
  \bibnamefont {{Lecoanet}}}, \bibinfo {author} {\bibfnamefont {Benjamin}\
  \bibnamefont {{Favier}}}, \ and\ \bibinfo {author} {\bibfnamefont {Michael}\
  \bibnamefont {{Le Bars}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Shape and size of large-scale vortices : a universal fluid pattern in
  geophysical fluid dynamics}},}\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1909.03244}}
  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1909.03244}
  {arXiv:1909.03244 [physics.flu-dyn]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Cheng}}\ \emph {et~al.}(2015)\citenamefont
  {{Cheng}}, \citenamefont {{Stellmach}}, \citenamefont {{Ribeiro}},
  \citenamefont {{Grannan}}, \citenamefont {{King}},\ and\ \citenamefont
  {{Aurnou}}}]{cheng&all2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
  {{Cheng}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {{Stellmach}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {{Ribeiro}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {{Grannan}}}, \bibinfo {author} {\bibfnamefont {E.~M.}\ \bibnamefont
  {{King}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
  {{Aurnou}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Laboratory-numerical models of rapidly rotating convection in planetary
  cores}},}\ }\href {\doibase 10.1093/gji/ggu480} {\bibfield  {journal}
  {\bibinfo  {journal} {Geophysical Journal International}\ }\textbf {\bibinfo
  {volume} {201}},\ \bibinfo {pages} {1--17} (\bibinfo {year}
  {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Julien}}\ \emph {et~al.}(2012)\citenamefont
  {{Julien}}, \citenamefont {{Knobloch}}, \citenamefont {{Rubio}},\ and\
  \citenamefont {{Vasil}}}]{julien&all2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Keith}\ \bibnamefont
  {{Julien}}}, \bibinfo {author} {\bibfnamefont {Edgar}\ \bibnamefont
  {{Knobloch}}}, \bibinfo {author} {\bibfnamefont {Antonio~M.}\ \bibnamefont
  {{Rubio}}}, \ and\ \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\
  \bibnamefont {{Vasil}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Heat Transport in Low-Rossby-Number Rayleigh-B{\'e}nard Convection}},}\
  }\href {\doibase 10.1103/PhysRevLett.109.254503} {\bibfield  {journal}
  {\bibinfo  {journal} {\prl}\ }\textbf {\bibinfo {volume} {109}},\ \bibinfo
  {eid} {254503} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Clarkson}}\ \emph {et~al.}(2018)\citenamefont
  {{Clarkson}}, \citenamefont {{Herwig}},\ and\ \citenamefont
  {{Pignatari}}}]{clarkson&all2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {{Clarkson}}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {{Herwig}}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {{Pignatari}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Pop III
  i-process nucleosynthesis and the elemental abundances of SMSS J0313-6708 and
  the most iron-poor stars}},}\ }\href {\doibase 10.1093/mnrasl/slx190}
  {\bibfield  {journal} {\bibinfo  {journal} {\mnras}\ }\textbf {\bibinfo
  {volume} {474}},\ \bibinfo {pages} {L37--L41} (\bibinfo {year} {2018})},\
  \Eprint {http://arxiv.org/abs/1710.01763} {arXiv:1710.01763 [astro-ph.SR]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Andrassy}}\ \emph {et~al.}(2020)\citenamefont
  {{Andrassy}}, \citenamefont {{Herwig}}, \citenamefont {{Woodward}},\ and\
  \citenamefont {{Ritter}}}]{andrassy&all2020}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {{Andrassy}}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {{Herwig}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {{Woodward}}}, \ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {{Ritter}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{3D
  hydrodynamic simulations of C ingestion into a convective O shell}},}\ }\href
  {\doibase 10.1093/mnras/stz2952} {\bibfield  {journal} {\bibinfo  {journal}
  {\mnras}\ }\textbf {\bibinfo {volume} {491}},\ \bibinfo {pages} {972--992}
  (\bibinfo {year} {2020})},\ \Eprint {http://arxiv.org/abs/1808.04014}
  {arXiv:1808.04014 [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Brummell}}\ \emph {et~al.}(2002)\citenamefont
  {{Brummell}}, \citenamefont {{Clune}},\ and\ \citenamefont
  {{Toomre}}}]{brummell&all2002}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nicholas~H.}\
  \bibnamefont {{Brummell}}}, \bibinfo {author} {\bibfnamefont {Thomas~L.}\
  \bibnamefont {{Clune}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Penetration and Overshooting in Turbulent Compressible Convection}},}\
  }\href {\doibase 10.1086/339626} {\bibfield  {journal} {\bibinfo  {journal}
  {\apj}\ }\textbf {\bibinfo {volume} {570}},\ \bibinfo {pages} {825--854}
  (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Pratt}}\ \emph {et~al.}(2017)\citenamefont
  {{Pratt}}, \citenamefont {{Baraffe}}, \citenamefont {{Goffrey}},
  \citenamefont {{Constantino}}, \citenamefont {{Viallet}}, \citenamefont
  {{Popov}}, \citenamefont {{Walder}},\ and\ \citenamefont
  {{Folini}}}]{pratt&all2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {{Pratt}}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {{Baraffe}}},
  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {{Goffrey}}}, \bibinfo
  {author} {\bibfnamefont {T.}~\bibnamefont {{Constantino}}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {{Viallet}}}, \bibinfo {author}
  {\bibfnamefont {M.~V.}\ \bibnamefont {{Popov}}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {{Walder}}}, \ and\ \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {{Folini}}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {{Extreme value statistics for two-dimensional convective
  penetration in a pre-main sequence star}},}\ }\href {\doibase
  10.1051/0004-6361/201630362} {\bibfield  {journal} {\bibinfo  {journal}
  {Astronomy \& Astrophysics}\ }\textbf {\bibinfo {volume} {604}},\ \bibinfo
  {eid} {A125} (\bibinfo {year} {2017})},\ \Eprint
  {http://arxiv.org/abs/1706.04852} {arXiv:1706.04852 [astro-ph.SR]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Brown}}\ \emph {et~al.}(2010)\citenamefont
  {{Brown}}, \citenamefont {{Browning}}, \citenamefont {{Brun}}, \citenamefont
  {{Miesch}},\ and\ \citenamefont {{Toomre}}}]{brown&all2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Benjamin~P.}\
  \bibnamefont {{Brown}}}, \bibinfo {author} {\bibfnamefont {Matthew~K.}\
  \bibnamefont {{Browning}}}, \bibinfo {author} {\bibfnamefont {Allan~Sacha}\
  \bibnamefont {{Brun}}}, \bibinfo {author} {\bibfnamefont {Mark~S.}\
  \bibnamefont {{Miesch}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Persistent Magnetic Wreaths in a Rapidly Rotating Sun}},}\ }\href {\doibase
  10.1088/0004-637X/711/1/424} {\bibfield  {journal} {\bibinfo  {journal}
  {\apj}\ }\textbf {\bibinfo {volume} {711}},\ \bibinfo {pages} {424--438}
  (\bibinfo {year} {2010})},\ \Eprint {http://arxiv.org/abs/1011.2831}
  {arXiv:1011.2831 [astro-ph.SR]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Yadav}}\ \emph {et~al.}(2016)\citenamefont
  {{Yadav}}, \citenamefont {{Christensen}}, \citenamefont {{Wolk}},\ and\
  \citenamefont {{Poppenhaeger}}}]{yadav&all2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Rakesh~K.}\
  \bibnamefont {{Yadav}}}, \bibinfo {author} {\bibfnamefont {Ulrich~R.}\
  \bibnamefont {{Christensen}}}, \bibinfo {author} {\bibfnamefont {Scott~J.}\
  \bibnamefont {{Wolk}}}, \ and\ \bibinfo {author} {\bibfnamefont {Katja}\
  \bibnamefont {{Poppenhaeger}}},\ }\bibfield  {title} {\enquote {\bibinfo
  {title} {{Magnetic Cycles in a Dynamo Simulation of Fully Convective M-star
  Proxima Centauri}},}\ }\href {\doibase 10.3847/2041-8213/833/2/L28}
  {\bibfield  {journal} {\bibinfo  {journal} {\apjl}\ }\textbf {\bibinfo
  {volume} {833}},\ \bibinfo {eid} {L28} (\bibinfo {year} {2016})},\ \Eprint
  {http://arxiv.org/abs/1610.02721} {arXiv:1610.02721 [astro-ph.SR]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Strugarek}}\ \emph {et~al.}(2017)\citenamefont
  {{Strugarek}}, \citenamefont {{Beaudoin}}, \citenamefont {{Charbonneau}},
  \citenamefont {{Brun}},\ and\ \citenamefont {{do
  Nascimento}}}]{strugarek&all2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {{Strugarek}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {{Beaudoin}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {{Charbonneau}}}, \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
  {{Brun}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont {{do
  Nascimento}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Reconciling
  solar and stellar magnetic cycles with nonlinear dynamo simulations}},}\
  }\href {\doibase 10.1126/science.aal3999} {\bibfield  {journal} {\bibinfo
  {journal} {Science}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
  {185--187} (\bibinfo {year} {2017})},\ \Eprint
  {http://arxiv.org/abs/1707.04335} {arXiv:1707.04335 [astro-ph.SR]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Strugarek}}\ \emph {et~al.}(2018)\citenamefont
  {{Strugarek}}, \citenamefont {{Beaudoin}}, \citenamefont {{Charbonneau}},\
  and\ \citenamefont {{Brun}}}]{strugarek&all2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {{Strugarek}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {{Beaudoin}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {{Charbonneau}}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~S.}\
  \bibnamefont {{Brun}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On
  the Sensitivity of Magnetic Cycles in Global Simulations of Solar-like
  Stars}},}\ }\href {\doibase 10.3847/1538-4357/aacf9e} {\bibfield  {journal}
  {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {863}},\ \bibinfo
  {eid} {35} (\bibinfo {year} {2018})},\ \Eprint
  {http://arxiv.org/abs/1806.09484} {arXiv:1806.09484 [astro-ph.SR]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Bordwell}}\ \emph {et~al.}(2018)\citenamefont
  {{Bordwell}}, \citenamefont {{Brown}},\ and\ \citenamefont
  {{Oishi}}}]{bordwell&all2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Baylee}\ \bibnamefont
  {{Bordwell}}}, \bibinfo {author} {\bibfnamefont {Benjamin~P.}\ \bibnamefont
  {{Brown}}}, \ and\ \bibinfo {author} {\bibfnamefont {Jeffrey~S.}\
  \bibnamefont {{Oishi}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Convective Dynamics and Disequilibrium Chemistry in the Atmospheres of
  Giant Planets and Brown Dwarfs}},}\ }\href {\doibase
  10.3847/1538-4357/aaa551} {\bibfield  {journal} {\bibinfo  {journal} {\apj}\
  }\textbf {\bibinfo {volume} {854}},\ \bibinfo {eid} {8} (\bibinfo {year}
  {2018})},\ \Eprint {http://arxiv.org/abs/1802.03026} {arXiv:1802.03026
  [astro-ph.EP]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {{Matilsky}}\ \emph {et~al.}(2019)\citenamefont
  {{Matilsky}}, \citenamefont {{Hindman}},\ and\ \citenamefont
  {{Toomre}}}]{matilsky&all2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Loren~I.}\
  \bibnamefont {{Matilsky}}}, \bibinfo {author} {\bibfnamefont {Bradley~W.}\
  \bibnamefont {{Hindman}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{The Role of Downflows in Establishing Solar Near-surface Shear}},}\ }\href
  {\doibase 10.3847/1538-4357/aaf647} {\bibfield  {journal} {\bibinfo
  {journal} {\apj}\ }\textbf {\bibinfo {volume} {871}},\ \bibinfo {eid} {217}
  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1810.00115}
  {arXiv:1810.00115 [astro-ph.SR]} \BibitemShut {NoStop}%
\end{thebibliography}%

\end{document}

### 2020-05-20 submission2_tex/redline/mixedft_evolution_ms_redline.tex
redline ms file for submission 2 is ready

--- 2020-05-20 tex/mixedft_evolution_ms.tex
@@
 \newcommand\apjl{{The Astrophysical Journal Letters}}%
+
+\graphicspath{{../}}
 
@@
 \begin{figure}[p!]
-\includegraphics[width=\textwidth]{./figs/rbc_evolution_dynamics.pdf}
+\includegraphics[width=\textwidth]{./rbc_evolution_dynamics.pdf}
 \caption{ 
@@
 \begin{figure}[t!]
-\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
+\includegraphics[width=\textwidth]{./rbc_scalar_comparisons.pdf}
 \caption{ 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
+\includegraphics[width=\textwidth]{./rbc_restart_description.pdf}
 \caption{ 
@@
 \begin{figure}[p!]
-\includegraphics[width=\textwidth]{./figs/rbc_3D_panels.pdf}
+\includegraphics[width=\textwidth]{./rbc_3D_panels.pdf}
 \caption{ 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
+\includegraphics[width=\textwidth]{./rbc_1D_profiles.pdf}
 \caption{ 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{./figs/rbc_dynamics_asymmetries.pdf}
+\includegraphics[width=\textwidth]{./rbc_dynamics_asymmetries.pdf}
 \caption{ 
@@
 \begin{figure}[t!]
-\includegraphics[width=\textwidth]{./figs/rotating_panels.pdf}
+\includegraphics[width=\textwidth]{./rotating_panels.pdf}
 \caption{ 
@@
 \end{acknowledgments}
-
-\bibliography{biblio.bib}
 
@@
 
+\begin{thebibliography}{51}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {{Spiegel}}\ and\ \citenamefont
+  {{Veronis}}(1960)}]{spiegel&veronis1960}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~A.}\ \bibnamefont
+  {{Spiegel}}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {{Veronis}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On the
+  Boussinesq Approximation for a Compressible Fluid.}}}\ }\href {\doibase
+  10.1086/146849} {\bibfield  {journal} {\bibinfo  {journal} {\apj}\ }\textbf
+  {\bibinfo {volume} {131}},\ \bibinfo {pages} {442} (\bibinfo {year}
+  {1960})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ahlers}\ \emph {et~al.}(2009)\citenamefont {Ahlers},
+  \citenamefont {Grossmann},\ and\ \citenamefont {Lohse}}]{ahlers&all2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Guenter}\ \bibnamefont
+  {Ahlers}}, \bibinfo {author} {\bibfnamefont {Siegfried}\ \bibnamefont
+  {Grossmann}}, \ and\ \bibinfo {author} {\bibfnamefont {Detlef}\ \bibnamefont
+  {Lohse}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Heat transfer and
+  large scale dynamics in turbulent rayleigh-b\'enard convection},}\ }\href
+  {\doibase 10.1103/RevModPhys.81.503} {\bibfield  {journal} {\bibinfo
+  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {503--537} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Plumley}}\ and\ \citenamefont
+  {{Julien}}(2019)}]{plumley&julien2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Meredith}\
+  \bibnamefont {{Plumley}}}\ and\ \bibinfo {author} {\bibfnamefont {Keith}\
+  \bibnamefont {{Julien}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Scaling Laws in Rayleigh-B{\'e}nard Convection}},}\ }\href {\doibase
+  10.1029/2019EA000583} {\bibfield  {journal} {\bibinfo  {journal} {Earth and
+  Space Science}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
+  {1580--1592} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Charbonneau}}(2014)}]{charbonneau2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Paul}\ \bibnamefont
+  {{Charbonneau}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Solar
+  Dynamo Theory}},}\ }\href {\doibase 10.1146/annurev-astro-081913-040012}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Astronomy and
+  Astrophysics}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages}
+  {251--290} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Toomre}}(2019)}]{toomre2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Some travels
+  in the land of nonlinear convection and magnetism}},}\ }in\ \href {\doibase
+  10.1051/eas/1982027} {\emph {\bibinfo {booktitle} {EAS Publications
+  Series}}},\ \bibinfo {series} {EAS Publications Series}, Vol.~\bibinfo
+  {volume} {82}\ (\bibinfo {year} {2019})\ pp.\ \bibinfo {pages}
+  {273--294}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Goluskin}}(2016)}]{goluskin2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {David}\ \bibnamefont
+  {{Goluskin}}},\ }\href {\doibase 10.1007/978-3-319-23941-5} {\emph {\bibinfo
+  {title} {{Internally heated convection and Rayleigh-B{\'e}nard
+  convection}}}}\ (\bibinfo  {publisher} {Springer International Publishing},\
+  \bibinfo {year} {2016})\ p.\ \bibinfo {pages} {arXiv:1506.01656},\ \Eprint
+  {http://arxiv.org/abs/1506.01656} {arXiv:1506.01656 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Glatzmaier}}\ and\ \citenamefont
+  {{Gilman}}(1982)}]{glatzmaier&gilman1982}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~A.}\ \bibnamefont
+  {{Glatzmaier}}}\ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
+  {{Gilman}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Compressible
+  convection in a rotating spherical shell. V - Induced differential rotation
+  and meridional circulation}},}\ }\href {\doibase 10.1086/159909} {\bibfield
+  {journal} {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {256}},\
+  \bibinfo {pages} {316--330} (\bibinfo {year} {1982})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Hurlburt}}\ \emph {et~al.}(1986)\citenamefont
+  {{Hurlburt}}, \citenamefont {{Toomre}},\ and\ \citenamefont
+  {{Massaguer}}}]{hurlburt&all1986}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
+  {{Hurlburt}}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {{Toomre}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {{Massaguer}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Nonlinear
+  compressible convection penetrating into stable layers and producing internal
+  gravity waves}},}\ }\href {\doibase 10.1086/164796} {\bibfield  {journal}
+  {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {311}},\ \bibinfo
+  {pages} {563--577} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Cattaneo}}\ \emph {et~al.}(1990)\citenamefont
+  {{Cattaneo}}, \citenamefont {{Hurlburt}},\ and\ \citenamefont
+  {{Toomre}}}]{cattaneo&all1990}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {{Cattaneo}}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
+  {{Hurlburt}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Supersonic
+  convection}},}\ }\href {\doibase 10.1086/185652} {\bibfield  {journal}
+  {\bibinfo  {journal} {Astrophys. J. Lett.}\ }\textbf {\bibinfo {volume}
+  {349}},\ \bibinfo {pages} {L63--L66} (\bibinfo {year} {1990})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {{Featherstone}}\ and\ \citenamefont
+  {{Hindman}}(2016)}]{featherstone&hindman2016a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nicholas~A.}\
+  \bibnamefont {{Featherstone}}}\ and\ \bibinfo {author} {\bibfnamefont
+  {Bradley~W.}\ \bibnamefont {{Hindman}}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{The Spectral Amplitude of Stellar Convection and Its
+  Scaling in the High-Rayleigh-number Regime}},}\ }\href {\doibase
+  10.3847/0004-637X/818/1/32} {\bibfield  {journal} {\bibinfo  {journal}
+  {\apj}\ }\textbf {\bibinfo {volume} {818}},\ \bibinfo {eid} {32} (\bibinfo
+  {year} {2016})},\ \Eprint {http://arxiv.org/abs/1511.02396} {arXiv:1511.02396
+  [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Korre}}\ \emph {et~al.}(2019)\citenamefont
+  {{Korre}}, \citenamefont {{Garaud}},\ and\ \citenamefont
+  {{Brummell}}}]{korre&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {{Korre}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {{Garaud}}}, \
+  and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {{Brummell}}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {{Convective overshooting and
+  penetration in a Boussinesq spherical shell}},}\ }\href {\doibase
+  10.1093/mnras/stz047} {\bibfield  {journal} {\bibinfo  {journal} {\mnras}\
+  }\textbf {\bibinfo {volume} {484}},\ \bibinfo {pages} {1220--1237} (\bibinfo
+  {year} {2019})},\ \Eprint {http://arxiv.org/abs/1810.06700} {arXiv:1810.06700
+  [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Wood}}\ and\ \citenamefont
+  {{Brummell}}(2018)}]{wood&brummell2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~S.}\ \bibnamefont
+  {{Wood}}}\ and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
+  {{Brummell}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{A
+  Self-consistent Model of the Solar Tachocline}},}\ }\href {\doibase
+  10.3847/1538-4357/aaa6d5} {\bibfield  {journal} {\bibinfo  {journal} {\apj}\
+  }\textbf {\bibinfo {volume} {853}},\ \bibinfo {eid} {97} (\bibinfo {year}
+  {2018})},\ \Eprint {http://arxiv.org/abs/1801.02565} {arXiv:1801.02565
+  [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{K{\"a}pyl{\"a}}}\ \emph {et~al.}(2019)\citenamefont
+  {{K{\"a}pyl{\"a}}}, \citenamefont {{Viviani}}, \citenamefont
+  {{K{\"a}pyl{\"a}}}, \citenamefont {{Brandenburg}},\ and\ \citenamefont
+  {{Spada}}}]{kapyla&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont
+  {{K{\"a}pyl{\"a}}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {{Viviani}}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {{K{\"a}pyl{\"a}}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Brandenburg}}}, \ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {{Spada}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Effects of a
+  subadiabatic layer on convection and dynamos in spherical wedge
+  simulations}},}\ }\href {\doibase 10.1080/03091929.2019.1571584} {\bibfield
+  {journal} {\bibinfo  {journal} {Geophysical and Astrophysical Fluid
+  Dynamics}\ }\textbf {\bibinfo {volume} {113}},\ \bibinfo {pages} {149--183}
+  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1803.05898}
+  {arXiv:1803.05898 [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Matilsky}}\ \emph {et~al.}(2019)\citenamefont
+  {{Matilsky}}, \citenamefont {{Hindman}},\ and\ \citenamefont
+  {{Toomre}}}]{matilsky&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Loren~I.}\
+  \bibnamefont {{Matilsky}}}, \bibinfo {author} {\bibfnamefont {Bradley~W.}\
+  \bibnamefont {{Hindman}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
+  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{The Role of Downflows in Establishing Solar Near-surface Shear}},}\ }\href
+  {\doibase 10.3847/1538-4357/aaf647} {\bibfield  {journal} {\bibinfo
+  {journal} {\apj}\ }\textbf {\bibinfo {volume} {871}},\ \bibinfo {eid} {217}
+  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1810.00115}
+  {arXiv:1810.00115 [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Ishiwatari}}\ \emph {et~al.}(1994)\citenamefont
+  {{Ishiwatari}}, \citenamefont {{Takehiro}},\ and\ \citenamefont
+  {{Hayashi}}}]{ishiwatari&all1994}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {{Ishiwatari}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {{Takehiro}}}, \ and\ \bibinfo {author} {\bibfnamefont {Y.~Y.}\ \bibnamefont
+  {{Hayashi}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The effects
+  of thermal conditions on the cell sizes of two-dimensional convection}},}\
+  }\href {\doibase 10.1017/S0022112094003022} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {281}},\
+  \bibinfo {pages} {33--50} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Otero}}\ \emph {et~al.}(2002)\citenamefont
+  {{Otero}}, \citenamefont {{Wittenberg}}, \citenamefont {{Worthing}},\ and\
+  \citenamefont {{Doering}}}]{otero&all2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {{Otero}}}, \bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont
+  {{Wittenberg}}}, \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+  {{Worthing}}}, \ and\ \bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
+  {{Doering}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Bounds on
+  Rayleigh B{\'e}nard convection with an imposed heat flux}},}\ }\href
+  {\doibase 10.1017/S0022112002002410} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {473}},\ \bibinfo
+  {pages} {191--199} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Chapman}}\ and\ \citenamefont
+  {{Proctor}}(1980)}]{chapman&proctor1980}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {{Chapman}}}\ and\ \bibinfo {author} {\bibfnamefont {M.~R.~E.}\ \bibnamefont
+  {{Proctor}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Nonlinear
+  Rayleigh-Benard convection between poorly conducting boundaries}},}\ }\href
+  {\doibase 10.1017/S0022112080001917} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {101}},\
+  \bibinfo {pages} {759--782} (\bibinfo {year} {1980})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Johnston}}\ and\ \citenamefont
+  {{Doering}}(2009)}]{johnston&doering2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {{Johnston}}}\ and\ \bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
+  {{Doering}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Comparison
+  of Turbulent Thermal Convection between Conditions of Constant Temperature
+  and Constant Flux}},}\ }\href {\doibase 10.1103/PhysRevLett.102.064501}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {eid} {064501} (\bibinfo {year}
+  {2009})},\ \Eprint {http://arxiv.org/abs/0811.0401} {arXiv:0811.0401
+  [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Anders}\ \emph {et~al.}(2018)\citenamefont {Anders},
+  \citenamefont {Brown},\ and\ \citenamefont {Oishi}}]{anders&all2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
+  {Anders}}, \bibinfo {author} {\bibfnamefont {Benjamin~P.}\ \bibnamefont
+  {Brown}}, \ and\ \bibinfo {author} {\bibfnamefont {Jeffrey~S.}\ \bibnamefont
+  {Oishi}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Accelerated
+  evolution of convective simulations},}\ }\href {\doibase
+  10.1103/PhysRevFluids.3.083502} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages}
+  {083502} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Julien}}\ \emph {et~al.}(1996)\citenamefont
+  {{Julien}}, \citenamefont {{Legg}}, \citenamefont {{McWilliams}},\ and\
+  \citenamefont {{Werne}}}]{julien&all1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {{Julien}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {{Legg}}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{McWilliams}}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{Werne}}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {{Rapidly rotating turbulent
+  Rayleigh-Benard convection}},}\ }\href {\doibase 10.1017/S0022112096002789}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid Mechanics}\
+  }\textbf {\bibinfo {volume} {322}},\ \bibinfo {pages} {243--273} (\bibinfo
+  {year} {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Stellmach}}\ \emph {et~al.}(2014)\citenamefont
+  {{Stellmach}}, \citenamefont {{Lischper}}, \citenamefont {{Julien}},
+  \citenamefont {{Vasil}}, \citenamefont {{Cheng}}, \citenamefont {{Ribeiro}},
+  \citenamefont {{King}},\ and\ \citenamefont {{Aurnou}}}]{stellmach&all2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {{Stellmach}}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {{Lischper}}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {{Julien}}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {{Vasil}}},
+  \bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont {{Cheng}}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {{Ribeiro}}}, \bibinfo {author}
+  {\bibfnamefont {E.~M.}\ \bibnamefont {{King}}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.~M.}\ \bibnamefont {{Aurnou}}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {{Approaching the Asymptotic Regime of Rapidly
+  Rotating Convection: Boundary Layers versus Interior Dynamics}},}\ }\href
+  {\doibase 10.1103/PhysRevLett.113.254501} {\bibfield  {journal} {\bibinfo
+  {journal} {\prl}\ }\textbf {\bibinfo {volume} {113}},\ \bibinfo {eid}
+  {254501} (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1409.7432}
+  {arXiv:1409.7432 [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2016)\citenamefont
+  {{Burns}}, \citenamefont {{Vasil}}, \citenamefont {{Oishi}}, \citenamefont
+  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {{Burns}}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {{Vasil}}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {{Oishi}}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {{Lecoanet}}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {{Brown}}},\ }\href@noop {}
+  {\enquote {\bibinfo {title} {{Dedalus: Flexible framework for spectrally
+  solving differential equations}},}\ }\bibinfo {howpublished} {Astrophysics
+  Source Code Library} (\bibinfo {year} {2016}),\ \Eprint
+  {http://arxiv.org/abs/1603.015} {ascl:1603.015} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2019)\citenamefont
+  {{Burns}}, \citenamefont {{Vasil}}, \citenamefont {{Oishi}}, \citenamefont
+  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Keaton~J.}\
+  \bibnamefont {{Burns}}}, \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\
+  \bibnamefont {{Vasil}}}, \bibinfo {author} {\bibfnamefont {Jeffrey~S.}\
+  \bibnamefont {{Oishi}}}, \bibinfo {author} {\bibfnamefont {Daniel}\
+  \bibnamefont {{Lecoanet}}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {Benjamin~P.}\ \bibnamefont {{Brown}}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Dedalus: A Flexible Framework for Numerical Simulations
+  with Spectral Methods}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1905.10388}} (\bibinfo
+  {year} {2019})},\ \Eprint {http://arxiv.org/abs/1905.10388} {arXiv:1905.10388
+  [astro-ph.IM]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Ascher}}\ \emph {et~al.}(1997)\citenamefont
+  {{Ascher}}, \citenamefont {{Ruuth}},\ and\ \citenamefont
+  {{Spiteri}}}]{ascher&all1997}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.~M.}\ \bibnamefont
+  {{Ascher}}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+  {{Ruuth}}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {{Spiteri}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Implicit-explicit Runge-Kutta methods for time-dependent partial
+  differential equations}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Applied Numerical Mathematics}\ }\textbf {\bibinfo {volume}
+  {25}},\ \bibinfo {pages} {151--167} (\bibinfo {year} {1997})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {{Anders}}\ \emph {et~al.}(2020)\citenamefont
+  {{Anders}}, \citenamefont {{Vasil}}, \citenamefont {{Brown}},\ and\
+  \citenamefont {{Korre}}}]{anders&all2020a_supp}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
+  {{Anders}}}, \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\ \bibnamefont
+  {{Vasil}}}, \bibinfo {author} {\bibfnamefont {Benjamin~P.}\ \bibnamefont
+  {{Brown}}}, \ and\ \bibinfo {author} {\bibfnamefont {Lydia}\ \bibnamefont
+  {{Korre}}},\ }\href {\doibase 10.5281/zenodo.3691954} {\enquote {\bibinfo
+  {title} {{Supplemental Materials for "Convective dynamics with mixed
+  temperature boundary conditions: why thermal relaxation matters and how to
+  accelerate it"}},}\ } (\bibinfo {year} {2020})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Anders}}(2020)}]{code:boussinesq_convection}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Evan~H.}\ \bibnamefont
+  {{Anders}}},\ }\href {\doibase 10.5281/zenodo.3690215} {\enquote {\bibinfo
+  {title} {{evanhanders/boussinesq\_convection: Version of Code released with
+  FT / TT paper (Anders+ 2020) submission.}}}\ } (\bibinfo {year}
+  {2020})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Calkins}}\ \emph {et~al.}(2015)\citenamefont
+  {{Calkins}}, \citenamefont {{Hale}}, \citenamefont {{Julien}}, \citenamefont
+  {{Nieves}}, \citenamefont {{Driggs}},\ and\ \citenamefont
+  {{Marti}}}]{calkins&all2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~A.}\
+  \bibnamefont {{Calkins}}}, \bibinfo {author} {\bibfnamefont {Kevin}\
+  \bibnamefont {{Hale}}}, \bibinfo {author} {\bibfnamefont {Keith}\
+  \bibnamefont {{Julien}}}, \bibinfo {author} {\bibfnamefont {David}\
+  \bibnamefont {{Nieves}}}, \bibinfo {author} {\bibfnamefont {Derek}\
+  \bibnamefont {{Driggs}}}, \ and\ \bibinfo {author} {\bibfnamefont {Philippe}\
+  \bibnamefont {{Marti}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{The asymptotic equivalence of fixed heat flux and fixed temperature thermal
+  boundary conditions for rapidly rotating convection}},}\ }\href {\doibase
+  10.1017/jfm.2015.606} {\bibfield  {journal} {\bibinfo  {journal} {Journal of
+  Fluid Mechanics}\ }\textbf {\bibinfo {volume} {784}},\ \bibinfo {eid} {R2}
+  (\bibinfo {year} {2015})},\ \Eprint {http://arxiv.org/abs/1507.07168}
+  {arXiv:1507.07168 [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Zhu}}\ \emph {et~al.}(2018)\citenamefont {{Zhu}},
+  \citenamefont {{Mathai}}, \citenamefont {{Stevens}}, \citenamefont
+  {{Verzicco}},\ and\ \citenamefont {{Lohse}}}]{zhu&all2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Xiaojue}\ \bibnamefont
+  {{Zhu}}}, \bibinfo {author} {\bibfnamefont {Varghese}\ \bibnamefont
+  {{Mathai}}}, \bibinfo {author} {\bibfnamefont {Richard J.~A.~M.}\
+  \bibnamefont {{Stevens}}}, \bibinfo {author} {\bibfnamefont {Roberto}\
+  \bibnamefont {{Verzicco}}}, \ and\ \bibinfo {author} {\bibfnamefont {Detlef}\
+  \bibnamefont {{Lohse}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Transition to the Ultimate Regime in Two-Dimensional Rayleigh-B{\'e}nard
+  Convection}},}\ }\href {\doibase 10.1103/PhysRevLett.120.144502} {\bibfield
+  {journal} {\bibinfo  {journal} {\prl}\ }\textbf {\bibinfo {volume} {120}},\
+  \bibinfo {eid} {144502} (\bibinfo {year} {2018})},\ \Eprint
+  {http://arxiv.org/abs/1804.03914} {arXiv:1804.03914 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{King}}\ \emph {et~al.}(2009)\citenamefont {{King}},
+  \citenamefont {{Stellmach}}, \citenamefont {{Noir}}, \citenamefont
+  {{Hansen}},\ and\ \citenamefont {{Aurnou}}}]{king&all2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Eric~M.}\ \bibnamefont
+  {{King}}}, \bibinfo {author} {\bibfnamefont {Stephan}\ \bibnamefont
+  {{Stellmach}}}, \bibinfo {author} {\bibfnamefont {Jerome}\ \bibnamefont
+  {{Noir}}}, \bibinfo {author} {\bibfnamefont {Ulrich}\ \bibnamefont
+  {{Hansen}}}, \ and\ \bibinfo {author} {\bibfnamefont {Jonathan~M.}\
+  \bibnamefont {{Aurnou}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Boundary layer control of rotating convection systems}},}\ }\href {\doibase
+  10.1038/nature07647} {\bibfield  {journal} {\bibinfo  {journal} {\nat}\
+  }\textbf {\bibinfo {volume} {457}},\ \bibinfo {pages} {301--304} (\bibinfo
+  {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Schmitz}}\ and\ \citenamefont
+  {{Tilgner}}(2009)}]{schmitz&tilgner2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {{Schmitz}}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Tilgner}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Heat
+  transport in rotating convection without Ekman layers}},}\ }\href {\doibase
+  10.1103/PhysRevE.80.015305} {\bibfield  {journal} {\bibinfo  {journal}
+  {\pre}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {eid} {015305} (\bibinfo
+  {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Zhong}}\ and\ \citenamefont
+  {{Ahlers}}(2010)}]{zhong&ahlers2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jin-Qiang}\
+  \bibnamefont {{Zhong}}}\ and\ \bibinfo {author} {\bibfnamefont {Guenter}\
+  \bibnamefont {{Ahlers}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Heat transport and the large-scale circulation in rotating turbulent
+  Rayleigh-B{\'e}nard convection}},}\ }\href {\doibase
+  10.1017/S002211201000399X} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {665}},\ \bibinfo
+  {pages} {300--333} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Julien}}\ \emph {et~al.}(2012)\citenamefont
+  {{Julien}}, \citenamefont {{Knobloch}}, \citenamefont {{Rubio}},\ and\
+  \citenamefont {{Vasil}}}]{julien&all2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Keith}\ \bibnamefont
+  {{Julien}}}, \bibinfo {author} {\bibfnamefont {Edgar}\ \bibnamefont
+  {{Knobloch}}}, \bibinfo {author} {\bibfnamefont {Antonio~M.}\ \bibnamefont
+  {{Rubio}}}, \ and\ \bibinfo {author} {\bibfnamefont {Geoffrey~M.}\
+  \bibnamefont {{Vasil}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Heat Transport in Low-Rossby-Number Rayleigh-B{\'e}nard Convection}},}\
+  }\href {\doibase 10.1103/PhysRevLett.109.254503} {\bibfield  {journal}
+  {\bibinfo  {journal} {\prl}\ }\textbf {\bibinfo {volume} {109}},\ \bibinfo
+  {eid} {254503} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Stevens}}\ \emph {et~al.}(2013)\citenamefont
+  {{Stevens}}, \citenamefont {{Clercx}},\ and\ \citenamefont
+  {{Lohse}}}]{stevens&all2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Richard J.~A.~M.}\
+  \bibnamefont {{Stevens}}}, \bibinfo {author} {\bibfnamefont {Herman J.~H.}\
+  \bibnamefont {{Clercx}}}, \ and\ \bibinfo {author} {\bibfnamefont {Detlef}\
+  \bibnamefont {{Lohse}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Heat transport and flow structure in rotating Rayleigh-B{\'e}nard
+  convection}},}\ }\href {\doibase 10.1016/j.euromechflu.2013.01.004}
+  {\bibfield  {journal} {\bibinfo  {journal} {European Journal of Mechanics B
+  Fluids}\ }\textbf {\bibinfo {volume} {40}},\ \bibinfo {pages} {41--49}
+  (\bibinfo {year} {2013})},\ \Eprint {http://arxiv.org/abs/1204.3396}
+  {arXiv:1204.3396 [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Ecke}}(2015)}]{ecke2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Robert~E.}\
+  \bibnamefont {{Ecke}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Scaling of heat transport near onset in rapidly rotating convection}},}\
+  }\href {\doibase 10.1016/j.physleta.2015.06.053} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physics Letters A}\ }\textbf {\bibinfo {volume}
+  {379}},\ \bibinfo {pages} {2221--2223} (\bibinfo {year} {2015})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {{Grooms}}(2015)}]{grooms2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ian}\ \bibnamefont
+  {{Grooms}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Asymptotic
+  behavior of heat transport for a class of exact solutions in rotating
+  Rayleigh-B{\'e}nard convection}},}\ }\href {\doibase
+  10.1080/03091929.2015.1036054} {\bibfield  {journal} {\bibinfo  {journal}
+  {Geophysical and Astrophysical Fluid Dynamics}\ }\textbf {\bibinfo {volume}
+  {109}},\ \bibinfo {pages} {145--158} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1403.0658} {arXiv:1403.0658 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Grooms}}\ and\ \citenamefont
+  {{Whitehead}}(2015)}]{grooms&whitehead2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ian}\ \bibnamefont
+  {{Grooms}}}\ and\ \bibinfo {author} {\bibfnamefont {Jared~P.}\ \bibnamefont
+  {{Whitehead}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Bounds on
+  heat transport in rapidly rotating Rayleigh-B{\'e}nard convection}},}\ }\href
+  {\doibase 10.1088/0951-7715/28/1/29} {\bibfield  {journal} {\bibinfo
+  {journal} {Nonlinearity}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo {eid}
+  {29} (\bibinfo {year} {2015})},\ \Eprint {http://arxiv.org/abs/1405.1458}
+  {arXiv:1405.1458 [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Rubio}}\ \emph {et~al.}(2014)\citenamefont
+  {{Rubio}}, \citenamefont {{Julien}}, \citenamefont {{Knobloch}},\ and\
+  \citenamefont {{Weiss}}}]{rubio&all2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Antonio~M.}\
+  \bibnamefont {{Rubio}}}, \bibinfo {author} {\bibfnamefont {Keith}\
+  \bibnamefont {{Julien}}}, \bibinfo {author} {\bibfnamefont {Edgar}\
+  \bibnamefont {{Knobloch}}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {Jeffrey~B.}\ \bibnamefont {{Weiss}}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Upscale Energy Transfer in Three-Dimensional Rapidly
+  Rotating Turbulent Convection}},}\ }\href {\doibase
+  10.1103/PhysRevLett.112.144501} {\bibfield  {journal} {\bibinfo  {journal}
+  {\prl}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo {eid} {144501}
+  (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Guervilly}}\ \emph {et~al.}(2014)\citenamefont
+  {{Guervilly}}, \citenamefont {{Hughes}},\ and\ \citenamefont
+  {{Jones}}}]{guervilly&all2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C{\'e}line}\
+  \bibnamefont {{Guervilly}}}, \bibinfo {author} {\bibfnamefont {David~W.}\
+  \bibnamefont {{Hughes}}}, \ and\ \bibinfo {author} {\bibfnamefont {Chris~A.}\
+  \bibnamefont {{Jones}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Large-scale vortices in rapidly rotating Rayleigh-B{\'e}nard
+  convection}},}\ }\href {\doibase 10.1017/jfm.2014.542} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo
+  {volume} {758}},\ \bibinfo {pages} {407--435} (\bibinfo {year} {2014})},\
+  \Eprint {http://arxiv.org/abs/1403.7442} {arXiv:1403.7442 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Guervilly}}\ and\ \citenamefont
+  {{Hughes}}(2017)}]{guervilly&hughes2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C{\'e}line}\
+  \bibnamefont {{Guervilly}}}\ and\ \bibinfo {author} {\bibfnamefont
+  {David~W.}\ \bibnamefont {{Hughes}}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Jets and large-scale vortices in rotating
+  Rayleigh-B{\'e}nard convection}},}\ }\href {\doibase
+  10.1103/PhysRevFluids.2.113503} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Fluids}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {eid}
+  {113503} (\bibinfo {year} {2017})},\ \Eprint
+  {http://arxiv.org/abs/1711.03030} {arXiv:1711.03030 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Favier}}\ \emph {et~al.}(2014)\citenamefont
+  {{Favier}}, \citenamefont {{Silvers}},\ and\ \citenamefont
+  {{Proctor}}}]{favier&all2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {{Favier}}}, \bibinfo {author} {\bibfnamefont {L.~J.}\ \bibnamefont
+  {{Silvers}}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~R.~E.}\
+  \bibnamefont {{Proctor}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Inverse cascade and symmetry breaking in rapidly rotating Boussinesq
+  convection}},}\ }\href {\doibase 10.1063/1.4895131} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physics of Fluids}\ }\textbf {\bibinfo {volume} {26}},\
+  \bibinfo {eid} {096605} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1408.6483} {arXiv:1408.6483 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Favier}}\ \emph {et~al.}(2019)\citenamefont
+  {{Favier}}, \citenamefont {{Guervilly}},\ and\ \citenamefont
+  {{Knobloch}}}]{favier&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Benjamin}\
+  \bibnamefont {{Favier}}}, \bibinfo {author} {\bibfnamefont {C{\'e}line}\
+  \bibnamefont {{Guervilly}}}, \ and\ \bibinfo {author} {\bibfnamefont {Edgar}\
+  \bibnamefont {{Knobloch}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Subcritical turbulent condensate in rapidly rotating Rayleigh-B{\'e}nard
+  convection}},}\ }\href {\doibase 10.1017/jfm.2019.58} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo
+  {volume} {864}},\ \bibinfo {eid} {R1} (\bibinfo {year} {2019})},\ \Eprint
+  {http://arxiv.org/abs/1901.04269} {arXiv:1901.04269 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Couston}}\ \emph {et~al.}(2019)\citenamefont
+  {{Couston}}, \citenamefont {{Lecoanet}}, \citenamefont {{Favier}},\ and\
+  \citenamefont {{Le Bars}}}]{couston&all2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Louis-Alexandre}\
+  \bibnamefont {{Couston}}}, \bibinfo {author} {\bibfnamefont {Daniel}\
+  \bibnamefont {{Lecoanet}}}, \bibinfo {author} {\bibfnamefont {Benjamin}\
+  \bibnamefont {{Favier}}}, \ and\ \bibinfo {author} {\bibfnamefont {Michael}\
+  \bibnamefont {{Le Bars}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Shape and size of large-scale vortices : a universal fluid pattern in
+  geophysical fluid dynamics}},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1909.03244}}
+  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1909.03244}
+  {arXiv:1909.03244 [physics.flu-dyn]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Cheng}}\ \emph {et~al.}(2015)\citenamefont
+  {{Cheng}}, \citenamefont {{Stellmach}}, \citenamefont {{Ribeiro}},
+  \citenamefont {{Grannan}}, \citenamefont {{King}},\ and\ \citenamefont
+  {{Aurnou}}}]{cheng&all2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
+  {{Cheng}}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {{Stellmach}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Ribeiro}}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Grannan}}}, \bibinfo {author} {\bibfnamefont {E.~M.}\ \bibnamefont
+  {{King}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {{Aurnou}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Laboratory-numerical models of rapidly rotating convection in planetary
+  cores}},}\ }\href {\doibase 10.1093/gji/ggu480} {\bibfield  {journal}
+  {\bibinfo  {journal} {Geophysical Journal International}\ }\textbf {\bibinfo
+  {volume} {201}},\ \bibinfo {pages} {1--17} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Clarkson}}\ \emph {et~al.}(2018)\citenamefont
+  {{Clarkson}}, \citenamefont {{Herwig}},\ and\ \citenamefont
+  {{Pignatari}}}]{clarkson&all2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {{Clarkson}}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {{Herwig}}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {{Pignatari}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Pop III
+  i-process nucleosynthesis and the elemental abundances of SMSS J0313-6708 and
+  the most iron-poor stars}},}\ }\href {\doibase 10.1093/mnrasl/slx190}
+  {\bibfield  {journal} {\bibinfo  {journal} {\mnras}\ }\textbf {\bibinfo
+  {volume} {474}},\ \bibinfo {pages} {L37--L41} (\bibinfo {year} {2018})},\
+  \Eprint {http://arxiv.org/abs/1710.01763} {arXiv:1710.01763 [astro-ph.SR]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Andrassy}}\ \emph {et~al.}(2020)\citenamefont
+  {{Andrassy}}, \citenamefont {{Herwig}}, \citenamefont {{Woodward}},\ and\
+  \citenamefont {{Ritter}}}]{andrassy&all2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {{Andrassy}}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {{Herwig}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {{Woodward}}}, \ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {{Ritter}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{3D
+  hydrodynamic simulations of C ingestion into a convective O shell}},}\ }\href
+  {\doibase 10.1093/mnras/stz2952} {\bibfield  {journal} {\bibinfo  {journal}
+  {\mnras}\ }\textbf {\bibinfo {volume} {491}},\ \bibinfo {pages} {972--992}
+  (\bibinfo {year} {2020})},\ \Eprint {http://arxiv.org/abs/1808.04014}
+  {arXiv:1808.04014 [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Brummell}}\ \emph {et~al.}(2002)\citenamefont
+  {{Brummell}}, \citenamefont {{Clune}},\ and\ \citenamefont
+  {{Toomre}}}]{brummell&all2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nicholas~H.}\
+  \bibnamefont {{Brummell}}}, \bibinfo {author} {\bibfnamefont {Thomas~L.}\
+  \bibnamefont {{Clune}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
+  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Penetration and Overshooting in Turbulent Compressible Convection}},}\
+  }\href {\doibase 10.1086/339626} {\bibfield  {journal} {\bibinfo  {journal}
+  {\apj}\ }\textbf {\bibinfo {volume} {570}},\ \bibinfo {pages} {825--854}
+  (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Pratt}}\ \emph {et~al.}(2017)\citenamefont
+  {{Pratt}}, \citenamefont {{Baraffe}}, \citenamefont {{Goffrey}},
+  \citenamefont {{Constantino}}, \citenamefont {{Viallet}}, \citenamefont
+  {{Popov}}, \citenamefont {{Walder}},\ and\ \citenamefont
+  {{Folini}}}]{pratt&all2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {{Pratt}}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {{Baraffe}}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {{Goffrey}}}, \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {{Constantino}}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {{Viallet}}}, \bibinfo {author}
+  {\bibfnamefont {M.~V.}\ \bibnamefont {{Popov}}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {{Walder}}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {{Folini}}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Extreme value statistics for two-dimensional convective
+  penetration in a pre-main sequence star}},}\ }\href {\doibase
+  10.1051/0004-6361/201630362} {\bibfield  {journal} {\bibinfo  {journal}
+  {Astronomy \& Astrophysics}\ }\textbf {\bibinfo {volume} {604}},\ \bibinfo
+  {eid} {A125} (\bibinfo {year} {2017})},\ \Eprint
+  {http://arxiv.org/abs/1706.04852} {arXiv:1706.04852 [astro-ph.SR]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Brown}}\ \emph {et~al.}(2010)\citenamefont
+  {{Brown}}, \citenamefont {{Browning}}, \citenamefont {{Brun}}, \citenamefont
+  {{Miesch}},\ and\ \citenamefont {{Toomre}}}]{brown&all2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Benjamin~P.}\
+  \bibnamefont {{Brown}}}, \bibinfo {author} {\bibfnamefont {Matthew~K.}\
+  \bibnamefont {{Browning}}}, \bibinfo {author} {\bibfnamefont {Allan~Sacha}\
+  \bibnamefont {{Brun}}}, \bibinfo {author} {\bibfnamefont {Mark~S.}\
+  \bibnamefont {{Miesch}}}, \ and\ \bibinfo {author} {\bibfnamefont {Juri}\
+  \bibnamefont {{Toomre}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Persistent Magnetic Wreaths in a Rapidly Rotating Sun}},}\ }\href {\doibase
+  10.1088/0004-637X/711/1/424} {\bibfield  {journal} {\bibinfo  {journal}
+  {\apj}\ }\textbf {\bibinfo {volume} {711}},\ \bibinfo {pages} {424--438}
+  (\bibinfo {year} {2010})},\ \Eprint {http://arxiv.org/abs/1011.2831}
+  {arXiv:1011.2831 [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Yadav}}\ \emph {et~al.}(2016)\citenamefont
+  {{Yadav}}, \citenamefont {{Christensen}}, \citenamefont {{Wolk}},\ and\
+  \citenamefont {{Poppenhaeger}}}]{yadav&all2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Rakesh~K.}\
+  \bibnamefont {{Yadav}}}, \bibinfo {author} {\bibfnamefont {Ulrich~R.}\
+  \bibnamefont {{Christensen}}}, \bibinfo {author} {\bibfnamefont {Scott~J.}\
+  \bibnamefont {{Wolk}}}, \ and\ \bibinfo {author} {\bibfnamefont {Katja}\
+  \bibnamefont {{Poppenhaeger}}},\ }\bibfield  {title} {\enquote {\bibinfo
+  {title} {{Magnetic Cycles in a Dynamo Simulation of Fully Convective M-star
+  Proxima Centauri}},}\ }\href {\doibase 10.3847/2041-8213/833/2/L28}
+  {\bibfield  {journal} {\bibinfo  {journal} {\apjl}\ }\textbf {\bibinfo
+  {volume} {833}},\ \bibinfo {eid} {L28} (\bibinfo {year} {2016})},\ \Eprint
+  {http://arxiv.org/abs/1610.02721} {arXiv:1610.02721 [astro-ph.SR]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Strugarek}}\ \emph {et~al.}(2017)\citenamefont
+  {{Strugarek}}, \citenamefont {{Beaudoin}}, \citenamefont {{Charbonneau}},
+  \citenamefont {{Brun}},\ and\ \citenamefont {{do
+  Nascimento}}}]{strugarek&all2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Strugarek}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {{Beaudoin}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {{Charbonneau}}}, \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
+  {{Brun}}}, \ and\ \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont {{do
+  Nascimento}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Reconciling
+  solar and stellar magnetic cycles with nonlinear dynamo simulations}},}\
+  }\href {\doibase 10.1126/science.aal3999} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages}
+  {185--187} (\bibinfo {year} {2017})},\ \Eprint
+  {http://arxiv.org/abs/1707.04335} {arXiv:1707.04335 [astro-ph.SR]}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{Strugarek}}\ \emph {et~al.}(2018)\citenamefont
+  {{Strugarek}}, \citenamefont {{Beaudoin}}, \citenamefont {{Charbonneau}},\
+  and\ \citenamefont {{Brun}}}]{strugarek&all2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {{Strugarek}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {{Beaudoin}}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {{Charbonneau}}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~S.}\
+  \bibnamefont {{Brun}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On
+  the Sensitivity of Magnetic Cycles in Global Simulations of Solar-like
+  Stars}},}\ }\href {\doibase 10.3847/1538-4357/aacf9e} {\bibfield  {journal}
+  {\bibinfo  {journal} {\apj}\ }\textbf {\bibinfo {volume} {863}},\ \bibinfo
+  {eid} {35} (\bibinfo {year} {2018})},\ \Eprint
+  {http://arxiv.org/abs/1806.09484} {arXiv:1806.09484 [astro-ph.SR]}
+  \BibitemShut {NoStop}%
+\end{thebibliography}%
+
 \end{document}

### 2020-05-20 tex/mixedft_evolution_ms.tex
moves bibliography to end of file
nominally removes redline from submission manuscript

@@
 Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately model natural systems.
-In this work, we study \RB convection (RBC) \ea{under the Boussinesq approximation}.
-\ea{We examine simulations with mixed temperature boundary conditions in which the flux is fixed at the bottom boundary and the temperature is fixed at the top (``FT'').}
-We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of \ea{thermal boundaries, in which the temperature is fixed} at the top and bottom of the domain (``TT'').
-\ea{We demonstrate that the timescale of thermal relaxation for FT simulations is dependent upon the initial conditions.
+In this work, we study \RB convection (RBC) under the Boussinesq approximation.
+We examine simulations with mixed temperature boundary conditions in which the flux is fixed at the bottom boundary and the temperature is fixed at the top (``FT'').
+We aim to understand how FT boundaries change the nature of the convective solution compared to the traditional choice of thermal boundaries, in which the temperature is fixed at the top and bottom of the domain (``TT'').
+We demonstrate that the timescale of thermal relaxation for FT simulations is dependent upon the initial conditions.
 ``Classic'' initial conditions which employ a hydrostatically- and thermally- balanced linear temperature profile exhibit a long thermal relaxation.
-This long relaxation is not seen in FT simulations which use a TT simulation's nonlinear state as initial conditions (``TT-to-FT'').}
-In the \ea{thermally} relaxed\ea{, statistically stationary} state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries\ea{, and time- and volume-averaged flow statistics like the Nusselt number and the P\'{e}clet number are indistinguishable between FT and TT simulations}.
-\ea{FT boundaries are fundamentally asymmetric, and we examine the asymmetries that these boundaries produce in the flow.
+This long relaxation is not seen in FT simulations which use a TT simulation's nonlinear state as initial conditions (``TT-to-FT'').
+In the thermally relaxed, statistically stationary state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries, and time- and volume-averaged flow statistics like the Nusselt number and the P\'{e}clet number are indistinguishable between FT and TT simulations.
+FT boundaries are fundamentally asymmetric, and we examine the asymmetries that these boundaries produce in the flow.
 We find that the fixed-flux boundary produces more extreme temperature events than the fixed-temperature boundary.
 However, these near-boundary asymmetries do not measurably break the symmetry in the convective interior.
-We briefly explore rotating RBC to demonstrate that our findings with respect to thermal relaxation carry over to this more complex case, and to show the power of TT-to-FT initial conditions.}
+We briefly explore rotating RBC to demonstrate that our findings with respect to thermal relaxation carry over to this more complex case, and to show the power of TT-to-FT initial conditions.
 \end{abstract}
@@
 
-In this work, we examine how the choice of using ``mixed'' \ea{thermodynamic boundary conditions} affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
-In RBC, temperature is the only thermodynamic quantity and throughout this work we will \ea{adopt the gnomenclature of past authors (see e.g., ref.~\cite{ishiwatari&all1994}) and} refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
+In this work, we examine how the choice of using ``mixed'' thermodynamic boundary conditions affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
+In RBC, temperature is the only thermodynamic quantity and throughout this work we will adopt the gnomenclature of past authors (see e.g., ref.~\cite{ishiwatari&all1994}) and refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
 We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2016}, our TT, FF, and FT are respectively called RB1, RB2, and RB3.}.
 
-It is generally assumed that, \ea{in their statistically stationary states, simulations with} FT boundaries should behave similarly to \ea{those with} FF boundaries \cite{goluskin2016, otero&all2002}.
-\ea{Early studies of FF convection often focused on flow morphologies, because large-to-infinite aspect ratio convective rolls are linearly unstable for this choice of boundary condition (see e.g., ref.~\cite{chapman&proctor1980}).
-However, the onset properties and resultant flow morphologies in FT simulations more strongly resemble TT dynamics \cite{ishiwatari&all1994}, in that both are linearly unstable at a well-defined, finite aspect ratio.}
-\ea{Despite these differences near convective onset,} FF and TT boundaries \ea{have been shown to} exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
+It is generally assumed that, in their statistically stationary states, simulations with FT boundaries should behave similarly to those with FF boundaries \cite{goluskin2016, otero&all2002}.
+Early studies of FF convection often focused on flow morphologies, because large-to-infinite aspect ratio convective rolls are linearly unstable for this choice of boundary condition (see e.g., ref.~\cite{chapman&proctor1980}).
+However, the onset properties and resultant flow morphologies in FT simulations more strongly resemble TT dynamics \cite{ishiwatari&all1994}, in that both are linearly unstable at a well-defined, finite aspect ratio.
+Despite these differences near convective onset, FF and TT boundaries have been shown to exhibit the same scaling of convective heat transport (quantified by the Nusselt number, Nu) as a function of increased convective driving (quantified by the Rayleigh number, Ra) \cite{johnston&doering2009}.
 However, FT boundaries introduce complexities into the convective solution which neither FF nor TT boundaries are exposed to.
@@
 We also compare relaxed FT solutions to TT solutions.
-\ea{When classic initial conditions which are in hydrostatic and thermal equilibrium are employed,} the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+When classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We find that this long thermal relaxation can be bypassed by \ea{constructing smarter initial conditions based on the expected evolved value of Nu, or by simply} using the results of TT simulations as initial conditions for FT simulations.
-Finally, FT boundaries create some asymmetries in the convective flows, \ea{particularly in the boundary layers,} but these asymmetries do not \ea{appreciably} change the \ea{bulk} convective state compared to TT simulations.
+We find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
+Finally, FT boundaries create some asymmetries in the convective flows, particularly in the boundary layers, but these asymmetries do not appreciably change the bulk convective state compared to TT simulations.
 
 We present these findings as follows.
-In section \ref{sec:simulations}, we describe our simulation setup, numerical methods, \ea{initial conditions, and timescales in the convective systems}.
-In section \ref{sec:results_timescales}, we describe our findings \ea{regarding} the time evolution of FT systems.
-\ea{In section \ref{sec:results_dynamics}, we study asymmetries in FT systems and compare them to TT systems.}
+In section \ref{sec:simulations}, we describe our simulation setup, numerical methods, initial conditions, and timescales in the convective systems.
+In section \ref{sec:results_timescales}, we describe our findings regarding the time evolution of FT systems.
+In section \ref{sec:results_dynamics}, we study asymmetries in FT systems and compare them to TT systems.
 In section \ref{sec:results_rotating}, we show that these findings carry over to a more complex system (rotating \RB convection) with some interesting implications.
@@
 \label{sec:simulations}
-\ea{
+
 \subsection{Equations, Control Parameters, Boundary Conditions, and Numerics}
-}
 We study incompressible RBC under a freefall nondimensionalization; for details of this nondimensionalization, we refer readers to our previous work \cite{anders&all2018}.
@@
 \end{align}
-where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is \ea{a background linearly unstable temperature profile} and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
+where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is a background linearly unstable temperature profile and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
 The dimensionless control parameters are the Rayleigh (Ra), Prandtl (Pr), and Ekman (Ek) numbers, defined respectively as
@@
 and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
-In non-rotating RBC (section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}), we set Ek$\,= \infty$.
+In non-rotating RBC (sections \ref{sec:results_timescales} \& \ref{sec:results_dynamics}), we set Ek$\,= \infty$.
 
 The extent of our numerical domain vertically is $z = [-0.5, 0.5]$ and horizontally is $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
-The \ea{background} temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
-The temperature scale, $\Delta$, is set by \ea{either} the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
+The background temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
+The temperature scale, $\Delta$, is set by either the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
 We respectively define a temperature (Ra$_{\Delta T}$) and a flux (Ra$_{\partial_z T}$) Rayleigh number for these cases,
@@
 
-In section\ea{s} \ref{sec:results_timescales} \ea{\& \ref{sec:results_dynamics}}, we study \ea{non-rotating convection}.
+In sections \ref{sec:results_timescales} \& \ref{sec:results_dynamics}, we study non-rotating convection.
 For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
 \begin{equation}
-u = \ea{v =}\, w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
+u = v =\, w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
 \label{eqn:vel_bcs}
 \end{equation}
-For this choice of boundary conditions, the critical values of the Rayleigh number \ea{and wavenumber are (Ra$_{\partial_z T}, k) = (1295.78, 2.5519)$} for FT boundaries and \ea{(Ra$_{\Delta T}, k) = (1707.76, 3.1163)$} for TT boundaries \cite{goluskin2016}.
-\ea{In our $\Gamma = 2$ box, the smallest wavenumber permitted is $k = \pi$, and at that wavenumber the critical values are Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which are slightly larger than the classical onset values}.
+For this choice of boundary conditions, the critical values of the Rayleigh number and wavenumber are (Ra$_{\partial_z T}, k) = (1295.78, 2.5519)$ for FT boundaries and (Ra$_{\Delta T}, k) = (1707.76, 3.1163)$ for TT boundaries \cite{goluskin2016}.
+In our $\Gamma = 2$ box, the smallest wavenumber permitted is $k = \pi$, and at that wavenumber the critical values are Ra$_{\partial_z T} = 1357.57$ for FT boundaries and Ra$_{\Delta T} = 1707.94$ for TT boundaries, which are slightly larger than the classical onset values.
 It is reasonable to expect important differences between FT and TT solutions at low supercriticalities due to the difference in onset.
 However, for the supercriticalities of O($10^{5+}$) studied here, we do not expect this difference in linear stability to be very important.
-\ea{Many of these simulations are restricted to} two-dimensional (2D) convection \ea{by setting} $\partial_y = v = 0$.
+Many of these simulations are restricted to two-dimensional (2D) convection by setting $\partial_y = v = 0$.
 
@@
 We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
-Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the \ea{IMEX}, second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
-The codes used to run the simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using \ea{v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and} v1.0.0 \ea{(for all other cases)} of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
+Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the IMEX, second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
+The codes used to run the simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and v1.0.1 (for all other cases) of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
 Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.
 
-\ea{
 \subsection{Output Quantities \& Mapping Between Temperature Nondimensionalizations}
-}
 \label{sec:ra_nu_relations}
@@
 where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
-\ea{In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
+In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
 \begin{equation}
@@
 \end{equation}
-This mapping is presented by ref.~\cite{calkins&all2015} for a diffusion timescale nondimensionalization, and we have expanded it here for a freefall timescale nondimensionalization.}
+This mapping is presented by ref.~\cite{calkins&all2015} for a diffusion timescale nondimensionalization, and we have expanded it here for a freefall timescale nondimensionalization.
 
@@
 
-\ea{
 \subsection{Initial Conditions}
@@
 As a result, we will examine ``TT-to-FT'' initial conditions, in which we run a TT simulation through its convective transient to statistical equilibrium, then use the full evolved nonlinear state as initial conditions for an FT simulation.
-}
 To achieve this, we perform these steps:
@@
 
-\ea{
 \paragraph{Nu-based ICs} 
@@
 For classic and Nu-based ICs,
-}
 we fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
@@
 
-\ea{
 \subsection{Timescales}
 \label{sec:timescales}
-}
-One \ea{result of the mapping in Eqn.~\ref{eqn:ra_relation}} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
+One result of the mapping in Eqn.~\ref{eqn:ra_relation} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
 The velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
 As a result, every nondimensional simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a time unit in an FT simulation.
-\ea{We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
-To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.}
+We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
+To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
 
-\ea{
 The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
@@
 
-}
-
 %%%%%%%%%%%%
@@
 
-In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of a \ea{classic-IC} FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
+In Fig.~\ref{fig:rbc_evolution_dynamics}, we compare the time evolution of the temperature field of a classic-IC FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ to two TT simulations (with Ra$_{\Delta T} = 10^{10}$ and Ra$_{\Delta T} = 10^9$, respectively).
 As shown in the top four panels, we see the expected convective roll solution in both TT simulations (top row) and at early and late times in the FT simulation (bottom row).
@@
 \caption{ 
-	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$ }at early and late times (bottom row).
+	(Upper four panels) Snapshots of the temperature anomaly in two TT simulations (top row) and in an FT simulation with Ra$_{\partial_z T} = 4.83 \times 10^{10}$ at early and late times (bottom row).
 	(Left two panels) Dynamics in a TT case at Ra$_{\Delta T} = 10^{10}$ and early in the FT simulation when Ra$_{\Delta T} \approx 10^{10}$.
@@
 	The relaxed FT simulation is visually indistinguishable from its comparable TT simulation.
-	\ea{Note that Ra$_{\Delta T}$ is a measured \emph{output} quantity for the FT simulation at two different times in its evolution.}
+	Note that Ra$_{\Delta T}$ is a measured \emph{output} quantity for the FT simulation at two different times in its evolution.
 \\	
@@
 In the bottom four panels, we examine these temperature fields statistically by displaying their probability distribution functions (PDFs).
-To create these PDFs, we sample the full simulation temperature field once every \ea{evolved} freefall time, \ea{$\tau_{\text{ff, ev}}$}, over the span of 500\ea{$\tau_{\text{ff, ev}}$}.
+To create these PDFs, we sample the full simulation temperature field once every evolved freefall time, $\tau_{\text{ff, ev}}$, over the span of 500$\tau_{\text{ff, ev}}$.
 We interpolate the (unevenly spaced) vertical Chebyshev grid points onto an evenly spaced grid before histogramming the flow values into 200 bins and creating the PDFs.
@@
 We find that FT simulations carry marginally more flux (higher Nu) and are more turbulent (higher Pe) than comparable TT simulations as they relax through this parameter space.
-\ea{By binning Ra$_{\Delta T}(t)$, Nu$(t)$, and Pe$(t)$ into ten bins over the evolution of our FT simulations, we can quantify the path through parameter space that our FT simulations trace out.
+By binning Ra$_{\Delta T}(t)$, Nu$(t)$, and Pe$(t)$ into ten bins over the evolution of our FT simulations, we can quantify the path through parameter space that our FT simulations trace out.
 By performing a least-squares fit to this data, the best-fit paths for Ra$_{\partial_z T} = 4.83 \times 10^{10}$ are $\text{Nu} = 0.0618\,\text{Ra}_{\Delta T}^{0.322}$ and $\text{Pe} = (5.73 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.597}$.
@@
 By comparison, the best fit scaling laws for our TT cases are $\text{Nu} = 0.141\,\text{Ra}_{\Delta T}^{0.282}$ (very similar to the law reported in ref.~\cite{johnston&doering2009}), $\text{Pe} = (0.303)\,\text{Ra}_{\Delta T}^{0.516}$ (for Ra$_{\Delta T} \geq 10^9$), and $\text{Pe} = (2.41 \times 10^{-2})\,\text{Ra}_{\Delta T}^{0.64}$ (for Ra$_{\Delta T} < 10^9$).
-}
 These heightened values of Nu and Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.
 
-Achieving thermal relaxation in \ea{classic} FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
+Achieving thermal relaxation in classic-IC FT simulations is computationally costly for two reasons: (1) the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state (compare the left and right dynamics in Fig.~\ref{fig:rbc_evolution_dynamics}), and (2) thousands of freefall times must pass during relaxation (see Fig.~\ref{fig:rbc_scalar_comparisons}).
 For example, for the cases displayed in the left panels of Fig.~\ref{fig:rbc_scalar_comparisons} with a modest Ra$_{\Delta T} = 10^9$, the shown evolution of $10^4$ time units of the FT simulation cost $\sim 4.5 \times 10^5$ cpu-hours, while the TT equivalent case cost only $5.6 \times 10^4$ cpu-hours -- nearly an order of magnitude difference.
 FT simulation dynamics evolve slowly during thermal relaxation, and these images, PDFs, and traces demonstrate the importance of waiting for thermal relaxation to be achieved when conducting an FT simulation.
-\ea{In practice, in this work, we find that the thermal relaxation of FT simulations with classic ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.}
+In practice, in this work, we find that the thermal relaxation of FT simulations with classic ICs takes $\sim 2.5\sqrt{\text{Ra}_{\partial_z T} \text{Pr}}\,\text{Nu}^{-1}$ simulation freefall time units.
 
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange\ea{, Ra$_{\partial_z T} = 4.81 \times 10^{10}$}) and TT (purple\ea{, Ra$_{\Delta T} = 10^9$}) simulation are shown.
+	(Left three panels) Time traces of scalar quantities in a classic-IC FT (orange, Ra$_{\partial_z T} = 4.81 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 10^9$) simulation are shown.
 	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
@@
 \caption{ 
-	(Left three panels) Time traces \ea{(in units of $\tau_{\text{ff, ev}}$)} of scalar quantities, which have been averaged over a rolling time window of 25\ea{$\tau_{\text{ff, ev}}$}, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions \ea{with Ra$_{\partial_z T} = 4.83 \times 10^{10}$}.
+	(Left three panels) Time traces (in units of $\tau_{\text{ff, ev}}$) of scalar quantities, which have been averaged over a rolling time window of 25$\tau_{\text{ff, ev}}$, are shown for a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions with Ra$_{\partial_z T} = 4.83 \times 10^{10}$.
 	The time of the change of boundary conditions is denoted by the vertical black line.
@@
 	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
-	(right four panels) PDFs are shown which compare TT-to-FT dynamics (black PDFs) to dynamics from \ea{the classic-IC} FT case from Fig.~\ref{fig:rbc_scalar_comparisons} (green PDFs).
+	(right four panels) PDFs are shown which compare TT-to-FT dynamics (black PDFs) to dynamics from the classic-IC FT case from Fig.~\ref{fig:rbc_scalar_comparisons} (green PDFs).
 	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
@@
 
-\ea{\subsubsection{TT-to-FT} Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.}
+\subsubsection{TT-to-FT} Figs.~\ref{fig:rbc_evolution_dynamics} \& \ref{fig:rbc_scalar_comparisons} demonstrate that the statistically-stationary states of FT and TT simulations are similar in a qualitative sense and in their volume-averaged flow statistics.
 It should therefore be possible to use results from a TT simulation to quickly reach the relaxed state of a comparable FT simulation, saving up to an order of magnitude in computational cost.
-We show \ea{the results of using our TT-to-FT initial conditions procedure} in practice in Fig.~\ref{fig:rbc_restart_description}.
+We show the results of using our TT-to-FT initial conditions procedure in practice in Fig.~\ref{fig:rbc_restart_description}.
 In the left three panels, we display the temporal behavior of (top) Ra, (middle) the flux at the bottom boundary, and (bottom) the temperature difference between the top and bottom boundaries.
@@
 
-In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable \ea{classic} FT simulation.
+In the right four panels of Fig.~\ref{fig:rbc_restart_description}, we compare PDFs of flow fields in this TT-to-FT simulation and the comparable classic FT simulation.
 Shown are PDFs of the temperature field (upper left), enstrophy (upper right), convective flux (lower left), and vertical velocity (lower right).
@@
 where $A$ is a flow quantity, $P(A)$ is the PDF of $A$, $\mu$ is the mean, $\sigma$ is the standard deviation, $\Delta A$ is the spacing between the discrete PDF bins, and $i$ is the index of the bin.
-\ea{We specifically report the Excess Kurtosis = Kurtosis $- 3$, to show how the Kurtosis of our PDFs differs from the Kurtosis of Normal Distributions.
+We specifically report the Excess Kurtosis = Kurtosis $- 3$, to show how the Kurtosis of our PDFs differs from the Kurtosis of Normal Distributions.
 The PDFs of all FT simulations agree well regardless of initial conditions, suggesting that all initial conditions do achieve a similar statistically stationary state.
@@
 It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
-}
 
@@
 \caption{ 
-	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below \ea{for the TT case with Ra$_{\Delta T} = 10^9$ and all FT cases with Ra$_{\partial_z T} = 4.83\times 10^{10}$}.
+	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below for the TT case with Ra$_{\Delta T} = 10^9$ and all FT cases with Ra$_{\partial_z T} = 4.83\times 10^{10}$.
 }
@@
 
-\ea{
 \subsubsection{Nu-based ICs}
@@
 Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classic ICs are very similar.
-}
 
-\subsection{\ea{Discussion of 2D results}} 
-We note briefly that \ea{Nu-based and} TT-to-FT \ea{ICs are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
+\subsection{Discussion of 2D results} 
+We note briefly that Nu-based and TT-to-FT ICs are only two of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 The thermal energy reservoir of TT simulations does not change between the initial and final state.
-The rapid relaxation of TT simulations\ea{, as well as FT simulations with Nu-based and TT-to-FT ICs}, therefore suggests that experimental restratification occurs rapidly in RBC. 
-The long rundown of \ea{classic-IC} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
+The rapid relaxation of TT simulations, as well as FT simulations with Nu-based and TT-to-FT ICs, therefore suggests that experimental restratification occurs rapidly in RBC. 
+The long rundown of classic-IC FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
 
-\ea{
 As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$.
@@
 We find that the kinetic energy increases by less than a factor of two from its initial post-transient value to its final value in the statistically-stationary state.
-}
 
@@
 \caption{ 
-	\ea{
 	(top six panels) Snapshots of the temperature anomaly are shown for select slices through the 3D TT simulation at Ra$_{\Delta T} = 10^8$ (left column) and the TT-to-FT simulation at Ra$_{\partial_z T} = 3.1 \times 10^9$ (right column).
@@
 	The extreme temperature events which stand out visually near the bottom boundary layer can be clearly seen in all PDFs except for the one near the upper boundary.
-	}
 	\label{fig:rbc_3D_panels} }
@@
 
-\ea{
 \subsection{3D verification of 2D results}
@@
 Unsurprisingly, we find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is similar, but not identical, to the PDFs of the temperature field of the full volume, suggesting that this one slice does not capture the full range of possible dynamics which occur in the domain over our sampling window.
-}
 
@@
 In Fig.~\ref{fig:rbc_1D_profiles}, we compare the time- and horizontally-averaged profiles of the temperature and fluxes in the evolved FT and TT cases presented in Fig.~\ref{fig:rbc_scalar_comparisons}.
-Time averages are taken over 500\ea{$\tau_{\text{ff, ev}}$}, sampled once every 0.1\ea{$\tau_{\text{ff, ev}}$}.
+Time averages are taken over 500$\tau_{\text{ff, ev}}$, sampled once every 0.1$\tau_{\text{ff, ev}}$.
 In the three left panels, we display profiles of (top) the mean temperature, (middle) the mean temperature in upflows (solid) and downflows (dashed), and (bottom) the convective enthalpy flux ($F_{\text{enth}} = wT$, solid) and the vertical conductive flux ($F_{\text{cond}} = -\Peff^{-1}\grad T$, dashed).
@@
 In the flux panels (bottom row), we do not plot the percentage difference in the conductive flux, as this quantity is undefined in the bulk of the interior where that flux is zero.
-The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the \ea{FT and TT cases differ by no more than 0.0025 in the plotted units} in the interior. 
-\ea{Here, we define the boundary layers as the heights above or below which conduction carries 95\% of the flux.
-By this definition, the boundary layer depth is $\sim 0.024$ at Ra$_{\Delta T} = 10^9$, and we show three times this depth in the zoomed-in panels.}
+The conductive flux of the two cases agrees to within a few \% in the boundary layers, and the FT and TT cases differ by no more than 0.0025 in the plotted units in the interior. 
+Here, we define the boundary layers as the heights above or below which conduction carries 95\% of the flux.
+By this definition, the boundary layer depth is $\sim 0.024$ at Ra$_{\Delta T} = 10^9$, and we show three times this depth in the zoomed-in panels.
 
@@
 When we split the temperature profile into upflows and downflows, we find that FT upflows/downflows are slightly warmer/cooler than their TT counterparts at the hot, bottom boundary.
-\ea{These (rather interesting) differences are illustrated in Fig.~\ref{fig:rbc_3D_panels}, and are explored further in the next section (also see Fig.~\ref{fig:rbc_dynamics_asymmetries}).
+These (rather interesting) differences are illustrated in Fig.~\ref{fig:rbc_3D_panels}, and are explored further in the next section (also see Fig.~\ref{fig:rbc_dynamics_asymmetries}).
 However, these differences do vanish in the interior and do not seem to affect the convective dynamics appreciably.
-}
 
@@
 
-\ea{
 Rotating convection is an excellent testbed for our TT-to-FT method.
@@
 Here we explore the parameter space that the classic-IC FT simulation explores as it thermally relaxes and demonstrate that the TT-to-FT approach leads to rapid convergence for a rotating simulation.
-}
 
 We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}.
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-\ea{We then take the TT case, do a TT-to-FT simulation, and compare the results of the TT-to-FT simulation to the classic-IC FT case.}
+We then take the TT case, do a TT-to-FT simulation, and compare the results of the TT-to-FT simulation to the classic-IC FT case.
 
-In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of \ea{a classic-IC} FT and TT case.
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of a classic-IC FT and TT case.
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
@@
 After achieving this peak value, Pe monotonically decreases toward its relaxed state.
-\ea{We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}\text{ Pr}}/\text{Nu}$ nondimensional freefall time units.}
+We find that the thermal relaxation of this case takes $\sim (2/3)\sqrt{\text{Ra}_{\partial_z T}\text{ Pr}}/\text{Nu}$ nondimensional freefall time units.
 
@@
 \caption{ 
-	(Left three panels) Time traces of scalar quantities in a \ea{classic-IC} FT (orange, $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 2.75\times 10^9$) simulation are shown.
+	(Left three panels) Time traces of scalar quantities in a classic-IC FT (orange, $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 2.75\times 10^9$) simulation are shown.
 	All traces have been averaged over a rolling window of 50 freefall time units to increase the clarity of the evolutionary trend.
@@
 As expected, the scaling of Nu vs.~Ra is steep in the rotationally constrained regime \cite{julien&all2012, plumley&julien2019}, which these simulations trace through.
-\ea{We find that at values of Ra$_{\Delta T} \gtrsim 8 \times 10^9$, scaling laws start to flatten towards the unconstrained regime.
+We find that at values of Ra$_{\Delta T} \gtrsim 8 \times 10^9$, scaling laws start to flatten towards the unconstrained regime.
 The FT simulation at all times when Ra$_{\Delta T} < 8 \times 10^9$ traces out $\text{Nu} = (1.08 \times 10^{-18})\,\text{Ra}_{\Delta T}^{2}$ and $\text{Pe} = (4.26 \times 10^{-20})\,\text{Ra}_{\Delta T}^{2.4}$.
-The TT simulations with Ra$_{\Delta T} < 8 \times 10^9$ trace out $\text{Nu} = (9.36 \times 10^{-17})\,\text{Ra}_{\Delta T}^{1.79}$ and $\text{Pe} = (4.78 \times 10^{-19})\,\text{Ra}_{\Delta T}^{2.27}$.}
-As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT \ea{scaling laws} are once again \ea{steeper than} the comparable TT \ea{laws}.
+The TT simulations with Ra$_{\Delta T} < 8 \times 10^9$ trace out $\text{Nu} = (9.36 \times 10^{-17})\,\text{Ra}_{\Delta T}^{1.79}$ and $\text{Pe} = (4.78 \times 10^{-19})\,\text{Ra}_{\Delta T}^{2.27}$.
+As in Fig.~\ref{fig:rbc_scalar_comparisons}, the FT scaling laws are once again steeper than the comparable TT laws.
 
@@
 
-\ea{
 We performed a TT-to-FT simulation starting from the evolved state of the TT simulation, and its time evolution matched that seen in Fig.~\ref{fig:rbc_restart_description}.
@@
 The difference in computational cost between classic-IC FT simulations and the TT/TT-to-FT simulations are even more striking here than in our previous examples.
-}
 The TT simulation shown in the left panels of Fig.~\ref{fig:rotating_panels} only cost $2.2 \times 10^3$ cpu-hours to run 5000 freefall times.
-\ea{The TT-to-FT simulation cost an additional $1.28 \times 10^3$ cpu-hours to run 1000$\tau_{\text{ff, ev}}$.}
+The TT-to-FT simulation cost an additional $1.28 \times 10^3$ cpu-hours to run 1000$\tau_{\text{ff, ev}}$.
 By comparison, the cost of the FT simulation shown in the same panels was \emph{roughly three orders of magnitude larger}---$2.3 \times 10^6$ cpu-hours.
-The TT \ea{and TT-to-FT} simulations \ea{had a} coefficient resolution \ea{of} $128^3$.
+The TT and TT-to-FT simulations had a coefficient resolution of $128^3$.
 The FT simulation's initial resolution required to resolve the convective transient was $512\times384^2$ coefficients.
@@
 \label{sec:discussion}
-In short, we find that FT simulations \ea{can} experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
+In short, we find that FT simulations can experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
 
 In this paper, we have studied the time evolution of \RB convection (RBC) under two different formulations of the thermal boundary conditions: ``FT'' boundaries, where the flux is fixed at the bottom and temperature is fixed at the top, and ``TT'' boundaries, where temperature is fixed at the top and bottom.
-\ea{In the case of FT boundaries, we studied three different sets of initial conditions and examined both the nature of thermal relaxation and the equilibrated, statistically stationary state.}
+In the case of FT boundaries, we studied three different sets of initial conditions and examined both the nature of thermal relaxation and the equilibrated, statistically stationary state.
 Through studying this relaxation and the relaxed states, we come to the following conclusions:
@@
 \item Thermal relaxation in RBC has two components: (a) changes in the energy reservoir and (b) changes in the stratification.
-We find that the long relaxation of \ea{classic-IC} FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations \ea{and FT simulations with Nu-based or TT-to-FT ICs} due to the lack of evolution of the \ea{temperature difference between the boundaries}.
-The rapid evolution of \ea{all of our simulations other than the classic-IC FT} simulations suggests that RBC \ea{thermally} restratifies itself instantaneously.
+We find that the long relaxation of classic-IC FT simulations is due to changes in the energy reservoir; this reservoir is roughly constant in TT simulations and FT simulations with Nu-based or TT-to-FT ICs due to the lack of evolution of the temperature difference between the boundaries.
+The rapid evolution of all of our simulations other than the classic-IC FT simulations suggests that RBC thermally restratifies itself instantaneously.
 \item Dynamical measurements taken during thermal relaxation may be misleading.
 Dynamics during the relaxation are more turbulent than in the evolved state, and exhibit evolving flow balances in the equation of motion (as quantified by e.g., the Rossby number).
-\ea{This is principly a concern in systems like classic-IC FT simulations which can have very long thermal relaxation timescales compared to dynamical times.}
-\item The thermal relaxation process of a \ea{classic-IC} FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
+This is principly a concern in systems like classic-IC FT simulations which can have very long thermal relaxation timescales compared to dynamical times.
+\item The thermal relaxation process of a classic-IC FT simulation performs a sweep through Ra$_{\Delta T}$ parameter space.
 We find that convective heat transport (the Nusselt number) and turbulent velocities (the P\'{e}clet number) are elevated above classic scaling laws along these parameter space sweeps.
-\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation, \ea{or by constructing an initial state which is characterized by a temperature difference similar to the evolved one}.
-\item Despite minor asymmetries near the \ea{boundaries}, we find no meaningful difference between the mean state of FT and TT simulations.
+\item Great computational expense achieving thermal relaxation in an FT simulation can be avoided by using the evolved state of a TT simulation as a ``better'' set of initial conditions for an FT simulation, or by constructing an initial state which is characterized by a temperature difference similar to the evolved one.
+\item Despite minor asymmetries near the boundaries, we find no meaningful difference between the mean state of FT and TT simulations.
 \end{enumerate}
@@
 For example, in the late stages of the lifetimes of stars, some core burning regions have sufficiently short lifetimes that they likely do not come into thermal relaxation \citep{clarkson&all2018, andrassy&all2020}.
-The use of \ea{classic-ICs with} FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
+The use of classic-ICs with FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
 However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
@@
 These dynamo simulations involve large numbers of timesteps through many freefall timescales in order to study the generation and evolution of magnetic fields and mean flows.
-We found in our \ea{classic-IC} FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
+We found in our classic-IC FT rotating simulation that the unrelaxed state generated a mean flow (a LSV, Fig.~\ref{fig:rotating_panels}) that was much more intense and large-scale than the eventual flows that developed in the relaxed state.
 If we had terminated our FT rotating simulation too early, we would not have seen the eventual destruction of this LSV or the later oscillatory behavior between jets and vortex pairs.
@@
 In conclusion, we note that our results here should provide astrophysical convection simulations with reason for optimism.
-Some problems that we encounter (e.g., long thermal rundown in \ea{classic-IC} FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.
+Some problems that we encounter (e.g., long thermal rundown in classic-IC FT simulations) can be completely avoided through a careful understanding of the numerical system being solved.
 
 \begin{acknowledgments}
-\ea{We thank the anonymous referee who suggested the idea of Nu-based ICs, and whose careful and thoughtful comments greatly improved both the quality and clarity of this manuscript.}
+We thank the anonymous referee who suggested the idea of Nu-based ICs, and whose careful and thoughtful comments greatly improved both the quality and clarity of this manuscript.
 We thank Daniel Lecoanet, who first pointed out to us the importance of examining Ra$_{\Delta T}$ in FT simulations. 
@@
 	Input and output values from the simulations in this work are shown; all simulations have a Prandtl number of 1.
-	Input quantities are the boundary conditions (BCs), \ea{initial conditions (ICs),} Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
+	Input quantities are the boundary conditions (BCs), initial conditions (ICs), Rayleigh number (Ra), coefficient resolution (nx$\times$ny$\times$nz, or horizontal $\times$ vertical), and the total simulation run time in freefall units $t_{\text{simulation}}$ and in cpu-hours.
 	Output quantities are the Nusselt (Nu), P\'{e}clet (Pe), and Rossby (Ro) numbers.
-	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units \ea{for all rotating cases and all 2D cases except the Ra$_{\partial_z T} = 9.51\times10^{11}$ TT-to-FT case, where samples were taken over 200 evolved freefall time units; samples were taken over 350 freefall time units for 3D non-rotating cases}.
+	Reported values of Nu, Re, and Ro are the sample mean over the last 500 freefall time units for all rotating cases and all 2D cases except the Ra$_{\partial_z T} = 9.51\times10^{11}$ TT-to-FT case, where samples were taken over 200 evolved freefall time units; samples were taken over 350 freefall time units for 3D non-rotating cases.
 	Reported uncertainties are the standard deviation of the sample mean; when the uncertainty is not reported, it is smaller than the number of reported digits.
@@
 
+\bibliography{biblio.bib}
+
 \end{document}

### 2020-05-20 submission2_tex/mixedft_evolution_ms.tex
submission folder ms ready to ship

--- 2020-05-20 submission2_tex/redline/mixedft_evolution_ms_redline.tex
@@
 
-\graphicspath{{../}}
-
 \begin{document}
@@
 
-\ea{
 \subsection{Timescales}
 \label{sec:timescales}
-}
-One \ea{result of the mapping in Eqn.~\ref{eqn:ra_relation}} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
+One result of the mapping in Eqn.~\ref{eqn:ra_relation} is that the nondimensional dynamical freefall timescale is a poor description of the \emph{evolved} freefall timescale.
 The velocities in an FT simulation are smaller than the velocities in a TT simulation by a factor of $\sqrt{\text{Nu}}$.
 As a result, every nondimensional simulation freefall time unit in a TT simulation samples a factor of $\sqrt{\text{Nu}}$ more dynamics than a time unit in an FT simulation.
-\ea{We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
-To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.}
-
-\ea{
+We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
+To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
+
 The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
@@
 In practice, we find that our non-rotating simulations equilibrate in $\sim 2.5\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ nondimensional time units (see section \ref{sec:time_evolution_classic_ICs}), and our rotating simulation equilibrates in $\sim (2/3)\sqrt{\text{Ra}\,\text{Pr}}/\text{Nu}$ time units (see section \ref{sec:results_rotating}).
-
-}
 
@@
 Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classic ICs are very similar.
-}
-
-\subsection{\ea{Discussion of 2D results}} 
-We note briefly that \ea{Nu-based and} TT-to-FT \ea{ICs are} only \ea{two} of many ways of accelerating the thermal relaxation of an FT simulation.
+
+\subsection{Discussion of 2D results} 
+We note briefly that Nu-based and TT-to-FT ICs are only two of many ways of accelerating the thermal relaxation of an FT simulation.
 We discuss other mechanisms, and explore one in detail, in our previous work \cite{anders&all2018}.
@@
 The thermal energy reservoir of TT simulations does not change between the initial and final state.
-The rapid relaxation of TT simulations\ea{, as well as FT simulations with Nu-based and TT-to-FT ICs}, therefore suggests that experimental restratification occurs rapidly in RBC. 
-The long rundown of \ea{classic-IC} FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
-
-\ea{
+The rapid relaxation of TT simulations, as well as FT simulations with Nu-based and TT-to-FT ICs, therefore suggests that experimental restratification occurs rapidly in RBC. 
+The long rundown of classic-IC FT experiments on display in Fig.~\ref{fig:rbc_scalar_comparisons} is entirely due to the energy reservoir (the temperature jump across the domain) drifting over time.
+
 As a final note, we find that measures of the velocity field (e.g., the kinetic energy and Pe) take a few hundred freefall timescales to relax to their final value in TT and FT (Nu-based IC) simulations in 2D at high values of Ra$_{\Delta T}\,\gtrsim 10^{8.67}$.
@@
 Here we explore the parameter space that the classic-IC FT simulation explores as it thermally relaxes and demonstrate that the TT-to-FT approach leads to rapid convergence for a rotating simulation.
-}
 
 We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \ea{\citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}.
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
-\ea{We then take the TT case, do a TT-to-FT simulation, and compare the results of the TT-to-FT simulation to the classic-IC FT case.}
-
-In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of \ea{a classic-IC} FT and TT case.
+We then take the TT case, do a TT-to-FT simulation, and compare the results of the TT-to-FT simulation to the classic-IC FT case.
+
+In the left three panels of Fig.~\ref{fig:rotating_panels}, we compare the time evolution of a classic-IC FT and TT case.
 The top left panel shows the evolution of Ra$_{\partial_z T}$ and Ra$_{\Delta T}$.
@@
 \end{thebibliography}%
-
 \end{document}

### 2020-07-07 referee_responses/submission2/referee_response.tex
rough referee response

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Emmanuel,
$\,$\newline

\begin{singlespace}

We return our revised manuscript, ``Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it.'' 
We thank the referee(s) for their time and effort in reviewing our work.
We have addressed the comments in the report, making changes that we describe inline in our response to the report.
We have additionally carefully read through the manuscript and made very small corrections (fixing typos, etc.) throughout the work.
No major changes have been made; all figures, tables, and simulation data are identical to the previous version of the manuscript.

We hope that the small clarifications which have been made in this round of the refereeing process are satisfactory, and we feel that they once again improve the quality and clarity of the manuscript.
Below we include our response to the referee report; the original text of the reports is included in italics, and our response follows inline in unitalicized blocks.

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Geoffrey M. Vasil, Benjamin P. Brown, and Lydia Korre

\newpage
\noindent
\Large{\textbf{Response to first report:}}\newline$\,$\newline\indent

\begin{myquotation}
The authors have satisfyingly answered all the questions raised in my first report. 
As I already wrote, I think the results presented in this paper are new, interesting, and useful. 
I recommend its publication, with only a few additional comments below.
\end{myquotation}
We would again like to thank the referee for their attention to detail and constructive criticism throughout this whole refereeing process.
We hope that the small changes to the manuscript, described inline to the comments below, sufficiently clear up any confusion and concerns.

\begin{myquotation}
- page 4: the choice of the letter ``w(z)" for the windowing function is not the best option, since w(z) is already the vertical velocity page 3.
\end{myquotation}
Thank you.
We have changed $w$ to $\xi$, which should not be used elsewhere in the manuscript.

\begin{myquotation}
- figure 3, and more generally: how do you define the ``FT final state" or ``evolved state"? 
Would the PDF and statistics in table I even better agree if the simulations were performed for longer computing times?
\end{myquotation}
We define the evolved or final state as the state in which a rolling time-average of $\Delta T$ (over a couple hundred freefall times) is within 1\% of its final value.
We generally evolve our classic-IC FT simulations at least a thousand evolved freefall times past this point, so that we can be certain that we are in an evolved or relaxed state.
We have added this definition to the text in section III.B.1.

Given a very long sampling window (thousands of freefall times), we would expect all FT simulations at the same input parameters to have identical output probability distributions, at least for our choices of $\Gamma = 2$ and no-slip boundaries.
While these are not often practical amounts of time to run simulations for, we have made a note of this in the text in section III.B.2.
We would also expect the PDF of e.g., the vertical heat transport of FT and TT simulations to be identical, but this will only be the case if the Ra$_{\partial_z T}$ of the FT simulation is properly chosen so that it exactly matches the infinite time-average of Ra$_{\partial_z T}$ in the corresponding TT simulation (at a given Ra$_{\Delta T}$).

\begin{myquotation}
- page 12: I am not sure to agree with your ``unsurprisingly"... With your periodic horizontal boundary conditions, I would expect to find the same PDF for the vertical slice at y=0 as for the whole volume. 
It might show that statistics are not fully converged for the vertical slice, no?
\end{myquotation}
Thank you.
Upon further examination, we agree with you that in a fully statistically converged sample which includes the full range of dynamics available to the simulation, a PDF from the slice at $y = 0$ should be identical to the PDF over the full volume.
Indeed, our FT PDFs for $y = 0$ and over the full volume are essentially identical.
The TT PDF at $y = 0$ shows excess probability in the tails, because we happened to capture a range of time in the simulation during which plume launching sites are clustered near $y = 0$, thus skewing our distribution.
We have explained this in the text as a reason to be cautious when gathering statistics from 2D slices of a full 3D domain.

\begin{myquotation}
- caption of figure 5: ``the right panels examines the top boundary layers" $\rightarrow$ examine
\end{myquotation}
Thank you.
We have fixed the singular/plural problem and changed ``examine'' to ``displays'' in this sentence.

\begin{myquotation}
- page 16: it might worth defining the ``Kelvin-Helmholtz timescale" for PRF readers.
\end{myquotation}
Thank you, good point.
We have now done so.

\end{singlespace}
\bibliography{../../biblio.bib}
\end{document}

### 2020-07-07 tex/mixedft_evolution_ms.tex
very minor cosmetic changes for submission 2
rough referee response

@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} + w(z)[-1 - (\grad T)_{\text{interior}}].
+\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} + \ea{\xi}(z)[-1 - (\grad T)_{\text{interior}}].
 \label{eqn:nu_based_gradT}
@@
 We set the initial temperature field by integrating Eqn.~\ref{eqn:nu_based_gradT} according to the top (fixed-temperature) boundary condition.
-Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $w(z)$, to set the temperature gradient to $-1$ near the boundaries,
+Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $\ea{\xi}(z)$, to set the temperature gradient to $-1$ near the boundaries,
 $$
-w(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_w)}{0.5\delta_w}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_w)}{0.5\delta_w}\right]\right).
+\ea{
+\xi(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_\xi)}{0.5\delta_\xi}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_\xi)}{0.5\delta_\xi}\right]\right).
+}
 $$
-Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+Here, $\ea{\delta_\xi} = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
 In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
@@
 The PDFs of all FT simulations agree well regardless of initial conditions, suggesting that all initial conditions do achieve a similar statistically stationary state.
+\ea{
+We consider the classic-IC FT simulation to be in its evolved, relaxed state once a rolling temporal average of $\Delta T$ over a couple hundred of freefall time units converges to within 1\% of its final value.
+We run our classic-IC FT simulations for at least a thousand $\tau_{\text{ff, ev}}$ past this point to ensure that the simulations are converged, and we gather statistics from the latest, most-converged simulation times that are available.
+TT-to-FT and Nu-based IC FT simulations are only evolved for 1000 $\tau_{\text{ff, ev}}$, and we gather statistics from the second half of these simulation.
+}
 
@@
 It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
+\ea{
+If we were to run each of these simulations for multiple thermal diffusion times, and gather PDF statistics over thousands of freefall times, we would expect to find near-perfect agreement between the PDFs of the different simulations (except were boundary conditions cause differences between FT and TT simulations).
+However, the good agreement between the PDFs of each of these simulations over our modest sampling windows suggests that the dynamics in each of these distinct simulations are being drawn from the same parent statistical distribution.
+}
 
-\begin{table}[b!]
+\begin{table}[t!]
 \vspace{-0.5cm}
@@
 However, near the bottom boundary, the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
-Unsurprisingly, we find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is similar, but not identical, to the PDFs of the temperature field of the full volume, suggesting that this one slice does not capture the full range of possible dynamics which occur in the domain over our sampling window.
+\ea{
+We find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is nearly identical to the PDF of the full-domain dynamics for the FT simulation, but that there are noticeable differences between these two PDFs for the TT simulation.
+The differences between the full-volume and $y = 0$ PDFs in the TT case are due to the fact that our sampling window occurs while plume-launching sites are clustered around $y = 0$ more frequently than one would expect from a random distribution of plume-launching sites.
+Over an infinite amount of time, these two PDFs should converge, but this demonstrates that it is important to be cautious when taking statistics from a 2D slice of a 3D simulation.
+}
 
@@
 	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
-	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
+	(Right six panels) The three panels on the left \ea{display} the bottom boundary layers while the right panels \ea{display} the top boundary layers.
 	The insets show the \% difference between the FT and TT solutions.
@@
 There was no long thermal evolutionary timescale.
-In the equilibrated classic FT simulation, we measured Nu$=7.90 \pm 0.01$, Pe$=1.70 \times 10^3$, and Ro$=0.115 \pm 0.006$.
+In the equilibrated classic-IC FT simulation, we measured Nu$=7.90 \pm 0.01$, Pe$=1.70 \times 10^3$, and Ro$=0.115 \pm 0.006$.
 In the TT-to-FT simulation, we measured Nu$=7.83 \pm 0.01$, Pe$=1.65 \times 10^3$, and Ro=$0.114 \pm 0.005$.
@@
 The use of classic-ICs with FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
+However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale (\ea{the time it would take for an astrophysical body to radiate its full gravitational potential energy given its current luminosity \cite{carroll&ostlie}}), it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
 

### 2020-07-09 referee_responses/submission2/referee_response.tex
ready to be read by co-authors

@@
 We have additionally carefully read through the manuscript and made very small corrections (fixing typos, etc.) throughout the work.
-No major changes have been made; all figures, tables, and simulation data are identical to the previous version of the manuscript.
+No major changes have been made; all tables and simulation data are identical to the previous version of the manuscript.
+All figures are identical to the previous manuscript, except that we have added an additional axis label to a panel in figure 1 to make it easier to read.
 
@@
 Given a very long sampling window (thousands of freefall times), we would expect all FT simulations at the same input parameters to have identical output probability distributions, at least for our choices of $\Gamma = 2$ and no-slip boundaries.
-While these are not often practical amounts of time to run simulations for, we have made a note of this in the text in section III.B.2.
-We would also expect the PDF of e.g., the vertical heat transport of FT and TT simulations to be identical, but this will only be the case if the Ra$_{\partial_z T}$ of the FT simulation is properly chosen so that it exactly matches the infinite time-average of Ra$_{\partial_z T}$ in the corresponding TT simulation (at a given Ra$_{\Delta T}$).
+Unfortunately, these are not practical amounts of time to run simulations for, and we have made a note of this with some discussion in the text in section III.B.2.
 

### 2020-07-09 tex/mixedft_evolution_ms.tex
ready to be read by co-authors

@@
 We also compare relaxed FT solutions to TT solutions.
-When classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+\ea{We find that} when classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
+We \ea{also} find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
 Finally, FT boundaries create some asymmetries in the convective flows, particularly in the boundary layers, but these asymmetries do not appreciably change the bulk convective state compared to TT simulations.
@@
 
-We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
+We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2020} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
 Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the IMEX, second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}.
+Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
 The codes used to run the simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}\footnote{Simulations were conducted using v1.1.0 (for Nu-based ICs and 3D non-rotating simulations) and v1.0.1 (for all other cases) of our \texttt{boussinesq\_convection} github repository \cite{code:boussinesq_convection}.}.
-Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.
 
@@
 
-The time evolution of FT simulations is sensitive to the initial conditions due to the fact that the evolved, nonlinear convective dynamics determine the magnitude of the temperature jump across the domain.
+\ea{In FT simulations, } the evolved, nonlinear dynamics determine the magnitude of \ea{$\Delta T$.}
+\ea{As a result,} the time evolution of FT simulations is sensitive to \ea{how well} the initial conditions \ea{guess the evolved $\Delta T$.}
 For this reason, we will study FT simulations which employ three different initial states.
@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} + \ea{\xi}(z)[-1 - (\grad T)_{\text{interior}}].
+\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} - \ea{\xi}(z)[1 + (\grad T)_{\text{interior}}].
 \label{eqn:nu_based_gradT}
@@
 Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $\ea{\xi}(z)$, to set the temperature gradient to $-1$ near the boundaries,
-$$
+\begin{equation}
 \ea{
@@
 }
-$$
+\end{equation}
 Here, $\ea{\delta_\xi} = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
@@
 	(Left three panels) Time traces of scalar quantities in a classic-IC FT (orange, Ra$_{\partial_z T} = 4.81 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 10^9$) simulation are shown.
-	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
+	All traces have been averaged over a rolling window of 100 \ea{simulation} time units to increase the clarity of the evolutionary trend.
 	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
@@
 The PDFs of all FT simulations agree well regardless of initial conditions, suggesting that all initial conditions do achieve a similar statistically stationary state.
+
 \ea{
-We consider the classic-IC FT simulation to be in its evolved, relaxed state once a rolling temporal average of $\Delta T$ over a couple hundred of freefall time units converges to within 1\% of its final value.
-We run our classic-IC FT simulations for at least a thousand $\tau_{\text{ff, ev}}$ past this point to ensure that the simulations are converged, and we gather statistics from the latest, most-converged simulation times that are available.
-TT-to-FT and Nu-based IC FT simulations are only evolved for 1000 $\tau_{\text{ff, ev}}$, and we gather statistics from the second half of these simulation.
+We consider the classic-IC FT simulation to be in its evolved, relaxed state once a rolling temporal average of $\Delta T$ over 200$\tau_{\text{ff, ev}}$ converges to within 1\% of its final value.
+We run our classic-IC FT simulations for at least $1000\tau_{\text{ff, ev}}$ past this point to ensure that the simulations are converged, and we gather statistics from the latest, most-converged simulation times that are available.
+TT-to-FT and Nu-based IC FT simulations are only evolved for $1000\tau_{\text{ff, ev}}$, and we gather statistics from the second half of these simulation.
 }
@@
 It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
+
 \ea{
-If we were to run each of these simulations for multiple thermal diffusion times, and gather PDF statistics over thousands of freefall times, we would expect to find near-perfect agreement between the PDFs of the different simulations (except were boundary conditions cause differences between FT and TT simulations).
-However, the good agreement between the PDFs of each of these simulations over our modest sampling windows suggests that the dynamics in each of these distinct simulations are being drawn from the same parent statistical distribution.
+The moments presented in table \ref{table:pdf_values} are not perfectly identical for all of the different FT cases, but we expect that this is due to the randomness of the turbulent motions in our simulations and our relatively short (500$\tau_{\text{ff, ev}}$) statistical sampling window.
+If we were to run each of these simulations for multiple thermal diffusion times, and gather PDF statistics over thousands of freefall times, we would expect to find precisely the same distribution for each case.
+However, each of the PDF moments for different FT cases agree to within a few percent (or are zero to within a few percent), so we are satisfied that our modest sampling windows are sufficiently long to meaningfully compare our various simulations.
 }
@@
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
-During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classic roll solution is achieved.
+During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which the interior is well mixed and a classic roll solution is achieved.
 This behavior is quite different from classic ICs, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
@@
 We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2020}.
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).

### 2020-07-09 figures_and_data/rbc_evolution_dynamics.py

@@ -240,7 +240,7 @@ axtt.set_xlim(0, ffunc(0.5)*2)
 axft.set_xlim(0, mfunc(0.5)*2)
 
 axtt.set_xticks((0, 0.25, 0.5, 0.75))
-axft.set_xticks((0, 0.05, 0.1, 0.15, 0.2, 0.25))
+axft.set_xticks((0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.30))
 axtt.xaxis.set_label_position('top')
 
 

### 2020-07-15 tex/mixedft_evolution_ms.tex
adds most of the comments from Lydia

@@
 The background temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
-The temperature scale, $\Delta$, is set by either the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient length scale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
+The temperature scale, $\Delta$, is set by either the temperature jump across the domain ($\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$) for TT boundaries or by the temperature gradient lengthscale ($\Delta = L_z \partial_z T_0$) for FT boundaries.
 We respectively define a temperature (Ra$_{\Delta T}$) and a flux (Ra$_{\partial_z T}$) Rayleigh number for these cases,
@@
 \end{equation}
-where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
+where $\angles{}$ represent a volume average ($\angles{\ea{s}} \equiv \iint \ea{s}\,dx\,dz / \Gamma$ in 2D and $\angles{\ea{s}} \equiv \iiint \ea{s}\,dx\,dy\,dz / \Gamma^2$ in 3D for some \ea{scalar} quantity \ea{$s$}), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
 In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
@@
 \end{equation}
-where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.
+where $|\bm{\ea{q}}|$ represents the magnitude of the vector \ea{quantity $\bm{q}$}.
 
@@
 We furthermore assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
-We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
+We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the \ea{corresponding} TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
 For classic and Nu-based ICs,
@@
 We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
-To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
+To ensure accurate comparisons, we measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
 
-The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
+The thermal energy reservoir of our 3D Cartesian systems and the rate of change of this reservoir due to conduction at the boundaries \ea{are derived from volume-integrals of the temperature and vertical fluxes,}
 \begin{equation}
-E = \iiint T\,dx\,dy\,dz = \Gamma^2 \int T\,dz,
+E = \ea{\iiint_V} T\,dx\,dy\,dz = \Gamma^2 \ea{\int_{z=-0.5}^{z=0.5}} T\,dz,
 \qquad
-\frac{dE}{dt} = -\iiint \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\ea{\iiint_V} \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
@@
 This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
-In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).
+In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from \ea{the} TT dynamics (top right).
 
@@
 The temperature PDF of the TT simulation unsurprisingly has a mean of 0.5, a Skewness close to zero (no asymmetry between upflows and downflows), and an appreciable Excess Kurtosis (the tails, which primarily sample the plumes, are more important than they are in a Normal Distribution).
-The FT temperature PDF, on the other hand, has a mean slightly larger than 0.5, a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis (implying more extreme plumes).
+The FT temperature PDF, on the other hand, has a mean slightly larger than 0.5, a small but noticeable Skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis (implying more extreme plumes).
 It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
@@
 \subsubsection{Nu-based ICs}
-The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.
+The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few \ea{small differences}.
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
@@
 Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classic ICs.
-Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classic ICs are very similar.
+Per table \ref{table:pdf_values}, the evolved states of FT simulations with Nu-based ICs and classic ICs are very similar.
 
@@
 We run a TT and TT-to-FT simulation at Ra$_{\Delta T} = 10^{10}$ and Ra$_{\partial_z T} = 9.51 \times 10^{11}$, respectively.
-In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries which FT boundaries introduce into the simulation near the fixed-flux boundary.
+In Fig.~\ref{fig:rbc_dynamics_asymmetries}, we examine the dynamical nature of the asymmetries that the FT boundaries introduce into the simulation near the fixed-flux boundary.
 In the left panel, we plot PDFs of the temperature fields of the two cases.
@@
 
-We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between FT and TT in Figs.~\ref{fig:rbc_scalar_comparisons}\&\ref{fig:rbc_1D_profiles}).
+We note briefly that these asymmetries do not seem to affect mean or volume-averaged quantities in these simulations appreciably (see the agreement between FT and TT in Figs.~\ref{fig:rbc_scalar_comparisons} \& \ref{fig:rbc_1D_profiles}).
 However, the fact that fixed-flux boundaries produce a wider temperature distribution with more extreme values may be important in some astrophysical studies.
@@
 We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2020}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large-scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2020}.
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
@@
 	(Bottom right panels) Snapshots of the vertically integrated z-component of the vorticity from the FT simulation.
-	At early times (left panel), a powerful large scale vortex with positive vorticity develops.
+	At early times (left panel), a powerful large-scale vortex with positive vorticity develops.
 	This vortex slowly decays and becomes a vortex pair (middle panel), as seen in ref.~\cite{stellmach&all2014}.
@@
 \end{enumerate}
+
 We now describe some lessons that should be applied from this work to astrophysical convection, and comment on some open areas of research.
-
 Throughout this work, we have made the assumption that convection is only ``interesting'' in its final, fully equilibrated state.

### 2020-07-15 submission3_tex/mixedft_evolution_ms.tex
ready to resubmit

--- 2020-05-20 submission2_tex/mixedft_evolution_ms.tex
@@
 We also compare relaxed FT solutions to TT solutions.
-When classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+We find that when classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
+We also find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
 Finally, FT boundaries create some asymmetries in the convective flows, particularly in the boundary layers, but these asymmetries do not appreciably change the bulk convective state compared to TT simulations.
@@
 \end{equation}
-where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
+where $\angles{}$ represent a volume average ($\angles{s} \equiv \iint s\,dx\,dz / \Gamma$ in 2D and $\angles{s} \equiv \iiint s\,dx\,dy\,dz / \Gamma^2$ in 3D for some scalar quantity $s$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
 In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
@@
 \end{equation}
-where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.
+where $|\bm{q}|$ represents the magnitude of the vector quantity $\bm{q}$.
 
@@
 
-The time evolution of FT simulations is sensitive to the initial conditions due to the fact that the evolved, nonlinear convective dynamics determine the magnitude of the temperature jump across the domain.
+In FT simulations, the evolved, nonlinear dynamics determine the magnitude of $\Delta T$.
+As a result, the time evolution of FT simulations is sensitive to how well the initial conditions guess the evolved $\Delta T$.
 For this reason, we will study FT simulations which employ three different initial states.
@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} + w(z)[-1 - (\grad T)_{\text{interior}}].
+\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} - \xi(z)[1 + (\grad T)_{\text{interior}}].
 \label{eqn:nu_based_gradT}
@@
 We set the initial temperature field by integrating Eqn.~\ref{eqn:nu_based_gradT} according to the top (fixed-temperature) boundary condition.
-Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $w(z)$, to set the temperature gradient to $-1$ near the boundaries,
-$$
-w(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_w)}{0.5\delta_w}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_w)}{0.5\delta_w}\right]\right).
-$$
-Here, $\delta_w = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $\xi(z)$, to set the temperature gradient to $-1$ near the boundaries,
+\begin{equation}
+\xi(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_\xi)}{0.5\delta_\xi}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_\xi)}{0.5\delta_\xi}\right]\right).
+\end{equation}
+Here, $\delta_\xi = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
 In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
@@
 We furthermore assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
-We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
+We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the corresponding TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
 For classic and Nu-based ICs,
@@
 We therefore define the \emph{evolved} freefall time, $\tau_{\text{ff, ev}} = \sqrt{\text{Nu}}$ (for FT simulations) or $\tau_{\text{ff, ev}} = 1$ (for TT simulations).
-To ensure accurate comparisons, we will measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
-
-The thermal energy reservoir of our 3D Cartesian systems, and the rate of change of this reservoir due to conduction at the boundaries, is
-\begin{equation}
-E = \iiint T\,dx\,dy\,dz = \Gamma^2 \int T\,dz,
+To ensure accurate comparisons, we measure flow statistics over multiples of $\tau_{\text{ff, ev}}$ rather than over multiples of the nondimensional time units.
+
+The thermal energy reservoir of our 3D Cartesian systems and the rate of change of this reservoir due to conduction at the boundaries are derived from volume-integrals of the temperature and vertical fluxes,
+\begin{equation}
+E = \iiint_V T\,dx\,dy\,dz = \Gamma^2 \int_{z=-0.5}^{z=0.5} T\,dz,
 \qquad
-\frac{dE}{dt} = -\iiint \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\iiint_V \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
@@
 This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
-In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from TT dynamics (top right).
+In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from the TT dynamics (top right).
 
@@
 	(Left three panels) Time traces of scalar quantities in a classic-IC FT (orange, Ra$_{\partial_z T} = 4.81 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 10^9$) simulation are shown.
-	All traces have been averaged over a rolling window of 100 freefall time units to increase the clarity of the evolutionary trend.
+	All traces have been averaged over a rolling window of 100 simulation time units to increase the clarity of the evolutionary trend.
 	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
@@
 
+We consider the classic-IC FT simulation to be in its evolved, relaxed state once a rolling temporal average of $\Delta T$ over 200$\tau_{\text{ff, ev}}$ converges to within 1\% of its final value.
+We run our classic-IC FT simulations for at least $1000\tau_{\text{ff, ev}}$ past this point to ensure that the simulations are converged, and we gather statistics from the latest, most-converged simulation times that are available.
+TT-to-FT and Nu-based IC FT simulations are only evolved for $1000\tau_{\text{ff, ev}}$, and we gather statistics from the second half of these simulation.
+
 \subsubsection{Statistical Comparison of BCs and ICs}
@@
 The temperature PDF of the TT simulation unsurprisingly has a mean of 0.5, a Skewness close to zero (no asymmetry between upflows and downflows), and an appreciable Excess Kurtosis (the tails, which primarily sample the plumes, are more important than they are in a Normal Distribution).
-The FT temperature PDF, on the other hand, has a mean slightly larger than 0.5, a small but noticeable skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis (implying more extreme plumes).
+The FT temperature PDF, on the other hand, has a mean slightly larger than 0.5, a small but noticeable Skewness (suggesting asymmetries between the F and T plates), and more Excess Kurtosis (implying more extreme plumes).
 It is also interesting that, in all cases, the vertical velocity, $w$, and the vertical heat transport, $wT$, demonstrate PDFs whose tails are well-described by normal distributions.
 
-\begin{table}[b!]
+The moments presented in table \ref{table:pdf_values} are not perfectly identical for all of the different FT cases, but we expect that this is due to the randomness of the turbulent motions in our simulations and our relatively short (500$\tau_{\text{ff, ev}}$) statistical sampling window.
+If we were to run each of these simulations for multiple thermal diffusion times, and gather PDF statistics over thousands of freefall times, we would expect to find precisely the same distribution for each case.
+However, each of the PDF moments for different FT cases agree to within a few percent (or are zero to within a few percent), so we are satisfied that our modest sampling windows are sufficiently long to meaningfully compare our various simulations.
+
+\begin{table}[t!]
 \vspace{-0.5cm}
@@
 \subsubsection{Nu-based ICs}
-The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few caveats.
+The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few small differences.
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
-During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which time the interior is well mixed and a classic roll solution is achieved.
+During the convective transient, plumes from the boundaries eat away at this interior stratification over a few tens of freefall timescales, after which the interior is well mixed and a classic roll solution is achieved.
 This behavior is quite different from classic ICs, in which the full domain is initially unstable and a roll solution is obtained immediately after the onset of nonlinear convection.
 Regardless, the time required for the temperature field to reach statistical equilibrium is a few tens of freefall times rather than a few thousands of freefall times for classic ICs.
-Per table \ref{table:pdf_values}, the evolved state of FT simulations with Nu-based ICs and classic ICs are very similar.
+Per table \ref{table:pdf_values}, the evolved states of FT simulations with Nu-based ICs and classic ICs are very similar.
 
@@
 However, near the bottom boundary, the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
-Unsurprisingly, we find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is similar, but not identical, to the PDFs of the temperature field of the full volume, suggesting that this one slice does not capture the full range of possible dynamics which occur in the domain over our sampling window.
+We find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is nearly identical to the PDF of the full-domain dynamics for the FT simulation, but that there are noticeable differences between these two PDFs for the TT simulation.
+The differences between the full-volume and $y = 0$ PDFs in the TT case are due to the fact that our sampling window occurs while plume-launching sites are clustered around $y = 0$ more frequently than one would expect from a random distribution of plume-launching sites.
+Over an infinite amount of time, these two PDFs should converge, but this demonstrates that it is important to be cautious when taking statistics from a 2D slice of a 3D simulation.
 
@@
 	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
-	(Right six panels) The three panels on the left examine the bottom boundary layers and the right panels examines the top boundary layers.
+	(Right six panels) The three panels on the left display the bottom boundary layers while the right panels display the top boundary layers.
 	The insets show the \% difference between the FT and TT solutions.
@@
 We now study 3D rotating RBC with Ek$ \,= 10^{-6}$.
-These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2019}.
+These simulations employ stress free boundary conditions which allow for the generation of mean flows such as large-scale vortices (LSV) \citep{stellmach&all2014, rubio&all2014, guervilly&all2014, guervilly&hughes2017, favier&all2014, favier&all2019, couston&all2020}.
 We study a TT case at Ra$_{\Delta T} = 2.75\times 10^9$, and a classic-IC FT case at $\text{Ra}_{\partial_z T} = 2.1 \times 10^{10}$ (the supercriticality of the TT case is $\sim 3$).
@@
 \label{sec:discussion}
-In short, we find that FT simulations can experience a long thermal relaxation which is not experienced by TT simulations and, to first order, FT boundaries do not introduce important asymmetries into the solution.
+In short, we find that simulations with mixed thermal boundary conditions can experience a long thermal relaxation which is not experienced by simulations with two fixed-temperature boundaries; furthermore, to first order, mixed thermal boundary conditions do not introduce important asymmetries into the solution.
 
@@
 The use of classic-ICs with FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale, it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
+However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale (the time it would take for an astrophysical body to radiate its full gravitational potential energy given its current luminosity \cite{carroll&ostlie}), it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
 
@@
 
-RBC is fundamentally symmetrical, but many natural convective processes occur in density-stratified domains in which the symmetries of the problem are fundamentally broken.
+RBC is fundamentally symmetrical, but many natural convective processes occur in density-stratified domains in which the symmetries of the problem are broken.
 In the present study, we observed that flux boundaries produce more extreme thermodynamic events than temperature boundaries.
@@
 
-\begin{thebibliography}{51}%
+\begin{thebibliography}{52}%
 \makeatletter
@@
   {http://arxiv.org/abs/1603.015} {ascl:1603.015} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2019)\citenamefont
+\bibitem [{\citenamefont {{Burns}}\ \emph {et~al.}(2020)\citenamefont
   {{Burns}}, \citenamefont {{Vasil}}, \citenamefont {{Oishi}}, \citenamefont
-  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2019}%
+  {{Lecoanet}},\ and\ \citenamefont {{Brown}}}]{burns&all2020}%
   \BibitemOpen
@@
   {Benjamin~P.}\ \bibnamefont {{Brown}}},\ }\bibfield  {title} {\enquote
-  {\bibinfo {title} {{Dedalus: A Flexible Framework for Numerical Simulations
-  with Spectral Methods}},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1905.10388}} (\bibinfo
-  {year} {2019})},\ \Eprint {http://arxiv.org/abs/1905.10388} {arXiv:1905.10388
+  {\bibinfo {title} {{Dedalus: A flexible framework for numerical simulations
+  with spectral methods}},}\ }\href {\doibase 10.1103/PhysRevResearch.2.023068}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Research}\
+  }\textbf {\bibinfo {volume} {2}},\ \bibinfo {eid} {023068} (\bibinfo {year}
+  {2020})},\ \Eprint {http://arxiv.org/abs/1905.10388} {arXiv:1905.10388
   [astro-ph.IM]} \BibitemShut {NoStop}%
@@
   \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {{Couston}}\ \emph {et~al.}(2019)\citenamefont
+\bibitem [{\citenamefont {{Couston}}\ \emph {et~al.}(2020)\citenamefont
   {{Couston}}, \citenamefont {{Lecoanet}}, \citenamefont {{Favier}},\ and\
-  \citenamefont {{Le Bars}}}]{couston&all2019}%
+  \citenamefont {{Le Bars}}}]{couston&all2020}%
   \BibitemOpen
@@
   \bibnamefont {{Le Bars}}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
-  {{Shape and size of large-scale vortices : a universal fluid pattern in
-  geophysical fluid dynamics}},}\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {arXiv e-prints}\ ,\ \bibinfo {eid} {arXiv:1909.03244}}
-  (\bibinfo {year} {2019})},\ \Eprint {http://arxiv.org/abs/1909.03244}
-  {arXiv:1909.03244 [physics.flu-dyn]} \BibitemShut {NoStop}%
+  {{Shape and size of large-scale vortices: A generic fluid pattern in
+  geophysical fluid dynamics}},}\ }\href {\doibase
+  10.1103/PhysRevResearch.2.023143} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Research}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {eid}
+  {023143} (\bibinfo {year} {2020})},\ \Eprint
+  {http://arxiv.org/abs/1909.03244} {arXiv:1909.03244 [physics.flu-dyn]}
+  \BibitemShut {NoStop}%
 \bibitem [{\citenamefont {{Cheng}}\ \emph {et~al.}(2015)\citenamefont
@@
   {arXiv:1808.04014 [astro-ph.SR]} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carroll}\ and\ \citenamefont
+  {Ostlie}(2017)}]{carroll&ostlie}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.W.}\ \bibnamefont
+  {Carroll}}\ and\ \bibinfo {author} {\bibfnamefont {D.A.}\ \bibnamefont
+  {Ostlie}},\ }\href@noop {} {\emph {\bibinfo {title} {An Introduction to
+  Modern Astrophysics}}}\ (\bibinfo  {publisher} {Cambridge University Press},\
+  \bibinfo {year} {2017})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {{Brummell}}\ \emph {et~al.}(2002)\citenamefont

### 2020-07-15 submission3_tex/redline/redline_mixedft_evolution_ms.tex
ready to resubmit

--- 2020-07-15 submission3_tex/mixedft_evolution_ms.tex
@@
 We also compare relaxed FT solutions to TT solutions.
-We find that when classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
+\ea{We find that} when classic initial conditions which are in hydrostatic and thermal equilibrium are employed, the thermal relaxation of FT systems is very long compared to TT systems, in which it is nearly instantaneous.
 The thermal relaxation of FT simulations is analogous to a sweep through parameter space in which dynamics are sampled over a range of values of Ra.
-We also find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
+We \ea{also} find that this long thermal relaxation can be bypassed by constructing smarter initial conditions based on the expected evolved value of Nu, or by simply using the results of TT simulations as initial conditions for FT simulations.
 Finally, FT boundaries create some asymmetries in the convective flows, particularly in the boundary layers, but these asymmetries do not appreciably change the bulk convective state compared to TT simulations.
@@
 \end{equation}
-where $\angles{}$ represent a volume average ($\angles{s} \equiv \iint s\,dx\,dz / \Gamma$ in 2D and $\angles{s} \equiv \iiint s\,dx\,dy\,dz / \Gamma^2$ in 3D for some scalar quantity $s$), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
+where $\angles{}$ represent a volume average ($\angles{\ea{s}} \equiv \iint \ea{s}\,dx\,dz / \Gamma$ in 2D and $\angles{\ea{s}} \equiv \iiint \ea{s}\,dx\,dy\,dz / \Gamma^2$ in 3D for some \ea{scalar} quantity \ea{$s$}), and $\Delta T = \angles{\partial_z T}$ is the (negative) temperature difference between the top and bottom plate.
 In a thermally relaxed, statistically stationary state \cite{calkins&all2015}, 
@@
 \end{equation}
-where $|\bm{q}|$ represents the magnitude of the vector quantity $\bm{q}$.
+where $|\bm{\ea{q}}|$ represents the magnitude of the vector \ea{quantity $\bm{q}$}.
 
@@
 
-In FT simulations, the evolved, nonlinear dynamics determine the magnitude of $\Delta T$.
-As a result, the time evolution of FT simulations is sensitive to how well the initial conditions guess the evolved $\Delta T$.
+\ea{In FT simulations, } the evolved, nonlinear dynamics determine the magnitude of \ea{$\Delta T$.}
+\ea{As a result,} the time evolution of FT simulations is sensitive to \ea{how well} the initial conditions \ea{guess the evolved $\Delta T$.}
 For this reason, we will study FT simulations which employ three different initial states.
@@
 \begin{equation}
-\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} - \xi(z)[1 + (\grad T)_{\text{interior}}].
+\frac{\partial T_N}{\partial z} = (\grad T)_{\text{interior}} - \ea{\xi}(z)[1 + (\grad T)_{\text{interior}}].
 \label{eqn:nu_based_gradT}
@@
 We set the initial temperature field by integrating Eqn.~\ref{eqn:nu_based_gradT} according to the top (fixed-temperature) boundary condition.
-Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $\xi(z)$, to set the temperature gradient to $-1$ near the boundaries,
-\begin{equation}
+Discontinuous profiles are unstable in our spectral methods, so we utilize a smooth windowing function, $\ea{\xi}(z)$, to set the temperature gradient to $-1$ near the boundaries,
+\begin{equation}
+\ea{
 \xi(z) = 1 + \frac{1}{2}\left(\text{erf}\left[\frac{z - (0.5 - 2\delta_\xi)}{0.5\delta_\xi}\right] - \text{erf}\left[\frac{z - (-0.5 + 2\delta_\xi)}{0.5\delta_\xi}\right]\right).
-\end{equation}
-Here, $\delta_\xi = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
+}
+\end{equation}
+Here, $\ea{\delta_\xi} = -\Delta T / 2$ is an estimate of the boundary layer width and the temperature gradient in the interior of the domain, $(\grad T)_{\text{interior}}$, is determined by setting $\int \partial_z T_N dz = \Delta T$.
 In this work, we use the best-fit law of ref.~\cite{johnston&doering2009} with $A = 0.138$ and $\alpha = 0.285$ when constructing Nu-based ICs.
@@
 We furthermore assume that the initial temperature profile is in hydrostatic equilibrium, and solve for $\varpi$ accordingly.
-We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the corresponding TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
+We assume zero velocity in the initial state, except in the case of TT-to-FT simulations, where velocities are taken directly from the \ea{corresponding} TT simulation and scaled according to Eqn.~\ref{eqn:ra_relation}.
 For classic and Nu-based ICs,
@@
 
-The thermal energy reservoir of our 3D Cartesian systems and the rate of change of this reservoir due to conduction at the boundaries are derived from volume-integrals of the temperature and vertical fluxes,
-\begin{equation}
-E = \iiint_V T\,dx\,dy\,dz = \Gamma^2 \int_{z=-0.5}^{z=0.5} T\,dz,
+The thermal energy reservoir of our 3D Cartesian systems and the rate of change of this reservoir due to conduction at the boundaries \ea{are derived from volume-integrals of the temperature and vertical fluxes,}
+\begin{equation}
+E = \ea{\iiint_V} T\,dx\,dy\,dz = \Gamma^2 \ea{\int_{z=-0.5}^{z=0.5}} T\,dz,
 \qquad
-\frac{dE}{dt} = -\iiint_V \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
+\frac{dE}{dt} = -\ea{\iiint_V} \grad\cdot \bm{F}_{\text{cond}}\,dx\,dy\,dz = -\Gamma^2 F_{\text{cond,z}}\bigg|_{z=-0.5}^{z=0.5}
 \end{equation}
@@
 This excess cold material slowly fills the domain and mixes, reducing the temperature difference between the top and bottom plates from $\Delta T = -1$ to $\Delta T = -\text{Nu}^{-1}$ in the relaxed state.
-In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from the TT dynamics (top right).
+In this relaxed state, the supply of warm fluid from the bottom plume and cold fluid from the top plume come into balance, and the FT dynamics (bottom right) are indistinguishable from \ea{the} TT dynamics (top right).
 
@@
 	(Left three panels) Time traces of scalar quantities in a classic-IC FT (orange, Ra$_{\partial_z T} = 4.81 \times 10^{10}$) and TT (purple, Ra$_{\Delta T} = 10^9$) simulation are shown.
-	All traces have been averaged over a rolling window of 100 simulation time units to increase the clarity of the evolutionary trend.
+	All traces have been averaged over a rolling window of 100 \ea{simulation} time units to increase the clarity of the evolutionary trend.
 	We display evolutionary traces of Ra (top, normalized by Ra$_{\Delta T}$ of the TT simulation) as well as Nu (middle) and Pe (bottom), both of which are normalized by their mean values measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
@@
 
+\ea{
 We consider the classic-IC FT simulation to be in its evolved, relaxed state once a rolling temporal average of $\Delta T$ over 200$\tau_{\text{ff, ev}}$ converges to within 1\% of its final value.
@@
 TT-to-FT and Nu-based IC FT simulations are only evolved for $1000\tau_{\text{ff, ev}}$, and we gather statistics from the second half of these simulation.
+}
 
@@
 
+\ea{
 The moments presented in table \ref{table:pdf_values} are not perfectly identical for all of the different FT cases, but we expect that this is due to the randomness of the turbulent motions in our simulations and our relatively short (500$\tau_{\text{ff, ev}}$) statistical sampling window.
@@
 However, each of the PDF moments for different FT cases agree to within a few percent (or are zero to within a few percent), so we are satisfied that our modest sampling windows are sufficiently long to meaningfully compare our various simulations.
+}
 
@@
 \subsubsection{Nu-based ICs}
-The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few small differences.
+The time evolution of FT simulations with Nu-based ICs is similar to the time evolution of TT simulations with classic ICs, with a few \ea{small differences}.
 The interior temperature gradient ($\grad_{\text{interior}}$ in Eqn.~\ref{eqn:nu_based_gradT}) is slightly positive at high Ra, which means that the interior is marginally thermally stable while the boundary layers are thermally unstable.
@@
 However, near the bottom boundary, the FT case instead exhibits a slightly larger number of neutral events ($T = 0.5\Delta T$) in addition to extreme temperature events ($T \geq \Delta T$).
+\ea{
 We find that the PDF of the temperature field of a vertical slice through the domain at $y = 0$ is nearly identical to the PDF of the full-domain dynamics for the FT simulation, but that there are noticeable differences between these two PDFs for the TT simulation.
@@
 Over an infinite amount of time, these two PDFs should converge, but this demonstrates that it is important to be cautious when taking statistics from a 2D slice of a 3D simulation.
+}
 
@@
 	The boundary layer regions are separated from the bulk by thin vertical lines and are examined in more detail in the right six panels.
-	(Right six panels) The three panels on the left display the bottom boundary layers while the right panels display the top boundary layers.
+	(Right six panels) The three panels on the left \ea{display} the bottom boundary layers while the right panels \ea{display} the top boundary layers.
 	The insets show the \% difference between the FT and TT solutions.
@@
 \label{sec:discussion}
-In short, we find that simulations with mixed thermal boundary conditions can experience a long thermal relaxation which is not experienced by simulations with two fixed-temperature boundaries; furthermore, to first order, mixed thermal boundary conditions do not introduce important asymmetries into the solution.
+In short, we find that \ea{simulations with mixed thermal boundary conditions} can experience a long thermal relaxation which is not experienced by \ea{simulations with two fixed-temperature boundaries; furthermore,} to first order, \ea{mixed thermal boundary conditions} do not introduce important asymmetries into the solution.
 
@@
 The use of classic-ICs with FT boundaries that we have here considered to be a ``bad'' choice may help in understanding these transient lifetime stages.
-However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale (the time it would take for an astrophysical body to radiate its full gravitational potential energy given its current luminosity \cite{carroll&ostlie}), it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
+However, for most convective studies where the lifetime of the natural convective system is much larger than its Kelvin-Helmholtz timescale (\ea{the time it would take for an astrophysical body to radiate its full gravitational potential energy given its current luminosity \cite{carroll&ostlie}}), it is essential to study relaxed convection, and our results point towards the importance of either choosing good initial conditions (TT or TT-to-FT simulations) or running simulations to thermal relaxation.
 
